---
title: "manuscript_analysis_clean"
author: "Jojo Hu"
date: "02/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Manuscript Analysis Cleaned (02/18/2021)


``` {r}
setwd("/Users/jojohu/Documents/Qlab/manuscript")

allData <- read.csv("allSLData.csv")
```

# Section 1: Demographic Analysis

## Gender
```{r}
library(reshape)

allData_gender_wide <- allData[,c("part_id", "group", "gender")]

allData_gender_long <- melt(allData_gender_wide, id.vars = c("part_id", "group"))

gender_wide <- cast(allData_gender_long, group~value, length)

# Chi-square on gender
# p<0.05 tells us that they are not matched for gender between group
print(gender_wide)

print(chisq.test(gender_wide))
```

**Gender is matched between group**

## Age
```{r}
allData$age_at_web_year <- allData$age_at_web_month/12

td_age <- 
  allData[which(allData$group == "TD"), 
                       c("part_id", "group", "age_at_web_month", "age_at_web_year")]
asd_age <- 
  allData[which(allData$group == "ASD"), 
                       c("part_id", "group", "age_at_web_month", "age_at_web_year")]

library("pastecs")

get_age_decrip <- function(AgeDF, group) {
  age_stat <- stat.desc(AgeDF)[c("mean", "std.dev", "max", "min", "nbr.val"),"age_at_web_year"]
  age_stat <- append(age_stat, group)
  age_stat <- data.frame(age_stat)
  age_stat <- cbind(c("mean", "std.dev", "max", "min", "n", "group"), age_stat)
  age_stat <- t(age_stat)
  return(age_stat)
  }


td_age_descrip <- get_age_decrip(td_age, "TD")
asd_age_descrip <- get_age_decrip(asd_age, "ASD")

age_descrip_stat <- rbind(td_age_descrip, asd_age_descrip)

print(age_descrip_stat)

age_descrip_stat[c(2,4),-c(6)] <- round(as.numeric(as.character(age_descrip_stat[c(2,4),-c(6)])),2)

#Test age difference between group, p <0.05 means age is significantly different between group
print(t.test(td_age$age_at_web_month, asd_age$age_at_web_month))

print(t.test(td_age$age_at_web_year, asd_age$age_at_web_year))

# write.csv(age_descrip_stat, "age_descrip_stat.csv")
```

# Remove outliers for RT and RT slope 
```{r, include = F}
library(stringr)

ssl_rt_hit_count <- read.csv("ssl_rt_hit_trial_count.csv")
tsl_rt_hit_count <- read.csv("tsl_rt_hit_trial_count.csv")
vsl_rt_hit_count <- read.csv("vsl_rt_hit_trial_count.csv")
lsl_rt_hit_count <- read.csv("lsl_rt_hit_trial_count.csv")

ssl_rt_hit_count$task <- "ssl"
tsl_rt_hit_count$task <- "tsl"
vsl_rt_hit_count$task <- "vsl"
lsl_rt_hit_count$task <- "lsl"

all_rt_hit_count <- 
  rbind(ssl_rt_hit_count,
      tsl_rt_hit_count,
      vsl_rt_hit_count,
      lsl_rt_hit_count)



rt_hit_count_child <- all_rt_hit_count[which(str_detect(
  all_rt_hit_count$part_id, "blast_c_|spoli_c")),]

rt_hit_count_child <- rt_hit_count_child[which(rt_hit_count_child$part_id %in%
                                                 allData$part_id),]


child_rt_outlier <- rt_hit_count_child[which(rt_hit_count_child$hit_trial_number < 6), 
                   c("part_id", "task")]
```



```{r}
rt_hit_count_child[which(rt_hit_count_child$hit_trial_number < 6), 
                   c("part_id", "task", "hit_trial_number")]
```
**Table above are RT outliers in children with less than 6 hit trials in the exposure phase**


# Remove outliers in the children group
```{r, include = F}
outlier_extract <-
  function(DF, task) {
    part_id <- DF[which(DF$task == task), "part_id"]
    return(part_id)
  }

ssl_rt_outlier <- outlier_extract(child_rt_outlier, "ssl")
tsl_rt_outlier <- outlier_extract(child_rt_outlier, "tsl")
vsl_rt_outlier <- outlier_extract(child_rt_outlier, "vsl")
lsl_rt_outlier <- outlier_extract(child_rt_outlier, "lsl")

if(length(ssl_rt_outlier) != 0) {
  allData[which(
    allData$part_id %in% ssl_rt_outlier),
  c("ssl_rt",
    "ssl_slope")] <- NA
}


if(length(tsl_rt_outlier) != 0) {
  allData[which(
    allData$part_id %in% tsl_rt_outlier),
  c("tsl_rt",
    "tsl_slope")] <- NA
}


if(length(vsl_rt_outlier) != 0) {
  allData[which(
    allData$part_id %in% vsl_rt_outlier),
    c("vsl_rt",
      "vsl_slope")] <- NA
}


if(length(lsl_rt_outlier) != 0) {
  allData[which(
    allData$part_id %in% lsl_rt_outlier),
    c("lsl_rt",
      "lsl_slope")] <- NA
}

# Spoli_c_097 has invalid key press (error due to jspsych during the experiment adminstartion)
if(length(which(allData$part_id %in% "spoli_c_097")) != 0) {
  allData[which(
    allData$part_id %in% "spoli_c_097"),
    c("ssl_rt",
      "ssl_slope")] <- NA
}

```

These are removed outliers in the children group: 

SSL RT and Slope < 6 hits: `r ssl_rt_outlier` + 1 ASD spoli_c_097 (jsPsyc technical error in SSL RT) 

TSL RT and Slope < 6 hits: `r tsl_rt_outlier` 

VSL RT and Slope < 6 hits: `r vsl_rt_outlier` 

LSL RT and Slope < 6 hits: `r lsl_rt_outlier` 



# Extract data for each measure (accuracy, slope, rt, entropy)
```{r, include = F}
extract_measure_child <-
function(df, taskCol) {
  df <- 
    allData[,which(str_detect(
      colnames(allData), paste0("part_id|group|age_at_web_year|", taskCol)))]
  
  df <- melt(df, id.vars = c("part_id", "group", "age_at_web_year"))
  
  colnames(df)[colnames(df) == "variable"] <- "task"
  colnames(df)[colnames(df) == "value"] <- taskCol
  
  return(df)
}

allData_acc <- extract_measure_child(allData_acc, "acc")
allData_slope <- extract_measure_child(allData_slope, "slope")
allData_rt <- extract_measure_child(allData_rt, "rt")
allData_entropy <- extract_measure_child(allData_entropy, "ent")

setdiff(unique(allData_acc$part_id), unique(allData$part_id))

colnames(allData_acc)[colnames(allData_acc) == "acc"] <- "accuracy"
colnames(allData_entropy)[colnames(allData_entropy) == "ent"] <- "entropy"
colnames(allData_rt)[colnames(allData_rt) == "rt"] <- "mean_rt"
colnames(allData_slope)[colnames(allData_slope) == "slope"] <- "rt_slope"

allData_acc <-
  allData_acc[-which(str_detect(allData_acc$task, "random|predictable")),]
    
allData_entropy <-
  allData_entropy[-which(str_detect(allData_entropy$task, "random|predictable")),]
```


# Count the number of completed participants for each task

```{r}
## Add language levels in ASD
demo_all <- read.csv("online_demo_all.csv")

allData <- merge(allData, 
                  demo_all[,c("part_id", "rbs_r", "lang_spark_age", "asd", "used_words_age_mos", "combined_words_age_mos",
                     "combined_phrases_age_mos", "cog_age_level", "cog_age_equivalent",
                  "cog_test_score", "function_age_level", "language_age_level")], by.x = "part_id", by.y = "part_id",
                  all.x = T)


library(dplyr)

allData %>%
  group_by(group, language_age_level) %>%
  dplyr::summarise(n = n())
```

```{r,include = F}
allData$scq_web <- as.numeric(as.character(allData$scq_web))

# allData$scq <- coalesce(allData$scq_total, allData$scq_web)

taskcomp_td <-
sapply(allData[which(allData$group == "TD"),
                           c("scq_web",
                             "scq_total",
                             "rbs_r",
                             "kbit_matrices_raw",
                           "rsr_raw", 
                           "a_prime",
                            "vsl_acc", 
                           "lsl_acc",
                           "tsl_acc", 
                           "ssl_acc",
                           "lsl_predictable_2afc_acc")],
       function(x)sum(!is.na(x)))


taskcomp_asd <-
  sapply(allData[which(allData$group == "ASD"),
                           c("scq_web",
                             "scq_total",
                             "rbs_r",
                             "kbit_matrices_raw",
                           "rsr_raw", 
                           "a_prime",
                            "vsl_acc", 
                           "lsl_acc",
                           "tsl_acc", 
                           "ssl_acc",
                           "lsl_predictable_2afc_acc")],
       function(x)sum(!is.na(x)))

taskcomp_count<- rbind(taskcomp_td, taskcomp_asd)

taskcomp_count <- data.frame(taskcomp_count)

colnames(taskcomp_count) <- c("SCQ Lifetime", "SCQ Current", "RBS-R", "KBIT", "Sentence Recall", "Grammaticality Judgement", "Image", "Letter", "Tone", "Syllable", "Letter Predictable")

missing_scq_web <- allData[which(is.na(allData$scq_web) & allData$group == "ASD"), "part_id"]
# write.csv(missing_scq_web, "missing_scq_web.csv")
```

```{r}
print(taskcomp_count)
```

**Missing SCQ: spoli_c_439; spoli_c_448: No SCQ-L scores from SPARK; blast_c_438: Not from SPARK**

## KBIT, SCQ Descriptive Stat
```{r, include = F}
td_sl <- 
  allData[which(allData$group == "TD"),]


asd_sl <- 
  allData[which(allData$group == "ASD"),]

library("pastecs")
td_sl$scq_web <- as.numeric(as.character(td_sl$scq_web))

td_kbit_scq_descrip_stat <-
  stat.desc(td_sl[, c(
    "kbit_matrices_raw",
    "kbit_matrices_std",
    "rbs_r",
    "scq_total",
    "rsr_raw",
    "rsr_std",
    "a_prime",
    "gjt_std"
  )])

td_kbit_scq_descrip_stat <-
  td_kbit_scq_descrip_stat[c("nbr.val", "mean", "std.dev"),
                           c("kbit_matrices_raw",
                             "kbit_matrices_std",
                             "rbs_r",
                             "scq_total",
                             "rsr_raw",
                             "rsr_std",
                             "a_prime",
                             "gjt_std"
                           )]

td_kbit_scq_descrip_stat[nrow(td_kbit_scq_descrip_stat) + 1,] <- "TD"
print(td_kbit_scq_descrip_stat)

asd_kbit_scq_descrip_stat <-
  stat.desc(asd_sl[, c(
    "kbit_matrices_raw",
    "kbit_matrices_std",
    "rbs_r",
    "scq_total" ,
    "scq_web",
    "rsr_raw",
    "rsr_std",
    "a_prime",
    "gjt_std"
  )])

asd_kbit_scq_descrip_stat <-
  asd_kbit_scq_descrip_stat[c("nbr.val", "mean", "std.dev"),
                            c("kbit_matrices_raw",
                              "kbit_matrices_std",
                              "rbs_r",
                              "scq_total" ,
                              "scq_web",
                              "rsr_raw",
                              "rsr_std",
                              "a_prime",
                              "gjt_std"
                            )]
asd_kbit_scq_descrip_stat[nrow(asd_kbit_scq_descrip_stat) + 1,] <- "ASD"
print(asd_kbit_scq_descrip_stat)
```

```{r}
print(td_kbit_scq_descrip_stat)
print(asd_kbit_scq_descrip_stat)
```

# RSR and GJT Descriptive Stat
```{r}
tdRSRDec <- stat.desc(td_sl[,c("rsr_std", "rsr_raw", "a_prime", "gjt_std")])
tdRSRDec <- tdRSRDec[c("nbr.val","mean", "std.dev", "max", "min"),]
tdRSRDec <- data.frame(tdRSRDec)
tdRSRDec[nrow(tdRSRDec)+1,] <- "TD"

asdRSRDec <- stat.desc(asd_sl[,c("rsr_std", "rsr_raw", "a_prime", "gjt_std")])
asdRSRDec <- asdRSRDec[c("nbr.val","mean", "std.dev", "max", "min"),]
asdRSRDec <- data.frame(asdRSRDec)
asdRSRDec[nrow(asdRSRDec)+1,] <- "ASD"

GJTrsrDec <- cbind(tdRSRDec, asdRSRDec)
print(GJTrsrDec)

asd_sl[which(is.na(asd_sl$language_age_level)), "gjt_std"]
asd_sl[which(is.na(asd_sl$language_age_level)), "a_prime"]

# write.csv(GJTrsrDec, "paper_analysis_matched/GJTrsrDec.csv")
```

```{r}
# SCQ comparison between online ASD and in lab TD
t.test(td_sl$scq_total, asd_sl$scq_web)

t.test(td_sl$rsr_raw, asd_sl$rsr_raw)

t.test(td_sl$a_prime, asd_sl$a_prime)

t.test(td_sl$rsr_std, asd_sl$rsr_std)

t.test(td_sl$gjt_std, asd_sl$gjt_std)
```



```{r, include = F}
library(ggplot2)

pd <- position_dodge(width = 0.2)

library(ggbeeswarm)
allData[which(allData$group == "ASD"),] %>%
ggplot(aes(x = language_age_level, y = a_prime)) +
  geom_bar(
    aes(fill = group),
    position = position_dodge(),
    width = 0.9,
    stat = "summary",
    fun.y = "mean",
  ) +
 labs(title = "Relationship between Language Level and GJT in ASD",
         x = "Language Level compared to Age (measured at younger or concurrent age as SL)",  # Change x-axis label
         y = "GJT Raw Score (A')") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=12, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=8, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold"),
        legend.title=element_text(size=15, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),         # Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) + 
  geom_beeswarm(
    aes(fill = group),
    dodge.width = 1,
    cex = 2.5,
    size = 0.8,
    show.legend = FALSE,
    shape = 1
  ) 

 # ggsave("manuscript_figure/ asd_lang_level_gjt.png")
allData[which(allData$group == "ASD"),] %>%
  ggplot(aes(x = language_age_level, y = lsl_slope)) +
  geom_bar(
    aes(fill = group),
    position = position_dodge(),
    width = 0.9,
    stat = "summary",
    fun.y = "mean",
  ) +
 labs(title = "Relationship between Language Level and Letter SL in ASD",
         x = "Language Level compared to Age (measured at younger or concurrent age as SL)",  # Change x-axis label
         y = "Letter SL Reaction Time Slope") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=12, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=8, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold"),
        legend.title=element_text(size=15, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),         # Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)  # Add line to y axis
  ) +
  geom_beeswarm(
    aes(fill = group),
    dodge.width = 1,
    cex = 2.5,
    size = 0.8,
    show.legend = FALSE, 
    shape = 1
  )
```

# SL Descriptive Analysis (Group accuracy against chance level; RT slope against 0)
# Accuracy against chance for TD and ASD
```{r}
t_test_against_chance <- 
  function(x){
  test <- t.test(x, mu=0.5, alternative= "greater")
  data.frame(p_value = test$p.value,
             df = test$parameter,
             t_stat = test$statistic)
  }

#TD without outliers
sapply(colnames(td_sl)[c(7:9, 25)], 
       function(x) t_test_against_chance(td_sl[,x]))

#ASD without outliers
sapply(colnames(asd_sl)[c(7:9, 25)], 
       function(x) t_test_against_chance(asd_sl[,x]))

# Checking to see ssl and lsl against chance in ASD are correct
t.test(asd_sl$ssl_acc, mu=0.5, alternative= "greater")
t.test(asd_sl$lsl_acc, mu=0.5, alternative= "greater")

t_test_against_zero <- 
  function(x){
  test <- t.test(x, mu=0, alternative= "less")
  data.frame(p_value = test$p.value,
             df = test$parameter,
             t_stat = test$statistic)
  }


sapply(colnames(td_sl)[c(21:24)], 
       function(x) t_test_against_zero(td_sl[,x]))

sapply(colnames(asd_sl)[c(21:24)], 
       function(x) t_test_against_zero(asd_sl[,x]))
```


# Group Comparison of SL

```{r, include = F}
# Add modality and domain category to long-format data
library("stringr")
add_dom_mod_func <- 
function(df) {
df[which(str_detect(df$task, "ssl")), "domain"] <- "ling"
df[which(str_detect(df$task, "lsl")), "domain"] <- "ling"
df[which(str_detect(df$task, "vsl")), "domain"] <- "nonling"
df[which(str_detect(df$task, "tsl")), "domain"] <- "nonling"
df[which(str_detect(df$task, "ssl")), "modality"] <- "auditory"
df[which(str_detect(df$task, "tsl")), "modality"] <- "auditory"
df[which(str_detect(df$task, "vsl")), "modality"] <- "visual"
df[which(str_detect(df$task, "lsl")), "modality"] <- "visual"
return (df)
}

allData_acc <- add_dom_mod_func(allData_acc)
allData_entropy <- add_dom_mod_func(allData_entropy)
allData_rt <- add_dom_mod_func(allData_rt)
allData_slope <- add_dom_mod_func(allData_slope)
```


# LMER for Domain and Modality for RT Slope for children
```{r, include = F}
library(lmerTest)

allData_slope$group <- factor(allData_slope$group,
                                    levels = c("ASD", 
                                               "TD"))

allData_slope$domain <- factor(allData_slope$domain,
                                    levels = c("nonling", 
                                               "ling"))

allData_slope$modality <- factor(allData_slope$modality,
                                             levels = c("auditory", 
                                               "visual"))

# Run LMER for RT slope by task
library("stringr")
allData_slope$task <- as.factor(allData_slope$task)

m1_slope <- lmer(rt_slope~group*task + (1+task|part_id),
          data=allData_slope,
          control=lmerControl(optimizer = "bobyqa",
                              check.nobs.vs.nRE="ignore"),
          contrasts = list(group = c(-1,1)))
summary(m1_slope)

# Run LMER for RT slope by domain and modality
m1_slope_dom_mod <- lmer(rt_slope~group*domain*modality + (0 +domain | part_id) + 
                           (0 + modality | part_id) + (1|part_id), 
                         data = allData_slope,
                         control=lmerControl(optimizer = "bobyqa"),
                         contrasts = list(domain = c(-1, 1),
                                          modality = c(-1, 1),
                                      group = c(-1,1)))
summary(m1_slope_dom_mod)


library(afex)
all_fit(m1_slope_dom_mod)

# Model was reduced by these steps:
# lmer(rt_slope~group*domain + (1+domain|part_id), 
#                          data = allData_slope,
#                          contrasts = list(domain = c(-1, 1),
#                                       group = c(-1,1)))
# to lmer(rt_slope~group*domain + (0+domain|part_id) + (1|part_id), same contrasts)
# to lmer(rt_slope~group*domain + (1|part_id), same contrasts)


m1_slope_dom <- lmer(rt_slope~group*domain + (0 + domain|part_id) + (1|part_id), 
                     data = allData_slope,
                     # control = lmerControl(optimizer = "bobyqa"),
                         # control=lmerControl(optimizer = "bobyqa", check.nobs.vs.nRE="ignore"),
                         contrasts = list(domain = c(-1, 1),
                                      group = c(-1,1)))
summary(m1_slope_dom)



```

```{r, include= F}
scaled_allData_slope <- allData_slope

scaled_allData_slope[which(scaled_allData_slope$modality == "visual"), "rt_slope"] <-
  scale(scaled_allData_slope[which(scaled_allData_slope$modality == "visual"), "rt_slope"], center = T)


scaled_allData_slope[which(scaled_allData_slope$modality == "auditory"), "rt_slope"] <-
  scale(scaled_allData_slope[which(scaled_allData_slope$modality == "auditory"), "rt_slope"], center = T)

scaled_allData_slope$group <- factor(scaled_allData_slope$group,
                                    levels = c("ASD", 
                                               "TD"))

scaled_allData_slope$domain <- factor(scaled_allData_slope$domain,
                                    levels = c("nonling", 
                                               "ling"))

scaled_allData_slope$modality <- factor(scaled_allData_slope$modality,
                                             levels = c("auditory", 
                                               "visual"))

m1_scaled_slope_dom_mod <- lmer(rt_slope~group*domain*modality + (0 + domain | part_id) + 
                           (0 + modality | part_id) + (1|part_id), 
                         data = scaled_allData_slope,
                         control=lmerControl(optimizer = "bobyqa", check.nobs.vs.nRE="ignore"),
                         contrasts = list(domain = c(-1, 1),
                                          modality = c(-1, 1),
                                      group = c(-1,1)))
summary(m1_scaled_slope_dom_mod)
```



# By trial Accuracy GLMER
```{r, include = F}
input_path3 <-
  "/Users/jojohu/Documents/Qlab/blast_online_data/data_summaries/blast_online_child/breakdown/acc_by_trial/acc_by_trial"

input_path4 <- "/Users/jojohu/Documents/Qlab/spoli/data_summaries/breakdown/acc_by_trial"

acclist <-
  list.files(path = input_path3,
             pattern = "*by_trial.csv", full.names = T)

acclistSPL <-
  list.files(path = input_path4,
             pattern = "*by_trial.csv", full.names = T)


library("stringr")

tname <- str_extract(basename(acclist), "(?<=blast_)\\S{3}")

tnameSPL <- str_extract(basename(acclistSPL), "(?<=spoli_)\\S{3}")


acc_trial <- lapply(acclist, read.csv)

acc_trialSPL <- lapply(acclistSPL, read.csv)



for (i in 1:length(acc_trial)) {
  acc_trial[[i]]$task <-tname[i]
}

acc_trial <- do.call(rbind, acc_trial)

acc_trial <- acc_trial[,!names(acc_trial) %in% "X"]


for (i in 1:length(acc_trialSPL)) {
  acc_trialSPL[[i]]$task <-tnameSPL[i]
}

acc_trialSPL <- do.call(rbind, acc_trialSPL)

acc_trialSPL <- acc_trialSPL[,!names(acc_trialSPL) %in% "X"]

acc_trial <- rbind(acc_trial, acc_trialSPL)


acc_trial <-
  merge(acc_trial,
      allData[,c("part_id", "group", "gender", "age_at_web_month", "age_at_web_year", "scq_web", "scq_total", 
                 "a_prime", "gjt_std")],
      by.x = "subj",
      by.y = "part_id",
      all.y = T)

setdiff(unique(allData$part_id), unique(acc_trial$subj))

acc_trial$corr <- as.factor(acc_trial$corr)
acc_trial$subj <- as.factor(acc_trial$subj)
acc_trial$task <- as.factor(acc_trial$task)
acc_trial$group <- as.factor(acc_trial$group)

# # write.csv(acc_trial, "/Users/jojohu/Documents/Qlab/bucld_2019_followup/acc_trial.csv")

# Important Step, match the dataset to the current analysis
acc_trial <- acc_trial[which(acc_trial$subj %in% allData$part_id),]


acc_trial <- add_dom_mod_func(acc_trial)
```

# GLMER results for children
```{r}
head(acc_trial)

acc_trial$task <- as.factor(acc_trial$task)
acc_trial$subj <- as.factor(acc_trial$subj)
acc_trial$age_at_web_year <- as.numeric(as.character(acc_trial$age_at_web_year))

typeof(acc_trial$trial_order)
typeof(acc_trial$task)
typeof(acc_trial$corr)
typeof(acc_trial$subj)

acc_trial$task <- 
  factor(acc_trial$task,
         levels = c("lsl", 
                    "ssl", 
                    "vsl", 
                    "tsl"))

acc_trial$group <- 
  factor(acc_trial$group,
         levels = c("ASD", 
                    "TD"))

acc_trial$domain <- 
  factor(acc_trial$domain,
         levels = c("nonling", 
                    "ling"))

acc_trial$modality <- 
  factor(acc_trial$modality,
         levels = c("auditory", 
                    "visual"))

# contr.sum(n=4)

```

```{r}
# This model reduction process helps the model to converge:
# (1+domain|subj) + (1+modality|subj) + (1|trial_order) (not converged)
# (1+domain|subj) + (0+modality|subj) + (1|trial_order) + (1|subj) (not converged)
# (0+domain|subj) + (0+modality|subj) + (1|trial_order) + (1|subj) (not converged)
# (1+domain|subj) + (0+modality|subj) (converged)
# (0+domain|subj) + (0+modality|subj) + (1|subj) (even simpler model, of course converged)

logacc_dom <-
  glmer(corr~group*domain*modality + (1+domain+modality|subj), data = acc_trial,
    family = binomial,
    contrasts = list(domain = c(-1, 1), modality = c(-1, 1), group = c(-1,1)),
    control=glmerControl(optimizer = "bobyqa"))

summary(logacc_dom)
# 
# logacc_dom_gjt <-
#   glmer(corr~group*domain*modality + gjt_std + (0+domain|subj) + (0+modality|subj) + (1|subj) + (1|trial_order), data = acc_trial,
#     family = binomial,
#     contrasts = list(domain = c(-1, 1), modality = c(-1, 1), group = c(-1,1)),
#     control=glmerControl(optimizer = "bobyqa"))
# 
# summary(logacc_dom_gjt)
```

```{r, eval = F, include = F}
# 
# Plot model fit whether the categorization of y is correctly predicted by x?:
# d <- acc_trial
# d <- d[which(!is.na(d$gjt_std)),]
# nrow(d)
# d$predicted <- predict(logacc_mod, type="response")
# d$residuals <- residuals(logacc_mod, type = "response")
# 
# d$corr <- as.numeric(d$corr)
# # Steps 3 and 4: plot the results
# ggplot(d, aes(x = group, y = corr)) +
#   geom_segment(aes(xend = group, yend = predicted), alpha = .2) +
#   geom_point(aes(color = residuals)) +
#   scale_color_gradient2(low = "blue", mid = "white", high = "red") +
#   guides(color = FALSE) +
#   geom_point(aes(y = predicted), shape = 1) +
#   theme_bw()

```





# T-test TD vs. ASD
```{r}
t_test_multi_pair <- 
  function(x,y){
  test <- t.test(x,y)

  data.frame(p_value = test$p.value,
             df = test$parameter,
             t_stat = test$statistic)
  }


#Results withOUT outliers
# T test for SL
sapply(intersect(colnames(td_sl),colnames(asd_sl))[c(7:9, 25)], 
                 function(x) t_test_multi_pair(td_sl[,x], asd_sl[,x]))

sapply(intersect(colnames(td_sl),colnames(asd_sl))[c(13:15, 26)], 
                 function(x) t_test_multi_pair(td_sl[,x], asd_sl[,x]))

sapply(intersect(colnames(td_sl),colnames(asd_sl))[c(17:20)], 
                 function(x) t_test_multi_pair(td_sl[,x], asd_sl[,x]))

sapply(intersect(colnames(td_sl),colnames(asd_sl))[c(21:24)], 
                 function(x) t_test_multi_pair(td_sl[,x], asd_sl[,x]))
# Still in lab sample comparison for Kbit and SCQ:in the lab 
sapply(intersect(colnames(td_sl),colnames(asd_sl))[c(27:28, 29)], 
                 function(x) t_test_multi_pair(td_sl[,x], asd_sl[,x]))

```


# By trial RT LMER (Need to use Scale RT for by trial RT LMER? Outlier removed)
# To Do: Scale by trial RT? Add target image as a random effect? Add mean RT as fixed effect?
```{r, include = F}
input_path5 <-
  "/Users/jojohu/Documents/Qlab/blast_online_data/data_summaries/blast_online_child/breakdown/acc_by_trial/rt_by_trial"

input_path6 <-
  "/Users/jojohu/Documents/Qlab/spoli/data_summaries/breakdown/rt_by_trial"


rtlist <-
  list.files(path = input_path5,
             pattern = "*by_trial.csv", full.names = T)

rtlistSpl <-
  list.files(path = input_path6,
             pattern = "*by_trial.csv", full.names = T)


library("stringr")

fname <- str_extract(basename(rtlist), "(?<=blast_)\\S{3}")
fnameSpl <- str_extract(basename(rtlistSpl), "(?<=spoli_)\\S{3}")



rt_trial <- lapply(rtlist, read.csv)
rt_trialSpl <- lapply(rtlistSpl, read.csv)


for (i in 1:length(rt_trial)) {
  rt_trial[[i]]$task <-fname[i]
}

for (i in 1:length(rt_trialSpl)) {
  rt_trialSpl[[i]]$task <-fnameSpl[i]
}


for (i in 2:length(rt_trial)) {
  rt_trial[[i]] <- rt_trial[[i]][,-6]
}

for (i in 2:length(rt_trialSpl)) {
  rt_trialSpl[[i]] <- rt_trialSpl[[i]][,-6]
}


rt_trial[[1]]$id <- str_extract(rt_trial[[1]]$id, "\\S+(?=_lsl)")
rt_trialSpl[[1]]$id <- str_extract(rt_trialSpl[[1]]$id, "\\S+(?=_lsl)")


# Save TD by trial VSL RT for BOLD Lab
# vslRTtriaTD <- rt_trial[[4]][which(rt_trial[[4]]$id %in% allData[which(allData$group == "TD"), "part_id"]),]
#
# vslRTtriaTD <- vslRTtriaTD[,c(4,5,3)]
#
# # write.csv(vslRTtriaTD, "vslRTtriaTD.csv", row.names = F)

rt_trial <- do.call(rbind, rt_trial)
rt_trialSpl <- do.call(rbind, rt_trialSpl)

rt_trial <- rbind(rt_trial, rt_trialSpl)

rt_trial <- rt_trial[,!names(rt_trial) %in% "X"]

if(length(ssl_rt_outlier) != 0) {
  rt_trial <-
  rt_trial[-which(
    rt_trial$id %in% ssl_rt_outlier &
      rt_trial$task == "ssl"),]
}

if(length(tsl_rt_outlier) != 0) {
  rt_trial <-
  rt_trial[-which(
    rt_trial$id %in% tsl_rt_outlier &
      rt_trial$task == "tsl"),]
}

if(length(vsl_rt_outlier) != 0) {
  rt_trial <-
  rt_trial[-which(
    rt_trial$id %in% vsl_rt_outlier &
      rt_trial$task == "vsl"),]
}

if(length(lsl_rt_outlier) != 0) {
  rt_trial <-
  rt_trial[-which(
    rt_trial$id %in% lsl_rt_outlier &
      rt_trial$task == "lsl"),]
}


# Spoli_c_097 has invalid key press (error due to jspsych during the experiment adminstartion)
if(length(which(rt_trial$id %in% "spoli_c_097")) != 0) {
  rt_trial[which(
    rt_trial$id %in% "spoli_c_097" & 
      rt_trial$task == "ssl"),
    c("reaction_time")] <- NA
}


rt_trial <-
  merge(rt_trial,
      allData[,c("part_id", "group", "gender", "age_at_web_month", "age_at_web_year", "a_prime", "gjt_std")],
      by.x = "id",
      by.y = "part_id",
      all.y = T)


rt_trial <- rt_trial[which(rt_trial$id %in% allData$part_id),]

setdiff(unique(allData$part_id), unique(rt_trial$id))
setdiff(unique(rt_trial$id), unique(allData$part_id))

# Outliers are already removed
rt_trialTD <- rt_trial[which(str_detect(rt_trial$group, "TD")),]

rt_trial <- add_dom_mod_func(rt_trial)
```

# Compare number of hit trials across groups
```{r}
hit_trialN <- 
  rt_trial %>%
  subset(., !is.na(reaction_time)) %>%
  group_by(group, id, task) %>%
  dplyr::summarise(hit_trial_n = n())

# Count N for each domain and modality
rt_trial %>%
  subset(., !is.na(reaction_time)) %>%
  group_by(group, task) %>%
  dplyr::summarise(hit_trial_n = n())


hit_trial_mean <-  
  hit_trialN %>%
  group_by(group, task) %>%
  dplyr::summarise(mean_hit_trial = mean(hit_trial_n))

print(hit_trial_mean)

# write.csv(hit_trial_mean, "hit_trial_mean.csv")

hit_trialN <- add_dom_mod_func(hit_trialN)

m1_hit_trial <-
lmer(hit_trial_n ~ group*domain*modality + (1+domain + modality|id), data = hit_trialN,
       contrasts = list(group = c(-1,1),
                        domain = c(-1,1),
                        modality = c(-1,1)))

summary(m1_hit_trial)

hitsASD <- subset(hit_trialN, group == "ASD")
hitsTD <- subset(hit_trialN, group == "TD")

hit_trialN <- hit_trialN[!colnames(hit_trialN) %in% "group"]

rt_trial <- 
  merge(rt_trial, hit_trialN[,c("id", "task", "hit_trial_n")], by.x = c("id", "task"), by.y = c("id", "task"), all.x = T)

hitsASD <- hitsASD[!colnames(hitsASD) %in% "group"]
hitsTD <- hitsTD[!colnames(hitsTD) %in% "group"]

t.test(hitsASD$hit_trial_n, hitsTD$hit_trial_n)
```

# Normalize RT
```{r, include = F}
rt_trial_scaled <- rt_trial

rt_trial_scaled <- rt_trial_scaled[!is.na(rt_trial_scaled$reaction_time),]

for(id in unique(rt_trial_scaled$id)) {
    #extract each id's individual rt by trial (results same as data summaries; checked)
    rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "lsl"), "scaled_rt"] <- 
      scale(rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "lsl"),"reaction_time"], center = T)
    rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "vsl"), "scaled_rt"] <- 
      scale(rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "vsl"),"reaction_time"], center = T)
    rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "tsl"), "scaled_rt"] <- 
      scale(rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "tsl"),"reaction_time"], center = T)
    rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "ssl"), "scaled_rt"] <- 
      scale(rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "ssl"),"reaction_time"], center = T)
    
    # Using the first 3 target trials as baseline do not seem to be a very good idea honestly; looking at the raw data the variances seem to be great among the first three trials
    # firstThreeTrial <- sort(rt_trial_scaled[which(rt_trial_scaled$id == "blast_c_002" & rt_trial_scaled$task == "lsl"), "targ_index"])[1:3]
    # rt_trial_scaled[which(rt_trial_scaled$id == "blast_c_213" & rt_trial_scaled$targ_index %in% firstThreeTrial & rt_trial_scaled$task == "lsl"), ] 
}


for(id in unique(rt_trial_scaled$id)) {
    #extract each id's individual rt by trial (results same as data summaries; checked)
    rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "lsl"), "log_rt"] <- 
      log(rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "lsl"),"reaction_time"] +
            (2- min(rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "lsl"),"reaction_time"], na.rm = T)))
    rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "vsl"), "log_rt"] <- 
      log(rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "vsl"),"reaction_time"] + 
            (2- min(rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "vsl"),"reaction_time"], na.rm = T)))
    rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "tsl"), "log_rt"] <- 
      log(rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "tsl"),"reaction_time"] + 
            (2- min(rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "tsl"),"reaction_time"], na.rm = T)))
    rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "ssl"), "log_rt"] <- 
      log(rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "ssl"),"reaction_time"] + 
            (2- min(rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "ssl"),"reaction_time"], na.rm = T)))
}


qnormRT <-
function(id, task) {
  rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == task),"ranked_rt"] <- 
    (rank(rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == task),"reaction_time"])-0.5) / length(rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == task),"reaction_time"])
  
  rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == task),"ranked_rt"] <- 
    as.numeric(as.character(rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == task),"ranked_rt"]))

  rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == task),"normed_rankRT"] <- 
    qnorm(rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == task),"ranked_rt"])
  
  return(rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == task),])
}

mean_rt <- allData[,c("part_id","lsl_rt", "vsl_rt", "tsl_rt", "ssl_rt")]

mean_rt <- melt(mean_rt, id.vars = ("part_id"))

colnames(mean_rt) <- c("part_id", "task", "mean_rt")

mean_rt$task <- gsub("_rt", "", mean_rt$task)

rt_trial_scaled <- merge(rt_trial_scaled, mean_rt, by.x = c("id", "task"), by.y = c("part_id", "task"), all.x = T)

qnormRTlsl <- list()
qnormRTtsl <- list()
qnormRTvsl <- list()
qnormRTssl <- list()
index = 0

for(id in unique(rt_trial_scaled$id)) {
  index <- index + 1
  qnormRTlsl[[index]]  <- qnormRT(id, "lsl")
  qnormRTvsl[[index]]  <- qnormRT(id, "vsl")
  qnormRTssl[[index]]  <- qnormRT(id, "ssl")
  qnormRTtsl[[index]]  <- qnormRT(id, "tsl")
}

qnormRTlsl <- do.call(rbind, qnormRTlsl)
qnormRTvsl <- do.call(rbind, qnormRTvsl)
qnormRTssl <- do.call(rbind, qnormRTssl)
qnormRTtsl <- do.call(rbind, qnormRTtsl)

qnormRTall <- rbind(qnormRTlsl, qnormRTvsl)
qnormRTall <- rbind(qnormRTall, qnormRTssl)
qnormRTall <- rbind(qnormRTall, qnormRTtsl)

hist(rt_trial_scaled$reaction_time)
hist(rt_trial_scaled$log_rt)
hist(rt_trial_scaled$scaled_rt)
hist(qnormRTall$normed_rankRT)

# write.csv(rt_trial_scaled, "/Users/jojohu/Documents/Qlab/manuscript/byTrialRTAll.csv")
```


# By trial RT results in children
```{r}
head(rt_trial_scaled)

rt_trial_scaled$reaction_time <- as.numeric(as.character(rt_trial_scaled$reaction_time))
rt_trial_scaled$id <- as.factor(rt_trial_scaled$id)
rt_trial_scaled$task <- as.factor(rt_trial_scaled$task)
rt_trial_scaled$targ_index <- as.numeric(as.character(rt_trial_scaled$targ_index))
rt_trial_scaled$mean_rt <- as.numeric(as.character(rt_trial_scaled$mean_rt))


rt_trial_scaled$task <- 
  factor(rt_trial_scaled$task,
         levels = c("lsl", 
                    "ssl", 
                    "vsl", 
                    "tsl"))

rt_trial_scaled$group <- 
  factor(rt_trial_scaled$group,
         levels = c("ASD", 
                    "TD"))

rt_trial_scaled$domain <- 
  factor(rt_trial_scaled$domain,
         levels = c("nonling", 
                    "ling"))

rt_trial_scaled$modality <- 
  factor(rt_trial_scaled$modality,
         levels = c("auditory", 
                    "visual"))

# plot(lmerrt_trial)
# To Do: plot other residual plots to check model
rt_trial_scaled %>%
  group_by(group, task) %>%
  dplyr::summarise(N = n(), partN = length(unique(id)), cellN = N/partN)
```


# Plot by trial RT
```{r}
library(dplyr)

rt_trialPlot <-
rt_trial_scaled %>% 
    group_by(group, task, targ_index) %>%
    dplyr::summarise(scaled_mean_rt = mean(scaled_rt, na.rm=T), sd = sd(scaled_rt, na.rm=T), sum = sum(scaled_rt, na.rm = T),
                     se=sd(scaled_rt, na.rm=T)/sqrt(sum(!is.na(scaled_rt))), n = sum(!is.na(scaled_rt)))


library(ggplot2)


plot_byTrialRT <- function(task) {
  rt_trialPlot[which(rt_trialPlot[,c("task")] == task),] %>%
    ggplot(aes(x = targ_index, y = scaled_mean_rt)) + 
    geom_errorbar(aes(ymin = scaled_mean_rt - se, ymax = scaled_mean_rt + se), width = .01, 
                  color = "grey") +
     geom_point(aes(color = group), size = 0.01, position = pd,show.legend = FALSE) +
     geom_line(aes(linetype = group, color = group), position = position_dodge(width = 0.2)) +
    labs(title = paste("By trial Scaled Mean RT", task),# Change x-axis label
         y = "Scaled Mean RT (arbitrary unit)") 
}
# 
# plot_byTrialRT("vsl")
# plot_byTrialRT("lsl")
# plot_byTrialRT("tsl")
# plot_byTrialRT("ssl")

plot_indivRT <- function(task) {
  rt_trial_scaled[which(rt_trial_scaled[,c("task")] == task),] %>%
                      # & rt_trial_scaled$group == group)
    ggplot(aes(x = targ_index, y = scaled_rt)) +
    facet_wrap(vars(group)) +
     geom_point(aes(group = id), size = 0.01, position = pd,show.legend = FALSE) +
     # geom_line(aes(color = id), position = position_dodge(width = 0.2), alpha = 0.5, show.legend = FALSE)
     geom_smooth(aes(group = id), method = "lm", se = FALSE, size=0.2) +
     scale_color_grey()+
    labs(title = paste(task, "By trial Scaled Mean RT"),# Change x-axis label
         y = "Scaled Mean RT (arbitrary unit)")
}

# plot_indivRT("lsl")
# ggsave("byTrialRTlsl_scaled.png")
# plot_indivRT("ssl")
# ggsave("byTrialRTssl_scaled.png")
# plot_indivRT("vsl")
# ggsave("byTrialRTvsl_scaled.png")
# plot_indivRT("tsl")
# ggsave("byTrialRTtsl_scaled.png")

```


```{r, include = F}
# hit trials interact with domain and modality and thus may affect raw by trial RT (more hit trials, lower raw RT (e.g., in auditory SL))
lmerrt_trial_dom <-
  lmer(reaction_time~group*targ_index*domain*modality  + hit_trial_n + hit_trial_n:domain + hit_trial_n:modality + (0+domain|id) + (0+modality|id) + (1|id),
       data = rt_trial_scaled,
       contrasts = list(group = c(-0.5,0.5),
                        modality = c(-0.5, 0.5),
                        domain = c(-0.5, 0.5)),
        control=lmerControl(optimizer = "bobyqa",
                               check.nobs.vs.nRE="ignore"))

summary(lmerrt_trial_dom)
```

```{r}
# Reducing from (1+domain|id) to (0 + domain) +  (1|id) 
# https://stats.stackexchange.com/questions/13166/rs-lmer-cheat-sheet
# https://stats.stackexchange.com/questions/242109/model-failed-to-converge-warning-in-lmer
# No optimizer yields the same results; not overfitting the model is more important
# Three different intercepts for ID.

lmerrt_scaled_m1 <-
  lmer(
    scaled_rt ~ group * targ_index * domain * modality + (1 + modality + domain |
                                                            id),
    # + (0 + (modality + domain) | id),
    data = rt_trial_scaled,
    contrasts = list(
      group = c(-0.5, 0.5),
      modality = c(-0.5, 0.5),
      domain = c(-0.5, 0.5)
    )
  )
summary(lmerrt_scaled_m1)


# all_fit(lmerrt_scaled_m1)

```

```{r}
# Using original reaction time and controlling for mean reaction time
lmerrt_m2 <-
  lmer(reaction_time~group*targ_index*domain*modality + mean_rt + (1 + modality + domain| id),
       data = rt_trial_scaled,
       contrasts = list(group = c(-0.5,0.5),
                        modality = c(-0.5, 0.5),
                        domain = c(-0.5, 0.5))
      )

summary(lmerrt_m2)

scaled_rt_group <- rt_trial_scaled
scaled_rt_group$scaled_rt_group <- scale(scaled_rt_group$reaction_time)

lmerrt_m5 <-
  lmer(scaled_rt_group~group*targ_index*domain*modality + (1 + modality + domain| id),
       data = scaled_rt_group,
       contrasts = list(group = c(-0.5,0.5),
                        modality = c(-0.5, 0.5),
                        domain = c(-0.5, 0.5)))
summary(lmerrt_m5)
```





```{r}
all_fit(lmerrt_scaled_m1)


print(lmerrt_scaled_m1, correlation=TRUE)
```

```{r}
library(afex)
# all_fit(lmerrt_trial_dom_scaled)


rt_trial_scaledLING <- rt_trial_scaled[which(rt_trial_scaled$domain == "ling"),]
rt_trial_scaledNonling <- rt_trial_scaled[which(rt_trial_scaled$domain == "nonling"),]

# Break down 4 way interaction group1:targ_index:domain1:modality1

lmer_slopeLING <-
  lmer(scaled_rt~group*targ_index*modality + (1+modality|id),
       data = rt_trial_scaledLING,
       contrasts = list(group = c(-1,1),
                        modality = c(-1, 1)),
       control=lmerControl(optimizer = "bobyqa"))

summary(lmer_slopeLING)

lmer_slopeNonling <-
  lmer(scaled_rt~group*targ_index*modality + (1+modality|id),
       data = rt_trial_scaledNonling,
       contrasts = list(group = c(-1,1),
                        modality = c(-1, 1)),
       control=lmerControl(optimizer = "bobyqa"))

summary(lmer_slopeNonling)
```


```{r}
library(afex)
# all_fit(lmerrt_trial_dom_scaled)


rt_trial_scaledVisual <- rt_trial_scaled[which(rt_trial_scaled$modality == "visual"),]
rt_trial_scaledAuditory <- rt_trial_scaled[which(rt_trial_scaled$modality == "auditory"),]

# Break down 4 way interaction group1:targ_index:domain1:modality1

lmer_slopeVisual <-
  lmer(reaction_time~group*targ_index*domain +  (1+domain|id),
       data = rt_trial_scaledVisual,
       contrasts = list(group = c(-1,1),
                        domain = c(-1, 1)),
       control=lmerControl(optimizer = "bobyqa"))

summary(lmer_slopeVisual)

lmer_slopeAuditory <-
  lmer(reaction_time~group*targ_index*domain + (1+domain|id),
       data = rt_trial_scaledAuditory,
       contrasts = list(group = c(-1,1),
                        domain = c(-1, 1)),
       control=lmerControl(optimizer = "bobyqa"))

summary(lmer_slopeAuditory)
```


```{r, include = F}
# Check whether hit trials interact with group or task
lmerrt_trial <-
  lmer(scaled_rt~group*targ_index*task + hit_trial_n:group + hit_trial_n + (0+task|id) + (1|id), 
       data = rt_trial_scaled,
       contrasts = list(group = c(-1,1)))

summary(lmerrt_trial)
```



```{r}
asd_composite <- allData

asd_composite[, c("lsl_slopeScaled", "ssl_slopeScaled","vsl_slopeScaled", "tsl_slopeScaled")] <-
  lapply(asd_composite[, c("lsl_slope", "ssl_slope","vsl_slope", "tsl_slope")], 
         function(x) {
           scale(0 -x)
           })

asd_composite[, c("lsl_accScaled", "ssl_accScaled","vsl_accScaled", "tsl_accScaled")] <-
  lapply(asd_composite[, c("lsl_acc", "ssl_acc","vsl_acc", "tsl_acc")], 
         function(x) {
           scale(x)
           })

# When composite score only includes the SL tasks, no significance was found in any of the analyses

sumComposite <- function(taskCol, nCol, column_list) {
  asd_composite[,taskCol] <-
  rowSums(asd_composite[, column_list], na.rm = T)
  
  asd_composite[,nCol] <-
  apply(asd_composite[column_list], 1, function(x) {
                              sum(!is.na(x)) })
  
   asd_composite[,taskCol] <- asd_composite[,taskCol]/ asd_composite[,nCol] 
  
  return(asd_composite)
}

asd_composite <-
  sumComposite("composite_ling", "completeN_ling", 
               c("lsl_accScaled", "ssl_accScaled", 
                 "lsl_slopeScaled", "ssl_slopeScaled"))

asd_composite <-
  sumComposite("composite_nonling", "completeN_nonling", 
               c("vsl_accScaled", "tsl_accScaled", 
                 "vsl_slopeScaled", "tsl_slopeScaled"))


asd_composite <-
  sumComposite("composite_ssl", "completeN_ssl", 
               c("ssl_accScaled", "ssl_slopeScaled"))

asd_composite <-
  sumComposite("composite_tsl", "completeN_tsl", 
               c("tsl_accScaled", "tsl_slopeScaled"))


asd_composite <-
  sumComposite("composite_vsl", "completeN_vsl", 
               c("vsl_accScaled", "vsl_slopeScaled"))

asd_composite <-
  sumComposite("composite_lsl", "completeN_lsl", 
               c("lsl_accScaled", "lsl_slopeScaled"))

compositeAge <- asd_composite[order(asd_composite$age_at_web_month),]

compositeAgeTD <- compositeAge[which(compositeAge$group == "TD"),]
compositeAgeASD <- compositeAge[which(compositeAge$group == "ASD"),]

hist(compositeAge$age_at_web_year)

compositeAgeTD[which(compositeAgeTD$age_at_web_month < mean(compositeAgeTD$age_at_web_month)),"age_group"] <- "Younger TD"
compositeAgeTD[which(compositeAgeTD$age_at_web_month > mean(compositeAgeTD$age_at_web_month)),"age_group"] <- "Older TD"
compositeAgeASD[which(compositeAgeASD$age_at_web_month < mean(compositeAgeASD$age_at_web_month)),"age_group"] <- "Younger ASD"
compositeAgeASD[which(compositeAgeASD$age_at_web_month > mean(compositeAgeASD$age_at_web_month)),"age_group"] <- "Older ASD"

# Median split of age (age distribution left skewed; median may not make the most sense)
# compositeAgeTD[1:round(length(compositeAgeTD$age_at_web_month)/2),"age_group"] <- "Younger TD"
# median <- round((length(compositeAgeTD$age_at_web_month)/2))+1
# compositeAgeTD[median:length(compositeAgeTD$age_at_web_month),"age_group"] <- "Older TD"
# 
# # compositeAgeASD$age_group <- "ASD"
# 
# compositeAgeASD[1:round(length(compositeAgeASD$age_at_web_month)/2),"age_group"] <- "Younger ASD"
# median <- round((length(compositeAgeASD$age_at_web_month)/2))+1
# compositeAgeASD[median:length(compositeAgeASD$age_at_web_month),"age_group"] <- "Older ASD"

compositeAge <- rbind(compositeAgeTD, compositeAgeASD)

compositeAge$ageSplit <- str_extract(compositeAge$age_group, "Young|Old")

compositeAge[which(compositeAge$age_at_web_year < 6.5 & compositeAge$group == "TD"), "ssl_acc"]

# Compare GJT in Younger vs. Older children
# t.test(compositeAge[which(compositeAge$group == "ASD" & compositeAge$age_group == "Older ASD"),]$gjt_std,
# compositeAge[which(compositeAge$group == "ASD" & compositeAge$age_group == "Younger ASD"),]$gjt_std)
```


```{r}
compositeGroup <-
  asd_composite[, c(
    "part_id",
    "group",
    "gender",
    "age_at_web_month",
    "age_at_web_year",
    "composite_lsl",
    "composite_ssl",
    "composite_vsl",
    "composite_tsl")]

compositeGroupL <-
  melt(
    compositeGroup,
    id.vars = c(
      "part_id",
      "group",
      "gender",
      "age_at_web_month",
      "age_at_web_year"))

colnames(compositeGroupL)[colnames(compositeGroupL) %in% c("variable", "value")] <-
  c("task", "composite_score")
compositeGroupL <- add_dom_mod_func(compositeGroupL)
compositeGroupL$task <- as.factor(compositeGroupL$task)
compositeGroupL$part_id <- as.factor(compositeGroupL$part_id)
compositeGroupL$age_at_web_month <-
  as.numeric(as.character(compositeGroupL$age_at_web_month))
compositeGroupL$composite_score <-
  as.numeric(as.character(compositeGroupL$composite_score))
compositeGroupL$group <-
  factor(compositeGroupL$group,
         levels = c("ASD",
                    "TD"))
compositeGroupL$domain <-
  factor(compositeGroupL$domain,
         levels = c("nonling",
                    "ling"))
compositeGroupL$modality <-
  factor(compositeGroupL$modality,
         levels = c("auditory",
                    "visual"))
# This model reduction process helps the model to converge:
# 1+domain*modality|part_id (not converged; too many random effect estimates)
# Scaling did not change the result of the model:
# compositeGroupL$composite_score <- scale(compositeGroupL$composite_score)
composite_m1 <-
  lmer(
    composite_score ~ group * domain * modality + (1 + domain + modality | part_id),
    data = compositeGroupL,
    contrasts = list(
      domain = c(-1, 1),
      modality = c(-1, 1),
      group = c(-1, 1))
    # control=lmerControl(optimizer = "bobyqa")
    )
summary(composite_m1)
```

# Post-hoc t-test for composite scores
```{r}
compositeGroupTD <- compositeGroup[which(compositeGroup$group == "TD"),]
compositeGroupASD <- compositeGroup[which(compositeGroup$group == "ASD"),]

sapply(intersect(colnames(compositeGroupTD),colnames(compositeGroupASD))[6:9], 
                 function(x) t_test_multi_pair(compositeGroupTD[,x], compositeGroupASD[,x]))
```

# Follow-up Analyses
**Why does the ASD group have specific weakness in Linguistic Tasks?**
**Check Composite SL Score differences in ASD between below age and at age language groups**

# SPARK language level and composite score (language level not a reliable measure based on its correlation with GJT)
```{r}
library("plyr")

compositeAge$language_age_level <-
revalue(compositeAge$language_age_level, c("signif_below_age"="below_age",
                                     "slight_below_age"="below_age",
                                     "at_age"="at_age",
                                     "above_age"="at_age"))
detach(package:plyr)

# compositeAge$language_age_level <- as.character(compositeAge$language_age_level)
# compositeAge[which(compositeAge$group == "TD"), "language_age_level"] <- "TD"

compositeAge$language_age_level <- as.factor(compositeAge$language_age_level)

compositeAge$language_age_level <- 
  factor(compositeAge$language_age_level,
         levels = c("below_age", 
                    "at_age"
                    # "TD"
                    ))

# Check Linguistic RT slope differences in ASD between below age and at age language groups using ancova
# compositeAge <- compositeAge[which(!is.na(compositeAge$language_age_level) &
#                                        !is.na(compositeAge$composite_ling)),]
# compositeAge <- compositeAge[which(!is.na(compositeAge$scq_web)),]
# compositeAge <- compositeAge[which(!is.na(compositeAge$rbs_r)),]

nrow(compositeAge[which(!is.na(compositeAge$a_prime) & !is.na(compositeAge$composite_ling)),])

compositeASD_m1 <- lm(composite_ling ~ a_prime + age_at_web_month,
                 # contrasts = list(modality = c(-0.5,0.5)),
               data = compositeAge)

summary(compositeASD_m1)

# a stronger correlation between nonlinguistic composite score and a_prime is found
compositeASD_m2 <- lm(composite_nonling ~ a_prime + age_at_web_month,
                 # contrasts = list(modality = c(-0.5,0.5)),
               data = compositeAge)

summary(compositeASD_m2)



# T.test of the composite SL scores indivudial tasks did not reach significance
t.test(compositeAge[which(compositeAge$language_age_level == "below_age"),"composite_ling"],
       compositeAge[which(compositeAge$language_age_level == "at_age"),"composite_ling"])

# library(ez)
# 
# ezANOVA(data=compositeAge, wid=part_id, dv=composite_ling, between = language_age_level,
#         type=3, detailed=TRUE)


# ezANOVA(data=compositeAge, wid=part_id, dv=composite, between = language_age_level,
#         between_covariates = c("age_at_web_year"),
#         type=3, detailed=TRUE)

# Check Linguistic RT slope differences in ASD between below age and at age language groups
rtASD <- compositeAge[which(compositeAge$group == "ASD"),
                    c("part_id", "group", 
                   # "lsl_acc","ssl_acc",
                    # "vsl_acc","tsl_acc",
                   "lsl_slope", "ssl_slope", 
                   # "tsl_slope", "vsl_slope",
                   "age_at_web_month", "age_at_web_year", "language_age_level",
                   "a_prime", "gjt_std", "scq_web", "rbs_r")]

# T.test of the accuracy or slope of indivudial tasks did not reach significance
t.test(rtASD[which(rtASD$language_age_level == "below_age"),"lsl_slope"],
       rtASD[which(rtASD$language_age_level == "at_age"),"lsl_slope"])

t.test(rtASD[which(rtASD$language_age_level == "below_age"),"ssl_slope"],
       rtASD[which(rtASD$language_age_level == "at_age"),"ssl_slope"])

# rtASD <- rtASD[which(!is.na(rtASD$lsl_slope) & !is.na(rtASD$ssl_slope)),]

rtASDlong <- melt(rtASD, id.vars = c("part_id", "group", "age_at_web_month", "age_at_web_year", 
                        "language_age_level", "a_prime", "gjt_std", "scq_web", "rbs_r"))


colnames(rtASDlong)[which(colnames(rtASDlong) == "variable")] <- "task"
rtASDlong$task <- gsub("_slope", "", rtASDlong$task)
colnames(rtASDlong)[which(colnames(rtASDlong) == "value")] <- "rt_slope"

rtASDlong <- add_dom_mod_func(rtASDlong)

rtASD_ling <- rtASDlong[which(rtASDlong$domain == "ling"),]

# Check Linguistic RT slope differences in ASD between below age and at age language groups using linear regression
rtASD_m1 <- lm(rt_slope ~ a_prime,
                 # contrasts = list(modality = c(-0.5,0.5)),
               data = rtASD_ling)

summary(rtASD_m1)

# T.test of RT slope of the linguistic tasks did not reach significance
t.test(rtASD_ling[which(rtASD_ling$language_age_level == "below_age"),"rt_slope"],
       rtASD_ling[which(rtASD_ling$language_age_level == "at_age"),"rt_slope"])


# library(ez)
# # Check Linguistic RT slope differences in ASD between below age and at age language groups using ancova
# rtASD_ling <- rtASD_ling[which(!is.na(rtASD_ling$language_age_level)),]
# # rtASD_ling <- rtASD_ling[which(!is.na(rtASD_ling$scq_web)),]
# # rtASD_ling <- rtASD_ling[which(!is.na(rtASD_ling$rbs_r)),]
# 
# ezANOVA(data=rtASD_ling, wid=part_id, dv=rt_slope, between = language_age_level, 
#         between_covariates = c("age_at_web_month"),
#         type=3, detailed=TRUE)

# Plot by language level in ASD
slopeByLang <- merge(allData_slope, allData[,c("part_id", "language_age_level")], all.x = T)

slopeByLang[which(slopeByLang$language_age_level == "slight_below_age" | 
        slopeByLang$language_age_level == "signif_below_age"), "Group"] <- "Delayed Language ASD"

slopeByLang[which(slopeByLang$language_age_level == "above_age" | 
        slopeByLang$language_age_level == "at_age"), "Group"] <- "Typical Language ASD"

slopeByLang[which(slopeByLang$group == "TD"), "Group"] <- "TD"

# LSL and SSL tasks by itself looks similar 
slopeByLang <- slopeByLang[which(slopeByLang$domain == "ling"), ]

slopeByLang %>%
  ggplot(aes(x = Group, y = rt_slope,fill = Group)) +
  geom_bar(position = position_dodge(),
           width = 0.9,
           stat = "summary", fun.y = "mean") +
   labs(title = "Lingustic SL RT Slope  Split by Language in ASD",
        x = "Age Group",  # Change x-axis label
         y = "Lingustic SL RT Slope (arbitrary unit/ trial)") +
  # scale_fill_manual(values = c("#F8766d", "#00BFC4", "#00BFC4")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold"),
        legend.title=element_text(size=15, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),         # Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) + 
  geom_beeswarm(
    aes(fill = Group),
    dodge.width = 1,
    cex = 2.5,
    size = 0.8,
    show.legend = FALSE,
    shape = 1
  )

# ggsave("asd_split_by_lang.png", width = 10, dpi = 150)
```



# Data Prep for post-hoc analysis
```{r}
# Regenerate a long data frame with GJT and scaled accuracy scores
compositeAge$age_scaled <- compositeAge$age_at_web_month
gjt_mulreg <- compositeAge[,c("part_id", "group", "age_at_web_month", "age_at_web_year", "age_scaled", "a_prime",
                               "scq_web", "rbs_r", "composite_ling", "composite_nonling", "ageSplit",
                              "composite_lsl", "composite_ssl","composite_tsl", "composite_vsl")]

gjt_mulregNscaled <- 
  melt(gjt_mulreg[,c("part_id", "group", "age_at_web_month", "age_at_web_year", "age_scaled", "a_prime",
                      "scq_web", "rbs_r", "ageSplit", "composite_nonling", "composite_ling")], 
       id.vars= c("part_id", "group", "age_at_web_month", "age_at_web_year", "age_scaled", "a_prime",
                               "scq_web", "rbs_r", "ageSplit"))

colnames(gjt_mulregNscaled)[which(colnames(gjt_mulregNscaled) == "variable")] <- "domain"
colnames(gjt_mulregNscaled)[which(colnames(gjt_mulregNscaled) == "value")] <- "composite_score"

compositeYoungNScaled <- gjt_mulregNscaled[which(gjt_mulregNscaled$ageSplit == "Young"),]
compositeOldNScaled <- gjt_mulregNscaled[which(gjt_mulregNscaled$ageSplit == "Old"),]
```


# Plot composite score in each age group
```{r}
compositeYoungPlot <- summarySEwithin(compositeYoungNScaled, measurevar = "composite_score", betweenvars = "group", 
                                    withinvars = "domain", idvar="part_id", na.rm=T, conf.interval=.95)

compositeYoungPlot$Age <- "Younger"

compositeOldPlot <- summarySEwithin(compositeOldNScaled, measurevar = "composite_score", betweenvars = "group", 
                                    withinvars = "domain", idvar="part_id", na.rm=T, conf.interval=.95)

compositeOldPlot$Age <- "Older"

compositeAgePlot <- rbind(compositeYoungPlot, compositeOldPlot)

compositeAgePlot$domain <- 
  factor(compositeAgePlot$domain,levels = c("composite_ling", 
                                              "composite_nonling"))

colnames(compositeAgePlot)[colnames(compositeAgePlot) == "group"] <- "Group"
# colnames(compositeAgePlot)[colnames(compositeAgePlot) == "domain"] <- "Domain"
# compositeAgePlot$Domain <- as.character(compositeAgePlot$Domain)
compositeAgePlot[which(compositeAgePlot$domain == "composite_nonling"), "Domain"] <- "Nonlinguistic"
compositeAgePlot[which(compositeAgePlot$domain == "composite_ling"), "Domain"] <- "Linguistic"

compositeAgePlot$Domain <- as.factor(compositeAgePlot$Domain)

labs <- c("Younger Children", "Older Children")
names(labs) <- c("Younger", "Older")
```

```{r}
library(ggplot2)
library(ggpattern)

compositeAgePlot %>%
  ggplot(
    aes(
      x = Domain,
      y = composite_score,
      ymin = composite_score - se,
      ymax = composite_score + se,
      group = Group
    )
  ) +
  scale_fill_manual(values = c(cbPalette[1], cbPalette[8])) +
  geom_bar(stat = "identity",
           position = position_dodge(),
           width = 0.9) +
  facet_wrap("Age", labeller = (labeller(Age = labs))) +
  geom_col_pattern(
    aes(
      x = Domain,
      y = composite_score,
      pattern = Domain,
      fill = Group
    ),
    # color = Group
    # pattern = 'stripe',
    position = position_dodge(),
    pattern_density = 0.1,
    pattern_spacing = 0.025,
    pattern_key_scale_factor = 0.6,
    color = "#000000",
    pattern_colour = "black",
    pattern_fill = "black"
  ) +
  scale_pattern_manual(values = c(Linguistic = "stripe", Nonlinguistic = "none")) +
  # scale_fill_grey(start = 0.6, end = 1)+
  guides(pattern = guide_legend(override.aes = list(fill = "white")),
         fill = guide_legend(override.aes = list(pattern = "none"))) +
  geom_errorbar(width = .1, position = position_dodge(width = 0.9)) +
  labs(x = "Group",  # Change x-axis label
       y = "SL Composite Score (arbitrary unit)") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title.x = element_text(size = 16, face = "bold"),
    axis.title.y = element_text(size = 16, face = "bold"),
    axis.text = element_text(size = 14, face = "bold")
  ) +
  theme(
    legend.text = element_text(size = 15, face = "bold"),
    legend.title = element_text(size = 16, face = "bold"),
    legend.key = element_rect(color = "black")
  ) +
  theme(
    panel.background = element_rect(fill = "white"),
    # Set plot background to whit
    axis.line.x = element_line(colour = "black", size = 1),
    # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1),
    # Add line to y axis
    strip.text = element_text(size = 16, face = "bold"),
    # Change facet text
    strip.background = element_rect(fill = "white", size = 1),
    # Change facet color
    panel.spacing = unit(.05, "lines"),
    # Add panel border
    panel.border = element_rect(color = "black", fill = NA, size = 0.5),
    # Change panel border color and size
    legend.position = c(0.05, 0.9),
    legend.background = element_rect(fill = "#ffffff00")
    # strip.text = element_blank()
  ) +
  guides(pattern = FALSE) +
  geom_text(
    size = 12,
    color = "black",
    data = data.frame(
      Group = 0,
      composite_score = 0.55,
      Age = "Older",
      se = 0,
      Domain = 0
    ),
    aes(x = 1.5, y = 0.53, label = paste0("*"))
  ) +
  geom_segment(
    aes(
      x = 1,
      xend = 2,
      y = 0.53,
      yend = 0.53
    ),
    data = data.frame(
      Group = 0,
      composite_score = 0.55,
      Age = "Older",
      se = 0,
      Domain = 0
    )
  ) +
  geom_text(
    size = 12,
    color = "black",
    data = data.frame(
      Group = 0,
      composite_score = 0.55,
      Age = "Older",
      se = 0,
      Domain = 0
    ),
    aes(x = 1.5, y = 0.53, label = paste0("*"))
  ) +
  geom_segment(
    aes(
      x = 1,
      xend = 2,
      y = 0.53,
      yend = 0.53
    ),
    data = data.frame(
      Group = 0,
      composite_score = 0.55,
      Age = "Older",
      se = 0,
      Domain = 0
    )
  ) +
  geom_text(
    size = 12,
    color = "black",
    data = data.frame(
      Group = 0,
      composite_score = 0.55,
      Age = "Older",
      se = 0,
      Domain = 0
    ),
    aes(x = 1, y = 0.42, label = paste0("*"))
  ) +
  geom_segment(
    aes(
      x = 0.8,
      xend = 1.2,
      y = 0.41,
      yend = 0.41
    ),
    data = data.frame(
      Group = 0,
      composite_score = 0.55,
      Age = "Older",
      se = 0,
      Domain = 0
    )
  )

# ggsave("/Users/jojohu/Documents/Qlab/manuscript/composite_age.png",
#        bg="transparent",width = 30, height = 15, units = "cm")
```

# Analyze the effect of age and composite SL scores
```{r}
# Scale the data 
gjt_mulreg[, c("age_scaled", "composite_lsl", "composite_ssl","composite_tsl", "composite_vsl")] <-
  lapply(gjt_mulreg[, c("age_at_web_year", "composite_lsl", "composite_ssl","composite_tsl", "composite_vsl")], 
         function(x) {
           scale(x)
           })

gjt_mulregScaled <- gjt_mulreg

gjt_mulreg <- 
  melt(gjt_mulreg[,c("part_id", "group", "age_at_web_month", "age_at_web_year", "age_scaled", "a_prime",
                      "scq_web", "rbs_r", "ageSplit", "composite_nonling", "composite_ling")], 
       id.vars= c("part_id", "group", "age_at_web_month", "age_at_web_year", "age_scaled", "a_prime",
                               "scq_web", "rbs_r", "ageSplit"))


colnames(gjt_mulreg)[which(colnames(gjt_mulreg) == "variable")] <- "domain"
colnames(gjt_mulreg)[which(colnames(gjt_mulreg) == "value")] <- "composite_score"

gjt_mulreg$domain <- as.factor(gjt_mulreg$domain)
gjt_mulreg$group <- as.factor(gjt_mulreg$group)
# gjt_mulreg$modality <- as.factor(gjt_mulreg$modality)


m1_gjt <- 
  lmer(composite_score ~ domain*a_prime + age_at_web_month  + (1 | part_id), data= gjt_mulreg,
       contrasts = list(domain = c(-0.5, 0.5)),
          control=lmerControl(optimizer = "bobyqa",
                              check.nobs.vs.nRE="ignore", optCtrl=list(maxfun=2e5)))

summary(m1_gjt)

 m2_gjt <- lm(composite_score ~ domain*a_prime + age_at_web_month, data = gjt_mulreg,
             contrasts = list(domain = c(-0.5, 0.5)),)
summary(m2_gjt)


```

# Multiple Regression for Age and Composite Score
```{r}
gjt_mulreg$ageSplit <- as.factor(gjt_mulreg$ageSplit)
gjt_mulreg$age_scaled <- as.numeric(as.character((gjt_mulreg$age_scaled)))

nCount <-
gjt_mulreg %>%
  group_by(part_id) %>%
  dplyr::summarise(n = n())

which(nCount$n == 1)
# Every participant has a linguistic and a nonlinguistic composite score

# Central coding within the data still turns out to be dummy coding in the model; no use
# gjt_mulreg$domainN <-revalue(gjt_mulreg$domain, c("composite_nonling"=-0.5, "composite_ling"=0.5))
# gjt_mulreg$groupN <-revalue(gjt_mulreg$group, c("TD"=-0.5, "ASD"=0.5))
# gjt_mulreg$domainN <- as.numeric(gjt_mulreg$domainN)
# gjt_mulreg$groupN <- as.numeric(gjt_mulreg$groupN)

gjt_mulreg$ageSplit <- 
  factor(gjt_mulreg$ageSplit,levels = c("Young", "Old"))
gjt_mulreg <- gjt_mulreg[order(gjt_mulreg$ageSplit),]

gjt_mulreg$group <- 
  factor(gjt_mulreg$group,levels = c("ASD", "TD"))
gjt_mulreg <- gjt_mulreg[order(gjt_mulreg$group),]

gjt_mulreg$domain <- 
  factor(gjt_mulreg$domain,levels = c("composite_nonling", "composite_ling"))
gjt_mulreg <- gjt_mulreg[order(gjt_mulreg$domain),]


# Rescaling the composite score
gjt_mulreg$composite_score <- scale(gjt_mulreg$composite_score)

age_composite_m1 <- 
  lmer(composite_score ~ domain*group*age_scaled + (1|part_id),  
       data = gjt_mulreg,
      contrasts = list(domain = c(-0.5, 0.5),
                       group = c(-0.5, 0.5))
     )
summary(age_composite_m1)
```


```{r}
age_composite_m4 <- 
  lmer(composite_score ~ domain*group*ageSplit + (1|part_id),  
       data = gjt_mulreg,
      contrasts = list(domain = c(-0.5, 0.5),
                       group = c(-0.5, 0.5),
                       ageSplit = c(-0.5, 0.5))
     )
summary(age_composite_m4)


library(ez)
ezANOVA(data=gjt_mulreg, wid=part_id, dv=composite_score, between = c("group", "ageSplit"), within = c("domain"), type=3)


# Rescaling in each age group:
compositeOld <- compositeOldNScaled
compositeOld$composite_score <- scale(compositeOld$composite_score)

age_composite_m2 <- 
  lmer(composite_score ~ domain*group + (1|part_id),  
       data = compositeOld,
     contrasts = list(domain = c(-0.5, 0.5),
                  group = c(-0.5, 0.5))
     )

summary(age_composite_m2)

compositeOld %>%
  filter(domain == "composite_ling") %>%
  t.test(data = ., composite_score~group)

# Rescaling in each age group:
compositeYoung <- compositeYoungNScaled
compositeYoung$composite_score <- scale(compositeYoung$composite_score)

age_composite_m3 <- 
  lmer(composite_score ~ domain*group + (1|part_id),  
       data = compositeYoung,
     contrasts = list(domain = c(-0.5, 0.5),
                      group = c(-0.5, 0.5))
     )

summary(age_composite_m3)
# See plotting to see how to break down the domain*age_at_web_month*group interaction
```


# Extract Younger and Older groups age stat
```{r}
getCorrCI <- 
  function(df, group, age, col1, col2) {
      corTestDF <- cor.test(df[,c(col1)], df[,c(col2)])
      pearsonr <- corTestDF$estimate
      ci_upper <- corTestDF$conf.int[1]
      ci_lower <- corTestDF$conf.int[2]
      p_value <- corTestDF$p.value
      n <- corTestDF$parameter + 2
      
      tempDF <- data.frame(cbind(pearsonr, ci_upper, ci_lower, p_value, n))
      
      tempDF$Group <- group
      tempDF$Age <- age
      
      return(tempDF)
  }



compositeAgeTD$Age <- str_extract(compositeAgeTD$age_group, "Young|Old")
compositeAgeTDY <- compositeAgeTD[which(compositeAgeTD$Age == "Young"),]
compositeAgeTDO <- compositeAgeTD[which(compositeAgeTD$Age == "Old"),]

compositeAgeASD$Age <- str_extract(compositeAgeASD$age_group, "Young|Old")
compositeAgeASDY <- compositeAgeASD[which(compositeAgeASD$Age == "Young"),]
compositeAgeASDO <- compositeAgeASD[which(compositeAgeASD$Age == "Old"),]

compositeAge %>%
  group_by(group, ageSplit, gender) %>%
   dplyr::summarise(n = n())

oldYoungAge <- 
  compositeAge %>%
    group_by(group, ageSplit) %>%
    dplyr::summarise(mean_age_month = mean(age_at_web_month), mean_age_year = mean(age_at_web_year), sd = sd(age_at_web_year), n = n(),
                     mean_ling = mean(composite_ling), sd_ling = sd(composite_ling), 
                     mean_nonling = mean(composite_nonling), sd_nonling = sd(composite_nonling)) %>%
    mutate(se_ling =  sd_ling / sqrt(n), se_nonling =  sd_nonling / sqrt(n),
           ci_lower_ling = mean_ling - qt(1 - (0.05 / 2), n - 1) * se_ling,
           ci_upper_ling = mean_ling + qt(1 - (0.05 / 2), n - 1) * se_ling,
           ci_lower_nonling = mean_nonling - qt(1 - (0.05 / 2), n - 1) * se_nonling,
           ci_upper_nonling = mean_nonling + qt(1 - (0.05 / 2), n - 1) * se_nonling)

oldYoungAge[, -c(1:2)] <- round(oldYoungAge[, -c(1:2)], 2)

 # compositeAge %>%
 #    group_by(group, ageSplit) %>%
 #    dplyr::summarise(mean_composite_ssl = mean(composite_ssl, na.rm = T))

print(oldYoungAge)

age_wide <- cast(compositeAge, group~ageSplit, length)
print(chisq.test(age_wide))

t.test(compositeAgeASDY$age_at_web_month, compositeAgeTDY$age_at_web_month)
t.test(compositeAgeASDO$age_at_web_month, compositeAgeTDO$age_at_web_month)
```


# Post-hoc t-test for age groups
```{r}
t.test(compositeAgeTDO$composite_ling, compositeAgeASDO$composite_ling, alternative = "greater")
t.test(compositeAgeTDY$composite_ling, compositeAgeASDY$composite_ling, alternative = "greater")
```



# Extract Younger and Older groups age correlations
```{r}
ageCorrTDY <- getCorrCI(compositeAgeTDY, "TD", "Young", "composite_ling", "age_at_web_month")
ageCorrTDO <- getCorrCI(compositeAgeTDO, "TD", "Old", "composite_ling", "age_at_web_month")
ageCorrASDY <- getCorrCI(compositeAgeASDY, "ASD", "Young", "composite_ling", "age_at_web_month")
ageCorrASDO <- getCorrCI(compositeAgeASDO, "ASD", "Old", "composite_ling", "age_at_web_month")

ageCorrPlot <- rbind(ageCorrTDY, ageCorrTDO, ageCorrASDY, ageCorrASDO)
# Age correlation with composite ling score in young vs. old groups
print(ageCorrPlot)

ageCorrTDY <- getCorrCI(compositeAgeTDY, "TD", "Young", "composite_nonling", "age_at_web_month")
ageCorrTDO <- getCorrCI(compositeAgeTDO, "TD", "Old", "composite_nonling", "age_at_web_month")
ageCorrASDY <- getCorrCI(compositeAgeASDY, "ASD", "Young", "composite_nonling", "age_at_web_month")
ageCorrASDO <- getCorrCI(compositeAgeASDO, "ASD", "Old", "composite_nonling", "age_at_web_month")

ageCorrPlot <- rbind(ageCorrTDY, ageCorrTDO, ageCorrASDY, ageCorrASDO)
# Age correlation with composite ling score in young vs. old groups
print(ageCorrPlot)
```



# Compare Younger and Older groups composite SL scores
```{r}
t.test(compositeAgeASDY$composite_ling, compositeAgeASDO$composite_ling)

```

# Extract Younger and Older groups task correlations
```{r}
lingCorrTDY <- getCorrCI(compositeAgeTDY, "TD", "Young", "composite_ssl", "composite_lsl")
lingCorrTDO <- getCorrCI(compositeAgeTDO, "TD", "Old", "composite_ssl", "composite_lsl")
lingCorrASDY <- getCorrCI(compositeAgeASDY, "ASD", "Young", "composite_ssl", "composite_lsl")
lingCorrASDO <- getCorrCI(compositeAgeASDO, "ASD", "Old", "composite_ssl", "composite_lsl")

lingCorr <- rbind(lingCorrTDY, lingCorrTDO, lingCorrASDY, lingCorrASDO)

print(lingCorr)
```

# Simple correlation comparison on composite LSL and SSL in ASD vs. TD
```{r}
library(cocor)
cocor.indep.groups(r1.jk=lingCorr[which(lingCorr$Group == "TD" & lingCorr$Age == "Young"), "pearsonr"], 
                   r2.hm=lingCorr[which(lingCorr$Group == "ASD" & lingCorr$Age == "Young"), "pearsonr"], 
                   n1=lingCorr[which(lingCorr$Group == "TD" & lingCorr$Age == "Young"), "n"], 
                   n2=lingCorr[which(lingCorr$Group == "ASD" & lingCorr$Age == "Young"), "n"], 
                   alternative="two.sided", alpha=0.05, conf.level=0.95, null.value=0)

cocor.indep.groups(r1.jk=lingCorr[which(lingCorr$Group == "TD" & lingCorr$Age == "Old"), "pearsonr"], 
                   r2.hm=lingCorr[which(lingCorr$Group == "ASD" & lingCorr$Age == "Old"), "pearsonr"], 
                   n1=lingCorr[which(lingCorr$Group == "TD" & lingCorr$Age == "Old"), "n"], 
                   n2=lingCorr[which(lingCorr$Group == "ASD" & lingCorr$Age == "Old"), "n"], 
                   alternative="two.sided", alpha=0.05, conf.level=0.95, null.value=0)
```



# Plot Composite Score Correlation in each group
```{r}
library(ggpattern)

labs <- c("Younger Children", "Older Children")
names(labs) <- c("Young", "Old")

lingCorr %>%
  ggplot(aes(
    x = Group,
    y = pearsonr,
    ymin = ci_lower,
    ymax = ci_upper,
    fill = Group
  )) +
  geom_bar(stat = "identity",
           position = position_dodge(),
           width = 0.9) +
  facet_wrap("Age", labeller = (labeller(Age = labs))) +
  geom_col_pattern(color = "black",
                   pattern = "null") +
  scale_fill_manual(values = c(cbPalette[1], cbPalette[8])) +
  geom_errorbar(width = .1, position = position_dodge(width = 0.9)) +
  labs(title = "Relationship between Letter and Syllable SL Composite Scores",
       x = "Group",  # Change x-axis label
       y = "Pearson's Correlation Estimate") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title.x = element_text(size = 14, face = "bold"),
    axis.title.y = element_text(size = 14, face = "bold"),
    axis.text = element_text(size = 12, face = "bold")
  ) +
  theme(
    legend.text = element_text(size = 14, face = "bold"),
    legend.title = element_text(size = 15, face = "bold")
  ) +
  theme(
    panel.background = element_rect(fill = "white"),
    # Set plot background to white
    legend.key  = element_rect(fill = "white"),
    # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),
    # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1),
    # Add line to y axis
    strip.text = element_text(size = 14, face = "bold"),
    # Change facet text
    strip.background = element_rect(fill = "white", size = 1),
    # Change facet color
    panel.spacing = unit(.05, "lines"),
    # Add panel border
    panel.border = element_rect(color = "black", fill = NA, size = 0.5),
    # Change panel border color and size
    legend.position = c(0.07, 0.9),
    legend.background = element_rect(fill = "#ffffff00")
    # strip.text = element_blank()
  ) +
  geom_text(
    size = 12,
    color = "black",
    data = data.frame(
      Group = "TD",
      pearsonr = 0.55,
      Age = "Old",
      ci_upper = 0,
      ci_lower = 0,
      Domain = 0
    ),
    aes(x = 1.5, y = 0.85, label = paste0("*"))
  ) +
  geom_segment(
    aes(
      x = 1,
      xend = 2,
      y = 0.85,
      yend = 0.85
    ),
    data = data.frame(
      Group = "TD",
      pearsonr = 0.55,
      Age = "Old",
      ci_upper = 0,
      ci_lower = 0,
      Domain = 0
    )
  )

# ggsave("/Users/jojohu/Documents/Qlab/manuscript/composite_lsl_ssl.png",
#        bg="transparent",width = 20, height = 15, units = "cm")
```

# Compare composite LSL and composite SSL relationship based on Age
```{r}
# Interaction term (ageSplit1:composite_ssl:group1) has the same result when tested with not re-scaled composite score:  
# compositeGroupAge <- merge(compositeGroup, gjt_mulregScaled[,c("part_id", "ageSplit")])
gjt_mulregScaled$ageSplit <- 
  factor(gjt_mulregScaled$ageSplit,levels = c("Young", "Old"))

gjt_mulregScaled$group <- 
  factor(gjt_mulregScaled$group,levels = c("ASD", "TD"))


compositeCorr_m1 <- lm(composite_lsl ~ ageSplit*composite_ssl*group, data = gjt_mulregScaled,
                      contrasts = list( 
                      group = c(-0.5, 0.5),
                      ageSplit = c(-0.5, 0.5)))

summary(compositeCorr_m1)


# When age was fit as a continous variable:
compositeCorr_m2 <- lm(composite_lsl ~ age_scaled*composite_ssl*group, data = gjt_mulregScaled,
                      contrasts = list( 
                      group = c(-0.5, 0.5)
                      ))

summary(compositeCorr_m2)

gjt_mulregScaledY <- gjt_mulregScaled[which(gjt_mulregScaled$ageSplit == "Young"),]
gjt_mulregScaledO <- gjt_mulregScaled[which(gjt_mulregScaled$ageSplit == "Old"),]

# Fitting the not re-scaled composite SL scores also did not change the results:
compositeCorr_m4 <- lm(composite_lsl ~ composite_ssl*group, data = gjt_mulregScaledO,
                      contrasts = list( 
                      group = c(-0.5, 0.5)))

summary(compositeCorr_m4)


compositeCorr_m3 <- lm(composite_lsl ~ composite_ssl*group, data = gjt_mulregScaledY,
                      contrasts = list( 
                      group = c(-0.5, 0.5)))

summary(compositeCorr_m3)
# 
# compositeCorr_m5 <- lm(composite_tsl ~ ageSplit*composite_vsl*group, data = gjt_mulregScaled,
#                       contrasts = list(
#                       group = c(-0.5, 0.5),
#                       ageSplit = c(-0.5, 0.5)))
# 
# summary(compositeCorr_m5)
# 
# compositeCorr_m6 <- lm(composite_tsl ~ age_scaled*composite_vsl*group, data = gjt_mulregScaled,
#                       contrasts = list(
#                       group = c(-0.5, 0.5)
#                      ))
# 
# summary(compositeCorr_m6)
```


# Individual difference: Correlations between tasks, age, measures
```{r}
# Correlation matrix between ASD Lingusitic rt slope, composite and SCQ, RBS-R, Age
library("RcmdrMisc")

compositeCorr <- function(group) {
  rcorr.adjust(as.matrix(compositeAge[which(compositeAge$group == group),
                                       c("composite_ling",
                                         "composite_nonling",
                                         "a_prime",
                                     "rbs_r",
                                     "scq_web",
                                     "lsl_slope",
                                     "ssl_slope",
                                     "lsl_acc",
                                     "ssl_acc",
                                      "tsl_slope",
                                     "vsl_slope",
                                     "tsl_acc",
                                     "vsl_acc",
                                     "composite_lsl",
                                     "composite_ssl",
                                     "composite_tsl",
                                     "composite_vsl",
                                     "age_at_web_month"
                                     )]),
      use=c("pairwise.complete.obs"))
}

asd_corr_posthoc <- compositeCorr("ASD")
td_corr_posthoc <- compositeCorr("TD")

flattenCorrMatrix <- function(cormat, pmat, nmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  = (cormat)[ut],
    p = pmat[ut],
    n = nmat[ut]
  )
}

asd_corr_posthoc <-
  flattenCorrMatrix(data.frame(asd_corr_posthoc$R[1]),
                  data.frame(asd_corr_posthoc$R[3]),
                  data.frame(asd_corr_posthoc$R[2]))

td_corr_posthoc <-
  flattenCorrMatrix(data.frame(td_corr_posthoc$R[1]),
                  data.frame(td_corr_posthoc$R[3]),
                  data.frame(td_corr_posthoc$R[2]))


                  
aprime_corr <- 
  asd_corr_posthoc[which(asd_corr_posthoc$row == "a_prime" | asd_corr_posthoc$column == "a_prime"),]

age_corr <- 
  asd_corr_posthoc[which(asd_corr_posthoc$row == "age_at_web_month" | asd_corr_posthoc$column == "age_at_web_month"),]

td_age_corr <- 
  td_corr_posthoc[which(td_corr_posthoc$row == "age_at_web_month" | td_corr_posthoc$column == "age_at_web_month"),]

# write.csv(asd_corr_posthoc, "asd_corr_posthoc_uncorrected.csv")
# write.csv(aprime_corr, "aprime_corr.csv")
# write.csv(age_corr, "age_corr.csv")
# write.csv(td_corr_posthoc, "td_corr_posthoc_uncorrected.csv")
```




# Prep Plotting
```{r}
#allData <- allData[,-c(1)]
bar_all <-  allData[,c(which(str_detect(colnames(allData), 
                                          "part_id|group|ssl|lsl|vsl|tsl")))]
```


# Accuracy Line Plot (no outliers)
# SL Accuracy Descriptive Stat
```{r}
library(plyr)
library(dplyr)
library(ggplot2)
library(data.table)

library("pastecs")

stat_desc <- 
function(df,group,task) {
  stat.desc(df[which(df$group == group & df$variable == task),])
}

bar_all_long <- melt(bar_all, id.vars=c("part_id", "group"))

bar_acc <-
  bar_all_long[which(str_detect(
    bar_all_long$variable, "\\S{1}(?=sl_acc)")),]

library("data.table")

bar_acc$variable <-
revalue(bar_acc$variable, c("lsl_acc"="Letter",
                                     "vsl_acc"="Image",
                                     "tsl_acc"="Tone",
                                     "ssl_acc"="Syllable"))

bar_acc$variable <- 
  factor(bar_acc$variable,levels = c("Image", 
                                              "Letter", 
                                              "Tone", 
                                              "Syllable"))

bar_acc <-
  bar_acc[order(bar_acc$variable), ]

bar_acc$value <- 
  as.numeric(as.character(bar_acc$value))


td_tone <- stat_desc(bar_acc, "TD", "Tone")
td_syllable <- stat_desc(bar_acc, "TD", "Syllable")
td_image <- stat_desc(bar_acc, "TD", "Image")
td_letter <- stat_desc(bar_acc, "TD", "Letter")
asd_tone <- stat_desc(bar_acc, "ASD", "Tone")
asd_syllable <- stat_desc(bar_acc, "ASD", "Syllable")
asd_image <- stat_desc(bar_acc, "ASD", "Image")
asd_letter <- stat_desc(bar_acc, "ASD", "Letter") 

extract_line_graph_stat <- function (x, group, task) {
y <- x[c("nbr.val","mean", "SE.mean", "std.dev", "CI.mean"),"value"]
dim(y) <- c(5, 1)
y <- t(y)
colnames(y) <- c("n", "mean", "std_error", "sd", "ci")
y <- data.frame(y)
y$ci_upper <- y$mean + y$ci 
y$ci_lower <- y$mean - y$ci 
y$group <- group
y$task <- task

return(y)
}

td_tone_stat <- extract_line_graph_stat(td_tone, "TD", "Tone")
td_syllable_stat <- extract_line_graph_stat(td_syllable, "TD", "Syllable")
td_image_stat <- extract_line_graph_stat(td_image, "TD", "Image")
td_letter_stat <- extract_line_graph_stat(td_letter, "TD", "Letter")

asd_tone_stat <- extract_line_graph_stat(asd_tone, "ASD", "Tone")
asd_syllable_stat <- extract_line_graph_stat(asd_syllable, "ASD", "Syllable")
asd_image_stat <- extract_line_graph_stat(asd_image, "ASD", "Image")
asd_letter_stat <- extract_line_graph_stat(asd_letter, "ASD", "Letter")

clean_stat <- function(df) {

  df <- rbind(td_tone_stat, td_syllable_stat, td_image_stat, td_letter_stat, 
                    asd_tone_stat, asd_syllable_stat, asd_image_stat, asd_letter_stat)
  
  colnames(df)[colnames(df) == "group"] <- "Group"
  
  df$task <- 
    factor(df$task,levels = c("Image", 
                                                "Letter", 
                                                "Tone", 
                                                "Syllable"))
  
  df <-
    df[order(df$task), ]
  
  
  library(reshape)
  acc_stat_descrip <- df[,c("Group", "task", "mean", "sd", "ci_lower", "ci_upper")]
  acc_stat_mean <- cast(acc_stat_descrip, task~Group, value = "mean")
  acc_stat_sd <- cast(acc_stat_descrip, task~Group, value = "sd")
  acc_stat_ci_lower <- cast(acc_stat_descrip, task~Group, value = "ci_lower")
  acc_stat_ci_upper <- cast(acc_stat_descrip, task~Group, value = "ci_upper")
  acc_stat_across_sd <- cbind(acc_stat_mean, acc_stat_sd, acc_stat_ci_lower, acc_stat_ci_upper)
  acc_stat_across_sd[,c(2:3, 5:6, 8:9, 11:12)] <- round(acc_stat_across_sd[,c(2:3, 5:6, 8:9, 11:12)], 4)

return(acc_stat_across_sd)
}

acc_stat_across_sd <- clean_stat(acc_stat)

# write.csv(acc_stat_across_sd, "acc_stat.csv")


```


# SL Accuracy within subject error 
```{r, include = F}
summarySEwithin <- function(data=NULL, measurevar, betweenvars=NULL, withinvars=NULL,
                            idvar=NULL, na.rm=FALSE, conf.interval=.95, .drop=TRUE) {

  # Ensure that the betweenvars and withinvars are factors
  factorvars <- vapply(data[, c(betweenvars, withinvars), drop=FALSE],
    FUN=is.factor, FUN.VALUE=logical(1))

  if (!all(factorvars)) {
    nonfactorvars <- names(factorvars)[!factorvars]
    message("Automatically converting the following non-factors to factors: ",
            paste(nonfactorvars, collapse = ", "))
    data[nonfactorvars] <- lapply(data[nonfactorvars], factor)
  }

  # Get the means from the un-normed data
  datac <- summarySE(data, measurevar, groupvars=c(betweenvars, withinvars),
                     na.rm=na.rm, conf.interval=conf.interval, .drop=.drop)

  # Drop all the unused columns (these will be calculated with normed data)
  datac$sd <- NULL
  datac$se <- NULL
  datac$ci <- NULL

  # Norm each subject's data
  ndata <- normDataWithin(data, idvar, measurevar, betweenvars, na.rm, .drop=.drop)

  # This is the name of the new column
  measurevar_n <- paste(measurevar, "_norm", sep="")

  # Collapse the normed data - now we can treat between and within vars the same
  ndatac <- summarySE(ndata, measurevar_n, groupvars=c(betweenvars, withinvars),
                      na.rm=na.rm, conf.interval=conf.interval, .drop=.drop)

  # Apply correction from Morey (2008) to the standard error and confidence interval
  #  Get the product of the number of conditions of within-S variables
  nWithinGroups    <- prod(vapply(ndatac[,withinvars, drop=FALSE], FUN=nlevels,
                           FUN.VALUE=numeric(1)))
  correctionFactor <- sqrt( nWithinGroups / (nWithinGroups-1) )

  # Apply the correction factor
  ndatac$sd <- ndatac$sd * correctionFactor
  ndatac$se <- ndatac$se * correctionFactor
  ndatac$ci <- ndatac$ci * correctionFactor

  # Combine the un-normed means with the normed results
  merge(datac, ndatac)
}

summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
    library(plyr)

    # New version of length which can handle NA's: if na.rm==T, don't count them
    length2 <- function (x, na.rm=FALSE) {
        if (na.rm) sum(!is.na(x))
        else       length(x)
    }

    # This does the summary. For each group's data frame, return a vector with
    # N, mean, and sd
    datac <- ddply(data, groupvars, .drop=.drop,
      .fun = function(xx, col) {
        c(N    = length2(xx[[col]], na.rm=na.rm),
          mean = mean   (xx[[col]], na.rm=na.rm),
          sd   = sd     (xx[[col]], na.rm=na.rm)
        )
      },
      measurevar
    )

    # Rename the "mean" column    
    datac <- rename(datac, c("mean" = measurevar))

    datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean

    # Confidence interval multiplier for standard error
    # Calculate t-statistic for confidence interval: 
    # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
    ciMult <- qt(conf.interval/2 + .5, datac$N-1)
    datac$ci <- datac$se * ciMult

    return(datac)
}

normDataWithin <- function(data=NULL, idvar, measurevar, betweenvars=NULL,
                           na.rm=FALSE, .drop=TRUE) {
    library(plyr)

    # Measure var on left, idvar + between vars on right of formula.
    data.subjMean <- ddply(data, c(idvar, betweenvars), .drop=.drop,
     .fun = function(xx, col, na.rm) {
        c(subjMean = mean(xx[,col], na.rm=na.rm))
      },
      measurevar,
      na.rm
    )

    # Put the subject means with original data
    data <- merge(data, data.subjMean)

    # Get the normalized data in a new column
    measureNormedVar <- paste(measurevar, "_norm", sep="")
    data[,measureNormedVar] <- data[,measurevar] - data[,"subjMean"] +
                               mean(data[,measurevar], na.rm=na.rm)

    # Remove this subject mean column
    data$subjMean <- NULL

    return(data)
}
```

```{r}
detach(package:plyr)

acc_within_stat <- summarySEwithin(bar_acc, measurevar="value", betweenvars = "group",
                                   withinvars="variable", idvar="part_id", na.rm=T, conf.interval=.95)


colnames(acc_within_stat)[colnames(acc_within_stat) == "group"] <- "Group"



acc_within_stat$variable <-
  factor(acc_within_stat$variable,
         levels = c("Letter",
                    "Syllable",
                    "Image",
                    "Tone"))

```

```{r}
cbPalette <- c('#a6cee3','#1f78b4','#b2df8a', '#66c2a5','#fc8d62','#8da0cb', '#1b9e77','#d95f02','#7570b3')
library(TeachingDemos)
cbPaletteGrey <- col2grey(cbPalette)
pd <- position_dodge(width = 0.2)

acc_within_stat %>%
  ggplot(aes(x = variable, y = value, group = Group)) +
  geom_line(aes(linetype = Group, color = Group),
            position = pd,
            size = 1.8) +
  geom_errorbar(aes(ymin = value - se, ymax = value + se),
                width = .1,
                position = pd) +
  geom_point(
    aes(color = Group),
    size = 4,
    position = pd,
    show.legend = FALSE
  ) +
  geom_point(size = 3,
             color = "white",
             position = pd) +
  labs(title = "SL Accuracy against Chance-level",
       x = "SL Task",  # Change x-axis label
       y = "Mean Accuracy (%)") +
  scale_color_manual(values = c(cbPalette[1], cbPalette[8])) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title.x = element_text(size = 14, face = "bold"),
    axis.title.y = element_text(size = 14, face = "bold"),
    axis.text = element_text(size = 12, face = "bold")
  ) +
  theme(
    legend.text = element_text(size = 14, face = "bold"),
    legend.title = element_text(size = 15, face = "bold")
  ) +
  theme(
    panel.background = element_rect(fill = "white"),
    # Set plot background to white
    legend.key  = element_rect(fill = "white"),
    # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),
    # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) +
  geom_hline(yintercept = 0.5, color = "grey") +
  geom_text(aes(
    x = 1,
    y = 0.505,
    label = paste0("chance", "-level")
  ), size = 5) +
  geom_text(aes(
    x = 0.95,
    y = 0.7,
    label = paste0("***")
  ),
  size = 7,
  color = cbPalette[1]) +
  geom_text(aes(x = 1.95, y = 0.7, label = paste0("**")),
            size = 7,
            color = cbPalette[1]) +
  geom_text(aes(
    x = 2.95,
    y = 0.7,
    label = paste0("***")
  ),
  size = 7,
  color = cbPalette[1]) +
  geom_text(aes(x = 3.95, y = 0.7, label = paste0("**")),
            size = 7,
            color = cbPalette[1]) +
  # geom_text(aes(x= 4.05, y = 0.7, label = paste0("")), size=7, color="#00BFC4") +
  geom_text(aes(x = 3.05, y = 0.51, label = paste0("*")),
            size = 7,
            color = cbPalette[8]) +
  # geom_text(aes(x= 1.95, y = 0.51, label = paste0("")), size=7, color="#F8766d") +
  geom_text(aes(x = 4.05, y = 0.51, label = paste0("**")),
            size = 7,
            color = cbPalette[8]) +
  geom_text(aes(x = 2.05, y = 0.494, label = paste0("*")),
            size = 7,
            color = cbPalette[8])


# ggsave("/Users/jojohu/Documents/Qlab/manuscript/behavioral_acc_across_group.png",
#        bg="transparent",width = 15, height = 15, units = "cm")
```



# Accuracy Bar Plot in Linguistics Task
```{r, include = F}

pd <- position_dodge(width = 0.2)

library(ggbeeswarm)
acc_bar <- bar_acc 
colnames(acc_bar)[colnames(acc_bar) == "group"] <- "Group"
acc_bar[which(acc_bar$variable == "Letter" | acc_bar$variable == "Syllable"),] %>%
  ggplot(aes(x = variable, y = value)) +
  geom_bar(
    aes(fill = Group),
    position = position_dodge(),
    width = 0.9,
    stat = "summary",
    fun.y = "mean",
  ) +
 labs(title = "Behavioral Accuracy in Linguistic SL",
         x = "SL Task",  # Change x-axis label
         y = "Mean Accuracy") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold"),
        legend.title=element_text(size=15, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),         # Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) + 
  geom_beeswarm(
    aes(fill = Group),
    dodge.width = 1,
    cex = 2.5,
    size = 0.8,
    show.legend = FALSE,
    shape=1
  ) + 
  geom_text(aes(x= 1, y = 1.04, label = paste0("**")), size=7) +
  geom_segment(aes(x=0.75,xend=1.25, y = 1.02, yend = 1.02)) +
  geom_segment(aes(x=0.75,xend=0.75, yend = 1, y = 1.02)) +
  geom_segment(aes(x=1.25,xend=1.25, yend = 1, y = 1.02)) +
  geom_text(aes(x= 2, y = 1.06, label = paste0("")), size=7) +
  geom_segment(aes(x=1.75,xend=2.25, y = 1.02, yend = 1.02)) +
  geom_segment(aes(x=1.75,xend=1.75, yend = 1, y = 1.02)) +
  geom_segment(aes(x=2.25,xend=2.25, yend = 1, y = 1.02))

```



```{r}
library(ggbeeswarm)
acc_bar <- bar_acc 
colnames(acc_bar)[colnames(acc_bar) == "group"] <- "Group"
acc_bar %>%
  ggplot(aes(x = variable, y = value)) +
  geom_bar(
    aes(fill = Group),
    position = position_dodge(),
    width = 0.9,
    stat = "summary",
    fun.y = "mean",
  ) +
 labs(title = "SL Accuracy Between Group Comparison",
         x = "SL Task",  # Change x-axis label
         y = "Mean Accuracy") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold"),
        legend.title=element_text(size=15, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),         # Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) + 
  geom_beeswarm(
    aes(fill = Group),
    dodge.width = 1,
    cex = 2.5,
    size = 0.8,
    show.legend = FALSE,
    shape = 1
  ) + 
  # geom_text(aes(x= 1, y = 1.04, label = paste0("")), size=7) +
  # geom_segment(aes(x=0.75,xend=1.25, y = 1.02, yend = 1.02)) +
  # geom_segment(aes(x=0.75,xend=0.75, yend = 1, y = 1.02)) +
  # geom_segment(aes(x=1.25,xend=1.25, yend = 1, y = 1.02)) +
  # geom_text(aes(x= 2, y = 1.06, label = paste0("*")), size=7) +
  geom_segment(aes(x=1.75,xend=2.25, y = 1.02, yend = 1.02)) +
  geom_segment(aes(x=1.75,xend=1.75, yend = 1, y = 1.02)) +
  geom_segment(aes(x=2.25,xend=2.25, yend = 1, y = 1.02)) +
   geom_segment(aes(x=0.75,xend=1.25, y = 1.02, yend = 1.02)) +
  geom_segment(aes(x=0.75,xend=0.75, yend = 1, y = 1.02)) +
  geom_segment(aes(x=1.25,xend=1.25, yend = 1, y = 1.02)) +
  geom_text(aes(x= 1, y = 1.06, label = paste0("")), size=7) +
  geom_text(aes(x= 2, y = 1.06, label = paste0("")), size=7) +
  # geom_segment(aes(x=2.75,xend=3.25, y = 1.02, yend = 1.02)) +
  # geom_segment(aes(x=2.75,xend=2.75, yend = 1, y = 1.02)) +
  # geom_segment(aes(x=2.25,xend=2.25, yend = 1, y = 1.02)) +
   geom_text(aes(x= 4, y = 1.06, label = paste0("*")), size=7) +
  geom_segment(aes(x=3.75,xend=4.25, y = 1.02, yend = 1.02)) +
  geom_segment(aes(x=3.75,xend=3.75, yend = 1, y = 1.02)) +
  geom_segment(aes(x=4.25,xend=4.25, yend = 1, y = 1.02)) 

# ggsave("srcd_figure/behavioral_acc_ling_bar.png",
       # bg="transparent",
       # # ggsave = 15, height = 15, units = "cm")
```



# Mean RT Line Plot (no outliers)
```{r}
library(dplyr)
library(ggplot2)

bar_all_long <- melt(bar_all, id.vars=c("part_id", "group"))


bar_rt <-
  bar_all_long[which(
    str_detect(bar_all_long$variable, "\\S{3}(_rt)")),]

bar_rt$variable <-
revalue(bar_rt$variable, c("lsl_rt"="Letter",
                                     "vsl_rt"="Image",
                                     "tsl_rt"="Tone",
                                     "ssl_rt"="Syllable"))

bar_rt$variable <- 
  factor(bar_rt$variable,levels = c("Image", 
                                                  "Letter", 
                                                  "Tone", 
                                                  "Syllable"))

bar_rt <-
  bar_rt[order(bar_rt$variable), ]

bar_rt$value <- 
  as.numeric(as.character(bar_rt$value))


library("pastecs")
stat_desc <- 
function(df,group,task) {
  stat.desc(df[which(df$group == group & df$variable == task),])
}

td_tone <- stat_desc(bar_rt, "TD", "Tone")
td_syllable <- stat_desc(bar_rt, "TD", "Syllable")
td_image <- stat_desc(bar_rt, "TD", "Image")
td_letter <- stat_desc(bar_rt, "TD", "Letter")

asd_tone <- stat_desc(bar_rt, "ASD", "Tone")
asd_syllable <- stat_desc(bar_rt, "ASD", "Syllable")
asd_image <- stat_desc(bar_rt, "ASD", "Image")
asd_letter <- stat_desc(bar_rt, "ASD", "Letter")
 
td_tone_stat <- extract_line_graph_stat(td_tone, "TD", "Tone")
td_syllable_stat <- extract_line_graph_stat(td_syllable, "TD", "Syllable")
td_image_stat <- extract_line_graph_stat(td_image, "TD", "Image")
td_letter_stat <- extract_line_graph_stat(td_letter, "TD", "Letter")

asd_tone_stat <- extract_line_graph_stat(asd_tone, "ASD", "Tone")
asd_syllable_stat <- extract_line_graph_stat(asd_syllable, "ASD", "Syllable")
asd_image_stat <- extract_line_graph_stat(asd_image, "ASD", "Image")
asd_letter_stat <- extract_line_graph_stat(asd_letter, "ASD", "Letter")



rt_stat <- rbind(td_tone_stat, td_syllable_stat, td_image_stat, td_letter_stat,
                      asd_tone_stat, asd_syllable_stat, asd_image_stat, asd_letter_stat)


colnames(rt_stat)[colnames(rt_stat) == "group"] <- "Group"

rt_stat$task <- 
  factor(rt_stat$task,levels = c("Image", 
                                              "Letter", 
                                              "Tone", 
                                              "Syllable"))

rt_stat <-
  rt_stat[order(rt_stat$task), ]


pd <- position_dodge(width = 0.2)

rt_stat %>%
  ggplot(aes(x = task, y = mean, group = Group)) +
  geom_line(aes(linetype = Group, color = Group), position = pd, size = 1.8) +
   geom_errorbar(aes(ymin = mean - std_error, ymax = mean + std_error), width = .1, position = pd) +
     geom_point(aes(color = Group), size = 4, position = pd,show.legend = FALSE) + 
          geom_point(size = 3, color = "white", position = pd) +
      labs(title = "Behavioral Reaction Time across Groups",
         x = "SL Task",  # Change x-axis label
         y = "Mean Reaction Time (ms)") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold"),
        legend.title=element_text(size=15, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),         # Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  )

# ggsave("behavioral_rt_across_group.png",
       # width = 15, height = 15, units = "cm")

# write.csv(blast_spoli_data_wide, "blast_spoli_data_all_measures.csv")
# write.csv(allData, "blast_spoli_data_all_measures_no_outlier.csv")
```



# RT Slope Line Plot (no outliers)
```{r, include = F}
library(dplyr)
library(ggplot2)

bar_all_long <- melt(bar_all, id.vars=c("part_id", "group"))


bar_slope <-
  bar_all_long[which(
    str_detect(bar_all_long$variable, "\\S{3}(?=_slope)")),]


bar_slope$variable <-
revalue(bar_slope$variable, c("lsl_slope"="Letter",
                                     "vsl_slope"="Image",
                                     "tsl_slope"="Tone",
                                     "ssl_slope"="Syllable"))

bar_slope$variable <- 
  factor(bar_slope$variable,levels = c("Image", 
                                                  "Letter", 
                                                  "Tone", 
                                                  "Syllable"))

bar_slope <-
  bar_slope[order(bar_slope$variable), ]

bar_slope$value <- 
  as.numeric(as.character(bar_slope$value))


library("pastecs")
stat_desc <- 
function(df,group,task) {
  stat.desc(df[which(df$group == group & df$variable == task),])
}

td_tone <- stat_desc(bar_slope, "TD", "Tone")
td_syllable <- stat_desc(bar_slope, "TD", "Syllable")
td_image <- stat_desc(bar_slope, "TD", "Image")
td_letter <- stat_desc(bar_slope, "TD", "Letter")

asd_tone <- stat_desc(bar_slope, "ASD", "Tone")
asd_syllable <- stat_desc(bar_slope, "ASD", "Syllable")
asd_image <- stat_desc(bar_slope, "ASD", "Image")
asd_letter <- stat_desc(bar_slope, "ASD", "Letter")

td_tone_stat <- extract_line_graph_stat(td_tone, "TD", "Tone")
td_syllable_stat <- extract_line_graph_stat(td_syllable, "TD", "Syllable")
td_image_stat <- extract_line_graph_stat(td_image, "TD", "Image")
td_letter_stat <- extract_line_graph_stat(td_letter, "TD", "Letter")

asd_tone_stat <- extract_line_graph_stat(asd_tone, "ASD", "Tone")
asd_syllable_stat <- extract_line_graph_stat(asd_syllable, "ASD", "Syllable")
asd_image_stat <- extract_line_graph_stat(asd_image, "ASD", "Image")
asd_letter_stat <- extract_line_graph_stat(asd_letter, "ASD", "Letter")

slope_stat <- clean_stat(slope_stat)

colnames(slope_stat)[colnames(slope_stat) == "group"] <- "Group"


# write.csv(slope_stat, "slope_stat.csv")

```

```{r, include = F}
detach(package:plyr)
slope_within_stat <- summarySEwithin(bar_slope, measurevar="value", betweenvars = "group", withinvars="variable",
                        idvar="part_id", na.rm=T, conf.interval=.95)

colnames(slope_within_stat)[colnames(slope_within_stat) == "group"] <- "Group"
colnames(slope_within_stat)[colnames(slope_within_stat) == "value"] <- "mean"
colnames(slope_within_stat)[colnames(slope_within_stat) == "se"] <- "std_error"
colnames(slope_within_stat)[colnames(slope_within_stat) == "variable"] <- "task"

slope_within_stat$task <-
  factor(slope_within_stat$task,
         levels = c("Letter",
                    "Syllable",
                    "Image",
                    "Tone"))

slope_within_stat$Group <-
  factor(slope_within_stat$Group, levels = c("TD",
                                             "ASD"))
```

# Median Split of Slope
```{r}
plot_medianSplit <- function(df, task) {
ssl_slope <- df[which(df$task == task & df$group == "TD"),]
ssl_slope <- ssl_slope[order(ssl_slope$age_at_web_year),]
ssl_slope[1:round(length(ssl_slope$age_at_web_year)/2),"Group"] <- "Younger TD" 
median <- round((length(ssl_slope$age_at_web_year)/2))+1
ssl_slope[median:length(ssl_slope$age_at_web_year),"Group"] <- "Older TD"

ssl_slopeASD <- df[which(df$task == task & df$group == "ASD"),]
ssl_slopeASD$Group <- "ASD"

# ssl_slopeASD <- ssl_slopeASD[order(ssl_slopeASD$age_at_web_year),]
# ssl_slopeASD[1:round(length(ssl_slopeASD$age_at_web_year)/2),"Group"] <- "Younger ASD" 
# medianASD <- round((length(ssl_slopeASD$age_at_web_year)/2))+1
# ssl_slopeASD[median:length(ssl_slopeASD$age_at_web_year),"Group"] <- "Older ASD"



ssl_slope_ASDtd <- rbind(ssl_slopeASD, ssl_slope)


ssl_slope_ASDtd$Group <- 
  factor(ssl_slope_ASDtd$Group,levels = c("ASD", 
                                             "Younger TD",
                                              # "Older ASD", 
                                             "Older TD"))
ssl_slope_ASDtd <-
  ssl_slope_ASDtd[order(ssl_slope_ASDtd$Group), ]

return(ssl_slope_ASDtd)
}

lslSlopeAge <- plot_medianSplit(allData_slope, "lsl_slope")
sslSlopeAge <- plot_medianSplit(allData_slope, "ssl_slope")
lslAccAge <- plot_medianSplit(allData_acc, "lsl_acc")
sslAccAge <- plot_medianSplit(allData_acc, "ssl_acc")


library(ez)
sslSlopeAge <- sslSlopeAge[which(!is.na(sslSlopeAge$rt_slope)),]
ezANOVA(data=sslSlopeAge, wid=part_id, dv=rt_slope, between = Group, type=3)

pairwise.t.test(sslSlopeAge$rt_slope, sslSlopeAge$Group, p.adjust.method = "bonferroni")

sslAccAge <- sslAccAge[which(!is.na(sslAccAge$accuracy)),]
ezANOVA(data=sslAccAge, wid=part_id, dv=accuracy, between = Group, type=3)


# Checked anova on LSL slope and accuracy, no difference.
```

```{r}

sslSlopeAge %>%
  ggplot(aes(x = Group, y = rt_slope,fill = Group)) +
  geom_bar(
           position = position_dodge(),
           width = 0.9,
           stat = "summary", fun.y = "mean") +
   labs(title = paste("Syllable SL RT Slope Median Split by Age in TD and ASD"),
        x = "Age Group",  # Change x-axis label
         y = paste("SL RT Slope (arbitrary unit/ trial)")) +
  scale_fill_manual(values = c("#F8766d", "#00BFC4", "#00BFC4")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold"),
        legend.title=element_text(size=15, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),         # Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) + 
  geom_beeswarm(
    aes(fill = Group),
    dodge.width = 1,
    cex = 2.5,
    size = 0.8,
    show.legend = FALSE,
    shape = 1
  )

# ggsave("ssl_slope_td_asd.png",
#        width = 18, height = 15, units = "cm")




sslAccAge %>%
  ggplot(aes(x = Group, y = accuracy,fill = Group)) +
  geom_bar(
           position = position_dodge(),
           width = 0.9,
           stat = "summary", fun.y = "mean") +
   labs(title = paste("Syllable SL Accuracy Median Split by Age in TD and ASD"),
        x = "Age Group",  # Change x-axis label
         y = paste("SL RT Slope (arbitrary unit/ trial)")) +
  scale_fill_manual(values = c("#F8766d", "#00BFC4", "#00BFC4")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold"),
        legend.title=element_text(size=15, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),         # Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) + 
  geom_beeswarm(
    aes(fill = Group),
    dodge.width = 1,
    cex = 2.5,
    size = 0.8,
    show.legend = FALSE,
    shape = 1
  )
# ggsave("ssl_acc_td_asd.png",
#        width = 18, height = 15, units = "cm")

# ggsave("lsl_slope_td_asd.png",
#        width = 18, height = 15, units = "cm")




```



```{r}
pd <- position_dodge(width = 0.2)

slope_within_stat %>%
  ggplot(aes(x = task, y = mean, group = Group)) +
  geom_line(aes(linetype = Group, color = Group),
            position = pd,
            size = 1.8) +
  geom_errorbar(
    aes(ymin = mean - std_error, ymax = mean + std_error),
    width = .1,
    position = pd
  ) +
  geom_point(
    aes(color = Group),
    size = 4,
    position = pd,
    show.legend = FALSE
  ) +
  geom_point(size = 3,
             color = "white",
             position = pd) +
  labs(title = "SL Reaction Time Slope across Tasks",
       x = "SL Task",  # Change x-axis label
       y = "Mean Reaction Time Slope (arbitrary unit/trial)") +
  scale_color_manual(values = c(cbPalette[1], cbPalette[8])) +
  # scale_y_reverse() +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title.x = element_text(size = 14, face = "bold"),
    axis.title.y = element_text(size = 14, face = "bold"),
    axis.text = element_text(size = 14, face = "bold")
  ) +
  theme(
    legend.text = element_text(size = 14, face = "bold"),
    legend.title = element_text(size = 15, face = "bold")
  ) +
  theme(
    panel.background = element_rect(fill = "white"),
    # Set plot background to white
    legend.key  = element_rect(fill = "white"),
    # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),
    # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  )  +
  geom_hline(yintercept = 0, color = "grey") +
  geom_text(aes(
    x = 1.95,
    y = -0.033,
    label = paste0("***")
  ),
  size = 7,
  color = cbPalette[1]) +
  geom_text(aes(
    x = 0.95,
    y = -0.033,
    label = paste0("**")
  ),
  size = 7,
  color = cbPalette[1]) +
  geom_text(aes(
    x = 3.05,
    y = -0.033,
    label = paste0("*")
  ),
  size = 7,
  color = cbPalette[8])

 
# ggsave(
#     "behavioral_slope_across_group.png",
#      width = 15, height = 15, units = "cm"
#  )
```


```{r}
boxplotSlope <- 
allData_slope %>%
  group_by(group, task) %>%
  dplyr::summarise(
            ymin = min(rt_slope, na.rm = T),
            ymax = max(rt_slope, na.rm = T),
            middle = median(rt_slope, na.rm = T),
            lower = quantile(rt_slope,0.25, na.rm = T),
            upper = quantile(rt_slope,0.75, na.rm = T))

revalue(boxplotSlope)

boxplotSlope$task <-
  revalue(boxplotSlope$task, c("lsl_slope" = "Letter",
                                    "tsl_slope" = "Tone",
                                    "ssl_slope" = "Syllable", 
                                    "vsl_slope" = "Image"))

colnames(boxplotSlope)[colnames(boxplotSlope) == "group"] <- "Group"

boxplotSlope <- merge(slope_within_stat, boxplotSlope, by = c("Group", "task"), all.x = T)

boxplotSlope$task <- 
  factor(boxplotSlope$task,levels = c("Letter", 
                                      "Syllable", 
                                      "Image", 
                                      "Tone"))
```


```{r}
ggplot(data = boxplotSlope, aes(x = task, color = Group)) +
  geom_errorbar(aes(ymin = ymin, ymax = ymax),
                width = .1,
                position = position_dodge(width = 0.8)) +
  geom_boxplot(
    aes(
      ymin = ymin,
      ymax = ymax,
      middle = mean,
      upper = upper,
      lower = lower
    ),
    stat = 'identity',
    outlier.shape = NA,
    position = position_dodge(width = 0.8)
  ) +
  labs(title = "SL Reaction Time Slope across Tasks",
       x = "SL Task",  # Change x-axis label
       y = "Mean Reaction Time Slope (arbitrary unit/trial)") +
  scale_y_reverse() +
  scale_color_manual(values = c(cbPalette[1], cbPalette[8])) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title.x = element_text(size = 14, face = "bold"),
    axis.title.y = element_text(size = 14, face = "bold"),
    axis.text = element_text(size = 14, face = "bold")
  ) +
  theme(
    legend.text = element_text(size = 14, face = "bold"),
    legend.title = element_text(size = 15, face = "bold")
  ) +
  theme(
    panel.background = element_rect(fill = "white"),
    # Set plot background to white
    legend.key  = element_rect(fill = "white"),
    # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),
    # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  )  +
  geom_hline(yintercept = 0, color = "grey") +
  geom_segment(aes(
    x = 0.8,
    xend = 1.2,
    y = -0.12,
    yend = -0.12
  ), color = "black") +
  geom_text(size = 12,
            color = "black",
            aes(
              x = 1,
              y = -0.12,
              label = paste0("*")
            )) +
  geom_segment(aes(
    x = 1.8,
    xend = 2.2,
    y = -0.07,
    yend = -0.07
  ), color = "black") +
  geom_text(size = 12,
            color = "black",
            aes(
              x = 2,
              y = -0.07,
              label = paste0("*")
            )) +
  geom_segment(aes(
    x = 1,
    xend = 2,
    y = -0.14,
    yend = -0.14
  ), color = "black") +
  geom_segment(aes(
    x = 3,
    xend = 4,
    y = -0.14,
    yend = -0.14
  ), color = "black") +
  geom_text(size = 12,
            color = "black",
            aes(
              x = 3.5,
              y = -0.14,
              label = paste0("*")
            )) +
  geom_segment(aes(
    x = 1.5,
    xend = 1.5,
    y = -0.16,
    yend = -0.17
  ), color = "black") +
  geom_segment(aes(
    x = 3.5,
    xend = 3.5,
    y = -0.16,
    yend = -0.17
  ), color = "black") +
  geom_segment(aes(
    x = 1.5,
    xend = 3.5,
    y = -0.17,
    yend = -0.17
  ), color = "black") +
  geom_text(size = 12,
            color = "black",
            aes(
              x = 2.5,
              y = -0.17,
              label = paste0("**")
            ))

 
 # ggsave(
 #    "behavioral_slope_across_group_boxplot.png",
 #     width = 15, height = 15, units = "cm"
 # )
 
```

```{r}
library(ggbeeswarm)
slope_bar <- bar_slope 
colnames(slope_bar)[colnames(slope_bar) == "group"] <- "Group"
slope_bar %>%
  ggplot(aes(x = variable, y = value)) +
  geom_bar(
    aes(fill = Group),
    position = position_dodge(),
    width = 0.9,
    stat = "summary",
    fun.y = "mean",
  ) +
 labs(title = "SL Reaction Time Slope Between Group Comparison",
         x = "SL Task",  # Change x-axis label
         y = "Mean Reaction Time Slope (arbitrary unit/trial)") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold"),
        legend.title=element_text(size=15, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),         # Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) + 
  geom_beeswarm(
    aes(fill = Group),
    dodge.width = 1,
    cex = 2.5,
    size = 0.8,
    show.legend = FALSE, 
    shape = 1
  ) + 
  # geom_text(aes(x= 1, y = 1.04, label = paste0("")), size=7) +
  # geom_segment(aes(x=0.75,xend=1.25, y = 1.02, yend = 1.02)) +
  # geom_segment(aes(x=0.75,xend=0.75, yend = 1, y = 1.02)) +
  # geom_segment(aes(x=1.25,xend=1.25, yend = 1, y = 1.02)) +
   geom_text(aes(x= 2, y = 0.102, label = paste0("*")), size=7) +
   geom_segment(aes(x=1.75,xend=2.25, y = 0.1, yend = 0.1)) +
   geom_segment(aes(x=1.75,xend=1.75, yend = 0.096, y = 0.1)) +
  geom_segment(aes(x=2.25,xend=2.25, yend = 0.096, y = 0.1))

# ggsave("srcd_figure/behavioral_slope_ling_bar.png",
       # bg="transparent",
       # width = 15.5, height = 15.5, units = "cm")

```

# Composite SL score Line Plot
```{r}
composite_within_stat <-
  summarySEwithin(
    compositeGroupL,
    measurevar = "composite_score",
    betweenvars = "group",
    withinvars = "task",
    idvar = "part_id",
    na.rm = T,
    conf.interval = .95
  )
colnames(composite_within_stat)[colnames(composite_within_stat) == "group"] <-
  "Group"
composite_within_stat$task <-
  revalue(
    composite_within_stat$task,
    c(
      "composite_lsl" = "Letter",
      "composite_tsl" = "Tone",
      "composite_ssl" = "Syllable",
      "composite_vsl" = "Image"
    )
  )
composite_within_stat$task <-
  factor(composite_within_stat$task,
         levels = c("Letter",
                    "Syllable",
                    "Image",
                    "Tone"))
composite_within_stat$Group <-
  factor(composite_within_stat$Group, levels = c("TD", "ASD"))


composite_within_stat %>%
  ggplot(aes(x = task, y = composite_score, group = Group)) +
  geom_line(aes(linetype = Group, color = Group),
            position = pd,
            size = 1.8) +
  geom_errorbar(
    aes(ymin = composite_score - se, ymax = composite_score + se),
    width = .1,
    position = pd
  ) +
  geom_point(
    aes(color = Group),
    size = 4,
    position = pd,
    show.legend = FALSE
  ) +
  geom_point(size = 3,
             color = "white",
             position = pd) +
  labs(title = "Composite Scores Across SL Tasks",
       x = "SL Task",  # Change x-axis label
       y = "Composite Score (arbitrary unit)") +
  scale_color_manual(values = c(cbPalette[1], cbPalette[8])) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title.x = element_text(size = 14, face = "bold"),
    axis.title.y = element_text(size = 14, face = "bold"),
    axis.text = element_text(size = 12, face = "bold")
  ) +
  theme(
    legend.text = element_text(size = 14, face = "bold"),
    legend.title = element_text(size = 15, face = "bold")
  ) +
  theme(
    panel.background = element_rect(fill = "white"),
    # Set plot background to white
    legend.key  = element_rect(fill = "white"),
    # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),
    # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  )

# ggsave(
#   "/Users/jojohu/Documents/Qlab/manuscript/behavioral_composite_across_group.png",
#   bg = "transparent",
#   width = 15,
#   height = 15,
#   units = "cm"
# )
```

# Plot GJT A-prime vs. Composite SL score in ASD
```{r}
compositeAge %>%
ggplot(aes(x = a_prime, y = composite_ling, color = language_age_level)) +
  geom_point(size = 4, shape = 1, position = pd, stroke = 1.7) +
  # scale_fill_brewer(palette = "Set2") +
      labs(title = "SCQ and Composite SL Score Correlation",
         x = "SCQ Score",  # hange x-axis label
         y = "Composite SL Score") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),
    legend.title = element_text(size = 16, face = "bold"),# Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) +
   geom_smooth(aes(x = a_prime, y = composite_ling),
              method=lm, se=T, show.legend = F, inherit.aes = F)
  # geom_smooth(data = subset(compositeAge, language_age_level == "below_age"),
  #             aes(x = scq_web, y = composite),
  #             method=lm, se=FALSE, show.legend = F, inherit.aes = F) +
  # geom_smooth(data = subset(compositeAge, language_age_level == "at_age"),
  #             aes(x = scq_web, y = composite),
  #             method=lm, se=FALSE, show.legend = F, inherit.aes = F)


# ggsave("srcd_figure/RSR_LSLcorr.png",
       # width = 17, height = 17, units = "cm")
```


## Correlations between Tasks
```{r, include = FALSE}
library("Hmisc")
allData_td <- allData[which(allData$group == "TD"),]
allData_asd <- allData[which(allData$group == "ASD"),]


extract_data_for_corr_task_asd <-
function(df) {rcorr(as.matrix(df[,c(
      "age_at_web_year",
      "scq_web",
      "rbs_r",
      "rsr_raw",
      "rsr_std",
      "gjt_std",
      "a_prime",
      "vsl_acc",
      "lsl_acc",
      "tsl_acc",
      "ssl_acc",
      "vsl_ent",
      "entropy_children_lsl_entropy",
      "tsl_ent",
      "ssl_ent",
      "vsl_rt",
      "lsl_rt",
      "tsl_rt",
      "ssl_rt",
      "vsl_slope",
      "lsl_slope",
      "tsl_slope",
      "ssl_slope"
      )]), 
      type = c("pearson"))}

extract_data_for_corr_task_td <-
function(df) {rcorr(as.matrix(df[,c(
      "age_at_web_year",
      "scq_web",
      "vsl_acc",
      "lsl_acc",
      "tsl_acc",
      "ssl_acc",
      "vsl_ent",
      "entropy_children_lsl_entropy",
      "tsl_ent",
      "ssl_ent",
      "vsl_rt",
      "lsl_rt",
      "tsl_rt",
      "ssl_rt",
      "vsl_slope",
      "lsl_slope",
      "tsl_slope",
      "ssl_slope")]), 
      type = c("pearson"))}

extract_data_for_corr_task_sl <-
  function(df) {rcorr(as.matrix(df[,c(
    "age_at_web_year",
      "vsl_acc",
      "lsl_acc",
      "tsl_acc",
      "ssl_acc",
      "vsl_slope",
      "lsl_slope",
      "tsl_slope",
      "ssl_slope")]), type = c("pearson"))}


corr_beh_result_across_task_asd <- extract_data_for_corr_task_asd(allData_asd)
corr_beh_result_across_task_td <- extract_data_for_corr_task_td(allData_td)

asdAccSlopeCorrTask <- extract_data_for_corr_task_sl(allData_asd)
tdAccSlopeCorrTask <- extract_data_for_corr_task_sl(allData_td)


flattenCorrMatrix <- function(cormat, pmat, nmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  = (cormat)[ut],
    p = pmat[ut],
    n = nmat[ut]
  )
}



beh_corr_result_pearson_task_td <- flattenCorrMatrix(corr_beh_result_across_task_td$r, 
                                              corr_beh_result_across_task_td$P, 
                                              corr_beh_result_across_task_td$n)


beh_corr_result_pearson_task_asd <- flattenCorrMatrix(corr_beh_result_across_task_asd$r, 
                                              corr_beh_result_across_task_asd$P, 
                                              corr_beh_result_across_task_asd$n)

beh_asdAccSlopeCorrTask <- flattenCorrMatrix(asdAccSlopeCorrTask$r, 
                                              asdAccSlopeCorrTask$P, 
                                              asdAccSlopeCorrTask$n)

beh_tdAccSlopeCorrTask <- flattenCorrMatrix(tdAccSlopeCorrTask$r, 
                                              tdAccSlopeCorrTask$P, 
                                              tdAccSlopeCorrTask$n)

#beh_corr_result_pearson_all[,c(3:5)] <- round(beh_corr_result_pearson_all[,c(3:5)], 3)


rounded_td <- round(beh_corr_result_pearson_task_td[,c(3:5)], 3)
beh_corr_result_pearson_task_td <- cbind(beh_corr_result_pearson_task_td[,c(1:2)], rounded_td)

rounded_asd <- round(beh_corr_result_pearson_task_asd[,c(3:5)], 3)
beh_corr_result_pearson_task_asd <- cbind(beh_corr_result_pearson_task_asd[,c(1:2)], rounded_asd)

#beh_corr_result_pearson_sig_all <- beh_corr_result_pearson_all[which(beh_corr_result_pearson_all$p <= 0.05),]
```


```{r}
beh_corr_result_pearson_sig_td <- beh_corr_result_pearson_task_td[which(beh_corr_result_pearson_task_td$p <= 0.05),]
beh_corr_result_pearson_sig_asd <- beh_corr_result_pearson_task_asd[which(beh_corr_result_pearson_task_asd$p <= 0.05),]

# write.csv(beh_corr_result_pearson_sig, "paper_analysis_matched/beh_corr_result_pearson_gender_matched_sample.csv")
# write.csv(beh_corr_result_pearson_sig_td, "paper_analysis_matched/beh_corr_result_pearson_gender_matched_sample_td.csv")
# write.csv(beh_corr_result_pearson_sig_asd, "paper_analysis_matched/beh_corr_result_pearson_gender_matched_sample_asd.csv")


print(beh_corr_result_pearson_sig_td)
print(beh_corr_result_pearson_sig_asd)
```

# Corrected Correlations between SL tasks for TD
```{r}
library(RcmdrMisc)
sl_corrTD <-
rcorr.adjust(as.matrix(allData_td[c("ssl_acc",
      "tsl_acc",
      "lsl_acc",
      "vsl_acc",
      "ssl_slope",
      "tsl_slope",
      "lsl_slope",
      "vsl_slope"
      )]),
      use=c("pairwise.complete.obs"))

sl_corrTD <-
flattenCorrMatrix(data.frame(sl_corrTD$R[1]),
                  data.frame(sl_corrTD$R[3]),
                  data.frame(sl_corrTD$R[2]))
                  
# write.csv(sl_corrTD, "tdSL_corr_corrected.csv")
```

# Corrected Correlation between SL tasks for ASD
```{r}
sl_corrASD <-
rcorr.adjust(as.matrix(allData_asd[c("ssl_acc",
      "tsl_acc",
      "lsl_acc",
      "vsl_acc",
      "ssl_slope",
      "tsl_slope",
      "lsl_slope",
      "vsl_slope")]),
      use=c("pairwise.complete.obs"))

sl_corrASD <-
flattenCorrMatrix(data.frame(sl_corrASD$R[1]),
                  sl_corrASD$P,
                  data.frame(sl_corrASD$R[2]))


# write.csv(sl_corrASD, "asdSL_corr_corrected.csv")
```


# Prep Heat Map 
```{r ,include = F}
library(plyr)
extract_heatmap_data_task <-
  function(df, column) {
    revalue(
      df[[column]],
      c(
        "age_at_web_year" = "Age",
        "kbit_matrices_std" = "KBIT Standardized Score",
        "scq_web" = "SCQ Total",
        "rsr_raw" = "Sentence Recall Raw Score",
        "rsr_std" = "Sentence Recall Standardized Score",
        "tsl_acc" = "Tone Accuracy",
        "ssl_acc" = "Syllable Accuracy",
        "vsl_acc" = "Image Accuracy",
        "lsl_acc" = "Letter Accuracy",
        "tsl_acc" = "Tone Accuracy",
        "ssl_acc" = "Syllable Accuracy",
        "vsl_acc" = "Image Accuracy",
        "tsl_ent" = "Tone Entropy",
        "ssl_ent" = "Syllable Entropy",
        "vsl_ent" = "Image Entropy",
        "entropy_children_lsl_entropy" = "Letter Entropy",
        "tsl_rt" = "Tone Mean RT",
        "ssl_rt" = "Syllable Mean RT",
        "vsl_rt" = "Image Mean RT",
        "lsl_rt" = "Letter Mean RT",
        "gjt_std" = "GJT Standardized Score",
        "a_prime" = "GJT Raw Score",
        "ssl_slope" = "Syllable RT Slope",
        "tsl_slope" = "Tone RT Slope",
        "vsl_slope" = "Image RT Slope",
        "lsl_slope" = "Letter RT Slope",
        "ssl_slope" = "Syllable RT Slope",
        "tsl_slope" = "Tone RT Slope",
        "vsl_slope" = "Image RT Slope",
        "lsl_slope" = "Letter RT Slope"
      )
    )
  }


beh_corr_result_pearson_task_asd$column <- extract_heatmap_data_task(beh_corr_result_pearson_task_asd, "column")
beh_corr_result_pearson_task_asd$row <- extract_heatmap_data_task(beh_corr_result_pearson_task_asd, "row")
beh_corr_result_pearson_task_td$column <- extract_heatmap_data_task(beh_corr_result_pearson_task_td, "column")
beh_corr_result_pearson_task_td$row <- extract_heatmap_data_task(beh_corr_result_pearson_task_td, "row")
beh_asdAccSlopeCorrTask$column <- extract_heatmap_data_task(beh_asdAccSlopeCorrTask, "column")
beh_asdAccSlopeCorrTask$row <- extract_heatmap_data_task(beh_asdAccSlopeCorrTask, "row")
beh_tdAccSlopeCorrTask$column <- extract_heatmap_data_task(beh_tdAccSlopeCorrTask, "column")
beh_tdAccSlopeCorrTask$row <- extract_heatmap_data_task(beh_tdAccSlopeCorrTask, "row")


reorder_heatmap_task_func <- 
function(df, column){
factor(
  df[[column]],
  levels =
    c("Age",
      "KBIT Standardized Score",
      "SCQ Total",
      "Sentence Recall Raw Score",
      "Sentence Recall Standardized Score",
      "GJT Standardized Score",
      "GJT Raw Score",
      "Image Accuracy",
      "Letter Accuracy",
      "Tone Accuracy",
      "Syllable Accuracy",
      "Image Entropy",
      "Letter Entropy",
      "Tone Entropy",
      "Syllable Entropy",
      "Image Mean RT",
      "Letter Mean RT",
      "Tone Mean RT",
      "Syllable Mean RT",
      "Image RT Slope",
      "Letter RT Slope",
      "Tone RT Slope",
      "Syllable RT Slope"
    )
)}


beh_corr_result_pearson_task_asd$column <- reorder_heatmap_task_func(beh_corr_result_pearson_task_asd, "column")
beh_corr_result_pearson_task_asd$row <- reorder_heatmap_task_func(beh_corr_result_pearson_task_asd, "row")

beh_corr_result_pearson_task_td$column <- reorder_heatmap_task_func(beh_corr_result_pearson_task_td, "column")
beh_corr_result_pearson_task_td$row <- reorder_heatmap_task_func(beh_corr_result_pearson_task_td, "row")
beh_asdAccSlopeCorrTask$column <- reorder_heatmap_task_func(beh_asdAccSlopeCorrTask, "column")
beh_asdAccSlopeCorrTask$row <- reorder_heatmap_task_func(beh_asdAccSlopeCorrTask, "row")
beh_tdAccSlopeCorrTask$column <- reorder_heatmap_task_func(beh_tdAccSlopeCorrTask, "column")
beh_tdAccSlopeCorrTask$row <- reorder_heatmap_task_func(beh_tdAccSlopeCorrTask, "row")


round_func <-
function(input_df) {
  input_df[order(input_df$row,
                 input_df$column), ]
}


heat_map_corr_data_task_asd <- round_func(beh_corr_result_pearson_task_asd)
heat_map_corr_data_task_asd$cor <- round(heat_map_corr_data_task_asd$cor, 2)
heat_map_corr_data_task_asd$p <- round(heat_map_corr_data_task_asd$p, 2)

heat_map_corr_data_task_td <- round_func(beh_corr_result_pearson_task_td)
heat_map_corr_data_task_td$cor <- round(heat_map_corr_data_task_td$cor, 2)
heat_map_corr_data_task_td$p <- round(heat_map_corr_data_task_td$p, 2)

heat_map_asdAccSlopeCorrTask <- round_func(beh_asdAccSlopeCorrTask)
heat_map_asdAccSlopeCorrTask$cor <- round(heat_map_asdAccSlopeCorrTask$cor, 2)
heat_map_asdAccSlopeCorrTask$p <- round(heat_map_asdAccSlopeCorrTask$p, 2)

heat_map_tdAccSlopeCorrTask <- round_func(beh_tdAccSlopeCorrTask)
heat_map_tdAccSlopeCorrTask$cor <- round(heat_map_tdAccSlopeCorrTask$cor, 2)
heat_map_tdAccSlopeCorrTask$p <- round(heat_map_tdAccSlopeCorrTask$p, 2)
```


# Plot Heat Map for R, P, N for behavioral correlations
# Across Behavioral Tasks, Within Measure (TD or ASD Only)
```{r}
library("ggplot2")

plot_heatmap_r_func <-
function(df) {
ggplot(data = df, aes(x = column, y = row, fill = cor)) +
  geom_tile(color = "white") +
  scale_fill_gradient2(
    low = "blue",
    high = "red",
    mid = "white",
    midpoint = 0,
    limit = c(-1, 1),
    space = "Lab",
    name = "pearson\nCorrelation r"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(
    angle = 90,
    vjust = 1,
    size = 10,
    hjust = 1
  )) +
  theme(axis.title.x = element_blank(),
        axis.text.y = element_text (size = 10),
        axis.title.y = element_blank()) +
  coord_fixed() +
  geom_text(aes(label = cor), color = "black", size = 2)
}

```

```{r}
library("ggplot2")

legend_name <- expression(paste("Pearson's ", italic("r")))

heat_map_tdAccSlopeCorrTask[which(heat_map_tdAccSlopeCorrTask$p < 0.06), "size"] <- 1
heat_map_tdAccSlopeCorrTask[-which(heat_map_tdAccSlopeCorrTask$p < 0.06), "size"] <- 0

heat_map_tdAccSlopeCorrTask[which(heat_map_tdAccSlopeCorrTask$column == "Image RT Slope" & heat_map_tdAccSlopeCorrTask$row == "Syllable Accuracy"), "size"] <- 0


ggplot(data = heat_map_tdAccSlopeCorrTask, aes(x = column, y = row, fill = cor)) +
  geom_tile(color = "white") +
  scale_fill_gradient2(
    low = "blue",
    high = "red",
    mid = "white",
    midpoint = 0,
    limit = c(-1, 1),
    space = "Lab",
    name = legend_name
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(
    angle = 90,
    vjust = 1,
    size = 10,
    hjust = 1
  )) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text (size = 14, face="bold"),
        axis.text.y = element_text (size = 14, face="bold"),
        axis.title.y = element_blank()) +
  coord_fixed() +
  geom_text(aes(label = cor, size = size), color = "black") +
  scale_size(range = c(2.5, 4.7), guide = F) +
  theme(legend.text = element_text(size=12), legend.title = element_text(size=14))

# # ggsave(
# #   "paper_analysis_matched/corrR_TD.png",
#   dpi = 150)


ggplot(data = heat_map_tdAccSlopeCorrTask, aes(x = column, y = row, fill = n)) +
  geom_tile(color = "white") +
  scale_fill_gradient2(
    low = "blue",
    high = "red",
    mid = "white",
    midpoint = 0,
    limit = c(-1, 1),
    space = "Lab",
    name = legend_name
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(
    angle = 90,
    vjust = 1,
    size = 10,
    hjust = 1
  )) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text (size = 14, face="bold"),
        axis.text.y = element_text (size = 14, face="bold"),
        axis.title.y = element_blank()) +
  coord_fixed() +
  geom_text(aes(label = n, size = size), color = "black") +
  scale_size(range = c(2.5, 4.7), guide = F) +
  theme(legend.text = element_text(size=12), legend.title = element_text(size=14))

# ggsave(
#   "paper_analysis_matched/corrN_TD.png",
#   dpi = 150)



ggplot(data = heat_map_tdAccSlopeCorrTask, aes(x = column, y = row, fill = p)) +
  geom_tile(color = "white") +
  scale_fill_gradient2(
    low = "blue",
    high = "red",
    mid = "white",
    midpoint = 0,
    limit = c(-1, 1),
    space = "Lab",
    name = legend_name
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(
    angle = 90,
    vjust = 1,
    size = 10,
    hjust = 1
  )) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text (size = 14, face="bold"),
        axis.text.y = element_text (size = 14, face="bold"),
        axis.title.y = element_blank()) +
  coord_fixed() +
  geom_text(aes(label = p, size = size), color = "black") +
  scale_size(range = c(2.5, 4.7), guide = F) +
  theme(legend.text = element_text(size=12), legend.title = element_text(size=14))

# ggsave(
#   "paper_analysis_matched/corrP_TD.png",
#   dpi = 150)
```

```{r}

heat_map_asdAccSlopeCorrTask[which(heat_map_asdAccSlopeCorrTask$p < 0.06), "size"] <- 1
heat_map_asdAccSlopeCorrTask[-which(heat_map_asdAccSlopeCorrTask$p < 0.06), "size"] <- 0

heat_map_asdAccSlopeCorrTask[which(heat_map_asdAccSlopeCorrTask$column == "Image RT Slope" & heat_map_asdAccSlopeCorrTask$row == "Tone Accuracy"), "size"] <- 0


ggplot(data = heat_map_asdAccSlopeCorrTask, aes(x = column, y = row, fill = cor)) +
  geom_tile(color = "white") +
  scale_fill_gradient2(
    low = "blue",
    high = "red",
    mid = "white",
    midpoint = 0,
    limit = c(-1, 1),
    space = "Lab",
    name = legend_name
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(
    angle = 90,
    vjust = 1,
    size = 10,
    hjust = 1
  )) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text (size = 14, face="bold"),
        axis.text.y = element_text (size = 14, face="bold"),
        axis.title.y = element_blank()) +
  coord_fixed() +
  geom_text(aes(label = cor, size = size), color = "black") +
  scale_size(range = c(2.5, 4.7), guide = F) +
  theme(legend.text = element_text(size=12), legend.title = element_text(size=14))


# ggsave(
#   "paper_analysis_matched/corrR_ASD.png",
#   dpi = 150)


ggplot(data = heat_map_asdAccSlopeCorrTask, aes(x = column, y = row, fill = n)) +
  geom_tile(color = "white") +
  scale_fill_gradient2(
    low = "blue",
    high = "red",
    mid = "white",
    midpoint = 0,
    limit = c(-1, 1),
    space = "Lab",
    name = legend_name
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(
    angle = 90,
    vjust = 1,
    size = 10,
    hjust = 1
  )) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text (size = 14, face="bold"),
        axis.text.y = element_text (size = 14, face="bold"),
        axis.title.y = element_blank()) +
  coord_fixed() +
  geom_text(aes(label = n, size = size), color = "black") +
  scale_size(range = c(2.5, 4.7), guide = F) +
  theme(legend.text = element_text(size=12), legend.title = element_text(size=14))


# ggsave(
#   "paper_analysis_matched/corrN_ASD.png",
#   dpi = 150)

ggplot(data = heat_map_asdAccSlopeCorrTask, aes(x = column, y = row, fill = p)) +
  geom_tile(color = "white") +
  scale_fill_gradient2(
    low = "blue",
    high = "red",
    mid = "white",
    midpoint = 0,
    limit = c(-1, 1),
    space = "Lab",
    name = legend_name
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(
    angle = 90,
    vjust = 1,
    size = 10,
    hjust = 1
  )) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text (size = 14, face="bold"),
        axis.text.y = element_text (size = 14, face="bold"),
        axis.title.y = element_blank()) +
  coord_fixed() +
  geom_text(aes(label = p, size = size), color = "black") +
  scale_size(range = c(2.5, 4.7), guide = F) +
  theme(legend.text = element_text(size=12), legend.title = element_text(size=14))


# ggsave(
#   "paper_analysis_matched/corrP_ASD.png",
#   dpi = 150)

```

# Plot post-hoc analyses in ASD
# Plot heat map for post-hoc analyses in ASD
```{r}
asd_corr_posthoc[which(asd_corr_posthoc$p < 0.08), "size"] <- 1
asd_corr_posthoc[-which(asd_corr_posthoc$p < 0.08), "size"] <- 0
asd_corr_posthoc$cor <- round(asd_corr_posthoc$cor, 2)

ggplot(data = asd_corr_posthoc, aes(x = column, y = row, fill = cor)) +
  geom_tile(color = "white") +
  scale_fill_gradient2(
    low = "blue",
    high = "red",
    mid = "white",
    midpoint = 0,
    limit = c(-1, 1),
    space = "Lab",
    name = legend_name
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(
    angle = 90,
    vjust = 1,
    size = 10,
    hjust = 1
  )) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text (size = 14, face="bold"),
        axis.text.y = element_text (size = 14, face="bold"),
        axis.title.y = element_blank()) +
  coord_fixed() +
  geom_text(aes(label = cor, size = size), color = "black") +
  scale_size(range = c(2.5, 4.7), guide = F) +
  theme(legend.text = element_text(size=12), legend.title = element_text(size=14))

# ggsave("asd_posthoc_corr.png")
```



# Plot RBS-R vs. SCQ in ASD
```{r}
rbs_rPlot <- allData
rbs_rPlot$Group <- rbs_rPlot$group

subset(rbs_rPlot, Group == "ASD") %>%
ggplot(aes(x = rbs_r , y = scq_web, color = Group)) +
  geom_point(size = 4, shape = 1, position = pd, stroke = 1.7) +
  scale_fill_brewer(palette = "Set2") +
      labs(title = "SCQ Score and RBS-R Correlation",
         x = "RBS-R Score",  # hange x-axis label
         y = "SCQ Score") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),
    legend.title = element_text(size = 16, face = "bold"),# Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) +
  geom_smooth(data = subset(rbs_rPlot, Group == "ASD"),
              aes(x = rbs_r, y = scq_web),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "#F8766d") 


# ggsave("srcd_figure/SCQ_RSRcorr.png",
       # width = 17, height = 17, units = "cm")
```

# Plot RBS-R vs. Linguistic RT slope in ASD
```{r}
rtASD_ling %>%
ggplot(aes(x = rbs_r , y = rt_slope, color = language_age_level)) +
  geom_point(size = 4, shape = 1, position = pd, stroke = 1.7) +
  # scale_fill_brewer(palette = "Set2") +
      labs(title = "RBS-R and Linguistic SL Slope Correlation",
         x = "RBS-R Score",  # hange x-axis label
         y = "Linguistic SL Slope") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),
    legend.title = element_text(size = 16, face = "bold"),# Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) +
  geom_smooth(data = subset(rtASD_ling, language_age_level == "below_age"),
              aes(x = rbs_r, y = rt_slope),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F) +
  geom_smooth(data = subset(rtASD_ling, language_age_level == "at_age"),
              aes(x = rbs_r, y = rt_slope),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F)


# ggsave("srcd_figure/RSR_LSLcorr.png",
       # width = 17, height = 17, units = "cm")
```




# Multiple Regression for SL Task Relationships
```{r}
# Compare correlations of lingusitic SL tasks between groups
summary(lm(ssl_acc ~ lsl_acc*group, data = allData))
summary(lm(ssl_slope ~ lsl_slope*group, data = allData))

```



# Plot Accuracy Correlation of SL taks across groups

# LSL vs. SSL Acc 
(stronger correaltion in TD, marginal interaction in multiple regression)
```{r}
library(ggpubr)
colnames(allData)[colnames(allData) == "group"] <- "Group"

pd <- position_dodge(width = 0.01)

allData %>%
ggplot(aes(x = ssl_acc, y = lsl_acc, color = Group)) +
  geom_point(size = 4, shape = 1, position = pd, stroke = 1.7) +
  scale_fill_brewer(palette = "Set2") +
      labs(title = "Syllable and Letter SL Accuracy Correlation",
         y = "Letter SL Accuracy",  # Change x-axis label
         x = "Syllable SL Accuracy") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),
    legend.title = element_text(size = 16, face = "bold"),# Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) +
  geom_smooth(data = subset(allData, Group == "TD"),
              aes(x = ssl_acc, y = lsl_acc),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "#00BFC4") +
  geom_smooth(data = subset(allData, Group == "ASD"),
              aes(x = ssl_acc, y = lsl_acc),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "#F8766d") +
  stat_cor(data = subset(allData, Group == "TD"),
              aes(x = ssl_acc, y = lsl_acc),
           method = "pearson", label.x = 0.55, label.y = 0.92,
           inherit.aes = F, color = "#00BFC4", size = 5) +
    stat_cor(data = subset(allData, Group == "ASD"),
              aes(x = ssl_acc, y = lsl_acc),
             method = "pearson", label.x = 0.55, label.y = 0.3, 
           inherit.aes = F, color = "#F8766d", size = 5)
  #+ 
  #geom_text(aes(x = 20, y = 120, label = paste("rho =", "-0.76**")),color = "red",size=4)

# ggsave("srcd_figure/bucld_ssl_lsl_corr.png",
       # width = 15, height = 15, units = "cm")
```


# TSL vs. VSL Acc (significant in ASD)
```{r}
library(ggpubr)
colnames(allData)[colnames(allData) == "group"] <- "Group"

pd <- position_dodge(width = 0.01)

allData %>%
ggplot(aes(x = tsl_acc, y = vsl_acc, color = Group)) +
  geom_point(size = 4, shape = 1, position = pd, stroke = 1.7) +
  scale_fill_brewer(palette = "Set2") +
      labs(title = "Tone and Image SL Accuracy Correlation",
         y = "Tone SL Accuracy",  # Change x-axis label
         x = "Image SL Accuracy") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),
    legend.title = element_text(size = 16, face = "bold"),# Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) +
  geom_smooth(data = subset(allData, Group == "TD"),
              aes(x = tsl_acc, y = vsl_acc),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "#00BFC4") +
  geom_smooth(data = subset(allData, Group == "ASD"),
              aes(x = tsl_acc, y = vsl_acc),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "#F8766d")
# +
#   stat_cor(data = subset(allData, Group == "TD"),
#               aes(x = tsl_acc, y = vsl_acc),
#            method = "pearson", label.x = 0.55, label.y = 0.95,
#            inherit.aes = F, color = "#00BFC4", size = 5) +
#     stat_cor(data = subset(allData, Group == "ASD"),
#               aes(x = tsl_acc, y = vsl_acc),
#              method = "pearson", label.x = 0.55, label.y = 0.3, 
#            inherit.aes = F, color = "#F8766d", size = 5)
#   #+ 
  #geom_text(aes(x = 20, y = 120, label = paste("rho =", "-0.76**")),color = "red",size=4)

# ggsave("bucld_tsl_vsl_corr.png",
       # width = 15, height = 15, units = "cm")
```




# LSL vs. VSL Acc (significant in ASD)
```{r}
library(ggpubr)
colnames(allData)[colnames(allData) == "group"] <- "Group"

pd <- position_dodge(width = 0.01)

allData %>%
ggplot(aes(x = lsl_acc, y = vsl_acc, color = Group)) +
  geom_point(size = 4, shape = 1, position = pd, stroke = 1.7) +
  scale_fill_brewer(palette = "Set2") +
      labs(title = "Letter and Image SL Accuracy Correlation",
         y = "letter SL Accuracy",  # Change x-axis label
         x = "Image SL Accuracy") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),
    legend.title = element_text(size = 16, face = "bold"),# Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) +
  geom_smooth(data = subset(allData, Group == "TD"),
              aes(x = lsl_acc, y = vsl_acc),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "#00BFC4") +
  geom_smooth(data = subset(allData, Group == "ASD"),
              aes(x = lsl_acc, y = vsl_acc),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "#F8766d") 
# +
#   stat_cor(data = subset(allData, Group == "TD"),
#               aes(x = lsl_acc, y = vsl_acc),
#            method = "pearson", label.x = 0.55, label.y = 0.95,
#            inherit.aes = F, color = "#00BFC4", size = 5) +
#     stat_cor(data = subset(allData, Group == "ASD"),
#               aes(x = lsl_acc, y = vsl_acc),
#              method = "pearson", label.x = 0.55, label.y = 0.3, 
#            inherit.aes = F, color = "#F8766d", size = 5)
  #+ 
  #geom_text(aes(x = 20, y = 120, label = paste("rho =", "-0.76**")),color = "red",size=4)

# ggsave("bucld_lsl_vsl_corr.png",
       # width = 15, height = 15, units = "cm")
```


# SSL vs. TSL Slope (reverse correlations in TD vs. ASD)
```{r}
library(ggpubr)
colnames(allData)[colnames(allData) == "group"] <- "Group"

pd <- position_dodge(width = 0.01)

allData %>%
ggplot(aes(x = ssl_slope, y = tsl_slope, color = Group)) +
  geom_point(size = 4, shape = 1, position = pd, stroke = 1.7) +
  scale_fill_brewer(palette = "Set2") +
      labs(title = "Syllable and Tone SL Slope Correlation",
         y = "Syllable SL Slope",  # Change x-axis label
         x = "Tone SL Slope") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),
    legend.title = element_text(size = 16, face = "bold"),# Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) +
  geom_smooth(data = subset(allData, Group == "TD"),
              aes(x = ssl_slope, y = tsl_slope),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "#00BFC4") +
  geom_smooth(data = subset(allData, Group == "ASD"),
              aes(x = ssl_slope, y = tsl_slope),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "#F8766d") 

# ggsave("bucld_lsl_vsl_corr.png",
       # width = 15, height = 15, units = "cm")
```


## Plot Age and Composite corr

```{r}
gjt_mulreg[which(gjt_mulreg$group == "TD"),] %>%
ggplot(aes(x = age_at_web_year, y = composite_score, color = domain)) +
  geom_point(size = 4, shape = 1, position = pd, stroke = 1.7) +
   scale_color_brewer(palette = "Set2") +
      labs(title = "Age and Composite SL score Correlation in TD",
         y = "Composite SL Score",  # Change x-axis label
         x = "Age") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),
    legend.title = element_text(size = 16, face = "bold"),# Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) +
  geom_smooth(data = gjt_mulreg[which(gjt_mulreg$group == "TD" & gjt_mulreg$domain == "composite_ling"),],
              aes(x = age_at_web_year, y = composite_score),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "dark green") +
  geom_smooth(data = gjt_mulreg[which(gjt_mulreg$group == "TD" & gjt_mulreg$domain == "composite_nonling"),],
              aes(x = age_at_web_year, y = composite_score),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "dark orange") +
  stat_cor(data = gjt_mulreg[which(gjt_mulreg$group == "TD" & gjt_mulreg$domain == "composite_ling"),],
              aes(x = age_at_web_year, y = composite_score),
           method = "pearson", label.x = 5, label.y = 0.95,
           inherit.aes = F, color = "dark green", size = 5) +
    stat_cor(data = gjt_mulreg[which(gjt_mulreg$group == "TD" & gjt_mulreg$domain == "composite_nonling"),],
              aes(x = age_at_web_year, y = composite_score),
             method = "pearson", label.x = 5, label.y = 0.3,
           inherit.aes = F, color = "dark orange", size = 5)


# ggsave("td_composite_age_corr.png", width = 20, height = 15, units = "cm")
```

```{r}
gjt_mulreg[which(gjt_mulreg$group == "ASD"),] %>%
ggplot(aes(x = age_at_web_year, y = composite_score, color = domain)) +
  geom_point(size = 4, shape = 1, position = pd, stroke = 1.7) +
   scale_color_brewer(palette = "Set2") +
      labs(title = "Age and Composite SL score Correlation in TD",
         y = "Composite SL Score",  # Change x-axis label
         x = "Age") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),
    legend.title = element_text(size = 16, face = "bold"),# Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) +
  geom_smooth(data = gjt_mulreg[which(gjt_mulreg$group == "ASD" & gjt_mulreg$domain == "composite_ling"),],
              aes(x = age_at_web_year, y = composite_score),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "dark green") +
  geom_smooth(data = gjt_mulreg[which(gjt_mulreg$group == "ASD" & gjt_mulreg$domain == "composite_nonling"),],
              aes(x = age_at_web_year, y = composite_score),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "dark orange") +
  stat_cor(data = gjt_mulreg[which(gjt_mulreg$group == "ASD" & gjt_mulreg$domain == "composite_ling"),],
              aes(x = age_at_web_year, y = composite_score),
           method = "pearson", label.x = 5, label.y = 0.95,
           inherit.aes = F, color = "dark green", size = 5) +
    stat_cor(data = gjt_mulreg[which(gjt_mulreg$group == "ASD" & gjt_mulreg$domain == "composite_nonling"),],
              aes(x = age_at_web_year, y = composite_score),
             method = "pearson", label.x = 5, label.y = 0.3,
           inherit.aes = F, color = "dark orange", size = 5)


# ggsave("compositeAge_age_corr.png", width = 20, height = 15, units = "cm")
```


## Plot Age and individual SL task corr
```{r}
allData %>%
ggplot(aes(x = age_at_web_year, y = lsl_slope, color = Group)) +
  geom_point(size = 4, shape = 1, position = pd, stroke = 1.7) +
  scale_fill_brewer(palette = "Set2") +
      labs(title = "Age and Letter SL RT Slope Correlation",
         y = "Letter SL RT Slope",  # Change x-axis label
         x = "Age") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),
    legend.title = element_text(size = 16, face = "bold"),# Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) +
  geom_smooth(data = subset(allData, Group == "TD"),
              aes(x = age_at_web_year, y = lsl_slope),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "#00BFC4") +
  geom_smooth(data = subset(allData, Group == "ASD"),
              aes(x = age_at_web_year, y = lsl_slope),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "#F8766d") +
  stat_cor(data = subset(allData, Group == "TD"),
              aes(x = age_at_web_year, y = lsl_slope),
           method = "pearson", label.x = 5, label.y = 0,
           inherit.aes = F, color = "#00BFC4", size = 5) +
    stat_cor(data = subset(allData, Group == "ASD"),
              aes(x = age_at_web_year, y = lsl_slope),
             method = "pearson", label.x = 5, label.y = 0.01, 
           inherit.aes = F, color = "#F8766d", size = 5)

# ggsave("paper_analysis_matched/sslSlope_age_corr.png",
#        width = 15, height = 15, units = "cm")
```

```{r}
allData %>%
ggplot(aes(x = age_at_web_year, y = vsl_acc, color = Group)) +
  geom_point(size = 4, shape = 1, position = pd, stroke = 1.7) +
  scale_fill_brewer(palette = "Set2") +
      labs(title = "Age and Image SL Accuracy Correlation",
         y = "Image SL Accuracy",  # Change x-axis label
         x = "Age") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),
    legend.title = element_text(size = 16, face = "bold"),# Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) +
  geom_smooth(data = subset(allData, Group == "TD"),
              aes(x = age_at_web_year, y = vsl_acc),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "#00BFC4") +
  geom_smooth(data = subset(allData, Group == "ASD"),
              aes(x = age_at_web_year, y = vsl_acc),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "#F8766d") +
  stat_cor(data = subset(allData, Group == "TD"),
              aes(x = age_at_web_year, y = vsl_acc),
           method = "pearson", label.x = 5, label.y = 0.95,
           inherit.aes = F, color = "#00BFC4", size = 5) +
    stat_cor(data = subset(allData, Group == "ASD"),
              aes(x = age_at_web_year, y = vsl_acc),
             method = "pearson", label.x = 5, label.y = 0.3, 
           inherit.aes = F, color = "#F8766d", size = 5)

# ggsave("paper_analysis_matched/vsl_age_corr.png",
#        width = 10, height = 15, units = "cm")

```


```{r}
allData %>%
ggplot(aes(x = age_at_web_year, y = ssl_acc, color = Group)) +
  geom_point(size = 4, shape = 1, position = pd, stroke = 1.7) +
  scale_fill_brewer(palette = "Set2") +
      labs(title = "Age and Syllable SL Accuracy Correlation",
         y = "Syllable SL Accuracy",  # Change x-axis label
         x = "Age") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),
    legend.title = element_text(size = 16, face = "bold"),# Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) +
  geom_smooth(data = subset(allData, Group == "TD"),
              aes(x = age_at_web_year, y = ssl_acc),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "#00BFC4") +
  geom_smooth(data = subset(allData, Group == "ASD"),
              aes(x = age_at_web_year, y = ssl_acc),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "#F8766d") +
  stat_cor(data = subset(allData, Group == "TD"),
              aes(x = age_at_web_year, y = ssl_acc),
           method = "pearson", label.x = 5, label.y = 0.95,
           inherit.aes = F, color = "#00BFC4", size = 5) +
    stat_cor(data = subset(allData, Group == "ASD"),
              aes(x = age_at_web_year, y = ssl_acc),
             method = "pearson", label.x = 5, label.y = 0.3, 
           inherit.aes = F, color = "#F8766d", size = 5)

# ggsave("paper_analysis_matched/ssl_age_corr.png",
#        width = 15, height = 15, units = "cm")

```

```{r}
allData %>%
ggplot(aes(x = age_at_web_year, y = ssl_slope, color = Group)) +
  geom_point(size = 4, shape = 1, position = pd, stroke = 1.7) +
  scale_fill_brewer(palette = "Set2") +
      labs(title = "Age and Syllable SL RT Slope Correlation",
         y = "Syllable SL RT Slope",  # Change x-axis label
         x = "Age") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),
    legend.title = element_text(size = 16, face = "bold"),# Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) +
  geom_smooth(data = subset(allData, Group == "TD"),
              aes(x = age_at_web_year, y = ssl_slope),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "#00BFC4") +
  geom_smooth(data = subset(allData, Group == "ASD"),
              aes(x = age_at_web_year, y = ssl_slope),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "#F8766d") +
  stat_cor(data = subset(allData, Group == "TD"),
              aes(x = age_at_web_year, y = ssl_slope),
           method = "pearson", label.x = 5, label.y = 0,
           inherit.aes = F, color = "#00BFC4", size = 5) +
    stat_cor(data = subset(allData, Group == "ASD"),
              aes(x = age_at_web_year, y = ssl_slope),
             method = "pearson", label.x = 5, label.y = 0.01, 
           inherit.aes = F, color = "#F8766d", size = 5)

# ggsave("paper_analysis_matched/sslSlope_age_corr.png",
#        width = 15, height = 15, units = "cm")
```


```{r}
allData %>%
ggplot(aes(x = age_at_web_year, y = tsl_acc, color = Group)) +
  geom_point(size = 4, shape = 1, position = pd, stroke = 1.7) +
  scale_fill_brewer(palette = "Set2") +
      labs(title = "Age and Tone SL Accuracy Correlation",
         y = "Tone SL Accuracy",  # Change x-axis label
         x = "Age") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),
    legend.title = element_text(size = 16, face = "bold"),# Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) +
  geom_smooth(data = subset(allData, Group == "TD"),
              aes(x = age_at_web_year, y = tsl_acc),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "#00BFC4") +
  geom_smooth(data = subset(allData, Group == "ASD"),
              aes(x = age_at_web_year, y = tsl_acc),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "#F8766d") +
  stat_cor(data = subset(allData, Group == "TD"),
              aes(x = age_at_web_year, y = tsl_acc),
           method = "pearson", label.x = 5, label.y = 0.95,
           inherit.aes = F, color = "#00BFC4", size = 5) +
    stat_cor(data = subset(allData, Group == "ASD"),
              aes(x = age_at_web_year, y = tsl_acc),
             method = "pearson", label.x = 5, label.y = 0.3, 
           inherit.aes = F, color = "#F8766d", size = 5)

# ggsave("srcd_figure/tsl_age_corr.png",
       # width = 10, height = 15, units = "cm")
```

# Plot Accuracy and RT Slope Correlation
```{r}
allData %>%
ggplot(aes(x = lsl_slope, y = lsl_acc, color = Group)) +
  geom_point(size = 4, shape = 1, position = pd, stroke = 1.7) +
  scale_fill_brewer(palette = "Set2") +
      labs(title = "Letter SL Accuracy and RT Slope Correlation",
         y = "Letter SL Accuracy",  # Change x-axis label
         x = "Letter SL RT Slope (arbitrary unit/ trial)") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),
    legend.title = element_text(size = 16, face = "bold"),# Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) +
  geom_smooth(data = subset(allData, Group == "TD"),
              aes(x = lsl_slope, y = lsl_acc),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "#00BFC4") +
  geom_smooth(data = subset(allData, Group == "ASD"),
              aes(x = lsl_slope, y = lsl_acc),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "#F8766d") +
  stat_cor(data = subset(allData, Group == "TD"),
              aes(x = lsl_slope, y = lsl_acc),
           method = "pearson", label.x = 0, label.y = 0.95,
           inherit.aes = F, color = "#00BFC4", size = 5) +
    stat_cor(data = subset(allData, Group == "ASD"),
              aes(x = lsl_slope, y = lsl_acc),
             method = "pearson", label.x = 0, label.y = 0.3, 
           inherit.aes = F, color = "#F8766d", size = 5)

# ggsave("srcd_figure/acc_slope_lslCorr.png",
       # width = 15, height = 15, units = "cm")
```


```{r}
allData %>%
ggplot(aes(x = ssl_slope, y = ssl_acc, color = Group)) +
  geom_point(size = 4, shape = 1, position = pd, stroke = 1.7) +
  scale_fill_brewer(palette = "Set2") +
      labs(title = "Syllable SL Accuracy and RT Slope Correlation",
         y = "Syllable SL Accuracy",  # Change x-axis label
         x = "Syllable SL RT Slope (arbitrary unit/ trial)") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),
    legend.title = element_text(size = 16, face = "bold"),# Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) +
  geom_smooth(data = subset(allData, Group == "TD"),
              aes(x = ssl_slope, y = ssl_acc),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "#00BFC4") +
  geom_smooth(data = subset(allData, Group == "ASD"),
              aes(x = ssl_slope, y = ssl_acc),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "#F8766d") +
  stat_cor(data = subset(allData, Group == "TD"),
              aes(x = ssl_slope, y = ssl_acc),
           method = "pearson", label.x = 0, label.y = 0.95,
           inherit.aes = F, color = "#00BFC4", size = 5) +
    stat_cor(data = subset(allData, Group == "ASD"),
              aes(x = ssl_slope, y = ssl_acc),
             method = "pearson", label.x = 0, label.y = 0.3, 
           inherit.aes = F, color = "#F8766d", size = 5) 

# ggsave("srcd_figure/acc_slope_sslCorr.png",
       # width = 10, height = 15, units = "cm")
```






```{r}
library(ggpubr)

pd <- position_dodge(width = 0.01)

compositeAge %>%
ggplot(aes(x = composite_ssl, y = composite_lsl, color = age_group)) +
  geom_point(size = 4, shape = 1, position = pd, stroke = 1.7) +
  scale_fill_brewer(palette = "Set1") +
      labs(title = "Syllable and Letter SL Composite Score Correlation",
         y = "Letter SL Composite Score",  # Change x-axis label
         x = "Syllable SL Composite Score") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),
    legend.title = element_text(size = 16, face = "bold"),# Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) +
  geom_smooth(data = subset(compositeAge, age_group == "Younger TD"),
              aes(x = composite_ssl, y = composite_lsl),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "purple") +
  geom_smooth(data = subset(compositeAge, age_group == "Older TD"),
              aes(x = composite_ssl, y = composite_lsl),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "dark green") +
  geom_smooth(data = subset(compositeAge, age_group == "Older ASD"),
              aes(x = composite_ssl, y = composite_lsl),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "red") +
   geom_smooth(data = subset(compositeAge, age_group == "Younger ASD"),
              aes(x = composite_ssl, y = composite_lsl),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "light blue") +
  stat_cor(data = subset(compositeAge, age_group == "Younger TD"),
              aes(x = composite_ssl, y = composite_lsl),
           method = "pearson", label.x = 0.55, label.y = 0.92,
           inherit.aes = F, color = "purple", size = 5) +
    stat_cor(data = subset(compositeAge, age_group == "Older TD"),
              aes(x = composite_ssl, y = composite_lsl),
             method = "pearson", label.x = 0.55, label.y = 0.6, 
           inherit.aes = F, color = "dark green", size = 5) +
   stat_cor(data = subset(compositeAge, age_group == "Older ASD"),
              aes(x = composite_ssl, y = composite_lsl),
             method = "pearson", label.x = 0.55, label.y = -1, 
           inherit.aes = F, color = "red", size = 5) + 
   stat_cor(data = subset(compositeAge, age_group == "Younger ASD"),
              aes(x = composite_ssl, y = composite_lsl),
             method = "pearson", label.x = 0.55, label.y = -0.3, 
           inherit.aes = F, color = "light blue", size = 5)
  #+ 
  #geom_text(aes(x = 20, y = 120, label = paste("rho =", "-0.76**")),color = "red",size=4)

# ggsave("srcd_figure/bucld_ssl_lsl_corr.png",
       # width = 15, height = 15, units = "cm")
```


```{r}
compositeAge %>%
ggplot(aes(x = composite_tsl, y = composite_vsl, color = age_group)) +
  geom_point(size = 4, shape = 1, position = pd, stroke = 1.7) +
  scale_fill_brewer(palette = "Set1") +
      labs(title = "Tone and Image SL Composite Score Correlation",
         y = "Letter SL Composite Score",  # Change x-axis label
         x = "Syllable SL Composite Score") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),
    legend.title = element_text(size = 16, face = "bold"),# Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) +
  geom_smooth(data = subset(compositeAge, age_group == "Younger TD"),
              aes(x = composite_tsl, y = composite_vsl),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "purple") +
  geom_smooth(data = subset(compositeAge, age_group == "Older TD"),
              aes(x = composite_tsl, y = composite_vsl),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "dark green") +
  geom_smooth(data = subset(compositeAge, age_group == "Older ASD"),
              aes(x = composite_tsl, y = composite_vsl),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "red") +
   geom_smooth(data = subset(compositeAge, age_group == "Younger ASD"),
              aes(x = composite_tsl, y = composite_vsl),
              method=lm, se=FALSE, show.legend = F, inherit.aes = F, color = "light blue") +
  stat_cor(data = subset(compositeAge, age_group == "Younger TD"),
              aes(x = composite_tsl, y = composite_vsl),
           method = "pearson", label.x = 0.55, label.y = 0.92,
           inherit.aes = F, color = "purple", size = 5) +
    stat_cor(data = subset(compositeAge, age_group == "Older TD"),
              aes(x = composite_tsl, y = composite_vsl),
             method = "pearson", label.x = 0.55, label.y = 0.6, 
           inherit.aes = F, color = "dark green", size = 5) +
   stat_cor(data = subset(compositeAge, age_group == "Older ASD"),
              aes(x = composite_tsl, y = composite_vsl),
             method = "pearson", label.x = 0.55, label.y = -1, 
           inherit.aes = F, color = "red", size = 5) + 
   stat_cor(data = subset(compositeAge, age_group == "Younger ASD"),
              aes(x = composite_tsl, y = composite_vsl),
             method = "pearson", label.x = 0.55, label.y = -0.3, 
           inherit.aes = F, color = "light blue", size = 5)
```


```{r}
installed.packages()[names(sessionInfo()$otherPkgs), "Version"]
```



# Update on SRCD:



# K-means of SL accuracy (TD + ASD, TD vs. ASD did not differ that much overall in optimal clusters)
```{r}
gjt_sl <- compositeAge[,c("part_id", "group", "vsl_accScaled", "tsl_accScaled", "ssl_accScaled", "lsl_accScaled", "gjt_std")]

completeRow <- complete.cases(gjt_sl)

completeSL <- gjt_sl[completeRow,]

# completeSL <- completeSL[which(completeSL$group == "TD"),]
# completeSL <- completeSL[which(completeSL$group == "ASD"),]
completeSL <- completeSL



# completeSL[,3:6] <- scale(completeSL[,3:6])

# determine the optimal number of clusters
## Elbow method for k-means clustering - optimal number of cluster is ?
set.seed(123)
### Compute and plot wss for k = 2 to k = 8
k.max <- 8 # Maximal number of clusters
data <- completeSL[,3:6]
wss <- sapply(1:k.max, 
              function(k){kmeans(data, k, nstart=10)$tot.withinss})

plot(1:k.max, wss,
     type="b", pch = 19, frame = FALSE, 
     xlab="Number of clusters K",
     ylab="Total within-clusters sum of squares") 

### alternatively,
library(factoextra)
fviz_nbclust(completeSL[,3:6], kmeans, method = "wss") 
```

# K-means with 5 clusters based on Elbow method
```{r}
set.seed(123)
kcluster <- kmeans(completeSL[, 3:6], 4, nstart = 10)
str(kcluster)
print(kcluster)
# Plotting the Elbow method in clusters
```
Notes:
K = 5
Cluster 1 (n = 3): High Accuracy in all SL 
Cluster 2 (n = 14): Low Accuracy in Letter  SL
Cluster 3 (n = 9): High Accuracy in Linguistic SL 
Cluster 4 (n = 3): Low Accuracy4in Syllable  SL

**The order of the clusters may be different when the script is run. However, the cluster sizes are replicable.**



# Plot K-means 5 clusters
```{r, include = F}
clusterP <- completeSL
clusterP$cluster <- kcluster$cluster
clusterP$cluster <- as.factor(clusterP$cluster)

clusterGJT <- 
  merge(clusterP[,c("part_id", "group", "cluster")], 
      allData[c("part_id", "a_prime", "gjt_std")], all.x = T)

clusterGJT$cluster <- as.factor(clusterGJT$cluster)


 clusterGJT$cluster <-
  factor(clusterGJT$cluster,levels = c("2","4","3", "1"))
 
clusterGJT <-
  clusterGJT[order(clusterGJT$cluster), ]

clusterGJT$cluster <-
plyr::revalue(clusterGJT$cluster, c("2" = "1",
                                    "4" = "2",
                                    "3" = "3", 
                                    "1" = "4"))

colorTemp <- c("#999999", "#E69F00", "#009E73", 
               "#AC5150")

library(ggbeeswarm)



ggplot(data=clusterGJT, aes(x=cluster, y= gjt_std, fill = cluster)) +
  geom_bar(stat= "summary", fun.y = "mean", color ="black", width = 0.83)+
  geom_point(aes(color = group),
             position = position_dodge(0.35),
             size = 4) +
  scale_color_manual(values = c("#F8766d", "#00BFC4"),
                     guide = guide_legend(title="Group")) +
  scale_fill_manual(values= colorTemp,
                    labels = c("Low Accuracy in Letter  SL",
                                 "Low Accuracy in Syllable  SL",
                                 "High Accuracy in Linguistic SL",
                                 "High Accuracy in all SL"),
                    guide = guide_legend(title="Cluster based on \n SL accuracy",
                                        override.aes = list(shape = NA)
                                        )) +
  labs(
         y = "Grammaticality Judgment Standard Score",  # Change axis label
         x = "Cluster"
        ) + 
  theme(
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold"),
        legend.title=element_text(size=15, face="bold")) +
  theme(legend.text=element_text(size=14, face="bold"),
        legend.title=element_text(size=15, face="bold")) +
  theme(
    panel.background = element_rect(fill = "white"),         # Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1),   # Add line to y axis
    panel.grid.minor = element_line(colour = "grey", size = 0.3),
    panel.grid.major = element_line(colour = "grey", size = 0.3)
  ) 

# ggsave("k_means_five_clusters_gjt_across_groups.png", bg="transparent", width = 25, height = 20, units = "cm")
```


