---
title: "trim_event_file"
author: "Jojo Hu"
date: "2/11/2022"
output: html_document
---

# Clean by trial event files for fMRI block analysis
```{r}
# Change paths to NAS (input path need to be created on NAS: change /Users/jojohu/Documents/Qlab/fmri/data/child/gen_eve_from_log_child.py script output to NAS )
input_path <- "/Volumes/data/projects/blast/data/derivatives/event_files/adults_new"
output_path <- "/Volumes/data/projects/blast/data/derivatives/event_files/adults_new/"

longeve <- list.files(path = input_path,
                       pattern = "*\\.txt$", full.names = T)

# Function to clean the raw event files
clean_event_file <- function(df) {
  # Set up a variable
  weird_event <- NA
  
  file_name <- basename(df)
  file_name <- str_extract(file_name, "\\S+(?=.txt?)")
  
  df <- read.csv(df,  sep ="\t", stringsAsFactors = F, header = T)
  
  # If the raw event file is not empty:
  if(nrow(df) > 0) {
    df[, "name"] <- file_name
  
    # If the condition in the current trial does not = the condition in the previous trial, then this current trial is the first trial of the block
    df[, "prev_cond"] <- append("place_holder", df$condition[1:(length(df$condition)-1)]) 
    # If the condition in the current trial does not = the condition in the next trial, then this current trial is the last trial of the block
    df[, "next_cond"] <- append(df$condition[2:length(df$condition)], "place_holder") 
    
    # Add mini block numbers
    df[which(df$condition != df$prev_cond), "mini_block"] <-
      seq(1:nrow(df[which(df$condition != df$prev_cond),]))
    
    library(dplyr)
    library(tidyr)
    df <-
      df %>% 
      tidyr::fill(mini_block, .direction = "down")
    
    # Add stimuli type (tone, syllable, rest, image, letter rest)
    if("soundFile" %in% colnames(df)) {
      # If the event file is ASL, find tone, syllable, rest
      df$soundFile <- str_trim(df$soundFile) 
      df[which(str_detect(df$soundFile, "[:digit:][:upper:]")), "stimuli"] <- "tone"
      df[which(str_detect(df$soundFile, "[:lower:][:lower:]$")), "stimuli"] <- "syllable"
      df[which(str_detect(df$soundFile, "silence")), "stimuli"] <- "rest"
    } else if ("image" %in% colnames(df)) {
       # If the event file is VSL, find image, letter, rest
      df$image <- str_trim(df$image) 
      df[which(str_detect(df$image, "[:alpha:]+[:digit:]+")), "stimuli"] <- "image"
      df[which(str_detect(df$image, "[:upper:]$")), "stimuli"] <- "letter"
      df[which(str_detect(df$image, "blank")), "stimuli"] <- "rest"
    }
    
    # If the condition in the current trial does not = the condition in the previous trial, then this current trial is the first trial of the block
    first_trials <- df[which(df$condition != df$prev_cond), c("onset", "name", "condition", "mini_block", "stimuli")]
    # If the condition in the current trial does not = the condition in the next trial, then this current trial is the last trial of the block
    last_trials <- df[which(df$condition != df$next_cond), c("onset", "name", "condition", "mini_block", "stimuli")]
    
    # Get the duration of each block
    colnames(last_trials)[which(colnames(last_trials) == "onset")] <- "onset_last"
    
    short_eve <- merge(first_trials, last_trials, by = c("condition", "name", "mini_block", "stimuli"))
    
    short_eve <- 
      short_eve %>%
      # Must arrange by mini block order first, and then by stimuli onset, because some event files have more than 12 blocks; and then the onset of the 13th block resets and starts again
      arrange(mini_block, onset)
    
    # If an event file has 24 blocks, that means the run was administered twice, only keep the later 24 blocks
    if(max(short_eve$mini_block) > 12) {
      # Get where the run was administered twice in the event file
      print(short_eve)
      
      first_usable_block <-
        short_eve %>%
        mutate(diff = onset - lag(onset))  %>%
        filter(diff < 0) %>%
        dplyr::select(mini_block) 
      
      # Save the later blocks
      if (nrow(first_usable_block) == 1) {
        short_eve <-
          short_eve %>%
          filter(mini_block > first_usable_block$mini_block | mini_block == first_usable_block$mini_block) %>%
          mutate(mini_block = seq(1:nrow(.)))

      } else if (nrow(first_usable_block) != 1) {
        
        print("This event file is weird:")
        print(short_eve)
        # Deal with weird event files case by case if needed
      
      }
    }
    
    # Cleaned event files should have 12 blocks only
    if(max(short_eve$mini_block) != 12) {
      weird_event <- short_eve
    }
    
    short_eve$duration <- short_eve$onset_last - short_eve$onset
    
    this_file_name <- unique(short_eve$name)
    this_file_name <-
      paste0(str_extract(this_file_name, "sub-blasta[:digit:]+"), "_task-", str_extract(this_file_name, "[:alpha:]sl_run"), "-0",
             str_extract(this_file_name,"(?<=run_)[:digit:]"), "_events.tsv")
  
    short_eve <- short_eve[,c("onset", "duration", "stimuli", "condition")]
    
    # Get rid of trailing white space and only keep the random 
    short_eve$condition <- gsub(" ", "", short_eve$condition)
    
    short_eve$stimcond <- paste0(short_eve$stimuli, short_eve$condition)
    
    short_eve[which(short_eve$stimcond == "restB"), "stimcond"] <- "rest"
    
    if(nrow(df[complete.cases(short_eve),]) != nrow(df)) {
      print(paste(this_file_name, "this file has NA"))
      print(short_eve)
    }
    write.table(short_eve, paste0(output_path, this_file_name), sep='\t', row.names = F)
  }
  return(weird_event)
}

# Run the functino to clean the raw event files; No need to save the output of the function as files are saved in the function; place_holder just to prevent printing of lapply
place_holder <- lapply(longeve, clean_event_file)
```




# Change imaging file names to make sure fMRI data runs match with behavioral data runs
## Compile Runs for all Participants
```{r}
input_path2 <- "/Volumes/data/projects/blast/data/mri/in_scanner_behavioral/sl_raw_data/adult/sl_raw_data"

csvFile <- list.files(path = input_path2,
                       pattern = "*blast_a_\\S+_(auditory|visual)\\S+.csv$", full.names = T)

validFile <- list()

read_behdata <- function(df) {
  fileTemp <- read.csv(df, stringsAsFactors = F)
  
  if(nrow(fileTemp) > 0) {
    # Corrected IDs in blast_a_026_auditory_2.csv and blast_a_026_auditory_3.csv files due to wrong IDs used during MRI administration
    # if(basename(df) == "blast_a_026_auditory_2.csv" | basename(df) == "blast_a_026_auditory_3.csv") {
    #   print(df)
    # }
    
    fileTemp[,c("file_name")] <- basename(df)
    fileTemp$repetition <- as.character(fileTemp$repetition)
    fileTemp$frameRate <- as.character(fileTemp$frameRate)
    fileTemp$PartID <- as.character(fileTemp$PartID)
    
    if(length(which(colnames(fileTemp) %in% "ltarget")) > 0) {
        fileTemp[,c("ltarget")] <- as.character(fileTemp[,c("ltarget")])
      }
  }
  return(fileTemp)
}

validFile <- lapply(csvFile, read_behdata)
validFile <- validFile[lapply(validFile,nrow)>0]

validFile <- do.call(dplyr::bind_rows, validFile)

dateRun <- validFile[,c("PartID", "date", "Run", "file_name")]

dateRun$task <- str_extract(dateRun$file_name, "(auditory|visual)")

dateRun$year_month_date <- str_extract(dateRun$date, "\\S+_\\S+_\\S+(?=_)")

dateRun$date_formatted <- as.Date(dateRun$year_month_date, "%Y_%b_%d")

dateRun$time <- sub('.*_', '', dateRun$date)

# Should return zero
dateRun %>%
  filter(str_detect(PartID, "blast_c"))


# Correct wrong naming in the raw data file
# dateRun[which(dateRun$PartID == "blast_c_0612"),]$PartID <- "blast_c_061"
```


## Manually Check the participants that have duplicated runs or irregular run orders
```{r}
# https://stackoverflow.com/questions/15933958/collapse-concatenate-aggregate-a-column-to-a-single-comma-separated-string-w

checkOrder <-
  dateRun %>%
  dplyr::select(PartID, task, date_formatted, time, Run) %>%
  dplyr::distinct(.) %>%
  mutate(date_formatted = as.Date(date_formatted),
         Run = as.factor(Run)) %>%
  arrange(PartID, task, date_formatted, time) %>%
  distinct(PartID, task, Run, .keep_all = TRUE) %>%
  group_by(PartID, task) %>%
  dplyr::filter(n() == 4) %>%
  summarise(run = toString(Run)) %>%
  ungroup() %>%
  filter(run != "1, 2, 3, 4" & run!= "3, 4, 1, 2")  %>%
  mutate(notes = "This is a subject with irregularly-ordered runs. Please check their runsheet to see if the runs were indeed ordered this way and leave notes on this spreadsheet.")
  
duplicatedRun <-
  dateRun %>%
  dplyr::select(PartID, task, date_formatted, time, Run) %>%
  dplyr::distinct(.) %>%
  mutate(date_formatted = as.Date(date_formatted),
         Run = as.factor(Run)) %>%
  arrange(PartID, task, date_formatted, time) %>%
  group_by(PartID, task, Run) %>%
  filter(n() > 1) %>%
  distinct(PartID, .keep_all = F) %>%
  dplyr::rename(run = Run) %>%
  mutate(notes = "This is the duplicated run in the in_scanner_behavioral data folder. Please remove the corresponding incomplete run from the behavioral and imaging data (bids and fmriprep).")

checkRun <- rbind(as.data.frame(duplicatedRun), as.data.frame(checkOrder))

write.csv(checkRun, "/Users/jojohu/Documents/Qlab/fmri/data/adult/manual_check_run.csv")
```

## Check what bids data exsitf
```{r}
bidsEvent <-
  list.files(path = "/Volumes/data/projects/blast/data/bids", pattern = "blast_*", recursive = F, full.names = T)

bidsEvent <- paste0(bidsEvent, "/func")

bidsEvent <- list.files(path = bidsEvent, pattern = "*\\_bold.nii.gz$", recursive = F, full.names = T)

bidsBold <- as.data.frame(bidsEvent)

bidsEvent <- as.data.frame(bidsEvent)

bidsEvent$PartID <- str_extract(bidsEvent$bidsEvent, "(?<=func/sub-blast(c|a))\\S+(?=_task)")

if(length(which(str_detect(bidsEvent$bidsEvent, "blastc"))) > 0) {
  bidsEvent[which(str_detect(bidsEvent$bidsEvent, "blastc")), "PartID"] <-
  paste0("blast_c_", bidsEvent[which(str_detect(bidsEvent$bidsEvent, "blastc")), "PartID"])
}

if(length(which(str_detect(bidsEvent$bidsEvent, "blasta"))) > 0) {
  bidsEvent[which(str_detect(bidsEvent$bidsEvent, "blasta")), "PartID"] <-
  paste0("blast_a_", bidsEvent[which(str_detect(bidsEvent$bidsEvent, "blasta")), "PartID"])
}

bidsEvent$task <- str_extract(bidsEvent$bidsEvent, "(?<=task-)\\S+(?=_run)")
bidsEvent$task <- gsub("asl", "auditory", bidsEvent$task)
bidsEvent$task <- gsub("vsl", "visual", bidsEvent$task)

bidsEvent$Run <- str_extract(bidsEvent$bidsEvent, "(?<=_run-0)\\S+(?=_bold)")

if (length(-which(str_detect(bidsEvent$bidsEvent, "incomplete"))) > 0) {
  bidsEvent <- bidsEvent[-which(str_detect(bidsEvent$bidsEvent, "incomplete")),]
}

# Manually correct some run numbers. This is working backwards from missingEvent and missingPreprocess generated below. If we eventually find these bids or behavioral runs, will remove these lines below:

# blast_a_057 Run 1 bids is partially completed and should be removed from bids data analyses
bidsEvent <- bidsEvent[-which(bidsEvent$PartID == "blast_a_057" & bidsEvent$task == "auditory" & bidsEvent$Run == 1),]
# blast_a_071 cannot hear Run 1; so run 1 bids is not usable; run 2 and 3 bids correspond to run 3 and 1 event files
bidsEvent <- bidsEvent[-which(bidsEvent$PartID == "blast_a_071" & bidsEvent$task == "auditory" & bidsEvent$Run == 1),]
# blast_a_008 is missing behavioral run 1, so removing run 1 from bids data analyses
bidsEvent <- bidsEvent[-which(bidsEvent$PartID == "blast_a_008" & bidsEvent$task == "auditory" & bidsEvent$Run == 1),]
# blast_a_001 Behavioral Log File run 2 has formatting problems, so removing run 2 from bids data analysis; not necessary because behavioral .csv files exist for all 4 runs
# bidsEvent <- bidsEvent[-which(bidsEvent$PartID == "blast_a_001" & bidsEvent$task == "auditory" & bidsEvent$Run == 2),]


bidsEvent <-
  bidsEvent %>%
  arrange(PartID, task, Run) %>%
  filter(task == "auditory" | task == "visual") %>%
  group_by(PartID, task) %>%
  dplyr::summarise(bids_run = toString(Run)) %>%
  ungroup()
```


# Check all the order of the bids run based on Acquisition Time .json files
# All bids should be in an ascending order
```{r}
# Read in bids json files
bidsJson <-
  list.files(path = "/Volumes/data/projects/blast/data/bids", pattern = "blast_*", recursive = F, full.names = T)

bidsJson <- paste0(bidsJson, "/func")

bidsJson <- list.files(path = bidsJson, pattern = "*\\_bold.json$", recursive = F, full.names = T)

library("jsonlite")
# Extract acquisition time
readTime <- function(df) {
  tempJSON <- fromJSON(df, flatten=TRUE)
  acq_time <- as.POSIXlt(tempJSON$AcquisitionTime,format="%H:%M:%S")
  
  acq <- as.data.frame(acq_time)
  
  acq$file_name <- basename(df)
  
  return(acq)
}

jsonDF <- lapply(bidsJson, readTime)
jsonDFL <- do.call(dplyr::bind_rows, jsonDF)

jsonDFL <-
  jsonDFL %>%
  mutate(PartID = str_extract(file_name, "blast\\S+[:digit:]{3}"), 
         Run = str_extract(file_name, "(?<=_run-0)[:digit:]{1}"),
         task = str_extract(file_name, "langloc|asl|vsl|rest")) 

# Check that the timing of the 4 bids runs (1, 2, 3, 4) should be in an ascending order. Output should be zero:
jsonDFL %>%
  filter(task == "asl" | task == "vsl") %>%
  arrange(PartID, task, acq_time) %>%
  group_by(PartID, task) %>%
  mutate(Run = as.numeric(as.character(Run))) %>%
  mutate(diff = Run - lag(Run)) %>%
  filter(diff > 1)
  
```


## Check the run orders that do not match between preprocessed data and in-scanner-behavioral data
```{r}
# Manually correct some run numbers. This is working backwards from missingEvent and missingPreprocess generated below. If we eventually find these bids or behavioral runs, will remove these lines below:
# Bids file run 4 are missing for these two IDs, so get rid of the behavioral run:
dateRun <- dateRun[-which(dateRun$PartID == "blast_a_015" & dateRun$task == "auditory" & dateRun$Run == 4),] 
dateRun <- dateRun[-which(dateRun$PartID == "blast_a_026" & dateRun$task == "auditory" & dateRun$Run == 4),]

runOnly <-
  dateRun %>%
  dplyr::select(PartID, task, date_formatted, time, Run) %>%
  dplyr::distinct(.) %>%
  mutate(date_formatted = as.Date(date_formatted)) %>%
  arrange(PartID, task, date_formatted, time) %>%
  dplyr::select(PartID, task, Run) %>%
  dplyr::distinct(.) %>%
  group_by(PartID, task) %>%
  summarise(run_order = toString(Run)) %>%
  ungroup()
```



```{r}
# Already found all of these csv files: blast_a_012 is not missing any event files, but just missing .csv files.
# runOnly[which(runOnly$PartID == "blast_a_012" & runOnly$task == "auditory"), "run_order"] <- "1, 2, 3, 4"
# blast_a_026 is not missing any event files, but just missing .csv files
# runOnly[which(runOnly$PartID == "blast_a_026" & runOnly$task == "auditory"), "run_order"] <- "1, 2, 3, 4"
# # blast_a_054 is not missing any event files, but just missing .csv files
# runOnly[-which(runOnly$PartID == "blast_a_054" & runOnly$task == "auditory"), "run_order"] <- "3, 4, 1, 2"
```



```{r}
runOnly <- merge(runOnly, unique(bidsEvent), by = c("PartID", "task"), all.x = T)

runOnly$event_count <- str_count(runOnly$run_order, "[0-9]")
runOnly$bids_count <- str_count(runOnly$bids_run, "[0-9]")

missingEvent <- runOnly[which(runOnly$event_count < runOnly$bids_count),]


missingPreprocessed <-
runOnly %>%
  filter(!is.na(run_order)) %>%
  filter(bids_count < event_count | is.na(bids_run))
  

mismatchRun <-
  runOnly[which(!runOnly$run_order %in% runOnly$bids_run),] %>%
  # filter(!is.na(bids_run)) %>%
  filter(event_count != bids_count)



write.csv(missingEvent, "/Users/jojohu/Documents/Qlab/fmri/data/adult/missing_event_file.csv")
write.csv(missingPreprocessed, "/Users/jojohu/Documents/Qlab/fmri/data/adult/missing_preprocessed.csv")
write.csv(runOnly, "/Users/jojohu/Downloads/blast_dev_adult_event_run_order.csv", row.names = F)
```


## Change event file names to match with actual imaging data sequence names
```{r}
# Only change event file names for those who have correct number of runs preprocessed
changeRun <-
  runOnly %>%
  filter(run_order != "1, 2, 3, 4") %>%
  filter(run_order != bids_run) %>%
  filter(event_count == bids_count)

changeRun <- merge(changeRun,  
                   unique(dateRun[,c("PartID", "task", "Run", "file_name", "date_formatted", "time")]),
                   all.x = T)

changeRun <-
  changeRun %>%
  arrange(PartID, task, date_formatted, time)


## Read in original event files
eventFile <- list.files(path = input_path,
                        pattern = "*\\.tsv$", full.names = T)

eventFile <- as.data.frame(eventFile)
eventFile$PartID <- str_extract(eventFile$eventFile, "(?<=-blast(c|a))\\S+(?=_task)")

if(length(which(str_detect(eventFile$eventFile, "blastc"))) > 0) {
  eventFile[which(str_detect(eventFile$eventFile, "blastc")), "PartID"] <-
  paste0("blast_c_", eventFile[which(str_detect(eventFile$eventFile, "blastc")), "PartID"])
}

if(length(which(str_detect(eventFile$eventFile, "blasta"))) > 0) {
  eventFile[which(str_detect(eventFile$eventFile, "blasta")), "PartID"] <-
  paste0("blast_a_", eventFile[which(str_detect(eventFile$eventFile, "blasta")), "PartID"])
}

eventFile$task <- str_extract(eventFile$eventFile, "(?<=task-)\\S+(?=_run)")
eventFile$task <- ifelse(eventFile$task == "asl", "auditory", "visual")

eventFile$Run <- str_extract(eventFile$eventFile, "(?<=_run-0)\\S+(?=_events)")

changeRun <- merge(changeRun, eventFile, by = c("PartID", "task", "Run"), all.x = T)

                      
# dir.create(file.path("/Volumes/data/projects/blast/data/derivatives/event_files/children_new/", "original_event_files"))
changeRun$basename <- basename(as.character(changeRun$eventFile))
changeRun$eventFile <- as.character(changeRun$eventFile)
changeRun$archive <- paste0("/Volumes/data/projects/blast/data/derivatives/event_files/adults_new/original_event_files/", changeRun$basename)

file.rename(as.character(changeRun$eventFile), changeRun$archive)
```


## Change event file names for those who have matching number of behavioral runs and bids runs (all subjects' ASL data should have been matched before this section)
```{r}
changeRun1 <-
  changeRun 
  # filter(bids_count == 4)

# Some subjects have more than 1 csv files for each run because the run was adminstered multiple times
changeRun1 <-
  changeRun1 %>%
  group_by(PartID, task, Run) %>%
  filter(row_number() == n())

# Reorder the data based on behavioral run order and bids run order
# Get behavioral run order
splitOrder <- 
  as.data.frame(do.call(rbind, str_split(str_pad(str_remove_all(changeRun1$run_order, ", "), 4, pad = "0", side = "right"), "")))

colnames(splitOrder) <- c("run1_name", "run2_name", "run3_name", "run4_name")

splitOrder <- as.data.frame(splitOrder)

changeRun1 <- dplyr::bind_cols(changeRun1, splitOrder)

# Put behavioral run order back to dataframe and reorder data
changeRun1 <- 
  changeRun1 %>%
  mutate(behavioral_order = ifelse(Run == run1_name, 1, ifelse(Run == run2_name, 2, ifelse(Run == run3_name, 3, ifelse(Run == run4_name, 4, NA)))))

changeRun1 <- 
  changeRun1 %>%
  arrange(PartID, task, behavioral_order)

# Get bids run order
uniqueBids <-
  changeRun1 %>%
  group_by(PartID, task) %>%
  filter(row_number() == 1) %>%
  dplyr::select(PartID, task, bids_run)

changeRun1$bids_order <- unlist(str_split(uniqueBids$bids_run, ", "))

# Check that the added bids order are correct. Bids runs are in ascending order, so:
changeRun1 %>%
  group_by(PartID, task) %>%
  mutate(check_bids_order = seq(1:n())) %>%
  filter(bids_order != check_bids_order)

changeRun1$renameFile <- str_replace(changeRun1$archive, "(?<=run-0)\\S{1}", changeRun1$bids_order)
changeRun1$renameFile <- str_remove(changeRun1$renameFile, "/original_event_files")
```


```{r}
changeRun1 %>%
  dplyr::select(PartID, Run, bids_order, archive, renameFile) %>%
  head()

file.rename(changeRun1$archive, changeRun1$renameFile)
```

## Remove the existing bids files first (If major changes have been made to the event files)
```{r}
bidsEvent <-
  list.files(path = "/Volumes/data/projects/blast/data/bids", pattern = "sub-blast*", recursive = F, full.names = T)

bidsEvent <- bidsEvent[which(str_detect(bidsEvent, "sub-blasta"))]

bidsEvent <- paste0(bidsEvent, "/func")

bidsEvent <- list.files(path = bidsEvent, pattern = "*\\_events.tsv$", recursive = F, full.names = T)

bidsEvent <- as.data.frame(bidsEvent)

bidsEvent$PartID <- str_extract(bidsEvent$bidsEvent, "(?<=func/sub-blast(c|a))\\S+(?=_task)")

if(length(which(str_detect(bidsEvent$bidsEvent, "blastc"))) > 0) {
  bidsEvent[which(str_detect(bidsEvent$bidsEvent, "blastc")), "PartID"] <-
  paste0("blast_c_", bidsEvent[which(str_detect(bidsEvent$bidsEvent, "blastc")), "PartID"])
}

if(length(which(str_detect(bidsEvent$bidsEvent, "blasta"))) > 0) {
  bidsEvent[which(str_detect(bidsEvent$bidsEvent, "blasta")), "PartID"] <-
  paste0("blast_a_", bidsEvent[which(str_detect(bidsEvent$bidsEvent, "blasta")), "PartID"])
}

bidsEvent$task <- str_extract(bidsEvent$bidsEvent, "(?<=task-)\\S+(?=_run)")
bidsEvent$task <- gsub("asl", "auditory", bidsEvent$task)
bidsEvent$task <- gsub("vsl", "visual", bidsEvent$task)

bidsEvent$Run <- str_extract(bidsEvent$bidsEvent, "(?<=_run-0)\\S+(?=_events.tsv)")

if (length(-which(str_detect(bidsEvent$bidsEvent, "incomplete"))) > 0) {
  bidsEvent <- bidsEvent[-which(str_detect(bidsEvent$bidsEvent, "incomplete")),]
}

aslEve <-
  bidsEvent %>%
  filter(task == "auditory")


file.remove(as.character(aslEve$bidsEvent))

# Manually correct some run numbers. This is working backwards from missingEvent and missingPreprocess generated below. If we eventually find these bids or behavioral runs, will remove these lines below:
```


# Put imaging files and event files into individual subject folders
```{r}
library(stringr)
# file.copy("/Users/jojohu/Documents/Qlab/fmri/data/child/clean_event/", 
#           "/Volumes/data/projects/blast/data/derivatives/event_files/children_new/", 
#           overwrite = F,
#           copy.mode = TRUE, 
#           copy.date = TRUE)

event_from <- 
  list.files("/Volumes/data/projects/blast/data/derivatives/event_files/adults_new", 
              pattern = "sub-\\S+(vsl|asl)_run-\\S+_events.tsv$", full.names = T)

event_from <- as.data.frame(event_from)

event_from[,"event_from_short"] <- basename(as.character(event_from$event_from))

event_to <- bidsBold

event_to$bidsEvent <- as.character(event_to$bidsEvent)

event_to[,"event_to_short"] <- str_extract(event_to$bidsEvent,
                                           "(?<=/func/)sub-\\S+(vsl|asl)_run-\\S+_bold.nii.gz$")

event_to$event_to_short <- str_replace(event_to$event_to_short, "_bold.nii.gz", "_events.tsv")

event_to <- merge(event_to, event_from, by.x = "event_to_short", by.y = "event_from_short", all.x = T)

event_to$event_to_path <- str_remove(event_to$bidsEvent,
                                           "(?<=/func)/sub-\\S+(vsl|asl)_run-\\S+_bold.nii.gz$")

event_to <- event_to[which(!is.na(event_to$event_from)),]

event_to$event_from <- as.character(event_to$event_from)

# event_to <- event_to[-which(str_detect(event_to$bidsEvent, "incomplete")),]

file.copy(event_to$event_from, file.path(event_to$event_to_path, basename(event_to$event_from)), 
          overwrite = T,
          copy.mode = TRUE, 
          copy.date = TRUE)

file.copy("/Volumes/data/projects/blast/data/bids/task-asl_bold.json", "/Volumes/data/projects/blast/data/derivatives_new/fmriprep/", 
          overwrite = F,
          copy.mode = TRUE, 
          copy.date = TRUE)

file.copy("/Volumes/data/projects/blast/data/bids/task-vsl_bold.json", "/Volumes/data/projects/blast/data/derivatives_new/fmriprep/", 
          overwrite = F,
          copy.mode = TRUE, 
          copy.date = TRUE)
```


# Make sure no event file has over 12 blocks of stimuli. This section should be run here, because event files have already been moved into bids folders. 
```{r}
bidsEvent <-
  list.files(path = "/Volumes/data/projects/blast/data/bids", pattern = "blast_*", recursive = F, full.names = T)

bidsEvent <- paste0(bidsEvent, "/func")

bidsEvent <- list.files(path = bidsEvent, pattern = "*\\_events.tsv$", recursive = F, full.names = T)

readBidsEve <- function(df) {
  
    file_name <- basename(df)
    
    file <- read.csv(df,  sep ="\t", stringsAsFactors = F, header = T)
    
    if(nrow(file) > 0) {
      file[,c("file_name")] <- file_name
      file[,c("orig_path")] <- df
    }
   
    return(file)
    }

bidsEventDF <- lapply(bidsEvent, readBidsEve)

bidsEventDF <- bidsEventDF[lapply(bidsEventDF, nrow)>0]

bidsEventDFL <- do.call(dplyr::bind_rows, bidsEventDF)

# Check whether there are any event files that have more than 12 blocks; should return zero
bidsEventDFL %>%
  filter(str_detect(file_name, "asl")) %>%
  filter(str_detect(file_name, "blasta")) %>%
  dplyr::select(onset, duration, stimuli, condition, stimcond, file_name, orig_path) %>%
  arrange(file_name) %>%
  group_by(file_name) %>%
  mutate(block_num = seq(1:n())) %>%
  group_by(file_name) %>%
  filter(max(block_num) > 12)

# Onset < 0; not sure how to deal with theses; should return zero
bidsEventDFL %>%
  filter(str_detect(file_name, "asl")) %>%
  dplyr::select(onset, duration, stimuli, condition, stimcond, file_name, orig_path) %>%
  arrange(file_name) %>%
  filter(onset < 0)
```

# Not needed anymore due to not using fitlins
# Modify participant.tsv file for first-level analysis in fitlins with those subjects that have at least one event file and have matched preprocessed bids run and behavioral event file runs
```{r}
part_id <- unique(str_extract(event_to$event_to_short, "sub-\\S+(?=_run)"))

part_id <- as.data.frame(part_id)

part_id[,"asl"] <- str_extract(part_id$part_id, "asl")
part_id$part_id_only <- str_extract(part_id$part_id, "sub-\\S+(?=_task)")
part_id_asl <- part_id[which(part_id$asl == "asl"),]

part_id[,"vsl"] <- str_extract(part_id$part_id, "vsl")
part_id$part_id_only <- str_extract(part_id$part_id, "sub-\\S+(?=_task)")
part_id_vsl <- part_id[which(part_id$vsl == "vsl"),]

part_id <- merge(part_id_asl[,c("part_id_only", "asl")], part_id_vsl[,c("part_id_only", "vsl")], all = T)

if(nrow(mismatchRun) > 0) {
  mismatchRun$participant_id <- paste0("sub-",gsub("_", "", mismatchRun$PartID))

  mismatchRun[which(mismatchRun$task == "visual"),]$task <- "vsl"
  # mismatchRun[which(mismatchRun$task == "auditory"),]$task <- "asl"
  
  mismatchRun$mismatch <- 1
  
  part_id <- 
    merge(part_id, mismatchRun[, c("participant_id", "task", "mismatch")], by.x = c("part_id_only", "asl"), by.y = c("participant_id", "task"), all.x = T)
  
  part_id <- 
    merge(part_id, mismatchRun[, c("participant_id", "task", "mismatch")], by.x = c("part_id_only", "vsl"), by.y = c("participant_id", "task"), all.x = T)
  
  
  # part_id[which(part_id$mismatch.x == 1),]$asl <- NA
  part_id[which(part_id$mismatch.y == 1),]$vsl <- NA
}


# part_id[,c("bug")] <- "no"
# part_id[which(part_id$participant_id == "sub-blastc224"), c("bug")] <- "yes"

part_with_event <-
  part_id %>%
  filter(!is.na(asl) | !is.na(vsl))
  

# %>%
#   subset(bug == "no")
# 
# filterSubj <- paste(part_tsv_with_event$participant_id, collapse = "\",\"")


write.csv(part_with_event, "/Volumes/data/projects/blast/data/derivatives/fitlins/participants_fitlins.csv")
```