---
title: "trim_event_file"
author: "Jojo Hu"
date: "2/11/2022"
output: html_document
---

# Clean by trial event files for fMRI block analysis
```{r}
# Change paths to NAS (input path need to be created on NAS: change /Users/jojohu/Documents/Qlab/fmri/data/child/gen_eve_from_log_child.py script output to NAS )
input_path <- "/Volumes/data/projects/blast/data/derivatives/event_files/children_new"
output_path <- "/Volumes/data/projects/blast/data/derivatives/event_files/children_new/"

library(stringr)

longeve <- list.files(path = input_path,
                       pattern = "*\\.txt$", full.names = T)

# Function to clean the raw event files
clean_event_file <- function(df) {
  # Set up a variable
  weird_event <- NA
  
  file_name <- basename(df)
  file_name <- str_extract(file_name, "\\S+(?=.txt?)")
  
  df <- read.csv(df,  sep ="\t", stringsAsFactors = F, header = T)
  # If the raw event file is not empty:
  if(nrow(df) > 0) {
    df[, "name"] <- file_name
  
    # If the condition in the current trial does not = the condition in the previous trial, then this current trial is the first trial of the block
    df[, "prev_cond"] <- append("place_holder", df$condition[1:(length(df$condition)-1)]) 
    # If the condition in the current trial does not = the condition in the next trial, then this current trial is the last trial of the block
    df[, "next_cond"] <- append(df$condition[2:length(df$condition)], "place_holder") 
    
    # Add mini block numbers
    df[which(df$condition != df$prev_cond), "mini_block"] <-
      seq(1:nrow(df[which(df$condition != df$prev_cond),]))
    
    library(dplyr)
    library(tidyr)
    df <-
      df %>% 
      tidyr::fill(mini_block, .direction = "down")
    
    # Add stimuli type (tone, syllable, rest, image, letter rest)
    if("soundFile" %in% colnames(df)) {
      # If the event file is ASL, find tone, syllable, rest
      df$soundFile <- str_trim(df$soundFile) 
      df[which(str_detect(df$soundFile, "[:digit:][:upper:]")), "stimuli"] <- "tone"
      df[which(str_detect(df$soundFile, "[:lower:][:lower:]$")), "stimuli"] <- "syllable"
      df[which(str_detect(df$soundFile, "silence")), "stimuli"] <- "rest"
    } else if ("image" %in% colnames(df)) {
       # If the event file is VSL, find image, letter, rest
      df$image <- str_trim(df$image) 
      df[which(str_detect(df$image, "[:alpha:]+[:digit:]+")), "stimuli"] <- "image"
      df[which(str_detect(df$image, "[:upper:]$")), "stimuli"] <- "letter"
      df[which(str_detect(df$image, "blank")), "stimuli"] <- "rest"
    }
    
    # If the condition in the current trial does not = the condition in the previous trial, then this current trial is the first trial of the block
    first_trials <- df[which(df$condition != df$prev_cond), c("onset", "name", "condition", "mini_block", "stimuli")]
    # If the condition in the current trial does not = the condition in the next trial, then this current trial is the last trial of the block
    last_trials <- df[which(df$condition != df$next_cond), c("onset", "name", "condition", "mini_block", "stimuli")]
    
    # Get the duration of each block
    colnames(last_trials)[which(colnames(last_trials) == "onset")] <- "onset_last"
    
    short_eve <- merge(first_trials, last_trials, by = c("condition", "name", "mini_block", "stimuli"))
    
    short_eve <- 
      short_eve %>%
      # Must arrange by mini block order first, and then by stimuli onset, because some event files have more than 12 blocks; and then the onset of the 13th block resets and starts again
      arrange(mini_block, onset)
    
    # If an event file has 24 blocks, that means the run was administered twice, only keep the later 24 blocks
    if(max(short_eve$mini_block) > 12) {
      # Get where the run was administered twice in the event file
      print(short_eve)
      
      first_usable_block <-
        short_eve %>%
        mutate(diff = onset - lag(onset))  %>%
        filter(diff < 0) %>%
        dplyr::select(mini_block) 
      
      # Save the later blocks
      if (nrow(first_usable_block) == 1) {
        short_eve <-
          short_eve %>%
          filter(mini_block > first_usable_block$mini_block | mini_block == first_usable_block$mini_block) %>%
          mutate(mini_block = seq(1:nrow(.)))

      } else if (nrow(first_usable_block) != 1) {
        
        print("This event file is weird:")
        print(short_eve)
        # Deal with weird event files case by case
        # if (unique(short_eve$name) == "sub-blastc522_asl_run_3_eve") {
        #   # sub-blastc522_asl_run_3_eve.txt contained 13 blocks, 1st block only contained three stimuli for some reason
        #   short_eve <-
        #     short_eve %>%
        #     filter(mini_block > 1) %>%
        #     mutate(mini_block = seq(1:nrow(.)))
        # }
        
        # if (unique(short_eve$name) == "sub-blastc210_asl_run_1_eve") {
        #   # sub-blastc522_asl_run_3_eve.txt contained 13 blocks, 1st block only contained three stimuli for some reason
        #   short_eve <-
        #     short_eve %>%
        #     filter(mini_block > 17) %>%
        #     mutate(mini_block = seq(1:nrow(.)))
        # }
      }
    }
    
    # Cleaned event files should have 12 blocks only
    if(max(short_eve$mini_block) != 12) {
      weird_event <- short_eve
    }
    
    short_eve$duration <- short_eve$onset_last - short_eve$onset
    
    this_file_name <- unique(short_eve$name)
    this_file_name <-
      paste0(str_extract(this_file_name, "sub-blastc[:digit:]+"), "_task-", str_extract(this_file_name, "[:alpha:]sl_run"), "-0",
             str_extract(this_file_name,"(?<=run_)[:digit:]"), "_events.tsv")
  
    short_eve <- short_eve[,c("onset", "duration", "stimuli", "condition")]
    
    # Get rid of trailing white space and only keep the random 
    short_eve$condition <- gsub(" ", "", short_eve$condition)
    
    short_eve$stimcond <- paste0(short_eve$stimuli, short_eve$condition)
    
    short_eve[which(short_eve$stimcond == "restB"), "stimcond"] <- "rest"
    
    if(nrow(df[complete.cases(short_eve),]) != nrow(df)) {
      print(paste(this_file_name, "this file has NA"))
      print(short_eve)
    }
    write.table(short_eve, paste0(output_path, this_file_name), sep='\t', row.names = F)
  }
  return(weird_event)
}

# Run the function to clean the raw event files; No need to save the output of the function as files are saved in the function; place_holder just to prevent printing of lapply; the place_holder variable contains weird event file names just in case the files need to be revisited
place_holder <- lapply(longeve, clean_event_file)
```





# Change event file names to make sure fMRI data runs match with behavioral data runs
## Compile Runs for all Participants
```{r}
input_path2 <- "/Volumes/data/projects/blast/data/mri/in_scanner_behavioral/sl_raw_data/child/sl_raw_data"

csvFile <- list.files(path = input_path2,
                       pattern = "*blast_c_\\S+_(auditory|visual)\\S+.csv$", full.names = T)

validFile <- list()

for (i in 1:length(csvFile)) {
  
  file_name <- basename(csvFile[i])
  orig_file <- read.csv(csvFile[i], stringsAsFactors = F)
  
  if (nrow(orig_file) == 0) {
    invalidFile <- orig_file 
    } else if (nrow(orig_file) > 0) {
      orig_file[,c("file_name")] <- file_name
      orig_file[,c("repetition")] <- as.character(orig_file[,c("repetition")])
      orig_file[,c("frameRate")] <- as.character(orig_file[,c("frameRate")])
      orig_file[,c("PartID")] <- as.character(orig_file[,c("PartID")])
      
      if(length(which(colnames(orig_file) %in% "ltarget")) > 0) {
        orig_file[,c("ltarget")] <- as.character(orig_file[,c("ltarget")])
      }
      
      edit_file <- orig_file
      validFile[[i]] <- edit_file
    }
}

validFile <- do.call(dplyr::bind_rows, validFile)

dateRun <- validFile[,c("PartID", "date", "Run", "file_name")]

dateRun$task <- str_extract(dateRun$file_name, "(auditory|visual)")

dateRun$year_month_date <- str_extract(dateRun$date, "\\S+_\\S+_\\S+(?=_)")

dateRun$date_formatted <- as.Date(dateRun$year_month_date, "%Y_%b_%d")

dateRun$time <- sub('.*_', '', dateRun$date)

# Correct wrong naming in the raw data file
dateRun[which(dateRun$PartID == "blast_c_0612"),]$PartID <- "blast_c_061"
```


## Manually Check the participants that have duplicated runs or irregular run orders
```{r}
# https://stackoverflow.com/questions/15933958/collapse-concatenate-aggregate-a-column-to-a-single-comma-separated-string-w

checkOrder <-
  dateRun %>%
  dplyr::select(PartID, task, date_formatted, time, Run) %>%
  dplyr::distinct(.) %>%
  dplyr::mutate(date_formatted = as.Date(date_formatted),
         Run = as.factor(Run)) %>%
  arrange(PartID, task, date_formatted, time) %>%
  distinct(PartID, task, Run, .keep_all = TRUE) %>%
  group_by(PartID, task) %>%
  dplyr::filter(n() == 4) %>%
  dplyr::summarise(run = toString(Run)) %>%
  ungroup() %>%
  filter(run != "1, 2, 3, 4" & run!= "3, 4, 1, 2")  %>%
  dplyr::mutate(notes = "This is a subject with irregularly-ordered runs. Please check their runsheet to see if the runs were indeed ordered this way and leave notes on this spreadsheet.")
  
duplicatedRun <-
  dateRun %>%
  dplyr::select(PartID, task, date_formatted, time, Run) %>%
  dplyr::distinct(.) %>%
  dplyr::mutate(date_formatted = as.Date(date_formatted),
         Run = as.factor(Run)) %>%
  arrange(PartID, task, date_formatted, time) %>%
  group_by(PartID, task, Run) %>%
  filter(n() > 1) %>%
  distinct(PartID, .keep_all = F) %>%
  dplyr::rename(run = Run) %>%
  dplyr::mutate(notes = "This is the duplicated run in the in_scanner_behavioral data folder. Please remove the corresponding incomplete run from the behavioral and imaging data (bids and fmriprep).")

checkRun <- rbind(as.data.frame(duplicatedRun), as.data.frame(checkOrder))

write.csv(checkRun, "/Users/jojohu/Documents/Qlab/fmri/data/child/manual_check_run.csv")
```

## Check what bids data exsit
```{r}
bidsEvent <-
  list.files(path = "/Volumes/data/projects/blast/data/bids",
           pattern = "sub-blastc", recursive = F, full.names = T)

bidsEvent <-
  list.files(path = paste0(bidsEvent, "/func"),
           pattern = "*\\_bold.nii.gz$", recursive = F, full.names = T)

bidsBold <- as.data.frame(bidsEvent)

bidsEvent <- as.data.frame(bidsEvent)
bidsEvent$PartID <- str_extract(bidsEvent$bidsEvent, "(?<=func/sub-blast(c|a))\\S+(?=_task)")

if(length(which(str_detect(bidsEvent$bidsEvent, "blastc"))) > 0) {
  bidsEvent[which(str_detect(bidsEvent$bidsEvent, "blastc")), "PartID"] <-
  paste0("blast_c_", bidsEvent[which(str_detect(bidsEvent$bidsEvent, "blastc")), "PartID"])
}

if(length(which(str_detect(bidsEvent$bidsEvent, "blasta"))) > 0) {
  bidsEvent[which(str_detect(bidsEvent$bidsEvent, "blasta")), "PartID"] <-
  paste0("blast_a_", bidsEvent[which(str_detect(bidsEvent$bidsEvent, "blasta")), "PartID"])
}

bidsEvent$task <- str_extract(bidsEvent$bidsEvent, "(?<=task-)\\S+(?=_run)")
bidsEvent$task <- gsub("asl", "auditory", bidsEvent$task)
bidsEvent$task <- gsub("vsl", "visual", bidsEvent$task)

bidsEvent$Run <- str_extract(bidsEvent$bidsEvent, "(?<=_run-0)\\S+(?=_bold)")

if (length(-which(str_detect(bidsEvent$bidsEvent, "incomplete"))) > 0) {
  bidsEvent <- bidsEvent[-which(str_detect(bidsEvent$bidsEvent, "incomplete")),]
}

# Manually correct some run numbers. This is working backwards from missingEvent and missingPreprocess generated below. If we eventually find these bids or behavioral runs, will remove these lines below:

# blast_c_112 Run 2 bids is probably not usable according to mri adminstration notes, there is only run 1 event file, remove run 2 from bids
bidsEvent <- bidsEvent[-which(bidsEvent$PartID == "blast_c_112" & bidsEvent$task == "auditory" & bidsEvent$Run == 2),]
# blast_c_168 is missing behavioral run 1, so removing run 1 from bids data analyses
bidsEvent <- bidsEvent[-which(bidsEvent$PartID == "blast_c_168" & bidsEvent$task == "auditory" & bidsEvent$Run == 1),]
# blast_c_209 is missing behavioral run 1, so removing run 1 from bids data analyses
bidsEvent <- bidsEvent[-which(bidsEvent$PartID == "blast_c_209" & bidsEvent$task == "auditory" & bidsEvent$Run == 1),]
# blast_c_213 log file is empty, remove bids run 1
bidsEvent <- bidsEvent[-which(bidsEvent$PartID == "blast_c_213" & bidsEvent$task == "auditory" & bidsEvent$Run == 1),] 

bidsEvent <-
  bidsEvent %>%
  arrange(PartID, task, Run) %>%
  filter(task == "auditory" | task == "visual") %>%
  group_by(PartID, task) %>%
  dplyr::summarise(bids_run = toString(Run)) %>%
  dplyr::ungroup()
```


# Check all the order of the bids run based on Acquisition Time .json files
# All bids should be in an ascending order
```{r}
# Read in bids json files
bidsJson <-
  list.files(path = "/Volumes/data/projects/blast/data/bids", pattern = "blast_*", recursive = F, full.names = T)

bidsJson <- paste0(bidsJson, "/func")

bidsJson <- list.files(path = bidsJson, pattern = "*\\_bold.json$", recursive = F, full.names = T)

library("jsonlite")
# Extract acquisition time
readTime <- function(df) {
  tempJSON <- fromJSON(df, flatten=TRUE)
  acq_time <- as.POSIXlt(tempJSON$AcquisitionTime,format="%H:%M:%S")
  
  acq <- as.data.frame(acq_time)
  
  acq$file_name <- basename(df)
  
  return(acq)
}

jsonDF <- lapply(bidsJson, readTime)
jsonDFL <- do.call(dplyr::bind_rows, jsonDF)

jsonDFL <-
  jsonDFL %>%
  mutate(PartID = str_extract(file_name, "blast\\S+[:digit:]{3}"), 
         Run = str_extract(file_name, "(?<=_run-0)[:digit:]{1}"),
         task = str_extract(file_name, "langloc|asl|vsl|rest")) 

# Check that all participants' bids should be in an ascending order. Output should be zero:
jsonDFL %>%
  filter(task == "asl" | task == "vsl") %>%
  arrange(PartID, task, acq_time) %>%
  group_by(PartID, task) %>%
  mutate(Run = as.numeric(as.character(Run))) %>%
  mutate(diff = Run - lag(Run)) %>%
  filter(diff > 1)
  
```



## Check the run orders that do not match between preprocessed data and in-scanner-behavioral data
```{r}
# Manually correct some run numbers. This is working backwards from missingEvent and missingPreprocess generated below. If we eventually find these bids or behavioral runs, will remove these lines below:

# blast_c_231 only got through 2 runs of ASL, asked to stop the experiment at the start of run 3, remove behavioral run 3
dateRun <- dateRun[-which(dateRun$PartID == "blast_c_231" & dateRun$task == "auditory" & dateRun$Run == 3),]
  
# blast_c_469 is not missing any event files, but just missing last run of bids, removing behavioral run 2 to match bids
dateRun <- dateRun[-which(dateRun$PartID == "blast_c_469" & dateRun$task == "auditory" & dateRun$Run == 2),]

# blast_c_520 is not missing any event files, but just missing bids files, removing the behavioral files to match bids
dateRun <- dateRun[-which(dateRun$PartID == "blast_c_520" & dateRun$task == "auditory" & dateRun$Run == 4),]
dateRun <- dateRun[-which(dateRun$PartID == "blast_c_520" & dateRun$task == "auditory" & dateRun$Run == 1),]
dateRun <- dateRun[-which(dateRun$PartID == "blast_c_520" & dateRun$task == "auditory" & dateRun$Run == 2),]
```


# TO DO: blast_c_513 Run 4 bids missing, has dicoms data, would need to reprocess bids and fmriPrep, removing event file run 4
```{r}
# The event file run order is 3, 4, 1, 2 corresponding to 1, 2, 3, 4 bids, bids run 4 missing, so removing run 2 from events
dateRun <- dateRun[-which(dateRun$PartID == "blast_c_513" & dateRun$task == "auditory" & dateRun$Run == 2),]
```


```{r}
# This one has log file, but no csv file: blast_c_230 is missing behavioral run 2 csv, manually add it
dateRun <- 
  rbind(dateRun, c("blast_c_230", "2019_Jul_24_1550", as.integer("2"), "blast_c_230_auditory_2.csv", "auditory", "2019_Jul_24", "2019-07-24", "1550"))



runOnly <-
  dateRun %>%
  dplyr::select(PartID, task, date_formatted, time, Run) %>%
  dplyr::distinct(.) %>%
  dplyr::mutate(date_formatted = as.Date(date_formatted)) %>%
  arrange(PartID, task, date_formatted, time) %>%
  dplyr::select(PartID, task, Run) %>%
  dplyr::distinct(.) %>%
  group_by(PartID, task) %>%
  dplyr::summarise(run_order = toString(Run)) %>%
  ungroup()
```


```{r}
runOnly <- merge(runOnly, unique(bidsEvent), by = c("PartID", "task"), all.x = T)

runOnly$event_count <- str_count(runOnly$run_order, "[0-9]")
runOnly$bids_count <- str_count(runOnly$bids_run, "[0-9]")

missingEvent <- runOnly[which(runOnly$event_count < runOnly$bids_count),]


missingPreprocessed <-
runOnly %>%
  filter(!is.na(run_order)) %>%
  filter(bids_count < event_count | is.na(bids_run))
  

mismatchRun <-
  runOnly[which(!runOnly$run_order %in% runOnly$bids_run),] %>%
  # filter(!is.na(bids_run)) %>%
  filter(event_count != bids_count)


write.csv(missingEvent, "/Users/jojohu/Documents/Qlab/fmri/data/child/missing_event_file.csv")
write.csv(missingPreprocessed, "/Users/jojohu/Documents/Qlab/fmri/data/child/missing_preprocessed.csv")
write.csv(runOnly, "/Users/jojohu/Documents/Qlab/fmri/data/child/blast_dev_child_event_run_order.csv", row.names = F)
```


# Change event file names to match with actual imaging data sequence names
```{r}
# This should be zero; if not, go to previous section to manually correct behavioral runs or bids
runOnly %>%
  filter(task == "auditory") %>%
  filter(event_count != bids_count)

changeRun <-
  runOnly %>%
  filter(run_order != "1, 2, 3, 4") %>%
  filter(run_order != bids_run) %>%
  filter(event_count == bids_count)

changeRun <- merge(changeRun,  
                   unique(dateRun[,c("PartID", "task", "Run", "file_name", "date_formatted", "time")]),
                   all.x = T)

changeRun <-
  changeRun %>%
  arrange(PartID, task, date_formatted, time)

## Read in original event files
eventFile <- list.files(path = input_path,
                        pattern = "*\\.tsv$", full.names = T)

eventFile <- as.data.frame(eventFile)
eventFile$PartID <- str_extract(eventFile$eventFile, "(?<=-blast(c|a))\\S+(?=_task)")

if(length(which(str_detect(eventFile$eventFile, "blastc"))) > 0) {
  eventFile[which(str_detect(eventFile$eventFile, "blastc")), "PartID"] <-
  paste0("blast_c_", eventFile[which(str_detect(eventFile$eventFile, "blastc")), "PartID"])
}

if(length(which(str_detect(eventFile$eventFile, "blasta"))) > 0) {
  eventFile[which(str_detect(eventFile$eventFile, "blasta")), "PartID"] <-
  paste0("blast_a_", eventFile[which(str_detect(eventFile$eventFile, "blasta")), "PartID"])
}

eventFile$task <- str_extract(eventFile$eventFile, "(?<=task-)\\S+(?=_run)")
eventFile$task <- ifelse(eventFile$task == "asl", "auditory", "visual")

eventFile$Run <- str_extract(eventFile$eventFile, "(?<=_run-0)\\S+(?=_events)")

changeRun <- merge(changeRun, eventFile, by = c("PartID", "task", "Run"), all.x = T)
                      
# dir.create(file.path("/Volumes/data/projects/blast/data/derivatives/event_files/children_new/", "original_event_files"))
changeRun$basename <- basename(as.character(changeRun$eventFile))
changeRun$eventFile <- as.character(changeRun$eventFile)
changeRun$archive <- paste0("/Volumes/data/projects/blast/data/derivatives/event_files/children_new/original_event_files/", changeRun$basename)

print(changeRun)
```


```{r}
file.rename(as.character(changeRun$eventFile), changeRun$archive)
```


## Change event file names for those who have matching number of behavioral runs and bids runs (all subjects' ASL data should have been matched before this section)
```{r}
changeRun1 <-
  changeRun 
  # filter(bids_count == 4)

# Some subjects have more than 1 csv files for each run because the run was adminstered multiple times
changeRun1 <-
  changeRun1 %>%
  group_by(PartID, task, Run) %>%
  filter(row_number() == n())

# Reorder the data based on behavioral run order and bids run order
# Get behavioral run order
splitOrder <- 
  as.data.frame(do.call(rbind, str_split(str_pad(str_remove_all(changeRun1$run_order, ", "), 4, pad = "0", side = "right"), "")))

colnames(splitOrder) <- c("run1_name", "run2_name", "run3_name", "run4_name")

splitOrder <- as.data.frame(splitOrder)

changeRun1 <- dplyr::bind_cols(changeRun1, splitOrder)

# Put behavioral run order back to dataframe and reorder data
changeRun1 <- 
  changeRun1 %>%
  mutate(behavioral_order = ifelse(Run == run1_name, 1, ifelse(Run == run2_name, 2, ifelse(Run == run3_name, 3, ifelse(Run == run4_name, 4, NA)))))

changeRun1 <- 
  changeRun1 %>%
  arrange(PartID, task, behavioral_order)

# Get bids run order
uniqueBids <-
  changeRun1 %>%
  group_by(PartID, task) %>%
  filter(row_number() == 1) %>%
  dplyr::select(PartID, task, bids_run)

changeRun1$bids_order <- unlist(str_split(uniqueBids$bids_run, ", "))

# Check that the added bids order are correct. Bids runs are in ascending order, so:
changeRun1 %>%
  group_by(PartID, task) %>%
  mutate(check_bids_order = seq(1:n())) %>%
  filter(bids_order != check_bids_order)

changeRun1$renameFile <- str_replace(changeRun1$archive, "(?<=run-0)\\S{1}", changeRun1$bids_order)
changeRun1$renameFile <- str_remove(changeRun1$renameFile, "/original_event_files")
```


```{r}
changeRun1 %>%
  dplyr::select(PartID, Run, bids_order, archive, renameFile) %>%
  head()

changeRun1 %>%
  filter(PartID == "blast_c_469") %>%
  dplyr::select(PartID, Run, bids_order, archive, renameFile)

file.rename(changeRun1$archive, changeRun1$renameFile)
```


# Generate a list of usable data based on existing event files after event file name correction has already taken place, so that a subject list can be generated for manuscript removal
```{r}
event_check <- 
  list.files("/Volumes/data/projects/blast/data/derivatives/event_files/children_new", 
              pattern = "sub-\\S+(vsl|asl)_run-\\S+_events.tsv$", full.names = T)

event_checkAd <- 
  list.files("/Volumes/data/projects/blast/data/derivatives/event_files/adults_new", 
              pattern = "sub-\\S+(vsl|asl)_run-\\S+_events.tsv$", full.names = T)

event_check <- append(event_check, event_checkAd)

event_check <- as.data.frame(event_check)

bidsCheck <-
  list.files(path = "/Volumes/data/projects/blast/data/bids",
           pattern = "sub-blast(a|c)", recursive = F, full.names = T)

bidsCheck <-
  list.files(path = paste0(bidsCheck, "/func"),
           pattern = "*\\_bold.nii.gz$", recursive = F, full.names = T)

bidsCheck <- as.data.frame(bidsCheck)

event_check <-
  event_check %>%
  mutate(event_check_short = basename(as.character(event_check))) %>%
  mutate(part_id = str_extract(event_check_short, "blast(a|c)[:digit:]+"),
         run = str_extract(event_check_short, "(?<=_run-0)[:digit:]"),
         task = str_extract(event_check_short, "(?<=_task-)\\S+(?=_run)"))

bidsCheck <-
  bidsCheck %>%
  mutate(bids_check_short = basename(as.character(bidsCheck))) %>%
  mutate(part_id = str_extract(bids_check_short, "blast(a|c)[:digit:]+"),
         run = str_extract(bids_check_short, "(?<=_run-0)[:digit:]"),
         task = str_extract(bids_check_short, "(?<=_task-)\\S+(?=_run)"))

missingEventRemove <- 
  merge(event_check, bidsCheck, all.y = T) %>%
  mutate(remove = ifelse(is.na(event_check_short), 1, 0))

missingEventRemove$source <- "missingEvent"

aslMissingEvent <- 
  missingEventRemove %>%
  filter(task == "asl") %>%
  dplyr::select(task, run, part_id, remove, source)

write.csv(aslMissingEvent, "/Volumes/data/projects/blast/data/derivatives_new/subject_list/aslMissingEvent.csv", row.names = F)
```


## Remove the existing bids files first (If major changes have been made to the event files)
```{r}
bidsEvent <-
  list.files(path = "/Volumes/data/projects/blast/data/bids", pattern = "blastc*", recursive = F, full.names = T)

bidsEvent <- paste0(bidsEvent, "/func")

bidsEvent <- list.files(path = bidsEvent, pattern = "*\\_events.tsv$", recursive = F, full.names = T)

bidsEvent <- as.data.frame(bidsEvent)

bidsEvent$PartID <- str_extract(bidsEvent$bidsEvent, "(?<=func/sub-blast(c|a))\\S+(?=_task)")

if(length(which(str_detect(bidsEvent$bidsEvent, "blastc"))) > 0) {
  bidsEvent[which(str_detect(bidsEvent$bidsEvent, "blastc")), "PartID"] <-
  paste0("blast_c_", bidsEvent[which(str_detect(bidsEvent$bidsEvent, "blastc")), "PartID"])
}

if(length(which(str_detect(bidsEvent$bidsEvent, "blasta"))) > 0) {
  bidsEvent[which(str_detect(bidsEvent$bidsEvent, "blasta")), "PartID"] <-
  paste0("blast_a_", bidsEvent[which(str_detect(bidsEvent$bidsEvent, "blasta")), "PartID"])
}

bidsEvent$task <- str_extract(bidsEvent$bidsEvent, "(?<=task-)\\S+(?=_run)")
bidsEvent$task <- gsub("asl", "auditory", bidsEvent$task)
bidsEvent$task <- gsub("vsl", "visual", bidsEvent$task)

bidsEvent$Run <- str_extract(bidsEvent$bidsEvent, "(?<=_run-0)\\S+(?=_events.tsv)")

if (length(-which(str_detect(bidsEvent$bidsEvent, "incomplete"))) > 0) {
  bidsEvent <- bidsEvent[-which(str_detect(bidsEvent$bidsEvent, "incomplete")),]
}

aslEve <-
  bidsEvent %>%
  filter(task == "auditory")


file.remove(as.character(aslEve$bidsEvent))

# Manually correct some run numbers. This is working backwards from missingEvent and missingPreprocess generated below. If we eventually find these bids or behavioral runs, will remove these lines below:
```



# Put imaging files and event files into individual subject folders
```{r}
library(stringr)
# file.copy("/Users/jojohu/Documents/Qlab/fmri/data/child/clean_event/", 
#           "/Volumes/data/projects/blast/data/derivatives/event_files/children_new/", 
#           overwrite = F,
#           copy.mode = TRUE, 
#           copy.date = TRUE)

event_from <- 
  list.files("/Volumes/data/projects/blast/data/derivatives/event_files/children_new", 
              pattern = "sub-\\S+(vsl|asl)_run-\\S+_events.tsv$", full.names = T)

event_from <- as.data.frame(event_from)

event_from[,"event_from_short"] <- basename(as.character(event_from$event_from))

event_to <- bidsBold

event_to$bidsEvent <- as.character(event_to$bidsEvent)

event_to[,"event_to_short"] <- str_extract(event_to$bidsEvent,
                                           "(?<=/func/)sub-\\S+(vsl|asl)_run-\\S+_bold.nii.gz$")

event_to$event_to_short <- str_replace(event_to$event_to_short, "_bold.nii.gz", "_events.tsv")

event_to <- merge(event_to, event_from, by.x = "event_to_short", by.y = "event_from_short", all.x = T)

event_to$event_to_path <- str_remove(event_to$bidsEvent,
                                           "(?<=/func)/sub-\\S+(vsl|asl)_run-\\S+_bold.nii.gz$")

event_to <- event_to[which(!is.na(event_to$event_from)),]

event_to$event_from <- as.character(event_to$event_from)

if(nrow(event_to[which(str_detect(event_to$bidsEvent, "incomplete")),]) > 0) {
  event_to <- event_to[-which(str_detect(event_to$bidsEvent, "incomplete")),] 
}

file.copy(event_to$event_from, file.path(event_to$event_to_path, basename(event_to$event_from)), 
          overwrite = T,
          copy.mode = TRUE, 
          copy.date = TRUE)

file.copy("/Volumes/data/projects/blast/data/bids/task-asl_bold.json", "/Volumes/data/projects/blast/data/derivatives/fmriprep/", 
          overwrite = F,
          copy.mode = TRUE, 
          copy.date = TRUE)

file.copy("/Volumes/data/projects/blast/data/bids/task-vsl_bold.json", "/Volumes/data/projects/blast/data/derivatives/fmriprep/", 
          overwrite = F,
          copy.mode = TRUE, 
          copy.date = TRUE)
```

# Remove the event files that have over 12 blocks of stimuli from all analyses. This section should be run here, because some event files might have already been moved into bids folders. 
```{r}
bidsEvent <-
  list.files(path = "/Volumes/data/projects/blast/data/bids", pattern = "blast_*", recursive = F, full.names = T)

bidsEvent <- bidsEvent[which(str_detect(bidsEvent, "sub-blastc"))]

bidsEvent <- paste0(bidsEvent, "/func")

bidsEvent <- list.files(path = bidsEvent, pattern = "*\\_events.tsv$", recursive = F, full.names = T)

readBidsEve <- function(df) {
  
    file_name <- basename(df)
    
    file <- read.csv(df,  sep ="\t", stringsAsFactors = F, header = T)
    
    if(nrow(file) > 0) {
      file[,c("file_name")] <- file_name
      file[,c("orig_path")] <- df
    }
   
    return(file)
    }

bidsEventDF <- lapply(bidsEvent, readBidsEve)

bidsEventDF <- bidsEventDF[lapply(bidsEventDF, nrow)>0]

bidsEventDFL <- do.call(dplyr::bind_rows, bidsEventDF)

# Should be zero if all event file cleaning is done above
bidsEventDFL %>%
  filter(str_detect(file_name, "asl")) %>%
  dplyr::select(onset, duration, stimuli, condition, stimcond, file_name, orig_path) %>%
  arrange(file_name) %>%
  group_by(file_name) %>%
  mutate(block_num = seq(1:n())) %>%
  group_by(file_name) %>%
  filter(max(block_num) > 12)

# Onset < 0; not sure how to deal with theses
bidsEventDFL %>%
  filter(str_detect(file_name, "asl")) %>%
  dplyr::select(onset, duration, stimuli, condition, stimcond, file_name, orig_path) %>%
  arrange(file_name) %>%
  filter(onset < 0)
```

# Not needed anymore due to not using fitlins
# Modify participant.tsv file for first-level analysis in fitlins with those subjects that have at least one event file and have matched preprocessed bids run and behavioral event file runs
```{r}
part_id <- unique(str_extract(event_to$event_to_short, "sub-\\S+(?=_run)"))

part_id <- as.data.frame(part_id)

part_id[,"asl"] <- str_extract(part_id$part_id, "asl")
part_id$part_id_only <- str_extract(part_id$part_id, "sub-\\S+(?=_task)")
part_id_asl <- part_id[which(part_id$asl == "asl"),]

part_id[,"vsl"] <- str_extract(part_id$part_id, "vsl")
part_id$part_id_only <- str_extract(part_id$part_id, "sub-\\S+(?=_task)")
part_id_vsl <- part_id[which(part_id$vsl == "vsl"),]

part_id <- merge(part_id_asl[,c("part_id_only", "asl")], part_id_vsl[,c("part_id_only", "vsl")], all = T)

if(nrow(mismatchRun) > 0) {
  
  mismatchRun$participant_id <- paste0("sub-",gsub("_", "", mismatchRun$PartID))
  
  # mismatchRun[which(mismatchRun$task == "vsl"),]$task <- "vsl"
  # mismatchRun[which(mismatchRun$task == "auditory"),]$task <- "asl"
  
  mismatchRun$mismatch <- 1
  
  part_id <- 
    merge(part_id, mismatchRun[, c("participant_id", "task", "mismatch")], by.x = c("part_id_only", "asl"), by.y = c("participant_id", "task"), all.x = T)
  
  part_id <- 
    merge(part_id, mismatchRun[, c("participant_id", "task", "mismatch")], by.x = c("part_id_only", "vsl"), by.y = c("participant_id", "task"), all.x = T)
  
  
  # part_id[which(part_id$mismatch.x == 1),]$asl <- NA
  part_id[which(part_id$mismatch.y == 1),]$vsl <- NA

}
# part_id[,c("bug")] <- "no"
# part_id[which(part_id$participant_id == "sub-blastc224"), c("bug")] <- "yes"

part_with_event <-
  part_id %>%
  filter(!is.na(asl) | !is.na(vsl))
  

# %>%
#   subset(bug == "no")
# 
# filterSubj <- paste(part_tsv_with_event$participant_id, collapse = "\",\"")


write.csv(part_with_event, "/Volumes/data/projects/blast/data/derivatives/fitlins/participants_fitlins.csv")
```