---
title: "splash_cloze_analysis"
author: "Jojo Hu"
date: "12/24/2019"
output: html_document
---

This script analyzes the cloze test results from Splash behavioral stimuli pilot. The script requires manual cleaning of answers.


# Load original stimuli
```{r}
setwd("/Users/jojohu/Documents/Splash/cloze_analysis")

stim <- read.csv("fill_blank_spreadsheet1.csv")

stimbp <- read.csv("fill_blank_spreadsheet2.csv")

stim <- cbind(stim, stimbp[,-c(1:7)])

stim <- stim[-1, ]

# Use the first sentence of each story to identify the story. The first sentence is the same for Luke and Lisa's story and its backup story.
stim_first <- stim[1, grep("fir", colnames(stim))]

stim_ver <- as.data.frame(t(stim_first))

library(data.table)
stim_ver <- setDT(stim_ver, keep.rownames = TRUE)[]
colnames(stim_ver) <- c("story", "text")
```

# Make long dataframe for story text
```{r}
library(reshape)
stim_long  <- melt(stim[,-which(names(stim) %in% c("randomise_blocks", "randomise_trials",
                                                   "display", "Progress_fillgaps", "First",
                                                   "Last"))], id.vars = c("Answer"))

library(stringr)
stim_long <- stim_long[-which(str_detect(stim_long$variable, "las$")),]
stim_long <- stim_long[-which(stim_long$Answer == "" | stim_long$Answer == "last_sentence"),]
colnames(stim_long) <- c("trial", "story", "str_text")
stim_long$trial <- as.character(stim_long$trial)
stim_long$story <- as.character(stim_long$story)
```

# Load fill blank raw data
```{r}
# This does not include pilot data. Because there are 3 versions, version 3 and 4 without demographic and used in lab consent form for version 3; version 4: used behavioral online consent form;  version 5: with demographic and used the behavioral online consent form.

data_list <-
  list.files(path = "/Users/jojohu/Documents/Splash/cloze_analysis/raw_data",
             pattern = "*v\\S+.csv", full.names = T)



# Get file name to identify story26
fname <-basename(data_list)

cdata <- lapply(data_list, read.csv)

col_list <- list()

for (i in 1:length(cdata)) {
  current_fname <- fname[i]
  current <- cdata[[i]][,c("Participant.Private.ID", "Participant.Status", "Y.Coordinate", "First")] 
  current[, "fname"] <- current_fname
  col_list[[i]] <- current
  }


cdata <- do.call(rbind, col_list)

fir_sen <- cdata$First[-1] 
fir_sen <- as.character(fir_sen)
fir_sen <- append(fir_sen, NA)

cdata <- cbind(cdata[ , -which(names(cdata) %in% "First")], fir_sen)
cdata <- cdata[-which(cdata$Y.Coordinate == ""),]
colnames(cdata)[which(colnames(cdata) == "Participant.Private.ID")] <- "subid"
colnames(cdata)[which(colnames(cdata) == "Y.Coordinate")] <- "answer"
colnames(cdata)[which(colnames(cdata) == "fir_sen")] <- "text"

library(stringr)
cdata$fname <- str_extract(cdata$fname, "\\S+(?=_v\\S+)")


cdata$text <- as.character(cdata$text)
```

# Check trial number for participants who reached timelimit and have wrong trials
```{r}
tldata <- cdata[which(cdata$Participant.Status == "rejected - time limit reached"), ]

library(dplyr)

tlcount <- 
  tldata %>%
  group_by(subid, fname) %>%
  dplyr::count(text) 

tlwrong <- tlcount[which(tlcount$n != 9),]

wrongd  <- list()
wrongdR = 0

for(i in 1:nrow(tlwrong)) {
  
  wrongdR = wrongdR + 1
  
  wrongd[[wrongdR]] <- 
    cdata[which(cdata$subid %in% tlwrong[i,"subid"] & cdata$text %in% tlwrong[i, "text"]),]
}

wrongd <- do.call(rbind, wrongd)

# Check wrongd to see which rows are the rows that should be excluded. May vary from file to file.
wrongd <- cbind(wrongd, rev(sequence(rev(tlwrong$n))), rownames(wrongd))

excluderow <- wrongd[which(wrongd$`rev(sequence(rev(tlwrong$n)))` > 9), "rownames(wrongd)"]

cdata <- cdata[!rownames(cdata) %in% excluderow,] 

# After cleaning trials for reach-timelimit ids, check whether all part have correct number of trials

# This process needs to be done again because the trials that should be excluded are different from the timelimit part

num_trial <- cdata %>% dplyr::count(subid) 


# if (sum(num_trial$n %% 9) != 0) {
#    stop("Check the number of trials for these participants:")
#    print(num_trial[which(num_trial$n != 234),])
#  }

wtrialID <- num_trial[which(num_trial$n %% 9 != 0), "subid"]

wtrial <- cdata[which(cdata$subid %in% wtrialID$subid),]

wtrialN <-
  wtrial %>%
  group_by(subid, fname) %>%
  dplyr::count(text) 

wtrialN <- wtrialN[which(wtrialN$n != 9),]

wtriald  <- list()
wtrialdR = 0

for(i in 1:nrow(wtrialN)) {
  
  wtrialdR = wtrialdR + 1
  
  wtriald[[wtrialdR]] <- 
    cdata[which(cdata$subid %in% wtrialN[i,"subid"] & cdata$text %in% wtrialN[i, "text"]),]
}

wtriald <- do.call(rbind, wtriald)

wtriald <- cbind(wtriald, sequence(wtrialN$n), rownames(wtriald))

# Check wtriald and raw data file, vary from case to case
excluderow <- wtriald[9:16, "rownames(wtriald)"]

cdata <- cdata[!rownames(cdata) %in% excluderow,] 

num_trial <- cdata %>% dplyr::count(subid) 


if (sum(num_trial$n %% 9) != 0) {
   stop("Check the number of trials for these participants:")
   print(num_trial[which(num_trial$n != 234),])
 }
```


# Add text to story 26 first sentence so that key can be merged to cdata correctly
```{r}
cdata[which(cdata$fname=="backup4"), "text"] <-
  paste(cdata[which(cdata$fname=="backup4"), "text"], "bp")
```

# Manual checking for trials that are missing text
```{r}
cdata[which(cdata$text == ""),]$text <- as.character(stim_ver[20]$text)

cdata[which(rownames(cdata) == 21898),]
```

# Load answer keys
```{r}
key <- read.csv("key.csv")
key <- key[-c(10:14),]
key <- melt(key, id.vars = "Answer")
colnames(key) <- c("trial", "story", "key")
```


# Calculate initial accuracy before typos are manually corrected, remove outliers
```{r}
cdata$trial <- rep(unique(key$trial), length(cdata$answer)/length(unique(key$trial)))

detach("package:dplyr")

library(plyr)

cdata <- join(cdata, stim_ver)

cdata <- join(cdata, key)

cdata$answer <- as.character(cdata$answer)
cdata$key <- as.character(cdata$key)

accuracy <- ifelse(cdata$answer == cdata$key,1,0)

cdata <- cbind(cdata, as.data.frame(accuracy))

length(unique(cdata$story))

print(unique(cdata$story))
```



```{r}
detach("package:plyr")

library(dplyr)


prelim_acc <-
  cdata %>%
  group_by(subid) %>%
  dplyr::summarise(correct_trial = sum(accuracy), total_trial = n(),accuracy = sum(accuracy)/ n())


# This outlier is also the out of timelimit part, did not complete the study.
prelim_outlier <- prelim_acc[which(prelim_acc$accuracy < 0.5), "subid"]
print(prelim_outlier)


# if(nrow(prelim_outlier) != 0) {
#   cdata <- cdata[-which(cdata$subid %in% prelim_outlier),]
#   stop("Check preliminary accuracy outliers")
#   print(prelim_outlier)
# }

prelim_acc_by_story <-
  cdata %>%
  group_by(story) %>%
  dplyr::summarise(correct_trial = sum(accuracy), total_trial = n(),accuracy = sum(accuracy)/ n())

print(prelim_acc_by_story)


write.csv(cdata, "cdata.csv")
```
**Accuracy lower than 50% before typo is removed: `r prelim_outlier`** Same as the incomplete part. Removed.


# Check Typos
```{r}
write.table(cdata$answer, file = "answer.txt", sep = "\t",
            row.names = F, col.names = F)

library(spelling)
typo <- spell_check_files("answer.txt", lang = "en_US")
print(typo)

typo_row <- gsub("answer.txt:", "", typo$found)

typo_row <- as.numeric(as.character(unlist(strsplit(typo_row, ","))))

cdata[typo_row, "typo"] <- 1

write.csv(cdata, "/Users/jojohu/Documents/Splash/cloze_analysis/typo.csv")
```

# Manual cleaning of typo
**Save manually cleaned typo and accuracy to typo_checked.csv**

# Calculate Accuracy after manual typo correction 
```{r}
library(dplyr)
library(stringr)

cdata <- read.csv("typo_checked.csv")

cdata<- cdata[!colnames(cdata) %in% "accuracy"]
  
cdata$answer <- as.character(cdata$answer)
cdata$key <- as.character(cdata$key)

# Get rid of all non-alphabetic characters
cdata$answer <- str_extract(cdata$answer, "[:alpha:]+")

accuracy <- ifelse(cdata$answer == cdata$key,1,0)

cdata<- cbind(cdata, as.data.frame(accuracy))

# cdata[which(cdata$story == "story21_fir" & is.na(cdata$accuracy)), "accuracy"] <- 0
           


acc_by_story <-
  cdata %>%
  group_by(story) %>%
  dplyr::summarise(correct_trial = sum(accuracy), total_trial = n(),accuracy = sum(accuracy)/ n())

which(is.na(cdata[which(cdata$story == "story21_fir"),"accuracy"]))

print(acc_by_story)

# write.csv(cdata, "wrong_answer.csv")
```

# Manual cleaning of wrong answers due to real synonymns (airplane-plane) 
Automate cleaning of formating error (extra space, etc.)

**Save manually cleaned typo and accuracy to typo_checked.csv**

# Generate wrong answers
```{r}
detach("package:dplyr")

library(plyr)

cdata <- join(cdata, stim_long)

cdata <- cdata[, -which(names(cdata) == "text")]

wrong_answer <- cdata[which(cdata$accuracy == 0),]

write.csv(wrong_answer, "wrong_answer.csv", row.names = FALSE)

detach("package:plyr")

library(dplyr)

wans_count <-
  wrong_answer %>%
  group_by(story, trial) %>%
  dplyr::summarise(n = n())

# wcount <- wans_count[which(wans_count$n > 3),]

highw <- 
  merge(wcount, wrong_answer, by = c("story", "trial"), all.x = T)

highw <-highw[!names(highw) %in% "fname"]

write.csv(highw, "wrong_trials.csv", row.names = FALSE)
```


# Recalculate Accuracy after answer key and synonym checked 
```{r}
cdataFinal <- read.csv("wrong_answer_all_corrected.csv")

cdataFinal <- cdataFinal[!colnames(cdataFinal) %in% "accuracy"]
  
cdataFinal$answer <- as.character(cdataFinal$answer)
cdataFinal$key <- as.character(cdataFinal$key)

# # Get rid of all non-alphabetic characters
# cdata$answer <- str_extract(cdata$answer, "[:alpha:]+")

accuracy <- ifelse(cdataFinal$answer == cdataFinal$key,1,0)

cdataFinal<- cbind(cdataFinal, as.data.frame(accuracy))

# cdata[which(cdata$story == "story21_fir" & is.na(cdata$accuracy)), "accuracy"] <- 0
```

```{r}
noun_condition <- read.csv("/Users/jojohu/Documents/Splash/cloze_analysis/stim_word/noun_cond_key.csv")

verb_condition <- read.csv("/Users/jojohu/Documents/Splash/cloze_analysis/stim_word/verb_cond_key.csv")

allCond <- rbind(noun_condition, verb_condition)

cdataFinal <- merge(cdataFinal, allCond, by = c("story", "trial"), all.x = T)

noun_story <- c("story1_fir",
                       "story2_fir",
                       "story3_fir",
                       "story4_fir",
                       "story5_fir",
                       "story6_fir",
                       "story7_fir",
                       "story8_fir",
                       "story9_fir",
                       "story10_fir",
                       "story21_fir")

cdataFinal[which(cdataFinal$story %in% noun_story), "word_class"] <- "noun"

cdataFinal[which(!cdataFinal$story %in% noun_story), "word_class"] <- "verb"


# All stories

acc_by_story <- 
  cdataFinal %>%
  group_by(story) %>%
  dplyr::summarise(correct_trial = sum(accuracy), total_trial = n(),accuracy = sum(accuracy)/ n())

print(acc_by_story)

# All Nouns
# All Verbs
cdataFinal[which(cdataFinal$word_class == "noun"),] %>%
  group_by(story, condition) %>%
  dplyr::summarise(correct_trial = sum(accuracy), total_trial = n(),accuracy = sum(accuracy)/ n())


# All Verbs
verbAcc <- 
cdataFinal[which(cdataFinal$word_class == "verb"),] %>%
  group_by(story, condition, trial) %>%
  dplyr::summarise(correct_trial = sum(accuracy), total_trial = n(),accuracy = sum(accuracy)/ n())


cdataFinal[which(cdataFinal$word_class == "noun"),] %>%
  group_by(story, condition, trial) %>%
  dplyr::summarise(correct_trial = sum(accuracy), total_trial = n(),accuracy = sum(accuracy)/ n())


verbAccStory <- 
  cdataFinal[which(cdataFinal$word_class == "verb"),] %>%
  group_by(story, condition) %>%
  dplyr::summarise(correct_trial = sum(accuracy), total_trial = n(),accuracy = sum(accuracy)/ n())

keyVerbLearn <- verbAcc[which(verbAcc$accuracy > 0.9 & verbAcc$condition == "M+"), c("story", "word")]

verbAccStory[which(verbAccStory$accuracy > 0.87), 
                    # & verbAccStory$condition == "M+"), 
             c("story", "condition")]



write.table(keyVerbLearn, "/Users/jojohu/Documents/Splash/cloze_analysis/stim_word/keyVerbLearn.txt", row.names = F, col.names = F, quote = F)
```

# Accuracy by condition
```{r}
acc_noun <- cdataFinal[which(cdataFinal$story %in% noun_story), 
                       c("subid", "story", "trial", "condition", "key", "answer", "accuracy", "word_class")]

acc_verb <- cdataFinal[-which(cdataFinal$story %in% noun_story), 
                       c("subid", "story", "trial", "condition", "key", "answer", "accuracy", "word_class")]


acc_noun$story <- as.factor(acc_noun$story)
acc_noun$subid <- as.factor(acc_noun$subid)
acc_noun$trial <- as.factor(acc_noun$trial)
acc_noun$condition <- as.factor(acc_noun$condition)
# acc_noun$accuracy <- as.factor(acc_noun$accuracy)

# head(acc_noun)

# library(lmerTest)

# acc_m1 <-
#   glmer(accuracy~story*condition  + (1 + condition| story) + (1 | subid), data = acc_noun,
#     family = binomial,control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
# 
# summary(acc_m1)


accN_by_trial <- 
acc_noun %>%
  group_by(story, condition) %>%
  dplyr::summarise(correct_trial = sum(accuracy), total_trial = n(),accuracy = sum(accuracy)/ n())

head(accN_by_trial)

library(ez)
ezANOVA(accN_by_trial, accuracy, wid = story, within = condition, type = 3, detailed = T)


acc_noun %>%
  group_by(story, condition) %>%
  dplyr::summarise(correct_trial = sum(accuracy), total_trial = n(),accuracy = sum(accuracy)/ n())
```


