---
title: "splash_beh_analysis"
author: "Jojo Hu"
date: "10/1/2021"
output: html_document
---
# Data Prep
## Get Demo Data
```{r, include = F}
library(stringr)

smile_demo <- read.csv("/Users/jojohu/Documents/Splash/beh_analysis/demo/MINDSPLASH-Smilechilddob_DATA_2022-11-07_0940.csv")

smile_demo$group <- ifelse(smile_demo$participant_group___1 == 1, "TD", "ASD")

smile_demo$participant_gender <- as.character(smile_demo$participant_gender)
# SMILE redcap has gender coding reversed... Fix this somewhere
smile_demo$participant_gender <- plyr::revalue(smile_demo$participant_gender, 
                                          c("1" = "M",
                                            "2" = "F"))

smile_demo <- smile_demo[,c("record_id", "group", "participant_gender", "participant_dob")]

smile_demo$short_id <- str_remove(smile_demo$record_id, "smile_c_")
smile_demo[which(smile_demo$record_id == "smile_c_008"), "short_id"] <- "smileCoo8"
```

## Get Ipad Data
```{r, include = F}
library(reshape2)
library(dplyr)
library(purrr)

ipad <-
  list.files(path = "/Users/jojohu/Documents/Splash/beh_analysis/ipad",
             pattern = "[[:digit:]] Assessment Scores.csv$", full.names = T, recursive = T)

ipadNAS <-
  list.files(path = "/Volumes/data/projects/smile/assessments/nih",
             pattern = "[[:digit:]] Assessment Scores.csv$", full.names = T, recursive = T)


ipad <- append(ipad, ipadNAS)

readIpad <- function(file) {
  temp <- read.csv(file, stringsAsFactors = F)
  return(temp)
}

# ipad <- lapply(ipad, readIpad)
# ipad <- do.call(bind_rows, ipad)

ipad <- 
  lapply(ipad, readIpad) %>%
  map_dfr(`[`, c("PIN", "Inst", "Uncorrected.Standard.Score",	"Age.Corrected.Standard.Score",	"National.Percentile..age.adjusted."))  %>%
  dplyr::bind_rows()

ipad <- ipad[,c("PIN", "Inst", "Uncorrected.Standard.Score",	"Age.Corrected.Standard.Score",	"National.Percentile..age.adjusted.")]
colnames(ipad) <- c("part_id", "ast", "raw_score", "std_score", "national_percentile")
ipad$part_id <- tolower(ipad$part_id)
ipad$ast <- str_extract(ipad$ast, "(Picture Vocab|Oral Reading)")

if(length(which(is.na(ipad$ast) | which(is.na(ipad$raw_score))))) {
  ipad <- ipad[-which(is.na(ipad$ast)),]
  ipad <- ipad[-which(is.na(ipad$raw_score)),]
}

ipad$ast <- 
  ipad$ast %>%
  str_replace_all(c("Picture Vocab" = "pvt", "Oral Reading" = "orr"))

# Very important to make sure that there is a unique identifier for every participant, thus no duplicated lines
ipad <- unique(ipad)

ipadL <- melt(ipad, id.vars = c("part_id", "ast"))

ipadL <-
  ipadL %>%
  filter(part_id != "smile_c_300") %>%
  filter(part_id != "test")

ipadL <- unique(ipadL)

ipadL <- 
  ipadL %>%
  filter(!str_detect(part_id, "test"))
```


```{r}
# Very important to get rid of duplicated IDs in the data frame for this to work:
ipad <- reshape2::dcast(ipadL, part_id ~ ast + variable)

ipad[which(ipad$part_id == "smile_c-206"),]$part_id <- "smile_c_206"
ipad[which(ipad$part_id == "ethan"),]$part_id <- "smile_c_001"
ipad[which(ipad$part_id == "smile_c_446"),]$part_id <- "smile_c__446"

nih_data <- ipad[which(str_detect(ipad$part_id, "smile") | str_detect(ipad$part_id, "blast")),]

# write.csv(ipad, "/Users/jojohu/Documents/Splash/beh_analysis/demo/ipad_scores.csv")
# write.csv(nih_data, "/Users/jojohu/Documents/Splash/beh_analysis/demo/smile_blast_nih_data.csv")
# write.csv(nih_data, "/Volumes/data/projects/smile/assessments/nih/smile_blast_nih_data.csv")
```

## Get Social Cognition Data
```{r, include = F}
scq <- read.csv("/Users/jojohu/Documents/Splash/beh_analysis/social_cognition/scq_scores_smile.csv")
mite <- read.csv("/Users/jojohu/Documents/Splash/beh_analysis/social_cognition/Mind in the Eyes_November 8, 2022_07.03.csv", stringsAsFactors = F)

# TO DO: Still need to fix the SCQ scoring and ID matching to avoid duplicationS
scq <- 
  scq %>% 
  distinct(record_id, .keep_all = TRUE)

ipad <- merge(ipad, scq[,c("record_id", "scq_total", "scq_rsid", "scq_cd", "scq_rrspb")], 
              by.x = c("part_id"), by.y = c("record_id"), all = T)

colnames(mite) <- mite[1,]

mite <- mite[-c(1:2),]

mite$record_id <- mite[,c("Please input the SMILE ID numbers here (ex: 001):")]

mite <- mite[,c("record_id", "Recorded Date", "Score")]

# 001 seems to be a test, remove it
mite <-
  mite %>%
  dplyr::filter(!record_id %in% c("001"))

mite[which(!str_detect(mite$record_id, "smile")),]$record_id <- 
  paste0("smile_c_", mite[which(!str_detect(mite$record_id, "smile")),]$record_id)

mite <- mite[which(str_detect(mite$record_id, "smile_c_[:digit:]")),]

mite$Score <- as.numeric(as.character(mite$Score))

mite <- mite[which(!is.na(mite$Score)),]

colnames(mite)[colnames(mite) == "Score"] <- "mite_total_score"

mite_more <-
  list.files(path = "/Volumes/data/projects/smile/assessments/mite",
             pattern = "smile*", full.names = T, recursive = T)

library("readxl")

excel <- ""

readMite <- function(file) {
  if(str_detect(file, "xlsx")) {
    part_id <- str_extract(file, "smile_c_[:digit:]+")
    excel <- readxl::read_excel(file)
    excel$part_id <- part_id
  }
  return(excel)
}

mite_excel <- lapply(mite_more, readMite)

csv <- ""

readMiteCSV <- function(file) {
  if(str_detect(file, "csv")) {
    part_id <- str_extract(file, "smile_c_[:digit:]+")
    csv <- read.csv(file, stringsAsFactors = F)
    csv$part_id <- part_id
  }
  return(csv)
}

mite_csv <- lapply(mite_more, readMiteCSV)

mite_excel <- do.call(rbind, mite_excel)
mite_csv <- do.call(rbind, mite_csv)

mite_more <- dplyr::bind_rows(mite_excel, mite_csv)

mite_more <- 
  mite_more %>%
  mutate(mite_indiv_score = ifelse(Response == ANSWER,1,0)) %>%
  filter(display == "task") %>%
  dplyr::select(part_id, Response, ANSWER, mite_indiv_score) %>%
  group_by(part_id) %>%
  dplyr::summarise(mite_total_score = sum(mite_indiv_score), n = n()) %>%
  mutate(record_id = part_id) %>%
  # Check if there are participants who are missing items (Anwer is No)
  # filter(n != 14) %>%
  dplyr::select(record_id, mite_total_score)

mite <- 
  dplyr::bind_rows(mite, mite_more) %>%
  arrange(record_id)

# ipad <- lapply(ipad, readIpad)
# ipad <- do.call(bind_rows, ipad)
# ipad <- 
#   lapply(ipad, readIpad) %>%
#   map_dfr(`[`, c("PIN", "Inst", "Uncorrected.Standard.Score",	"Age.Corrected.Standard.Score",	"National.Percentile..age.adjusted."))  %>%
#   dplyr::bind_rows()

ipad <- merge(ipad, mite[,c("record_id", "mite_total_score")], 
              by.x = c("part_id"), by.y = c("record_id"), all = T)

ipad <-
  ipad %>%
  distinct(.)

# Duplicated scores for smile_c_292 MITE (did twice, but did not have SPLASH data)
ipad[which(duplicated(ipad$part_id)),]
```


## Compile all Data
```{r, include = F}
library(stringr)
library(dplyr)

output_path <- "/Users/jojohu/Documents/Splash/beh_analysis/results/"
# https://stackoverflow.com/questions/28700906/r-rbind-a-list-of-data-frames-with-different-columns-in-different-data-frames
behDF <-
  list.files(path = "/Users/jojohu/Documents/Splash/beh_analysis",
             pattern = "data\\S+.csv$", full.names = T, recursive = T)

behDF <- lapply(behDF, read.csv)

# Rbind data frames with different column length, fill = TRUE fills nonmatched columns with NA in the nonmatched dataframe
library(data.table)
indx <- sapply(behDF, ncol)
behDF <- lapply(split(behDF, indx), rbindlist, fill=TRUE )

# Data with 51 columns actually did not have data; failed at eye tracking tests
behDF <- behDF[-which(names(behDF) %in% c(51, 53))]

colList <- sapply(behDF, colnames)
colList <- Reduce(intersect, colList)

behDF <- rbindlist(behDF, fill=TRUE)
behDF$Response <- as.character(behDF$Response)
behDF <- behDF[which(behDF$Response != ""),]
```


```{r}
behDF$Participant.Public.ID <- str_pad(behDF$Participant.Public.ID, 3, pad = "0")
behDF$Participant.Public.ID <- as.character(behDF$Participant.Public.ID)
behDF[which(!str_detect(behDF$Participant.Public.ID, "smile")),]$Participant.Public.ID <- 
  paste0("smile_c_", behDF[which(!str_detect(behDF$Participant.Public.ID, "smile")),]$Participant.Public.ID)

behDF <- merge(behDF, smile_demo[,c("record_id", "short_id")], by.x = "Participant.Public.ID", by.y = "short_id", all.x = T)

behDF[which(!is.na(behDF$record_id)),]$Participant.Public.ID <- behDF[which(!is.na(behDF$record_id)),]$record_id
 
# Remove pilot participants and smile_c_011 who only completed half of the task; smile_c_023 did the task over three weeks:
behDF <- behDF[-which(behDF$Participant.Public.ID == "smile_c_test7" | behDF$Participant.Public.ID == "smile_c_011" | behDF$Participant.Public.ID == "smile_c_904_1"),]

behDF$Participant.Public.ID <- str_extract(behDF$Participant.Public.ID, "smile_c_[[:alnum:]]+")

behDF %>%
  filter(is.na(Participant.Public.ID)) %>%
  dplyr::select(Participant.Private.ID)

sort(unique(behDF$Participant.Public.ID))

# Wrong ID was used on Gorilla SPLASH project, must be corrected
behDF[which(behDF$Participant.Public.ID == "smile_c_384"),]$Participant.Public.ID <- "smile_c_449"
```

## Merge Demo and medium split age group
```{r, include = F}
behDF <- merge(behDF, smile_demo, by.x = "Participant.Public.ID", by.y = "record_id", all.x = T)

# https://stackoverflow.com/questions/13456241/convert-unix-epoch-to-date-object
behDF$UTC.Date <- as.Date(as.POSIXct(behDF$UTC.Timestamp/1000, origin="1970-01-01"))

behDF$participant_dob <- as.Date(behDF$participant_dob, "%Y-%m-%d")

behDF %>%
  group_by(group) %>%
  dplyr::summarise(n = length(unique(Participant.Public.ID)))

behDF %>%
  filter(is.na(group)) %>%
  dplyr::select(Participant.Private.ID) %>%
  distinct(.)

private_id <-
  behDF %>%
  dplyr::select(Participant.Public.ID, Participant.Private.ID) %>%
  distinct(.)

id_group <-
  behDF %>%
  dplyr::select(Participant.Public.ID, group) %>%
  distinct(.)

write.csv(private_id, "/Users/jojohu/Documents/Splash/beh_analysis/demo/private_id.csv", row.names = F)
write.csv(id_group, "/Users/jojohu/Documents/Splash/beh_analysis/demo/group.csv", row.names = F)
```


# Immediate Recall Analysis
## Immediate Recall Data Clean up
```{r, include = F}
library(stringr)
immRe <- behDF[which(str_detect(behDF$display, ("videoblock|videoblock_verb"))), ]

splash_date <- unique(immRe[,c("Participant.Public.ID", "UTC.Date", "participant_dob")])
#Calculate age in months---------------------------------------------------------------------------------------------
#From Stackoverflow: https://stackoverflow.com/questions/1995933/number-of-months-between-two-dates
#Answer by https://stackoverflow.com/users/143305/dirk-eddelbuettel
#Credit to: Dirk Eddelbuettel

# turn a date into a 'monthnumber' relative to an origin
monnb <- function(d) {
  lt <- as.POSIXlt(as.Date(d, origin="1900-01-01"))
  lt$year*12 + lt$mon
  } 
# compute a month difference as a difference between two monnb's
mondf <- function(d1, d2) { 
  monnb(d2) - monnb(d1) 
}

#Put month difference into a new column
for (i in 1:length(splash_date$participant_dob)) { 
  if (!is.na(splash_date[i, "UTC.Date"])) {
    splash_date[i, "age_month"] <-
      mondf(splash_date$participant_dob[i], splash_date$UTC.Date[i])
  } 
}

splash_date$age_year <- splash_date$age_month/12

immRe <- merge(immRe, splash_date, by = c("Participant.Public.ID", "UTC.Date", "participant_dob"), all.x = T)


immRe <- immRe[,c("Participant.Public.ID", "group", "participant_gender", "age_month", "age_year", 
                  "Response", "video_file", "UTC.Date", "Event.Index", "Spreadsheet", "Spreadsheet.Row", "Task.Name",
                  "block", "target", "text_dist",	"taxonomic_dist",	"thematic_dist")]
immRe <- immRe[which(str_detect(immRe$Response, "(jpg|png)")),]

immRe$video_file <- gsub("$", "", immRe$video_file, fixed = T)
immRe$video_file <- gsub("{", "", immRe$video_file, fixed = T)
immRe$video_file <- gsub("_v1|.mp4|}", "", immRe$video_file)

immRe$Response <- gsub("transparent_|.png", "", immRe$Response)


immRe$story <- sapply(strsplit(immRe$video_file,"_"), `[`, 1)
immRe$social_cond <- sapply(strsplit(immRe$video_file,"_"), `[`, 2)
immRe$listener_side <- sapply(strsplit(immRe$video_file,"_"), `[`, 4)
immRe[which(is.na(immRe$listener_side)), "listener_side"] <- "left"
immRe$speaker_side <- NULL
immRe[which(immRe$listener_side == "right"), "speaker_side"] <- "left"
immRe[which(immRe$listener_side == "left"), "speaker_side"] <- "right"
```

# Demo Summary
```{r}
demo_wide <- 
  immRe %>%
  dplyr::select(Participant.Public.ID, group, age_year) %>%
  distinct(.) %>%
  group_by(group) %>%
  filter(!(Participant.Public.ID == "smile_c_006" & age_year == 8)) %>%
  filter(!(Participant.Public.ID == "smile_c_037" & age_year == 6)) %>%
  # filter(age_year < 10) %>%
  mutate(group = as.factor(group), 
         age_month = age_year*12)

demo_wideTD <-
  demo_wide %>%
  filter(group == "TD") %>%
  mutate(age_group = c("older", "younger")[1 + (age_year <= median(age_year))])

demo_wideASD <-
  demo_wide %>%
  filter(group == "ASD") %>%
  mutate(age_group = c("older", "younger")[1 + (age_year <= median(age_year))])

demo_wide <- rbind(demo_wideTD, demo_wideASD)

immRe <- immRe[which(immRe$Participant.Public.ID %in% demo_wide$Participant.Public.ID),]

immRe <-
  immRe %>%
  dplyr::select(-one_of("age_year", "age_month"))

immRe <- merge(immRe, demo_wide[c("Participant.Public.ID", "group", "age_year", "age_month", "age_group")], 
               by = c("Participant.Public.ID", "group"), all.x = T)

immRe %>%
  dplyr::select(Participant.Public.ID, age_year) %>%
  distinct(.) %>%
  group_by(Participant.Public.ID) %>%
  dplyr::summarise(n = n()) %>%
  filter(n > 1)

demo_wide %>%
  group_by(group) %>%
  distinct(.) %>%
  dplyr::summarise(mean_age = mean(age_year, na.rm = T), 
                   min = min(age_year, na.rm = T), 
                   max = max(age_year, na.rm = T),
                   sd = sd(age_year, na.rm = T)) %>%
  mutate_if(is.numeric, round, digits=2)


immRe %>%
  dplyr::select(Participant.Public.ID, group, participant_gender) %>%
  distinct(.) %>%
  group_by(group, participant_gender) %>%
  dplyr::summarise(n = n()) %>%
  tidyr::spread(participant_gender, n)


demo_wide %>%
  group_by(group, age_group) %>%
  distinct(.) %>%
  dplyr::summarise(mean_age = mean(age_year, na.rm = T), 
                   min = min(age_year, na.rm = T), 
                   max = max(age_year, na.rm = T),
                   sd = sd(age_year, na.rm = T),
                   n = n()) %>%
  mutate_if(is.numeric, round, digits=2)
```

# Demo Analyses
```{r}
# Age
t.test(age_year~group, data = demo_wide)

# Gender
library(reshape)

gender_wide <- 
  immRe %>%
  dplyr::select(Participant.Public.ID, group, participant_gender) %>%
  distinct(.) 

gender_long <- melt(gender_wide, id.vars = c("Participant.Public.ID", "group"))

gender_wide <- cast(gender_long, group~value, length)

# Chi-square on gender
# p<0.05 tells us that they are not matched for gender between group
print(chisq.test(gender_wide))

```



```{r, eval = F, include = F}
# Match between groups

# library(MatchIt)  
# 
# matchFunc <- function(seed, dataf) {
#   set.seed(seed)
#   
#   matchit <-matchit(group ~ age_year, data = dataf, method="optimal")
#   
#   m.data1 <- match.data(matchit, data = dataf, distance = "prop.score")
#   
#   m.data2 <- m.data1[,c("Participant.Public.ID", "group", "age_year")]
#   
#   m.data2ASD <- subset(m.data2, group == "ASD")
#   m.data2TD <- subset(m.data2, group == "TD")
# 
#   outputDF <- dataf[which(dataf$Participant.Public.ID %in% m.data2$Participant.Public.ID),]
#   
#   return(outputDF)
# }
# 
# demo_wide <- matchFunc(1234, demo_wide)
# 
# demo_wide %>%
#   group_by(group) %>%
#   dplyr::summarise(n = n(), age = mean(age_year), sd = sd(age_year), min_age = min(age_year), max_age = max(age_year)) %>%
#   mutate_if(is.numeric, round, 2)
# 
# immRe <- immRe[which(immRe$Participant.Public.ID %in% demo_wide$Participant.Public.ID),]
```


```{r, include = F}
library(dplyr)
library(reshape2)
answer <- read.csv("/Users/jojohu/Documents/Splash/design/bigListA.csv", stringsAsFactors = F)[,c("story", "novel_word", "key", "word_type",
                                                                                                  "thematic_dist", "text_dist", "taxonomic_dist", 
                                                                                                  "thematic_pdist", "text_pdist", "taxonomic_pdist")]
answer <- unique(answer)

# Find the actual verb trial responses
colImm <- c("Participant.Public.ID", "video_file", "story", "target", "text_dist",	"taxonomic_dist",	"thematic_dist")

longVerb <- melt(immRe[, ..colImm], id.vars = c("Participant.Public.ID", "video_file", "story"))
longVerb <- unique(longVerb)
  
colnames(longVerb)[colnames(longVerb) %in% "variable"] <- "verb_key"
colnames(longVerb)[colnames(longVerb) %in% "value"] <- "verb_response"

immRe <- merge(immRe, longVerb, by.x = c("Participant.Public.ID", "video_file",  "story", "Response"), 
               by.y = c("Participant.Public.ID", "video_file", "story", "verb_key"), all.x = T)
  
immRe[which(!is.na(immRe$verb_response)), "Response"] <- immRe[which(!is.na(immRe$verb_response)), "verb_response"]

# Remove the wrong immediate test trials (very few participants had wrong story and test phase match due to Gorilla errors)
longVerb <-
  longVerb %>%
  arrange(Participant.Public.ID, story, video_file)

answerL <- unique(melt(answer[,c("story", "key", "text_dist",	"taxonomic_dist",	"thematic_dist")], id.vars = c("story")))

longVerb <- merge(longVerb, answerL, by.x = c("story", "verb_response"), by.y = c("story", "value"), all.x = T)
```

```{r, include = F}
# Extract and remove the wrong story trials for the corresponding participants
wrongTrial <- unique(longVerb[which(is.na(longVerb$variable)),])

wrongTest <- immRe[which(immRe$Participant.Public.ID %in% wrongTrial$Participant.Public.ID & 
                        immRe$video_file %in% wrongTrial$video_file),]

if(nrow(wrongTrial) > 0) {
  immRe <- immRe[-which(immRe$Participant.Public.ID %in% wrongTrial$Participant.Public.ID & 
                        immRe$video_file %in% wrongTrial$video_file),]
}
# Remove the multiple keypresses, take the last keypress
# immRe <- unique(immRe)
immRe <- 
  immRe %>%
  group_by(Participant.Public.ID, story, video_file) %>%
  arrange(Participant.Public.ID, story, video_file, Event.Index) %>%
  filter(row_number()==n())

# Make sure there is only one trial per story per participant, 0 rows expected
immRe %>%
  group_by(Participant.Public.ID, story) %>%
  dplyr::summarise(n = n()) %>%
  filter(n > 1)

nrow(immRe) == nrow(unique(immRe[,c("Participant.Public.ID", "video_file")]))

## Save this for extracting eye tracking videos to code
# write.csv(immRe, "/Users/jojohu/Documents/Splash/beh_analysis/results/immRe.csv", row.names = F)
```



## Calculate Immediate Recall Accuracy
```{r, include = F}
immRe <- merge(immRe, answer[,c("story", "key", "word_type")], by.x = "story", by.y = "story", all.x = T)
# To Do: Manually Score the participant that does not have verb story scores and merge smile_c_003 data
immRe[which(str_detect(immRe$Response,"transparent")), "Response"] <- NA

immRe$corr <- ifelse(immRe$Response ==immRe$key, 1, 0)

write.csv(immRe, "/Users/jojohu/Documents/Splash/beh_analysis/results/immRe_data.csv", row.names = F)
```



## Change data and subset groups (Change who to include based on trial numbers)
**n > 1: include everyone; n > 20: include full data set**
```{r}
# Remove those that have too few learning trials
fullImmID <-
  immRe %>%
  group_by(Participant.Public.ID, story) %>%
  distinct(.) %>%
  group_by(Participant.Public.ID) %>%
  dplyr::summarise(n = n()) %>%
  filter(n > 1)

immRe <- immRe[which(immRe$Participant.Public.ID %in% fullImmID$Participant.Public.ID),]
```

```{r}
immRe$group <- as.factor(immRe$group)
immRe$age_group <- as.factor(immRe$age_group)
immRe$social_cond <- as.factor(immRe$social_cond)
immRe$word_type <- as.factor(immRe$word_type)
immRe$Participant.Public.ID <- as.factor(immRe$Participant.Public.ID)

immRe$scaled_age <- scale(immRe$age_year, center = T)

immRe <- merge(immRe, ipad, by.x = "Participant.Public.ID", by.y = "part_id", all.x = T)

immRe$group <- factor(immRe$group, levels = c("ASD", "TD"))
immRe <- immRe[order(immRe$group),]

immRe$social_cond <- factor(immRe$social_cond, levels = c("front", "side"))
immRe <- immRe[order(immRe$social_cond),]

immRe$word_type <- factor(immRe$word_type, levels = c("noun", "verb"))
immRe <- immRe[order(immRe$word_type),]

immReTD <- immRe[which(immRe$group == "TD"),]
immReASD <- immRe[which(immRe$group == "ASD"),]

immReTD$social_cond <- factor(immReTD$social_cond, levels = c("front", "side"))
immReTD <- immReTD[order(immReTD$social_cond),]

immRe %>%
  group_by(group, social_cond) %>%
  dplyr::summarise(n = sum(length(unique(Participant.Public.ID))))
```


# Immediate Recall Group Analysis (Binomial Accuracy Models)
```{r}
library(lmerTest)

simple_immRe <- glmer(corr ~ group*social_cond + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                   data = immRe,
                   family = binomial,
                   contrasts = list(group = c(-0.5, 0.5), 
                                    social_cond = c(-0.5, 0.5)),
                   control = glmerControl(optimizer = "bobyqa"))

summary(simple_immRe)

simple_immRe2 <- glmer(corr ~ group*social_cond*scaled_age + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                   data = immRe,
                   family = binomial,
                   contrasts = list(group = c(-0.5, 0.5), 
                                    social_cond = c(-0.5, 0.5)),
                   control = glmerControl(optimizer = "bobyqa"))

summary(simple_immRe2)

m1_immRe <- glmer(corr ~ group*social_cond*scaled_age*word_type + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                   data = immRe,
                   family = binomial,
                   contrasts = list(group = c(-0.5, 0.5), 
                                    social_cond = c(-0.5, 0.5), 
                                    word_type = c(-0.5, 0.5)),
                   control = glmerControl(optimizer = "bobyqa"))

summary(m1_immRe)

## with PVT and MITE (Need to scale them as the scores have larger range)
immRe$scaled_pvt_all <- scale(immRe$pvt_std_score)
immRe$scaled_mite_all <- scale(immRe$mite_total_score)

m2_immRe <- glmer(corr ~ group*social_cond*scaled_age*word_type*scaled_pvt_all + 
                    (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                   data = immRe,
                   family = binomial,
                   contrasts = list(group = c(-0.5, 0.5), 
                                    social_cond = c(-0.5, 0.5), 
                                    word_type = c(-0.5, 0.5)),
                   control = glmerControl(optimizer = "bobyqa"))

summary(m2_immRe)

m3_immRe <- glmer(corr ~ group*social_cond*scaled_age*word_type*scaled_mite_all + 
                    (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                   data = immRe,
                   family = binomial,
                   contrasts = list(group = c(-0.5, 0.5), 
                                    social_cond = c(-0.5, 0.5), 
                                    word_type = c(-0.5, 0.5)),
                   control = glmerControl(optimizer = "bobyqa"))

summary(m3_immRe)
```


## Follow up for Immediate Recall Group Analysis By Diagnostic Group
## Immediate Recall TD Analysis
```{r}
immReTD$scaled_age_td <- scale(immReTD$age_year)

simple_immReTD <- glmer(corr ~ social_cond + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                   data = immReTD,
                   family = binomial,
                   contrasts = list(social_cond = c(-0.5, 0.5)),
                   control = glmerControl(optimizer = "bobyqa"))

summary(simple_immReTD)

simple_immReTD2 <- glmer(corr ~ social_cond*scaled_age_td + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                   data = immReTD,
                   family = binomial,
                   contrasts = list(social_cond = c(-0.5, 0.5)),
                   control = glmerControl(optimizer = "bobyqa"))

summary(simple_immReTD2)

m1_immReTD <- glmer(corr ~ social_cond*scaled_age_td*word_type + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                   data = immReTD,
                   family = binomial,
                   contrasts = list(social_cond = c(-0.5, 0.5),
                                    word_type = c(-0.5, 0.5)),
                   control = glmerControl(optimizer = "bobyqa"))

summary(m1_immReTD)


# with PVT and MITE
immReTD$scaled_pvt_std <- scale(immReTD$pvt_std_score)
immReTD$scaled_mite <- scale(immReTD$mite_total_score)

m3_immReTD <- glmer(corr ~ social_cond*word_type*scaled_age_td*scaled_mite + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                   data = immReTD,
                   family = binomial,
                   contrasts = list(social_cond = c(-0.5, 0.5), 
                                    word_type = c(-0.5, 0.5) ),
                   control = glmerControl(optimizer = "bobyqa"))

summary(m3_immReTD)

m2_immReTD <- glmer(corr ~ social_cond*word_type*scaled_age_td*scaled_pvt_std + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                   data = immReTD,
                   family = binomial,
                   contrasts = list(social_cond = c(-0.5, 0.5), 
                                    word_type = c(-0.5, 0.5) ),
                   control = glmerControl(optimizer = "bobyqa"))

summary(m2_immReTD)
```

## Prep Plotting
```{r, include = F}
library(ggplot2)
styling <-
  theme(
      plot.title = element_text(size = 30, face = "bold"),
      axis.title.x = element_text(size = 26, face = "bold"),
      axis.title.y = element_text(size = 22, face = "bold"),
      axis.text = element_text(size = 24, face = "bold"),
      legend.text = element_text(size = 22, face = "bold"),
      legend.title = element_text(size = 22, face = "bold"),
      panel.background = element_rect(fill = "white"),
      # Set plot background to whit
      axis.line.x = element_line(colour = "black", size = 1),
      # Add line to x axis
      axis.line.y = element_line(colour = "black", size = 1),
      # Add line to y axis
      strip.text = element_text(size = 24, face = "bold"),
      # Change facet text
      strip.background = element_rect(fill = "white", size = 1),
      # Change facet color
      panel.spacing = unit(.05, "lines"),
      # Add panel border
      panel.border = element_rect(color = "black", fill = NA, size = 0.5),
      # Change panel border color and size
      legend.background = element_rect(fill = "#ffffff00")
      # strip.text = element_blank()
      # legend.position = c(.78, 0.85)
    ) 
```


## Immediate Recall Social Condition Main Effect (from m2_immReTD; overhearing > direct address)
```{r}
library(ggbeeswarm)

labsWord <- c("Noun", "Verb")
names(labsWord) <- c("noun", "verb")

immRe %>%
  # filter(group == "TD") %>%
  filter(!is.na(corr)) %>%
  group_by(Participant.Public.ID, group, word_type, social_cond) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T)) %>%
  arrange(group, word_type, social_cond) %>%
  dplyr::mutate(social_cond = dplyr::recode(social_cond, "front" = "Direct", "side" = "Overhearing")) %>%
  ggplot(aes(x = social_cond, y = corr)) +
  geom_bar(
    aes(fill = social_cond),
    position = position_dodge(),
    width = 0.9,
    stat = "summary",
    fun.y = "mean"
  ) +
  facet_grid(~group,  labeller = (labeller(word_type = labsWord))) +
  guides(fill = guide_legend(title = "Social Condition")) +
  labs(title = "Immediate Recall Accuracy",
       x = "Social Condition",  # Change x-axis label
       y = "Accuracy (%)") +
  geom_beeswarm(
    aes(group = Participant.Public.ID),
    dodge.width = 0.3,
    cex = 1.5,
    size = 3,
    alpha = 0.5,
    show.legend = FALSE,
    stat = "summary",
    fun.y = "mean"
  ) +
  styling

immRe %>%
  filter(group == "TD") %>%
  filter(!is.na(corr)) %>%
  group_by(Participant.Public.ID, group, word_type, social_cond) %>%
  dplyr::summarise(mean_acc = mean(corr, na.rm = T), sd = sd(corr, na.rm = T)) %>%
  tail(.)
```


## Immediate Recall Social Condition * Age Interaction Effect (from m2_immReTD)
```{r}
library(ggbeeswarm)

immRe %>%
  filter(group == "TD") %>%
  filter(!is.na(corr)) %>%
  # group_by(Participant.Public.ID, group, age_year, age_month, age_group, word_type, social_cond) %>%
  # dplyr::summarise(corr = mean(corr, na.rm = T)) %>%
  arrange(group, word_type, social_cond) %>%
  dplyr::mutate(social_cond = dplyr::recode(social_cond, "front" = "Direct", "side" = "Overhearing")) %>%
  ggplot(aes(x = social_cond, y = corr)) +
  geom_bar(
    aes(fill = social_cond),
    position = position_dodge(),
    width = 0.9,
    stat = "summary",
    fun.y = "mean"
  ) +
  facet_grid(~group + age_group,  labeller = (labeller(word_type = labsWord))) +
  guides(fill = guide_legend(title = "Social Condition")) +
  labs(title = "Immediate Recall Accuracy",
       x = "Social Condition",  # Change x-axis label
       y = "Accuracy (%)") +
  geom_beeswarm(
    aes(group = Participant.Public.ID),
    dodge.width = 0.3,
    cex = 1.5,
    size = 3,
    alpha = 0.5,
    show.legend = FALSE,
    stat = "summary",
    fun.y = "mean"
  ) +
  styling


immRe %>%
  filter(group == "TD") %>%
  group_by(group, age_group, social_cond) %>%
  dplyr::summarise(mean_acc = mean(corr, na.rm = T))
```




## Immediate Recall ASD Analysis
```{r}
immReASD$scaled_age_asd <- scale(immReASD$age_year)

simple_immReASD <- glmer(corr ~ social_cond + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                   data = immReASD,
                   family = binomial,
                   contrasts = list(social_cond = c(-0.5, 0.5)),
                   control = glmerControl(optimizer = "bobyqa"))

summary(simple_immReASD)

simple_immReASD2 <- glmer(corr ~ social_cond*scaled_age_asd + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                   data = immReASD,
                   family = binomial,
                   contrasts = list(social_cond = c(-0.5, 0.5)),
                   control = glmerControl(optimizer = "bobyqa"))

summary(simple_immReASD2)

simple_immReASD3 <- glmer(corr ~ social_cond*scaled_age_asd*word_type + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                   data = immReASD,
                   family = binomial,
                   contrasts = list(social_cond = c(-0.5, 0.5),
                                    word_type = c(-0.5, 0.5)),
                   control = glmerControl(optimizer = "bobyqa"))

summary(simple_immReASD3)

m1_immReASD <- glmer(corr ~ social_cond*scaled_age_asd*word_type + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                   data = immReASD,
                   family = binomial,
                   contrasts = list(social_cond = c(-0.5, 0.5), 
                                    word_type = c(-0.5, 0.5)),
                   control = glmerControl(optimizer = "bobyqa"))

summary(m1_immReASD)

immReASD$scaled_pvt_std <- scale(immReASD$pvt_std_score)
immReASD$scaled_mite <- scale(immReASD$mite_total_score)

m2_immReASD <- glmer(corr ~ social_cond*word_type*scaled_age_asd*scaled_pvt_std + 
                       (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                   data = immReASD,
                   family = binomial,
                   contrasts = list(social_cond = c(-0.5, 0.5), 
                                    word_type = c(-0.5, 0.5)),
                   control = glmerControl(optimizer = "bobyqa"))

summary(m2_immReASD)

m3_immReASD <- glmer(corr ~ social_cond*word_type*scaled_age_asd*scaled_mite + 
                       (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                   data = immReASD,
                   family = binomial,
                   contrasts = list(social_cond = c(-0.5, 0.5), 
                                    word_type = c(-0.5, 0.5)),
                   control = glmerControl(optimizer = "bobyqa"))

summary(m3_immReASD)
```


## Immediate Recall Social Condition * Word Type * Age Effect (from multiple ASD models)
```{r}
library(ggbeeswarm)

labsWord <- c("Noun", "Verb")
names(labsWord) <- c("noun", "verb")

immRe %>%
  filter(group == "ASD") %>%
  filter(!is.na(corr)) %>%
  # group_by(Participant.Public.ID, group, age_year, age_month, age_group, word_type, social_cond) %>%
  # dplyr::summarise(corr = mean(corr, na.rm = T)) %>%
  arrange(group, word_type, social_cond) %>%
  dplyr::mutate(social_cond = dplyr::recode(social_cond, "front" = "Direct", "side" = "Overhearing")) %>%
  ggplot(aes(x = social_cond, y = corr)) +
  geom_bar(
    aes(fill = social_cond),
    position = position_dodge(),
    width = 0.9,
    stat = "summary",
    fun.y = "mean"
  ) +
  facet_grid(~group + age_group + word_type,  labeller = (labeller(word_type = labsWord))) +
  guides(fill = guide_legend(title = "Social Condition")) +
  labs(title = "Immediate Recall Accuracy",
       x = "Social Condition",  # Change x-axis label
       y = "Accuracy (%)") +
  geom_beeswarm(
    aes(group = Participant.Public.ID),
    dodge.width = 0.3,
    cex = 1.5,
    size = 3,
    alpha = 0.5,
    show.legend = FALSE,
    stat = "summary",
    fun.y = "mean"
  ) +
  styling
```


```{r, include = F, eval = F}
## Follow up for Immediate Recall Group Analysis By Age Group
m1_immReOld <- glmer(corr ~ group*social_cond*word_type + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                   data = immRe[which(immRe$age_group == "older"),],
                   family = binomial,
                   contrasts = list(group = c(-0.5, 0.5), 
                                    social_cond = c(-0.5, 0.5), 
                                    word_type = c(-0.5, 0.5)),
                   control = glmerControl(optimizer = "bobyqa"))

summary(m1_immReOld)

m1_immReYoungASD <- glmer(corr ~ social_cond*word_type*scaled_mite  + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                   data = immReASD[which(immReASD$age_group == "younger"),],
                   family = binomial,
                   contrasts = list(group = c(-0.5, 0.5), 
                                    social_cond = c(-0.5, 0.5), 
                                    word_type = c(-0.5, 0.5)),
                   control = glmerControl(optimizer = "bobyqa"))

summary(m1_immReYoungASD)

m1_immReOldASD <- glmer(corr ~ social_cond*word_type*scaled_mite  + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                   data = immReASD[which(immReASD$age_group == "older"),],
                   family = binomial,
                   contrasts = list(group = c(-0.5, 0.5), 
                                    social_cond = c(-0.5, 0.5), 
                                    word_type = c(-0.5, 0.5)),
                   control = glmerControl(optimizer = "bobyqa"))

summary(m1_immReOldASD)
```



# Immediate Recall Individual Difference Analysis
## Calculate mean accuracy by subject (meanAcc)
```{r}
## Calculate Individual Mean Accuracy
meanAccImm <- 
  immRe %>%
  group_by(Participant.Public.ID, group, age_year, age_month, age_group, word_type, social_cond, pvt_raw_score,
           pvt_std_score, mite_total_score) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T)) %>%
  arrange(group, word_type, social_cond)

meanAccImmLog <- 
  immRe %>%
  group_by(Participant.Public.ID, group, age_year, age_month, age_group, social_cond, pvt_raw_score,
           pvt_std_score, mite_total_score) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T)) %>%
  arrange(group, social_cond) %>%
  mutate(corr_log = log(corr))
```


## Immediate Recall TD Against Chance-level
```{r}
t_test_against_chance <- 
  function(x){
  test <- t.test(x, mu=0.25, alternative= "greater")
  data.frame(p_value = test$p.value,
             df = test$parameter,
             t_stat = test$statistic)
  }

wrap_t <-
  function(meanDF, groupID, conditionID) {
  temp <-
  meanDF %>%
  filter(group == groupID) %>%
  filter(social_cond == conditionID) %>%
  group_by(Participant.Public.ID) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T), n = n())
  
  t_result <-
    sapply(colnames(temp)[str_detect(colnames(temp) ,"corr")], 
       function(x) t_test_against_chance(temp[,x]))
  
  return(t_result)
  }

wrap_t(meanAccImm, "TD", "front")
wrap_t(meanAccImm, "ASD", "front")
wrap_t(meanAccImm, "TD", "side")
wrap_t(meanAccImm, "ASD", "side")

meanAccImmD <-
  meanAccImm %>%
  filter(social_cond == "front")

meanAccImmO <-
  meanAccImm %>%
  filter(social_cond == "side")

t.test(corr~group, data = meanAccImmD)
t.test(corr~group, data = meanAccImmO)
```




# Mediation Analyses
```{r}
# Invididuals missing PVT
immRe %>%
  filter(is.na(pvt_std_score)) %>%
  dplyr::select(Participant.Public.ID, group) %>%
  group_by(group) %>%
  distinct(.) %>%
  dplyr::summarise(n = n())

# Invididuals missing MITE
immRe %>%
  filter(is.na(mite_total_score)) %>%
  dplyr::select(Participant.Public.ID, group) %>%
  group_by(group) %>%
  distinct(.) %>%
  dplyr::summarise(n = n())
```


```{r, include = F}
library(mediation)

medSocial <-
function(social, diagnostic_group, age, mediator, seed) {
  set.seed(seed)
  meanAccImmOH <-
    meanAccImmLog %>%
    filter(social_cond == social) %>%
    filter(group == diagnostic_group)
  
  if(age != "all") {
    meanAccImmOH <-
      meanAccImmOH %>%
      filter(age_group == age)
  }
  
  meanAccImmOH[,c("scaled_mediator")] <- scale(meanAccImmOH[,c(mediator)])
  meanAccImmOH[,c("scaled_age")] <- scale(meanAccImmOH$age_year)
  
  # model.M <- lm(M ~ X, myData)
  # model.Y <- lm(Y ~ X + M, myData)
  # results <- mediate(model.M, model.Y, treat='X', mediator='M',
  #                    boot=TRUE, sims=100)
  
  # Using non-scale is the same
  model.M <- lm(scaled_mediator ~ scaled_age, data = meanAccImmOH)
  model.Y <- lm(corr_log ~ scaled_age + scaled_mediator, data = meanAccImmOH)
  results <- mediate(model.M, model.Y, treat='scaled_age', mediator='scaled_mediator',
                     boot=TRUE, sims=100)
  resultsTemp <- summary(results)
  
  return(resultsTemp)
}
```

```{r}
# Accuracy and Age Relationship is fully mediated by PVT
medSocial("side", "TD", "all", "pvt_raw_score", 123)
medSocial("front", "TD", "all", "pvt_raw_score", 124)

# Accuracy and Age Relationship is not mediated by MITE
medSocial("side", "TD","all", "mite_total_score", 125)
medSocial("front", "TD", "all","mite_total_score", 126)

medSocial("side", "ASD", "all", "mite_total_score", 127)
medSocial("front", "ASD", "all", "mite_total_score", 128)

medSocial("side", "ASD", "all", "pvt_raw_score", 127)
medSocial("front", "ASD", "all", "pvt_raw_score", 128)
```



## Plot Social Condition and PVT 
**(Significant in TD; Marginal in ASD in GLMER model)**
```{r}
meanAccImm %>%
  filter(!is.na(corr)) %>%
  group_by(Participant.Public.ID, group, age_group, social_cond, pvt_std_score) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T), n = n()) %>%
  arrange(group, social_cond) %>%
  dplyr::mutate(social_cond = dplyr::recode(social_cond, "front" = "Direct", "side" = "Overhearing"),
                pvt_std_score = as.numeric(as.character(pvt_std_score)),
                corr = as.numeric(as.character(corr))) %>%
  ggplot(aes(x = pvt_std_score, y = corr)) +
  geom_point(
    aes(color = social_cond),
    stat = "identity",
    size = 3,
    na.rm=TRUE,
    position = position_dodge(width = 4),
    show.legend = FALSE,
    alpha = 0.5,
    shape=1,
    stroke = 2
  ) +
  facet_grid(~group,  labeller = (labeller(word_type = labsWord))) +
  geom_smooth(method='lm', formula= y~x, aes(color = social_cond), se = F) +
  guides(fill = guide_legend(title = "Social Condition")) +
  labs(title = "Immediate Recall Accuracy",
       x = "PVT Standard Score",  # Change x-axis label
       y = "Accuracy (%)") +
  styling
```


## Plot TD Social * Age * PVT Interaction
```{r}
meanAccImm %>%
  filter(group == "TD") %>%
  filter(!is.na(corr)) %>%
  group_by(Participant.Public.ID, group, age_group, social_cond, pvt_raw_score) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T), n = n()) %>%
  arrange(group, social_cond) %>%
  dplyr::mutate(social_cond = dplyr::recode(social_cond, "front" = "Direct", "side" = "Overhearing"),
                pvt_raw_score = as.numeric(as.character(pvt_raw_score)),
                corr = as.numeric(as.character(corr))) %>%
  ggplot(aes(x = pvt_raw_score, y = corr)) +
  geom_point(
    aes(color = social_cond),
    stat = "identity",
    size = 3,
    na.rm=TRUE,
    position = position_dodge(width = 4),
    show.legend = FALSE,
    alpha = 0.5,
    shape=1,
    stroke = 2
  ) +
  facet_grid(~group + age_group,  labeller = (labeller(word_type = labsWord))) +
  geom_smooth(method='lm', formula= y~x, aes(color = social_cond), se = F) +
  guides(fill = guide_legend(title = "Social Condition")) +
  labs(title = "Immediate Recall Accuracy",
       x = "PVT Raw Score",  # Change x-axis label
       y = "Accuracy (%)") +
  styling

# N for this plot
meanAccImm %>%
  filter(group == "TD") %>%
  filter(!is.na(corr)) %>%
  filter(!is.na(pvt_std_score)) %>%
  group_by(group, age_group, social_cond) %>%
  distinct(.) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T), n = length(unique(Participant.Public.ID))) %>%
  arrange(group, social_cond) 
```


## Plot Social Condition and MITE 
**(Significant in TD; Marginal in ASD in GLMER model)**
```{r}
meanAccImm %>%
  filter(!is.na(corr)) %>%
  group_by(Participant.Public.ID, group, age_group, social_cond, mite_total_score) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T), n = n()) %>%
  arrange(group, social_cond) %>%
  dplyr::mutate(social_cond = dplyr::recode(social_cond, "front" = "Direct", "side" = "Overhearing"),
                mite_total_score = as.numeric(as.character(mite_total_score)),
                corr = as.numeric(as.character(corr))) %>%
  ggplot(aes(x = mite_total_score, y = corr)) +
  geom_point(
    aes(color = social_cond),
    stat = "identity",
    size = 3,
    na.rm=TRUE,
    # position = position_dodge(width = 4),
    show.legend = FALSE,
    alpha = 0.5,
    shape=1,
    stroke = 2
  ) +
  facet_grid(~group,  labeller = (labeller(word_type = labsWord))) +
  geom_smooth(method='lm', formula= y~x, aes(color = social_cond), se = F) +
  guides(fill = guide_legend(title = "Social Condition")) +
  labs(title = "Immediate Recall Accuracy",
       x = "MITE Total Score",  # Change x-axis label
       y = "Accuracy (%)") +
  styling
```

## Plot ASD Social * Age * Mite Interaction
```{r}
meanAccImm %>%
  filter(group == "ASD") %>%
  filter(!is.na(corr)) %>%
  group_by(Participant.Public.ID, group, age_group, social_cond, mite_total_score) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T), n = n()) %>%
  arrange(group, social_cond) %>%
  dplyr::mutate(social_cond = dplyr::recode(social_cond, "front" = "Direct", "side" = "Overhearing"),
                mite_total_score = as.numeric(as.character(mite_total_score)),
                corr = as.numeric(as.character(corr))) %>%
  ggplot(aes(x = mite_total_score, y = corr)) +
  geom_point(
    aes(color = social_cond),
    stat = "identity",
    size = 3,
    na.rm=TRUE,
    # position = position_dodge(width = 4),
    show.legend = FALSE,
    alpha = 0.5,
    shape=1,
    stroke = 2
  ) +
  facet_grid(~group + age_group,  labeller = (labeller(word_type = labsWord))) +
  geom_smooth(method='lm', formula= y~x, aes(color = social_cond), se = F) +
  guides(fill = guide_legend(title = "Social Condition")) +
  labs(title = "Immediate Recall Accuracy",
       x = "MITE Total Score",  # Change x-axis label
       y = "Accuracy (%)") +
  styling

# N for this plot
meanAccImm %>%
  filter(group == "ASD") %>%
  filter(!is.na(corr)) %>%
  filter(!is.na(mite_total_score)) %>%
  group_by(group, age_group, social_cond) %>%
  distinct(.) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T), n = length(unique(Participant.Public.ID))) %>%
  arrange(group, social_cond) 
```


## Plot Age Effect Continuous
```{r}
meanAccImm %>%
  filter(!is.na(corr)) %>%
  group_by(Participant.Public.ID, group, age_year, social_cond) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T), n = n()) %>%
  arrange(group, social_cond) %>%
  dplyr::mutate(social_cond = dplyr::recode(social_cond, "front" = "Direct", "side" = "Overhearing"),
                corr = as.numeric(as.character(corr))) %>%
  ggplot(aes(x = age_year, y = corr)) +
  geom_point(
    aes(color = social_cond),
    stat = "identity",
    size = 3,
    na.rm=TRUE,
    # position = position_dodge(width = 4),
    show.legend = FALSE,
    alpha = 0.5,
    shape=1,
    stroke = 2
  ) +
  facet_grid(~group,  labeller = (labeller(word_type = labsWord))) +
  geom_smooth(method='lm', formula= y~x, aes(color = social_cond), se = F) +
  guides(fill = guide_legend(title = "Social Condition")) +
  labs(title = "Immediate Recall Accuracy",
       x = "Age (years)",  # Change x-axis label
       y = "Accuracy (%)") +
  styling
```





# Block Test, Immediate Retention, and Delayed Retention Clean up
```{r, include = F}
library(reshape2)
blockRe <- behDF[which(str_detect(behDF$display, ("block_test|block_testV|post-test|post-testV")) & str_detect(behDF$Response, ("jpg|png"))),]

blockRe <- blockRe[,c("Participant.Public.ID", "UTC.Date", "Tree.Node.Key", "Response", "display", "Event.Index", "Spreadsheet", "Spreadsheet.Row", "Task.Name", "block_position", "target", "text_dist",	"taxonomic_dist",	"thematic_dist", "text_pdist",	"taxonomic_pdist",	"thematic_pdist")]
```


# Read in the satndalone retention task data
```{r, include = F}
library(dplyr)

moreRe <-
  list.files(path = "/Users/jojohu/Documents/Splash/beh_analysis/",
             pattern = "splash_retention.csv$|-oz4o.csv", full.names = T, recursive = T)

read_moreRe <-
  function(x) {
    x <- read.csv(x, stringsAsFactors = F)
    x$Participant.Public.ID <- as.character(x$Participant.Public.ID)
    x$Reaction.Time <- as.character(x$Reaction.Time)
    
    return(x)
  }

moreRe <- lapply(moreRe, read_moreRe)
moreRe <- do.call(dplyr::bind_rows, moreRe)

# moreRe %>%
#   filter(is.na(Participant.Public.ID))
moreRe$Participant.Public.ID <- as.character(moreRe$Participant.Public.ID)
moreRe$Participant.Public.ID <- str_pad(moreRe$Participant.Public.ID, 3, pad = "0")
moreRe[which(!str_detect(moreRe$Participant.Public.ID, "smile")),]$Participant.Public.ID <- 
  paste0("smile_c_", moreRe[which(!str_detect(moreRe$Participant.Public.ID, "smile")),]$Participant.Public.ID)

moreRe <- moreRe[-which(moreRe$Participant.Public.ID == "smile_c_904_1"),]

moreRe <-
  moreRe %>%
  filter(Participant.Public.ID != "smile_c_000") %>%
  filter(!is.na(Participant.Public.ID))

unique(moreRe$Participant.Public.ID)

moreRe$Participant.Public.ID <- as.factor(moreRe$Participant.Public.ID)

moreRe$UTC.Date <- as.Date(as.POSIXct(moreRe$UTC.Timestamp/1000, origin="1970-01-01"))

blockRe <- dplyr::bind_rows(blockRe, moreRe)

blockRe <- blockRe[,c("Participant.Public.ID", "UTC.Date", "Tree.Node.Key", "Response", "display", "Event.Index", "Spreadsheet", "Spreadsheet.Row", "Task.Name", "block_position", "target", "text_dist",	"taxonomic_dist",	"thematic_dist", "text_pdist",	"taxonomic_pdist",	"thematic_pdist")]

if(length(which(blockRe$display == "practice")) > 0) {
  blockRe <- blockRe[-which(blockRe$display == "practice"),]
}

blockRe %>%
  filter(is.na(Participant.Public.ID)) %>%
  filter(Event.Index != "END OF FILE")
```


```{r, include = F}
# Delayed retention for some reason has leading zeros with ID, get rid of leading zeros
blockRe$Participant.Public.ID <- str_remove(blockRe$Participant.Public.ID, "^0+")

blockRe[which(blockRe$display %in% c("post-test", "post-testV")), c("text_dist", "taxonomic_dist", "thematic_dist")] <- NA
blockRe[which(blockRe$display %in% c("block_test", "block_testV")), c("text_pdist", "taxonomic_pdist", "thematic_pdist")] <- NA
blockRe$text_dist <- coalesce(blockRe$text_dist, as.character(blockRe$text_pdist))
blockRe$taxonomic_dist <- coalesce(blockRe$taxonomic_dist, blockRe$taxonomic_pdist)
blockRe$thematic_dist <- coalesce(blockRe$thematic_dist, blockRe$thematic_pdist)

blockRe$block <- str_extract(blockRe$block_position, "[:digit:]")
blockRe$block <- as.numeric(as.character(blockRe$block))
blockRe <- blockRe[which(str_detect(blockRe$Response, "(jpg|png)")),]

# Important for finding actual verb responses
blockRe$Response <- str_remove(blockRe$Response, "[:digit:](?=.)")
blockRe$Response <- str_remove_all(blockRe$Response, "transparent_|.png|p+(?=dist)|p+(?=target)")

blockRe <- 
  blockRe %>% 
  dplyr::mutate_at(vars(target, text_dist, taxonomic_dist, thematic_dist), str_remove, "[:digit:](?=.)")

blockRe %>%
  group_by(Participant.Public.ID, UTC.Date, display) %>%
  dplyr::summarise(n = n()) %>%
  tidyr::spread(display, n)
```


# Remove trials that participants did not experience in immediate learning from retention 
```{r, include = F}
# Remove wrong test trials during learning by story
blockReL <- melt(blockRe[,c("Participant.Public.ID", "UTC.Date", "Spreadsheet.Row", "Tree.Node.Key", "Task.Name",
                                       "target", "text_dist",	"taxonomic_dist",	"thematic_dist")], 
                          id.vars = c("Participant.Public.ID", "UTC.Date", "Spreadsheet.Row", "Tree.Node.Key", "Task.Name"))

answerLpost <- unique(melt(answer[,c("story", "key", "text_dist",	"taxonomic_dist",	"thematic_dist",
                                     "text_pdist",	"taxonomic_pdist",	"thematic_pdist")], id.vars = c("story")))

answerLpost <- unique(answerLpost[,-which(names(answerLpost) %in% c("variable"))])

blockReL <- merge(blockReL, answerLpost, by.x = c("value"), by.y = c("value"), all.x = T)

rowStory <- unique(blockReL[,c("Participant.Public.ID", "UTC.Date", "Spreadsheet.Row", "Tree.Node.Key", "story")])

blockRe <- merge(blockRe, rowStory, by.x = c("Participant.Public.ID", "UTC.Date", "Spreadsheet.Row", "Tree.Node.Key"), 
                 by.y = c("Participant.Public.ID", "UTC.Date", "Spreadsheet.Row", "Tree.Node.Key"), all.x = T)


wrongID <- immRe %>%
  group_by(Participant.Public.ID) %>%
   dplyr::summarise(n = length(unique(story))) %>%
   filter(n < 20) %>%
   dplyr::select(Participant.Public.ID)

if(nrow(wrongID) > 0) {
  missStory <-
    immRe %>%
    filter(Participant.Public.ID %in% wrongID$Participant.Public.ID) %>%
    group_by(Participant.Public.ID) %>%
    dplyr::summarise(story = setdiff(unique(answer$story), story))
  
  missStory$mismatch <- "wrong"
  
  blockRe <-
    merge(
      blockRe,
      missStory,
      by = c("Participant.Public.ID", "story"),
      all.x = T
    )
  
  blockRe <- blockRe[-which(blockRe$mismatch == "wrong"), ]
  
}
``` 


```{r, include = F}
# Remove the multiple keypresses, take the last keypress
blockRe <- 
  blockRe %>%
  group_by(Participant.Public.ID, UTC.Date, Spreadsheet.Row) %>%
  arrange(Participant.Public.ID, UTC.Date, Spreadsheet.Row, Event.Index) %>%
  filter(row_number()==n())

# Sort data by date and find delayed retention
test_time <-
  blockRe %>%
  group_by(Participant.Public.ID, UTC.Date) %>%
  arrange(Participant.Public.ID, UTC.Date) %>%
  dplyr::summarise(test_time = unique(UTC.Date)) %>%
  group_by(Participant.Public.ID) %>%
  dplyr::mutate(test_time = LETTERS[row_number()]) %>%
  dplyr::mutate(test_time = dplyr::recode(test_time,
                            "A" = "attainment",
                            "B" = "retention",
                           "C" = "third_session"))

test_time$session_time <- test_time$test_time

test_time <-
  test_time %>%
   mutate(session_time = dplyr::recode(session_time,
                            "attainment" = "week1",
                            "retention" = "week2",
                            "third_session" = "week3"))

# Merge test time with retention data  
blockRe <- merge(blockRe, test_time, by = c("Participant.Public.ID", "UTC.Date"), all.x = T)

# For participants who have third session, extract their ID for labelling correct attainment vs. retention trials later
thirdID <- unique(blockRe[which(blockRe$test_time == "third_session"),]$Participant.Public.ID)  

# Make sure there is only less than 20 block test trials per participant and less than 20 post test trials per participant
blockRe %>%
  group_by(Participant.Public.ID, test_time, UTC.Date, display) %>%
  dplyr::summarise(n = n()) %>%
  tidyr::spread(display, n)
```


```{r, include = F}
# Find the actual verb trial responses
colImmB <- c("Participant.Public.ID", "Spreadsheet.Row", "UTC.Date", "Tree.Node.Key", "story", "target", "text_dist",	"taxonomic_dist", "thematic_dist")

longVerbB <- melt(blockRe[,colImmB], id.vars = c("Participant.Public.ID", "Spreadsheet.Row", "UTC.Date", "Tree.Node.Key", "story"))
longVerbB <- unique(longVerbB)
  
colnames(longVerbB)[colnames(longVerbB) %in% "variable"] <- "verb_key"
colnames(longVerbB)[colnames(longVerbB) %in% "value"] <- "verb_response"

blockRe <- merge(blockRe, longVerbB, by.x = c("Participant.Public.ID",  "Spreadsheet.Row", "UTC.Date", "Tree.Node.Key", "story", "Response"), 
                 by.y = c("Participant.Public.ID","Spreadsheet.Row", "UTC.Date", "Tree.Node.Key", "story", "verb_key"), all.x = T)
  
blockRe[which(!is.na(blockRe$verb_response)), "Response"] <- as.character(blockRe[which(!is.na(blockRe$verb_response)), "verb_response"])
```


# Relabel the attainment and retention trials for participants that had a third session
```{r, include = F}
# Remove the block-test trials that were ran at the time of retention because these block-test trials are simply duplicating the post-test trials
# For participants who have only 2 sessions, yet have block-test at time 2 (IDs that do not have a third session, but block-test trials labelled as retention)
blockRe <- 
  blockRe[-which(!blockRe$Participant.Public.ID %in% thirdID &
                (blockRe$display == "block_testV" | blockRe$display == "block_test" )  &
                blockRe$test_time == "retention"),]

# For participants who have a third session, relabel attainment vs. retention trials
storyDate <- merge(immRe, test_time, by = c("Participant.Public.ID", "UTC.Date"), all.x = T)

correctLabel <- storyDate[which(storyDate$Participant.Public.ID %in% thirdID),
                          c("Participant.Public.ID", "UTC.Date", "story", "test_time", "session_time")]

# Stories run in week1 should be labelled as retention for their block-test and post-test run in week 2
correctLabel$correct_time <- "temp"

correctLabel[which(correctLabel$session_time == "week1"),]$correct_time <- "retention"

# Stories run in week2 should be labelled as attainment for their block-test and post-test run in week 2
# Stories labeled as attainment are very long-term retention in post-test run in the third session (don't need to label this; all counted as long-term retention)
correctLabel[which(correctLabel$session_time == "week2"),]$correct_time <- "attainment"

# For participants who have three sessions, their first two sessions added together should have less than or equal to 20 stories
correctLabel %>%
  group_by(Participant.Public.ID) %>%
  dplyr::summarise(n = n())

# Relabel the block-test and post-test in week2 to the correct labels using stories
correctLabel <- correctLabel[,c("Participant.Public.ID", "story", "correct_time")]

blockRe <- merge(blockRe, correctLabel, by = c("Participant.Public.ID", "story"), all.x = T)

blockRe <-
  blockRe %>%
  mutate(test_time = ifelse(Participant.Public.ID %in% thirdID & 
                              display %in% c("post-test", "post-testV", "block_test", "block_testV") &
                              session_time == "week2", correct_time, test_time))

# The block-test trials run with one-week gap from first learning expsoure should be removed
# If participants did block test in week2 for stories that were learned in week1, remove the trials
# If the correct label is retention, that means the stories were learned in week 1, remove the block tests for stories learned in week1
blockRe <- blockRe[-which(blockRe$Participant.Public.ID %in% thirdID & 
                blockRe$display %in% c("block_test", "block_testV") & 
                blockRe$test_time == "retention"),]

# Change week3 trials to long retention
blockRe[which(blockRe$Participant.Public.ID %in% thirdID &
                blockRe$display %in% c("post-test", "post-testV") &
                blockRe$test_time == "third_session"),]$test_time <- "long_retention"

# Change week3 trials to retention
# blockRe[which(blockRe$Participant.Public.ID %in% thirdID &
#                 blockRe$display %in% c("post-test", "post-testV") &
#                 blockRe$test_time == "third_session"),]$test_time <- "retention"
```


# Add label for Short-Term retention after all stories VS. one-week-retention
```{r, include = F}
blockRe$test_time <- as.character(blockRe$test_time)
blockRe$test_three <- blockRe$test_time

blockRe[which(blockRe$test_time == "attainment" & blockRe$display %in% c("post-test", "post-testV")),]$test_time <- "short_retention"
```


# Remove the Attainment and Retention trials that are not in Immediate Recall
```{r, include = F}
# Remove the trials that the participants have not experienced from their Attainment or Retention trials
immStory <- 
  immRe %>%
  dplyr::select(Participant.Public.ID, story) %>%
  distinct(.) %>%
  mutate(inImm = 1)

blockRe <- 
  merge(blockRe, immStory, by.x = c("Participant.Public.ID", "story"), by.y =  c("Participant.Public.ID", "story"), all.x = T)

removeImm <- 
  blockRe %>%
  filter(is.na(inImm))

if(nrow(removeImm) > 0) {
  print("Have not removed the trials that the participants have not experienced from their Attainment or Retention trials.")
}

blockRe <-
  blockRe %>%
  dplyr::select(-one_of("inImm"))

blockRe %>%
  group_by(Participant.Public.ID, test_time, UTC.Date, display) %>%
  dplyr::summarise(n = n()) %>%
  tidyr::spread(display, n)
```



# Calculate Accuracy for block test, immediate retention, delayed retention
```{r, include = F}
blockRe <- merge(blockRe, answer[,c("story", "key", "word_type")], by.x = "story", by.y = "story", all.x = T)
blockRe <- merge(blockRe, unique(immRe[,c("Participant.Public.ID", "group", "participant_gender", 
                                          "age_month", "age_year", "story", "social_cond", "age_group")]), 
                 by.x = c("Participant.Public.ID", "story"), 
                 by.y = c("Participant.Public.ID", "story"), all.x = T)
# To Do: Manually Score the participant that does not have verb story scores and merge smile_c_003 data
blockRe[which(str_detect(blockRe$Response,"transparent")), "Response"] <- NA

blockRe$corr <- ifelse(blockRe$Response ==blockRe$key, 1, 0)
```

# Change data and subset groups (full dataset: any number of trials)
```{r}
fullReID <-
  blockRe %>%
  group_by(Participant.Public.ID, test_time, UTC.Date) %>%
  dplyr::summarise(n = n()) %>%
  filter(n > 1) %>%
  mutate(full_data = 1)

blockRe <- 
  merge(blockRe, fullReID, by = c("Participant.Public.ID", "test_time", "UTC.Date"), all.x = T) %>%
  filter(full_data == 1) %>%
  dplyr::select(-one_of("full_data", "n"))

blockRe <- blockRe[which(blockRe$Participant.Public.ID %in% immRe$Participant.Public.ID),]

blockRe %>% 
  filter(is.na(group))

blockRe %>%
  group_by(Participant.Public.ID, test_time, UTC.Date) %>%
  dplyr::summarise(n = n())
```


```{r}
blockRe$group <- as.factor(blockRe$group)
blockRe$age_group <- as.factor(blockRe$age_group)
blockRe$social_cond <- as.factor(blockRe$social_cond)
blockRe$word_type <- as.factor(blockRe$word_type)
blockRe$test_time <- as.factor(blockRe$test_time)
blockRe$test_three <- as.factor(blockRe$test_three)
blockRe$Participant.Public.ID <- as.factor(blockRe$Participant.Public.ID)

blockRe <-
  blockRe %>%
  mutate(social_cond = dplyr::recode(social_cond, front = "Direct", side = "Overhearing"))

blockRe$group <- factor(blockRe$group, levels = c("ASD", "TD"))
blockRe <- blockRe[order(blockRe$group),]

blockRe$social_cond <- factor(blockRe$social_cond, levels = c("Direct", "Overhearing"))
blockRe <- blockRe[order(blockRe$social_cond),]

blockRe$word_type <- factor(blockRe$word_type, levels = c("noun", "verb"))
blockRe <- blockRe[order(blockRe$word_type),]

blockRe$scaled_age <- scale(blockRe$age_year, center = T)

blockRe$test_time <- factor(blockRe$test_time, levels = c("attainment", "short_retention", "retention"))
blockRe <- blockRe[order(blockRe$test_time),]

blockRe$test_three <- factor(blockRe$test_three, levels = c("attainment", "retention"))
blockRe <- blockRe[order(blockRe$test_three),]

blockRe <- merge(blockRe, ipad, by.x = "Participant.Public.ID", by.y = "part_id", all.x = T)

blockReTD <- blockRe[which(blockRe$group == "TD"),]
blockReASD <- blockRe[which(blockRe$group == "ASD"),]

# three_helmert = matrix(c(2/3, -1/3, -1/3, 0, .5, -.5), ncol = 2)
three_helmert = matrix(c(-1/3, -1/3, 2/3, -0.5, 0.5, 0), ncol = 2)
contrasts(blockRe$test_time) = three_helmert
contrasts(blockReTD$test_time) = three_helmert
contrasts(blockReASD$test_time) = three_helmert

blockRe %>%
  group_by(group, test_time) %>%
  dplyr::summarise(n = sum(!is.na(unique(Participant.Public.ID))))
```




# Attainment Group Analysis (Binomial Accuracy Models)
```{r}
library(lmerTest)

simple_att <- glmer(corr ~ group*social_cond + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                   data = blockRe[which(blockRe$test_three == "attainment"),],
                   family = binomial,
                   contrasts = list(group = c(-0.5, 0.5), 
                                    social_cond = c(-0.5, 0.5)),
                   control = glmerControl(optimizer = "bobyqa"))

summary(simple_att)

simple_att2 <- glmer(corr ~ group*social_cond*scaled_age + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                   data = blockRe[which(blockRe$test_three == "attainment"),],
                   family = binomial,
                   contrasts = list(group = c(-0.5, 0.5), 
                                    social_cond = c(-0.5, 0.5)),
                   control = glmerControl(optimizer = "bobyqa"))

summary(simple_att2)

m1_att <- glmer(corr ~ group*social_cond*scaled_age*word_type + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                   data = blockRe[which(blockRe$test_three == "attainment"),],
                   family = binomial,
                   contrasts = list(group = c(-0.5, 0.5), 
                                    social_cond = c(-0.5, 0.5), 
                                    word_type = c(-0.5, 0.5)),
                   control = glmerControl(optimizer = "bobyqa"))

summary(m1_att)

## with PVT and MITE (Need to scale them as the scores have larger range)
blockRe$scaled_pvt_all <- scale(blockRe$pvt_std_score)
blockRe$scaled_mite_all <- scale(blockRe$mite_total_score)

m3_att <- glmer(corr ~ group*social_cond*word_type*age_year*scaled_mite_all + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = blockRe[which(blockRe$test_three == "attainment"),],
                    family = binomial,
                    contrasts = list(
                    group = c(-0.5, 0.5),
                    social_cond = c(-0.5, 0.5),
                    word_type = c(-0.5, 0.5)),
                    control = glmerControl(optimizer = "bobyqa"))

summary(m3_att)

m2_att <- glmer(corr ~ group*social_cond*word_type*age_year*scaled_pvt_all + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = blockRe[which(blockRe$test_three == "attainment"),],
                    family = binomial,
                    contrasts = list(
                    group = c(-0.5, 0.5),
                    social_cond = c(-0.5, 0.5),
                    word_type = c(-0.5, 0.5)),
                    control = glmerControl(optimizer = "bobyqa"))

summary(m2_att)
```


```{r, include = F, eval = F}
m1_attYoung <- 
  glmer(corr ~ social_cond + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = blockRe[which(blockRe$test_three == "attainment" & 
                                           blockRe$age_group == "younger" &
                                           blockRe$group == "TD"),],
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5)),
                    control = glmerControl(optimizer = "bobyqa"))

summary(m1_attYoung)

m1_attOld <- 
  glmer(corr ~ social_cond + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = blockRe[which(blockRe$test_three == "attainment" & 
                                           blockRe$age_group == "older" &
                                           blockRe$group == "TD"),],
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5)),
                    control = glmerControl(optimizer = "bobyqa"))

summary(m1_attOld)

```


## Follow up for Immediate Recall Group Analysis By Diagnostic Group
## Attainment TD Analysis
```{r}
scale_var <-
  function(df, test_time, group) {
      df[which(df$test_three == test_time & df$group == group), "scaled_age_group"] <-
    scale(df[which(df$test_three == test_time & df$group == group),]$age_year)

      df[which(df$test_three == test_time & df$group == group), "scaled_pvt_std"] <-
    scale(df[which(df$test_three == test_time & df$group == group),]$pvt_std_score)

      df[which(df$test_three == test_time & df$group == group), "scaled_mite"] <-
    scale(df[which(df$test_three == test_time & df$group == group),]$mite_total_score)

  return(df)
  }

blockRe <- scale_var(blockRe, "attainment", "TD")

simple_attTD <- glmer(corr ~ social_cond + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = blockRe[which(blockRe$test_three == "attainment" & blockRe$group == "TD"),],
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5)
                   ),
                    control = glmerControl(optimizer = "bobyqa"))

summary(simple_attTD)

simple_attTD2 <- glmer(corr ~ social_cond*scaled_age + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = blockRe[which(blockRe$test_three == "attainment" & blockRe$group == "TD"),],
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5)
                   ),
                    control = glmerControl(optimizer = "bobyqa"))

summary(simple_attTD2)

simple_attTD3 <- glmer(corr ~ social_cond*scaled_age*word_type + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = blockRe[which(blockRe$test_three == "attainment" & blockRe$group == "TD"),],
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5),
                    word_type = c(-0.5, 0.5)
                   ),
                    control = glmerControl(optimizer = "bobyqa"))

summary(simple_attTD3)

m1_attTD <- glmer(corr ~ social_cond*word_type*age_year*scaled_pvt_std + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = blockRe[which(blockRe$test_three == "attainment" & blockRe$group == "TD"),],
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5),
                    word_type = c(-0.5, 0.5)),
                    control = glmerControl(optimizer = "bobyqa"))

summary(m1_attTD)

m2_attTD <- glmer(corr ~ social_cond*word_type*age_year*scaled_mite + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = blockRe[which(blockRe$test_three == "attainment" & blockRe$group == "TD"),],
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5),
                    word_type = c(-0.5, 0.5)),
                    control = glmerControl(optimizer = "bobyqa"))

summary(m2_attTD)
```


## Plot Attainment Social Condition Main Effect in TD
```{r}
library(ggbeeswarm)

labsWord <- c("Noun", "Verb")
names(labsWord) <- c("noun", "verb")

blockRe %>%
  filter(test_three == "attainment") %>%
  # filter(group == "TD") %>%
  filter(!is.na(corr)) %>%
  group_by(Participant.Public.ID, group, test_three, word_type, social_cond) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T)) %>%
  arrange(group, word_type, social_cond) %>%
  dplyr::mutate(social_cond = dplyr::recode(social_cond, "front" = "Direct", "side" = "Overhearing")) %>%
  ggplot(aes(x = social_cond, y = corr)) +
  geom_bar(
    aes(fill = social_cond),
    position = position_dodge(),
    width = 0.9,
    stat = "summary",
    fun.y = "mean"
  ) +
  facet_grid(~group + test_three,  labeller = (labeller(word_type = labsWord))) +
  guides(fill = guide_legend(title = "Social Condition")) +
  labs(title = "Attainment Accuracy",
       x = "Social Condition",  # Change x-axis label
       y = "Accuracy (%)") +
  geom_beeswarm(
    aes(group = Participant.Public.ID),
    dodge.width = 0.3,
    cex = 1.5,
    size = 3,
    alpha = 0.5,
    show.legend = FALSE,
    stat = "summary",
    fun.y = "mean"
  ) +
  styling

blockRe %>%
  # filter(group == "TD") %>%
  filter(test_three == "attainment") %>%
  group_by(group, test_three, social_cond) %>%
  dplyr::summarise(mean_acc = mean(corr, na.rm = T))
```


## Attainment Social Condition * Age Interaction Effect in TD
```{r}
library(ggbeeswarm)

labs <- c("Younger Children", "Older Children")
names(labs) <- c("younger", "older")

blockRe %>%
    filter(group == "TD") %>%
    filter(!is.na(corr)) %>%
    # filter(!is.na(test_three)) %>%
    filter(test_three == "attainment") %>%
    arrange(group) %>%
    mutate(age_group = factor(age_group, levels = c("younger", "older"))) %>%
    mutate(social_cond = dplyr::recode(social_cond, Direct = "Direct Address"),
           age_group = dplyr::recode(age_group, younger = "Younger Children", older = "Older Children"),
           test_three = dplyr::recode(test_three, immediate = "0 min", attainment = "Same-Day", retention = "One Week")) %>%
    group_by(group, age_group, social_cond, test_three) %>%
    dplyr::summarise(mean = mean(corr, na.rm = TRUE),
                    sd = sd(corr, na.rm = TRUE),
                    n = n()) %>%
    mutate(se = sd / sqrt(n),
            lower_ci = mean - qt(1 - (0.05 / 2), n - 1) * se,
            upper_ci = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
    ggplot(aes(x = age_group, y = mean, group = social_cond,  fill = social_cond)) +
    geom_bar(color = "black",
              position = position_dodge(),
              width = 0.7,
              stat = "summary",
              fun = "mean",
             alpha = 0.5) +
    geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                  width = .1,
                  position = position_dodge(width = 0.7)) +
    geom_point(color = "black",
               position = position_dodge(width=0.7),
               shape = 21,
               size = 3,
               stat = "summary",
               fun = "mean") +
    # facet_wrap(~age_group,  labeller = (labeller(age_group = labs))) +
    # scale_fill_manual(values=c("white", "grey")) +
   guides(fill = guide_legend(title="Same-Day Test Accuracy")) +
    labs(y = "Accuracy (%)") +
    labs(title = "Same-Day Test Accuracy") +
    styling +
    guides(fill = guide_legend(title = "Social Condition")) +
    guides(color = "none") +
    coord_cartesian(ylim = c(0.5, 1))  +
    theme(axis.title.x=element_blank()) +
    geom_segment(aes(x = 1.67, xend = 2.33, y = 0.94, yend = 0.94)) +
    geom_segment(aes(x = 0.67, xend = 1.33, y = 0.68, yend = 0.68)) +
    # geom_text(aes(x = 2, y = 0.94, label = paste0("***")), size = 11, color = "black") +
    geom_segment(aes(x = 1, xend = 2, y = 0.98, yend = 0.98)) +
    geom_segment(aes(x = 1, xend = 1, y = 0.69, yend = 0.98)) +
    geom_segment(aes(x = 2, xend = 2, y = 0.95, yend = 0.98)) +
    geom_segment(aes(x = 1.5, xend = 1.5, y = 0.98, yend = 0.99)) +
    geom_text(aes(x = 1.5, y = 0.99, label = paste0("*")), size = 11, color = "black")

ggsave(paste0(output_path, "ageTD_att.png"), bg="transparent", width = 25, height = 15, units = "cm")

blockRe %>%
  filter(group == "TD" & test_three == "attainment") %>%
  group_by(group, test_three, age_group, social_cond) %>%
  dplyr::summarise(mean_acc = mean(corr, na.rm = T))
```


## Attainment ASD Analysis
```{r}
blockRe <- scale_var(blockRe, "attainment", "ASD")

simple_attASD <- glmer(corr ~ social_cond + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = blockRe[which(blockRe$test_three == "attainment" & blockRe$group == "ASD"),],
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5)
                   ),
                    control = glmerControl(optimizer = "bobyqa"))

summary(simple_attASD)

simple_attASD2 <- glmer(corr ~ social_cond*scaled_age + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = blockRe[which(blockRe$test_three == "attainment" & blockRe$group == "ASD"),],
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5)
                   ),
                    control = glmerControl(optimizer = "bobyqa"))

summary(simple_attASD2)

simple_attASD3 <- glmer(corr ~ social_cond*scaled_age*word_type + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = blockRe[which(blockRe$test_three == "attainment" & blockRe$group == "ASD"),],
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5),
                    word_type = c(-0.5, 0.5)
                   ),
                    control = glmerControl(optimizer = "bobyqa"))

summary(simple_attASD3)


m1_attASD <- glmer(corr ~ social_cond*word_type*age_year*scaled_pvt_std + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = blockRe[which(blockRe$test_three == "attainment" & blockRe$group == "ASD"),],
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5),
                    word_type = c(-0.5, 0.5)),
                    control = glmerControl(optimizer = "bobyqa"))

summary(m1_attASD)

m2_attASD <- glmer(corr ~ social_cond*word_type*age_year*scaled_mite + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = blockRe[which(blockRe$test_three == "attainment" & blockRe$group == "ASD"),],
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5),
                    word_type = c(-0.5, 0.5)),
                    control = glmerControl(optimizer = "bobyqa"))

summary(m2_attASD)
```

## Attainment Social Condition * Word_Type * Age Interaction Effect in ASD
```{r}
library(ggbeeswarm)

blockRe %>%
  filter(group == "ASD") %>%
  filter(test_three == "attainment") %>%
  filter(!is.na(corr)) %>%
  # group_by(Participant.Public.ID, group, age_year, age_month, age_group, word_type, social_cond) %>%
  # dplyr::summarise(corr = mean(corr, na.rm = T)) %>%
  arrange(group, word_type, social_cond) %>%
  dplyr::mutate(social_cond = dplyr::recode(social_cond, "front" = "Direct", "side" = "Overhearing")) %>%
  ggplot(aes(x = social_cond, y = corr)) +
  geom_bar(
    aes(fill = social_cond),
    position = position_dodge(),
    width = 0.9,
    stat = "summary",
    fun.y = "mean"
  ) +
  facet_grid(~group + age_group + word_type,  labeller = (labeller(word_type = labsWord))) +
  guides(fill = guide_legend(title = "Social Condition")) +
  labs(title = "Attainment Accuracy",
       x = "Social Condition",  # Change x-axis label
       y = "Accuracy (%)") +
  geom_beeswarm(
    aes(group = Participant.Public.ID),
    dodge.width = 0.3,
    cex = 1.5,
    size = 3,
    alpha = 0.5,
    show.legend = FALSE,
    stat = "summary",
    fun.y = "mean"
  ) +
  styling

blockRe %>%
  filter(group == "TD" & test_three == "attainment") %>%
  group_by(group, test_three, age_group, word_type,social_cond) %>%
  dplyr::summarise(mean_acc = mean(corr, na.rm = T))
```


# Follow-up Analyses on Group Analysis for Attainment
## Calculate mean accuracy by subject for attainment
```{r}
meanAccAtt <-
  blockRe %>%
  filter(test_three == "attainment") %>%
  group_by(Participant.Public.ID, group, age_year, age_month, age_group, test_three, word_type, social_cond, pvt_raw_score,
           pvt_std_score, mite_total_score) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T)) %>%
  arrange(group, word_type, social_cond)

meanAccAttLog <- 
  meanAccAtt %>%
  group_by(Participant.Public.ID, group, age_year, age_month, age_group, test_three, social_cond, pvt_raw_score,
           pvt_std_score, mite_total_score) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T)) %>%
  arrange(group, social_cond) %>%
  mutate(corr_log = log(corr))

# Attainment against chance-level
wrap_t(meanAccAtt, "TD", "Direct")
wrap_t(meanAccAtt, "TD", "Overhearing")
wrap_t(meanAccAtt, "ASD", "Direct")
wrap_t(meanAccAtt, "ASD", "Overhearing")

# Group comparisons
#TD
library(tidyr)
meanAccAttTDOld <-
  blockRe %>%
  filter(group == "TD") %>%
  filter(age_group == "older") %>%
  group_by(Participant.Public.ID, age_group, social_cond) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T), n = n()) %>%
  spread(social_cond, corr)

t.test(meanAccAttTDOld$Overhearing, meanAccAttTDOld$Direct, paired = T, alternative = "less")

meanAccAttTDYoung <-
  meanAccAtt %>%
  filter(group == "TD") %>%
  filter(age_group == "younger") %>%
  group_by(Participant.Public.ID, age_group, social_cond) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T), n = n()) %>%
  spread(social_cond, corr)

t.test(meanAccAttTDYoung$Overhearing, meanAccAttTDYoung$Direct, paired = T, alternative = "less")

t.test(blockRe[which(blockRe$test_time == "attainment" & blockRe$social_cond == "Direct" & 
                       blockRe$group == "TD" & blockRe$age_group == "older"),  "corr"], 
       blockRe[which(blockRe$test_time == "attainment" & blockRe$social_cond == "Direct" & 
                       blockRe$group == "TD" & blockRe$age_group == "younger"),  "corr"])
```



# Attainment Individual Difference Analysis
```{r}
# Invididuals missing PVT
blockRe %>%
  filter(test_three == "attainment") %>%
  filter(is.na(pvt_std_score)) %>%
  dplyr::select(Participant.Public.ID, group) %>%
  group_by(group) %>%
  distinct(.) %>%
  dplyr::summarise(n = n())

# Invididuals missing MITE
blockRe %>%
  filter(test_three == "attainment") %>%
  filter(is.na(mite_total_score)) %>%
  dplyr::select(Participant.Public.ID, group) %>%
  group_by(group) %>%
  distinct(.) %>%
  dplyr::summarise(n = n())
```

# Mediation Analyses
```{r, include = F}
library(mediation)
# Cannot use Log scores due to accuracy = 0
medSocial <-
function(social, diagnostic_group, age, mediator, seed) {
  set.seed(seed)
  meanAccImmOH <-
    meanAccAttLog %>%
    filter(social_cond == social) %>%
    filter(group == diagnostic_group)
  
  if(age != "all") {
    meanAccImmOH <-
      meanAccImmOH %>%
      filter(age_group == age)
  }
  
  meanAccImmOH[,c("scaled_mediator")] <- scale(meanAccImmOH[,c(mediator)])
  meanAccImmOH[,c("scaled_age")] <- scale(meanAccImmOH$age_year)
  
  # model.M <- lm(M ~ X, myData)
  # model.Y <- lm(Y ~ X + M, myData)
  # results <- mediate(model.M, model.Y, treat='X', mediator='M',
  #                    boot=TRUE, sims=100)
  
  # Using non-scale is the same
  model.M <- lm(scaled_mediator ~ scaled_age, data = meanAccImmOH)
  model.Y <- lm(corr ~ scaled_age + scaled_mediator, data = meanAccImmOH)
  results <- mediate(model.M, model.Y, treat='scaled_age', mediator='scaled_mediator',
                     boot=TRUE, sims=100)
  resultsTemp <- summary(results)
  
  return(resultsTemp)
}
```

```{r}
# Accuracy and Age Relationship is not mediated by PVT
medSocial("Overhearing", "TD", "all", "pvt_raw_score", 128)
medSocial("Direct", "TD", "all", "pvt_raw_score", 129)
medSocial("Overhearing", "TD", "all", "mite_total_score", 130)
medSocial("Direct", "TD", "all", "mite_total_score", 131)

# Accuracy and Age Relationship is not mediated by MITE
medSocial("Overhearing", "ASD", "all", "mite_total_score", 140)
medSocial("Direct", "ASD", "all", "mite_total_score", 141)
medSocial("Overhearing", "ASD", "all", "pvt_raw_score", 142)
medSocial("Direct", "ASD", "all", "pvt_raw_score", 143)
```



## Plot ASD Social Condition * MITE (* Age)
**(Significant in ASD m3_attASD GLMER model)**
```{r}
meanAccAtt %>%
  filter(group == "ASD") %>%
  filter(!is.na(corr)) %>%
  group_by(Participant.Public.ID, group, age_group, social_cond, mite_total_score) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T), n = n()) %>%
  arrange(group, social_cond) %>%
  dplyr::mutate(social_cond = dplyr::recode(social_cond, "front" = "Direct", "side" = "Overhearing"),
                mite_total_score = as.numeric(as.character(mite_total_score)),
                corr = as.numeric(as.character(corr))) %>%
  ggplot(aes(x = mite_total_score, y = corr)) +
  geom_point(
    aes(color = social_cond),
    stat = "identity",
    size = 3,
    na.rm=TRUE,
    position = position_dodge(width = 4),
    show.legend = FALSE,
    alpha = 0.5,
    shape=1,
    stroke = 2
  ) +
  facet_grid(~group,  labeller = (labeller(word_type = labsWord))) +
  geom_smooth(method='lm', formula= y~x, aes(color = social_cond), se = F) +
  guides(fill = guide_legend(title = "Social Condition")) +
  labs(title = "Attainment Accuracy",
       x = "MITE Total Score",  # Change x-axis label
       y = "Accuracy (%)") +
  styling

meanAccAtt %>%
  filter(group == "ASD") %>%
  filter(!is.na(corr)) %>%
  group_by(Participant.Public.ID, group, age_group, social_cond, mite_total_score) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T), n = n()) %>%
  arrange(group, social_cond) %>%
  dplyr::mutate(social_cond = dplyr::recode(social_cond, "front" = "Direct", "side" = "Overhearing"),
                mite_total_score = as.numeric(as.character(mite_total_score)),
                corr = as.numeric(as.character(corr))) %>%
  ggplot(aes(x = mite_total_score, y = corr)) +
  geom_point(
    aes(color = social_cond),
    stat = "identity",
    size = 3,
    na.rm=TRUE,
    position = position_dodge(width = 4),
    show.legend = FALSE,
    alpha = 0.5,
    shape=1,
    stroke = 2
  ) +
  facet_grid(~group + age_group,  labeller = (labeller(word_type = labsWord))) +
  geom_smooth(method='lm', formula= y~x, aes(color = social_cond), se = F) +
  guides(fill = guide_legend(title = "Social Condition")) +
  labs(title = "Attainment Accuracy",
       x = "MITE Total Score",  # Change x-axis label
       y = "Accuracy (%)") +
  styling

# N for this plot
meanAccAtt %>%
  filter(group == "ASD") %>%
  filter(!is.na(corr)) %>%
  filter(!is.na(mite_total_score)) %>%
  group_by(group, age_group, social_cond) %>%
  distinct(.) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T), n = length(unique(Participant.Public.ID))) %>%
  arrange(group, social_cond) 
```



## Plot Attainment Age Effect Continuous 
```{r}
meanAccAtt %>%
  filter(!is.na(corr)) %>%
  group_by(Participant.Public.ID, group, age_year, social_cond) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T), n = n()) %>%
  arrange(group, social_cond) %>%
  dplyr::mutate(social_cond = dplyr::recode(social_cond, "front" = "Direct", "side" = "Overhearing"),
                corr = as.numeric(as.character(corr))) %>%
  ggplot(aes(x = age_year, y = corr)) +
  geom_point(
    aes(color = social_cond),
    stat = "identity",
    size = 3,
    na.rm=TRUE,
    # position = position_dodge(width = 4),
    show.legend = FALSE,
    alpha = 0.5,
    shape=1,
    stroke = 2
  ) +
  facet_grid(~group,  labeller = (labeller(word_type = labsWord))) +
  geom_smooth(method='lm', formula= y~x, aes(color = social_cond), se = F) +
  guides(fill = guide_legend(title = "Social Condition")) +
  labs(title = "Attainment Accuracy",
       x = "Age (years)",  # Change x-axis label
       y = "Accuracy (%)") +
  styling
```







# Retention Group Analysis (Binomial Accuracy Models)
```{r}
simple_ret <- glmer(corr ~ group*social_cond + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                   data = blockRe[which(blockRe$test_three == "retention"),],
                   family = binomial,
                   contrasts = list(group = c(-0.5, 0.5), 
                                    social_cond = c(-0.5, 0.5)),
                   control = glmerControl(optimizer = "bobyqa"))

summary(simple_ret)

simple_ret2 <- glmer(corr ~ group*social_cond*scaled_age + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                   data = blockRe[which(blockRe$test_three == "retention"),],
                   family = binomial,
                   contrasts = list(group = c(-0.5, 0.5), 
                                    social_cond = c(-0.5, 0.5)),
                   control = glmerControl(optimizer = "bobyqa"))

summary(simple_ret2)

m1_ret <- glmer(corr ~ group*social_cond*scaled_age*word_type + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                   data = blockRe[which(blockRe$test_three == "retention"),],
                   family = binomial,
                   contrasts = list(group = c(-0.5, 0.5), 
                                    social_cond = c(-0.5, 0.5), 
                                    word_type = c(-0.5, 0.5)),
                   control = glmerControl(optimizer = "bobyqa"))

summary(m1_ret)

m2_ret <- glmer(corr ~ group*social_cond*word_type*age_year*scaled_pvt_all + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = blockRe[which(blockRe$test_three == "retention"),],
                    family = binomial,
                    contrasts = list(
                    group = c(-0.5, 0.5),
                    social_cond = c(-0.5, 0.5),
                    word_type = c(-0.5, 0.5)),
                    control = glmerControl(optimizer = "bobyqa"))

summary(m2_ret)

m3_ret <- glmer(corr ~ group*social_cond*word_type*age_year*scaled_mite_all + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = blockRe[which(blockRe$test_three == "retention"),],
                    family = binomial,
                    contrasts = list(
                    group = c(-0.5, 0.5),
                    social_cond = c(-0.5, 0.5),
                    word_type = c(-0.5, 0.5)),
                    control = glmerControl(optimizer = "bobyqa"))

summary(m3_ret)
```



## Follow up for Retention Group Analysis By Diagnostic Group
## Retention TD Analysis
```{r}
blockRe <- scale_var(blockRe, "retention", "TD")

simple_retTD <- glmer(corr ~ social_cond + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = blockRe[which(blockRe$test_three == "retention" & blockRe$group == "TD"),],
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5)
                   ),
                    control = glmerControl(optimizer = "bobyqa"))

summary(simple_retTD)

simple_retTD2 <- glmer(corr ~ social_cond*scaled_age + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = blockRe[which(blockRe$test_three == "retention" & blockRe$group == "TD"),],
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5)
                   ),
                    control = glmerControl(optimizer = "bobyqa"))

summary(simple_retTD2)

simple_retTD3 <- glmer(corr ~ social_cond*scaled_age*word_type + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = blockRe[which(blockRe$test_three == "retention" & blockRe$group == "TD"),],
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5),
                    word_type = c(-0.5, 0.5)
                   ),
                    control = glmerControl(optimizer = "bobyqa"))

summary(simple_retTD3)

m1_retTD <- glmer(corr ~ social_cond*word_type*scaled_age*scaled_pvt_std + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = blockRe[which(blockRe$test_three == "retention" & blockRe$group == "TD"),],
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5),
                    word_type = c(-0.5, 0.5)),
                    control = glmerControl(optimizer = "bobyqa"))

summary(m1_retTD)

m2_retTD <- glmer(corr ~ social_cond*word_type*scaled_age*scaled_mite + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = blockRe[which(blockRe$test_three == "retention" & blockRe$group == "TD"),],
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5),
                    word_type = c(-0.5, 0.5)),
                    control = glmerControl(optimizer = "bobyqa"))

summary(m2_retTD)
```

## Retention TD Social * Age * Word Type Interaction (Only in simple_retTD3)
```{r}
blockRe %>%
  filter(group == "TD") %>%
  filter(test_three == "retention") %>%
  filter(!is.na(corr)) %>%
  # group_by(Participant.Public.ID, group, age_year, age_month, age_group, word_type, social_cond) %>%
  # dplyr::summarise(corr = mean(corr, na.rm = T)) %>%
  arrange(group, word_type, social_cond) %>%
  dplyr::mutate(social_cond = dplyr::recode(social_cond, "front" = "Direct", "side" = "Overhearing")) %>%
  ggplot(aes(x = social_cond, y = corr)) +
  geom_bar(
    aes(fill = social_cond),
    position = position_dodge(),
    width = 0.9,
    stat = "summary",
    fun.y = "mean"
  ) +
  facet_grid(~group + age_group + word_type + test_three,  labeller = (labeller(word_type = labsWord))) +
  guides(fill = guide_legend(title = "Social Condition")) +
  labs(title = "Retention Accuracy",
       x = "Social Condition",  # Change x-axis label
       y = "Accuracy (%)") +
  geom_beeswarm(
    aes(group = Participant.Public.ID),
    dodge.width = 0.3,
    cex = 1.5,
    size = 3,
    alpha = 0.5,
    show.legend = FALSE,
    stat = "summary",
    fun.y = "mean"
  ) +
  styling

blockRe %>%
  filter(group == "TD" & test_three == "retention") %>%
  group_by(group, test_three, age_group, word_type,social_cond) %>%
  dplyr::summarise(mean_acc = mean(corr, na.rm = T))
```


## Retention ASD Analysis
```{r}
blockRe <- scale_var(blockRe, "retention", "ASD")

simple_retASD <- glmer(corr ~ social_cond + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = blockRe[which(blockRe$test_three == "retention" & blockRe$group == "ASD"),],
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5)
                   ),
                    control = glmerControl(optimizer = "bobyqa"))

summary(simple_retASD)

simple_retASD2 <- glmer(corr ~ social_cond*scaled_age + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = blockRe[which(blockRe$test_three == "retention" & blockRe$group == "ASD"),],
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5)
                   ),
                    control = glmerControl(optimizer = "bobyqa"))

summary(simple_retASD2)

simple_retASD3 <- glmer(corr ~ social_cond*scaled_age*word_type + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = blockRe[which(blockRe$test_three == "retention" & blockRe$group == "ASD"),],
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5),
                    word_type = c(-0.5, 0.5)
                   ),
                    control = glmerControl(optimizer = "bobyqa"))

summary(simple_retASD3)

m1_retASD <- glmer(corr ~ social_cond*word_type*scaled_age*scaled_pvt_std + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = blockRe[which(blockRe$test_three == "retention" & blockRe$group == "ASD"),],
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5),
                    word_type = c(-0.5, 0.5)),
                    control = glmerControl(optimizer = "bobyqa"))

summary(m1_retASD)

m2_retASD <- glmer(corr ~ social_cond*word_type*scaled_age*scaled_mite + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = blockRe[which(blockRe$test_three == "retention" & blockRe$group == "ASD"),],
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5),
                    word_type = c(-0.5, 0.5)),
                    control = glmerControl(optimizer = "bobyqa"))

summary(m2_retASD)


blockRe[which(blockRe$test_three == "retention"),] %>%
  group_by(group, age_group, social_cond, test_three) %>%
  dplyr::summarise(mean_acc = mean(corr, na.rm = T), n = n())
```


# Retention Individual Difference Analysis
## Calculate mean accuracy by subject for retention
```{r}
meanAccRet <-
  blockRe %>%
  filter(test_three == "retention") %>%
  group_by(Participant.Public.ID, group, age_year, age_month, age_group, test_three, word_type, social_cond, pvt_raw_score,
           pvt_std_score, mite_total_score) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T)) %>%
  arrange(group, word_type, social_cond)

meanAccRetLog <- 
  meanAccRet %>%
  group_by(Participant.Public.ID, group, age_year, age_month, age_group, test_three, social_cond, pvt_raw_score,
           pvt_std_score, mite_total_score) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T)) %>%
  arrange(group, social_cond) %>%
  mutate(corr_log = log(corr))

# Against chance-level
wrap_t(meanAccRet, "TD", "Direct")
wrap_t(meanAccRet, "TD", "Overhearing")
wrap_t(meanAccRet, "ASD", "Direct")
wrap_t(meanAccRet, "ASD", "Overhearing")

# Group comparisons
#TD
library(tidyr)

meanAccRetTD <-
  meanAccRet %>%
  filter(group == "TD")

t.test(corr~social_cond, paired = T, data = meanAccRetTD, alternative = "greater")

meanAccRetASD <-
  meanAccRet %>%
  filter(group == "ASD")

t.test(corr~social_cond, paired = T, data = meanAccRetASD, alternative = "less")

t.test(meanAccAttTDYoung$Overhearing, meanAccAttTDYoung$Direct, paired = T, alternative = "less")
```



```{r}
# Invididuals missing PVT
blockRe %>%
  filter(test_three == "retention") %>%
  filter(is.na(pvt_std_score)) %>%
  dplyr::select(Participant.Public.ID, group) %>%
  group_by(group) %>%
  distinct(.) %>%
  dplyr::summarise(n = n())

# Invididuals missing MITE
blockRe %>%
  filter(test_three == "retention") %>%
  filter(is.na(mite_total_score)) %>%
  dplyr::select(Participant.Public.ID, group) %>%
  group_by(group) %>%
  distinct(.) %>%
  dplyr::summarise(n = n())
```

# Mediation Analyses
```{r, include = F}
library(mediation)
# Cannot use Log scores due to accuracy = 0
medSocial <-
function(social, diagnostic_group, age, mediator, seed) {
  set.seed(seed)
  meanAccImmOH <-
    meanAccRetLog %>%
    filter(social_cond == social) %>%
    filter(group == diagnostic_group)
  
  if(age != "all") {
    meanAccImmOH <-
      meanAccImmOH %>%
      filter(age_group == age)
  }
  
  meanAccImmOH[,c("scaled_mediator")] <- scale(meanAccImmOH[,c(mediator)])
  meanAccImmOH[,c("scaled_age")] <- scale(meanAccImmOH$age_year)
  
  # model.M <- lm(M ~ X, myData)
  # model.Y <- lm(Y ~ X + M, myData)
  # results <- mediate(model.M, model.Y, treat='X', mediator='M',
  #                    boot=TRUE, sims=100)
  
  # Using non-scale is the same
  model.M <- lm(scaled_mediator ~ scaled_age, data = meanAccImmOH)
  model.Y <- lm(corr ~ scaled_age + scaled_mediator, data = meanAccImmOH)
  results <- mediate(model.M, model.Y, treat='scaled_age', mediator='scaled_mediator',
                     boot=TRUE, sims=100)
  resultsTemp <- summary(results)
  
  return(resultsTemp)
}
```

```{r}
# Accuracy and Age Relationship is not mediated by PVT
medSocial("Overhearing", "TD", "all", "pvt_raw_score", 140)
medSocial("Direct", "TD", "all", "pvt_raw_score", 141)
medSocial("Overhearing", "TD", "all", "mite_total_score", 142)
medSocial("Direct", "TD", "all", "mite_total_score", 143)

# Accuracy and Age Relationship is not mediated by MITE
medSocial("Overhearing", "ASD", "all", "mite_total_score", 160)
medSocial("Direct", "ASD", "all", "mite_total_score", 161)

medSocial("Overhearing", "ASD", "all", "pvt_raw_score", 162)
medSocial("Direct", "ASD", "all", "pvt_raw_score", 163)

```

## Plot TD Social * Age * PVT Interaction
```{r}
meanAccRet %>%
  filter(group == "TD") %>%
  filter(!is.na(corr)) %>%
  group_by(Participant.Public.ID, group, age_group, social_cond, pvt_raw_score) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T), n = n()) %>%
  arrange(group, social_cond) %>%
  dplyr::mutate(social_cond = dplyr::recode(social_cond, "front" = "Direct", "side" = "Overhearing"),
                pvt_raw_score = as.numeric(as.character(pvt_raw_score)),
                corr = as.numeric(as.character(corr))) %>%
  ggplot(aes(x = pvt_raw_score, y = corr)) +
  geom_point(
    aes(color = social_cond),
    stat = "identity",
    size = 3,
    na.rm=TRUE,
    position = position_dodge(width = 4),
    show.legend = FALSE,
    alpha = 0.5,
    shape=1,
    stroke = 2
  ) +
  facet_grid(~group + age_group,  labeller = (labeller(word_type = labsWord))) +
  geom_smooth(method='lm', formula= y~x, aes(color = social_cond), se = F) +
  guides(fill = guide_legend(title = "Social Condition")) +
  labs(title = "Immediate Recall Accuracy",
       x = "PVT Raw Score",  # Change x-axis label
       y = "Accuracy (%)") +
  styling

# N for this plot
meanAccRet %>%
  filter(group == "TD") %>%
  filter(!is.na(corr)) %>%
  filter(!is.na(pvt_std_score)) %>%
  group_by(group, age_group, social_cond) %>%
  distinct(.) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T), n = length(unique(Participant.Public.ID))) %>%
  arrange(group, social_cond) 
```



# Immediate Recall vs. Retention Analysis
# Combine Immediate Recall, Attainment, and Retention
```{r, include = F}
immRe$test_time <- "immediate"
immRe$test_three <- "immediate"
  
allRe <- dplyr::bind_rows(immRe, blockRe)

allRe$test_time <- as.factor(allRe$test_time)
allRe$test_three <- as.factor(allRe$test_three)
```

# Change dataset and subset by group for Immediate Recall vs. Retention Analysis
```{r}
allRe <-
  allRe %>%
  arrange(Participant.Public.ID, Event.Index) %>%
  dplyr::mutate(social_cond = dplyr::recode(social_cond, "front" = "Direct", "side" = "Overhearing"),
                test_time_num = dplyr::recode(test_three, "immediate" = 1, "attainment" = 2, "retention" = 3))

# allRe$test_time_num <- as.numeric(as.character(allRe$test_time_num))
allRe$scaled_time <- scale(allRe$test_time_num, center = T)
allRe$scaled_age <- scale(allRe$age_year, center = T)
allRe$scaled_pvt <- scale(allRe$pvt_std_score, center = T)
allRe$scaled_orr <- scale(allRe$orr_std_score, center = T)
allRe$scaled_mite <- scale(allRe$mite_total_score, center = T)
allRe$test_time_num <- as.factor(allRe$test_time_num)


allRe$group <- factor(allRe$group, levels = c("ASD", "TD"))
allRe <- allRe[order(allRe$group),]

allRe$social_cond <- factor(allRe$social_cond, levels = c("Direct", "Overhearing"))
allRe <- allRe[order(allRe$social_cond),]

allRe$test_time <- factor(allRe$test_time, levels = c("immediate", "attainment", "short_retention", "retention"))
allRe <- allRe[order(allRe$test_time),]

allRe$test_three <- factor(allRe$test_three, levels = c("immediate", "attainment", "retention"))
allRe <- allRe[order(allRe$test_three),]

allRe$word_type <- factor(allRe$word_type, levels = c("noun", "verb"))
allRe <- allRe[order(allRe$word_type),]

allReTD <- allRe[which(allRe$group == "TD"),]
allReASD <- allRe[which(allRe$group == "ASD"),]

# four_helmert = matrix(c(3/4, -1/4, -1/4, -1/4, 0, 2/3, -1/3, -1/3, 0, 0, 1/2, -1/2), ncol = 3)

allRe %>%
  group_by(group, test_time) %>%
  dplyr::summarise(n = sum(!is.na(unique(Participant.Public.ID))))

allRe %>%
  group_by(group, test_time) %>%
  dplyr::summarise(n = sum(!is.na(unique(Participant.Public.ID))))

allRe %>%
  dplyr::select(Participant.Public.ID, group, test_three, participant_gender, age_year) %>%
  distinct(.) %>%
  group_by(group, test_three) %>%
  dplyr::summarise(n = sum(!is.na(unique(Participant.Public.ID))), 
                   mean_age = mean(age_year, na.rm = T),
                   sd = sd(age_year, na.rm = T))

allRe %>%
  dplyr::select(Participant.Public.ID, group, test_three, participant_gender, age_year) %>%
  distinct(.) %>%
  group_by(group, test_three, participant_gender) %>%
  dplyr::summarise(n = sum(!is.na(unique(Participant.Public.ID))), 
                   mean_age = mean(age_year, na.rm = T),
                   sd = sd(age_year, na.rm = T))
```


# Immediate Recall vs. Retention Analysis
```{r, include = F}
immRetention <- allRe[which(allRe$test_three %in% c("immediate", "retention")),]

immRetention <-
  immRetention %>%
  dplyr::mutate(test_time_num = dplyr::recode(test_three, "immediate" = 1, "retention" = 2))

immRetention$scaled_time <- scale(immRetention$test_time_num, center = T)
immRetention$scaled_time <- as.numeric(as.character(immRetention$scaled_time))

immRetention$test_three <- factor(immRetention$test_three, levels = c("immediate", "retention"))
immRetention <- immRetention[order(immRetention$test_three),]

immRetentionTD <- immRetention[which(immRetention$group == "TD"),]
immRetentionASD <- immRetention[which(immRetention$group == "ASD"),]

m1_immRetention <- glmer(corr ~ social_cond*test_three*word_type*age_group + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                          data = immRetentionTD,
                          family = binomial,
                          contrasts = list(
                          group = c(-0.5, 0.5),
                          test_three = c(-0.5, 0.5),
                          word_type = c(-0.5, 0.5),
                          social_cond = c(-0.5, 0.5),
                          age_group = c(-0.5, 0.5)
                          ),
                          control = glmerControl(optimizer = "bobyqa"))

summary(m1_immRetention)


m1_immRetentionOld <- glmer(corr ~ social_cond*test_three*word_type + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                          data = immRetentionTD[which(immRetentionTD$age_group == "older"),],
                          family = binomial,
                          contrasts = list(
                          group = c(-0.5, 0.5),
                          test_three = c(-0.5, 0.5),
                          word_type = c(-0.5, 0.5),
                          social_cond = c(-0.5, 0.5),
                          age_group = c(-0.5, 0.5)
                          ),
                          control = glmerControl(optimizer = "bobyqa"))

summary(m1_immRetentionOld)

m1_immRetentionYoung <- glmer(corr ~ social_cond*test_three*word_type + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                          data = immRetentionTD[which(immRetentionTD$age_group == "younger"),],
                          family = binomial,
                          contrasts = list(
                          group = c(-0.5, 0.5),
                          test_three = c(-0.5, 0.5),
                          word_type = c(-0.5, 0.5),
                          social_cond = c(-0.5, 0.5),
                          age_group = c(-0.5, 0.5)
                          ),
                          control = glmerControl(optimizer = "bobyqa"))

summary(m1_immRetentionYoung)

m2_immRetention <- glm(corr ~ social_cond*test_three*scaled_age,
                          data = immRetentionTD,
                          family = binomial,
                          contrasts = list(
                          group = c(-0.5, 0.5),
                          test_three = c(-0.5, 0.5),
                          word_type = c(-0.5, 0.5),
                          social_cond = c(-0.5, 0.5)
                          ))

summary(m2_immRetention)

immRetention %>%
  group_by(group, test_three) %>%
  dplyr::summarise(mean_acc = mean(corr, na.rm = T))
```



## Immediate Recall, Attainment, Retention Group Analysis (GLMER)
```{r}
three_helmert = matrix(c(2/3, -1/3, -1/3, 0, .5, -.5), ncol = 2)
# three_helmert = matrix(c(-1/3, -1/3, 2/3, -0.5, 0.5, 0), ncol = 2)

simple_allRe <- glmer(corr ~ group*social_cond + (1 + social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = allRe,
                    family = binomial,
                    contrasts = list(
                    group = c(-0.5, 0.5),
                    social_cond = c(-0.5, 0.5)
                    ),
                    control = glmerControl(optimizer = "bobyqa"))

summary(simple_allRe)

simple_allRe2 <- glmer(corr ~ group*social_cond*scaled_age + (1 + social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = allRe,
                    family = binomial,
                    contrasts = list(
                    group = c(-0.5, 0.5),
                    social_cond = c(-0.5, 0.5)
                    ),
                    control = glmerControl(optimizer = "bobyqa"))

summary(simple_allRe2)

simple_allRe3 <- glmer(corr ~ group*social_cond*scaled_age*test_three + 
                          (1 + social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = allRe[which(allRe$test_three == "attainment" | 
                                           allRe$test_three == "retention"),],
                    family = binomial,
                    contrasts = list(
                    group = c(-0.5, 0.5),
                    social_cond = c(-0.5, 0.5),
                    # test_three = three_helmert,
                    test_three = c(-0.5, 0.5)
                    ),
                    control = glmerControl(optimizer = "bobyqa"))

summary(simple_allRe3)


# Run within group analysis and across groups; get rid of age in group analysis as long as they are matched
# is it more interesting to look at a certain time point
# m1_allRe <- glmer(corr ~ group*social_cond*word_type*test_three*scaled_age + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
#                     data = allRe,
#                     family = binomial,
#                     contrasts = list(
#                     test_three = three_helmert,
#                     social_cond = c(-0.5, 0.5),
#                     word_type = c(-0.5, 0.5),
#                     group = c(-0.5, 0.5),
#                     age_group = c(-0.5, 0.5)
#                     ),
#                     control = glmerControl(optimizer = "bobyqa"))
# 
# summary(m1_allRe)
```

## Immediate Recall, Attainment, Retention Analysis in TD
```{r}
simple_allReTD <- glmer(corr ~ social_cond + (1 + social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = allReTD,
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5)
                    ),
                    control = glmerControl(optimizer = "bobyqa"))

summary(simple_allReTD)


simple_allReTD2 <- glmer(corr ~ social_cond*scaled_age + 
                          (1 + social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = allReTD,
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5)
                    ),
                    control = glmerControl(optimizer = "bobyqa"))

summary(simple_allReTD2)

three_helmert = matrix(c(2/3, -1/3, -1/3, 0, .5, -.5), ncol = 2)

simple_allReTD3 <- glmer(corr ~ social_cond*scaled_age*test_three + 
                          (1 + social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = allReTD[which(allReTD$test_three == "attainment" | 
                                           allReTD$test_three == "retention"),],
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5),
                    # test_three = three_helmert,
                    test_three = c(-0.5, 0.5)
                    ),
                    control = glmerControl(optimizer = "bobyqa"))

summary(simple_allReTD3)

m1_allReTD <- glmer(corr ~ social_cond*scaled_age*scaled_pvt + 
                          (1 + social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = allReTD,
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5),
                    test_three = three_helmert
                    ),
                    control = glmerControl(optimizer = "bobyqa"))

summary(m1_allReTD)

m2_allReTD <- glmer(corr ~ social_cond*scaled_age*scaled_mite + 
                          (1 + social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = allReTD,
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5),
                    test_three = three_helmert
                    ),
                    control = glmerControl(optimizer = "bobyqa"))

summary(m2_allReTD)
```



```{r, include = F, eval = F}
m1_allReOld <- glmer(corr ~ social_cond*test_three + (1 + social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = allReTD[which(allReTD$age_group == "older"),],
                    family = binomial,
                    contrasts = list(
                    test_three = three_helmert,
                    social_cond = c(-0.5, 0.5),
                    word_type = c(-0.5, 0.5)
                    ),
                    control = glmerControl(optimizer = "bobyqa"))

summary(m1_allReOld)

m1_allReYoung <- glmer(corr ~ social_cond*test_three*word_type + (1 + social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = allReTD[which(allReTD$age_group == "younger"),],
                    family = binomial,
                    contrasts = list(
                    test_three = three_helmert,
                    social_cond = c(-0.5, 0.5),
                    word_type = c(-0.5, 0.5)
                    ),
                    control = glmerControl(optimizer = "bobyqa"))

summary(m1_allReYoung)

m1_allReN <- glmer(corr ~ social_cond*test_three*age_group + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = allReTD[which(allReTD$word_type == "noun"),],
                    family = binomial,
                    contrasts = list(
                    test_three = three_helmert,
                    social_cond = c(-0.5, 0.5),
                    age_group = c(-0.5, 0.5),
                    group = c(-0.5, 0.5)
                    ),
                    control = glmerControl(optimizer = "bobyqa"))

summary(m1_allReN)


m1_allReV <- glmer(corr ~ social_cond*test_three*age_group + (1+social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = allReTD[which(allReTD$word_type == "verb"),],
                    family = binomial,
                    contrasts = list(
                    test_three = three_helmert,
                    social_cond = c(-0.5, 0.5),
                    age_group = c(-0.5, 0.5),
                    group = c(-0.5, 0.5)
                    ),
                    control = glmerControl(optimizer = "bobyqa"))

summary(m1_allReV)


m2_allRe <- glm(corr ~ group*social_cond*test_three*age_year*word_type,
                    data = allRe,
                    family = binomial,
                    contrasts = list(
                    test_time = four_helmert,
                    test_three = three_helmert,
                    social_cond = c(-0.5, 0.5),
                    word_type = c(-0.5, 0.5),
                    group = c(-0.5, 0.5)
                    ))

summary(m2_allRe)

m2_allReN <- glm(corr ~ group*social_cond*test_three*age_year,
                    data = allRe[which(allRe$word_type== "noun"),],
                    family = binomial,
                    contrasts = list(
                    test_time = four_helmert,
                    test_three = three_helmert,
                    social_cond = c(-0.5, 0.5),
                    word_type = c(-0.5, 0.5),
                    group = c(-0.5, 0.5)
                    ))

summary(m2_allReN)

m2_allReV <- glm(corr ~ group*social_cond*test_three*age_year,
                    data = allRe[which(allRe$word_type== "verb"),],
                    family = binomial,
                    contrasts = list(
                    test_time = four_helmert,
                    test_three = three_helmert,
                    social_cond = c(-0.5, 0.5),
                    word_type = c(-0.5, 0.5),
                    group = c(-0.5, 0.5)
                    ))

summary(m2_allReV)

cor.test(allRe$age_year, allRe$corr)
```


## Immediate Recall, Attainment, Retention Analysis in ASD
```{r}
simple_allReASD <- glmer(corr ~ social_cond + (1 + social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = allReASD,
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5)
                    ),
                    control = glmerControl(optimizer = "bobyqa"))

summary(simple_allReASD)


simple_allReASD2 <- glmer(corr ~ social_cond*scaled_age + 
                          (1 + social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = allReASD,
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5)
                    ),
                    control = glmerControl(optimizer = "bobyqa"))

summary(simple_allReASD2)

simple_allReASD3 <- glmer(corr ~ social_cond*scaled_age*test_three + 
                          (1 + social_cond|Participant.Public.ID) + (1+social_cond|story),
                    data = allReASD[which(allReASD$test_three == "attainment" | 
                                           allReASD$test_three == "retention"),],
                    family = binomial,
                    contrasts = list(
                    social_cond = c(-0.5, 0.5),
                    # test_three = three_helmert,
                    test_three = c(-0.5, 0.5)
                    ),
                    control = glmerControl(optimizer = "bobyqa"))

summary(simple_allReASD3)
```


## Plot Social * Age Interaction across all timepoints in TD (from multiple TD models)
```{r}
library(ggbeeswarm)

allRe %>%
  filter(group == "TD") %>%
  filter(test_time == "retention") %>%
  filter(!is.na(corr)) %>%
  # group_by(Participant.Public.ID, group, age_year, age_month, age_group, word_type, social_cond) %>%
  # dplyr::summarise(corr = mean(corr, na.rm = T)) %>%
  arrange(group, word_type, social_cond) %>%
  dplyr::mutate(social_cond = dplyr::recode(social_cond, "front" = "Direct", "side" = "Overhearing")) %>%
  ggplot(aes(x = social_cond, y = corr)) +
  geom_bar(
    aes(fill = social_cond),
    position = position_dodge(),
    width = 0.9,
    stat = "summary",
    fun.y = "mean"
  ) +
  facet_grid(~group,  labeller = (labeller(word_type = labsWord))) +
  guides(fill = guide_legend(title = "Social Condition")) +
  labs(title = "Accuracy Across All Time Points",
       x = "Social Condition",  # Change x-axis label
       y = "Accuracy (%)") +
  geom_beeswarm(
    aes(group = Participant.Public.ID),
    dodge.width = 0.3,
    cex = 1.5,
    size = 3,
    alpha = 0.5,
    show.legend = FALSE,
    stat = "summary",
    fun.y = "mean"
  ) +
  styling

blockRe %>%
  filter(group == "TD" & test_three == "attainment") %>%
  group_by(group, test_three, age_group, word_type,social_cond) %>%
  dplyr::summarise(mean_acc = mean(corr, na.rm = T))
```


# Across Time Individual Difference Analysis
## Calculate mean accuracy by subject across time
```{r}
meanAllRet <-
  allRe %>%
  group_by(Participant.Public.ID, group, age_year, age_month, age_group, word_type, social_cond, pvt_raw_score,
           pvt_std_score, mite_total_score) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T)) %>%
  arrange(group, word_type, social_cond)

meanAccRetLog <- 
  meanAllRet %>%
  group_by(Participant.Public.ID, group, age_year, age_month, age_group, social_cond, pvt_raw_score,
           pvt_std_score, mite_total_score) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T)) %>%
  arrange(group, social_cond) %>%
  mutate(corr_log = log(corr))
```

```{r}
# Invididuals missing PVT
allRe %>%
  filter(is.na(pvt_std_score)) %>%
  dplyr::select(Participant.Public.ID, group) %>%
  group_by(group) %>%
  distinct(.) %>%
  dplyr::summarise(n = n())

# Invididuals missing MITE
allRe %>%
  filter(test_three == "retention") %>%
  filter(is.na(mite_total_score)) %>%
  dplyr::select(Participant.Public.ID, group) %>%
  group_by(group) %>%
  distinct(.) %>%
  dplyr::summarise(n = n())
```

# Mediation Analyses
```{r}
library(mediation)
# Cannot use Log scores due to accuracy = 0
medSocial <-
function(social, diagnostic_group, age, mediator, seed) {
  set.seed(seed)
  meanAccImmOH <-
    meanAccRetLog %>%
    filter(social_cond == social) %>%
    filter(group == diagnostic_group)
  
  if(age != "all") {
    meanAccImmOH <-
      meanAccImmOH %>%
      filter(age_group == age)
  }
  
  meanAccImmOH[,c("scaled_mediator")] <- scale(meanAccImmOH[,c(mediator)])
  meanAccImmOH[,c("scaled_age")] <- scale(meanAccImmOH$age_year)
  
  # model.M <- lm(M ~ X, myData)
  # model.Y <- lm(Y ~ X + M, myData)
  # results <- mediate(model.M, model.Y, treat='X', mediator='M',
  #                    boot=TRUE, sims=100)
  
  # Using non-scale is the same
  model.M <- lm(scaled_mediator ~ scaled_age, data = meanAccImmOH)
  model.Y <- lm(corr ~ scaled_age + scaled_mediator, data = meanAccImmOH)
  results <- mediate(model.M, model.Y, treat='scaled_age', mediator='scaled_mediator',
                     boot=TRUE, sims=100)
  resultsTemp <- summary(results)
  
  return(resultsTemp)
}
```

```{r}
# Accuracy and Age Relationship is not mediated by PVT
medSocial("Overhearing", "TD", "all", "pvt_raw_score", 128)
medSocial("Direct", "TD", "all", "pvt_raw_score", 129)
medSocial("Overhearing", "ASD", "all", "pvt_raw_score", 170)
medSocial("Direct", "ASD", "all", "pvt_raw_score", 171)

# Accuracy and Age Relationship is not mediated by MITE
medSocial("Overhearing", "TD", "all", "mite_total_score", 130)
medSocial("Direct", "TD", "all", "mite_total_score", 131)
medSocial("Overhearing", "ASD", "all", "mite_total_score", 150)
medSocial("Direct", "ASD", "all", "mite_total_score", 151)

```


## Plot TD Social (* Age) * PVT Interaction Across Time
**(Both main effect of PVT and Social * PVT * Age in models)**
```{r}
meanAllRet %>%
  filter(group == "TD") %>%
  filter(!is.na(corr)) %>%
  group_by(Participant.Public.ID, group, age_group, social_cond, pvt_std_score) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T), n = n()) %>%
  arrange(group, social_cond) %>%
  dplyr::mutate(social_cond = dplyr::recode(social_cond, "front" = "Direct", "side" = "Overhearing"),
                pvt_std_score = as.numeric(as.character(pvt_std_score)),
                corr = as.numeric(as.character(corr))) %>%
  ggplot(aes(x = pvt_std_score, y = corr)) +
  geom_point(
    aes(color = social_cond),
    stat = "identity",
    size = 3,
    na.rm=TRUE,
    position = position_dodge(width = 4),
    show.legend = FALSE,
    alpha = 0.5,
    shape=1,
    stroke = 2
  ) +
  facet_grid(~group,  labeller = (labeller(word_type = labsWord))) +
  geom_smooth(method='lm', formula= y~x, aes(color = social_cond), se = F) +
  guides(fill = guide_legend(title = "Social Condition")) +
  labs(title = "Accuracy Across Time",
       x = "PVT Std Score",  # Change x-axis label
       y = "Accuracy (%)") +
  styling

meanAllRet %>%
  filter(group == "TD") %>%
  filter(!is.na(corr)) %>%
  group_by(Participant.Public.ID, group, age_group, social_cond, pvt_std_score) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T), n = n()) %>%
  arrange(group, social_cond) %>%
  dplyr::mutate(social_cond = dplyr::recode(social_cond, "front" = "Direct", "side" = "Overhearing"),
                pvt_std_score = as.numeric(as.character(pvt_std_score)),
                corr = as.numeric(as.character(corr))) %>%
  ggplot(aes(x = pvt_std_score, y = corr)) +
  geom_point(
    aes(color = social_cond),
    stat = "identity",
    size = 3,
    na.rm=TRUE,
    position = position_dodge(width = 4),
    show.legend = FALSE,
    alpha = 0.5,
    shape=1,
    stroke = 2
  ) +
  facet_grid(~group + age_group,  labeller = (labeller(word_type = labsWord))) +
  geom_smooth(method='lm', formula= y~x, aes(color = social_cond), se = F) +
  guides(fill = guide_legend(title = "Social Condition")) +
  labs(title = "Accuracy Across Time",
       x = "PVT Std Score",  # Change x-axis label
       y = "Accuracy (%)") +
  styling

# N for this plot
meanAllRet %>%
  filter(group == "TD") %>%
  filter(!is.na(corr)) %>%
  filter(!is.na(pvt_std_score)) %>%
  group_by(group, age_group, social_cond) %>%
  distinct(.) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T), n = length(unique(Participant.Public.ID))) %>%
  arrange(group, social_cond) 
```



## Plot TD Social (* Age) * MITE Interaction Across Time
**(Only main effect of MITE in models)**
```{r}
meanAllRet %>%
  filter(group == "TD") %>%
  filter(!is.na(corr)) %>%
  group_by(Participant.Public.ID, group, age_group, social_cond, mite_total_score) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T), n = n()) %>%
  arrange(group, social_cond) %>%
  dplyr::mutate(social_cond = dplyr::recode(social_cond, "front" = "Direct", "side" = "Overhearing"),
                mite_total_score = as.numeric(as.character(mite_total_score)),
                corr = as.numeric(as.character(corr))) %>%
  ggplot(aes(x = mite_total_score, y = corr)) +
  geom_point(
    aes(color = social_cond),
    stat = "identity",
    size = 3,
    na.rm=TRUE,
    position = position_dodge(width = 4),
    show.legend = FALSE,
    alpha = 0.5,
    shape=1,
    stroke = 2
  ) +
  facet_grid(~group,  labeller = (labeller(word_type = labsWord))) +
  geom_smooth(method='lm', formula= y~x, aes(color = social_cond), se = F) +
  guides(fill = guide_legend(title = "Social Condition")) +
  labs(title = "Accuracy Across Time",
       x = "Mite Total Score",  # Change x-axis label
       y = "Accuracy (%)") +
  styling

meanAllRet %>%
  filter(group == "TD") %>%
  filter(!is.na(corr)) %>%
  group_by(Participant.Public.ID, group, age_group, social_cond, mite_total_score) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T), n = n()) %>%
  arrange(group, social_cond) %>%
  dplyr::mutate(social_cond = dplyr::recode(social_cond, "front" = "Direct", "side" = "Overhearing"),
                mite_total_score = as.numeric(as.character(mite_total_score)),
                corr = as.numeric(as.character(corr))) %>%
  ggplot(aes(x = mite_total_score, y = corr)) +
  geom_point(
    aes(color = social_cond),
    stat = "identity",
    size = 3,
    na.rm=TRUE,
    position = position_dodge(width = 4),
    show.legend = FALSE,
    alpha = 0.5,
    shape=1,
    stroke = 2
  ) +
  facet_grid(~group + age_group,  labeller = (labeller(word_type = labsWord))) +
  geom_smooth(method='lm', formula= y~x, aes(color = social_cond), se = F) +
  guides(fill = guide_legend(title = "Social Condition")) +
  labs(title = "Accuracy Across Time",
       x = "Mite Total Score",  # Change x-axis label
       y = "Accuracy (%)") +
  styling
```



## Calculate date differences between immediate recall, attainment, retention for each subject
https://stackoverflow.com/questions/56265669/compare-adjacent-rows-in-r
```{r, include = F}

```


# Plot across time and social condition accuracy
```{r, include = F}
library(ggplot2)
cbPalette <- c("#a6cee3", "#1f78b4", "#b2df8a", "#66c2a5", "#fc8d62", "#8da0cb", "#1b9e77", "#d95f02", "#7570b3")


labsWord <- c("Noun", "Verb")
names(labsWord) <- c("noun", "verb")

plot_across_time <-
  function(word_class1, word_class2, df) {
  df %>%
    filter(word_type == word_class1 | word_type == word_class2) %>%
    # filter(group == group_name) %>%
    filter(!is.na(corr)) %>%
    filter(!is.na(test_three)) %>%
    arrange(group) %>%    # First sort by val. This sort the dataframe but NOT the factor levels
    mutate(group = factor(group, levels=c("TD", "ASD"))) %>%
    # filter(age_year < 8.5) %>%
    mutate(
          # test_time = factor(test_time, levels=c("immediate", "attainment", "short_retention", "retention")),
           test_three = factor(test_three, levels=c("immediate", "attainment", "retention"))) %>%
    mutate(social_cond = dplyr::recode(social_cond, Direct = "Direct Address"),
           # test_time = dplyr::recode(test_time, immediate = "0 min", attainment = "5 min", short_retention = "10 min", retention = "1 week"),
           test_three = dplyr::recode(test_three, immediate = "0 min", attainment = "10 min", retention = "1 week")) %>%
    group_by(group, social_cond, test_three) %>%
    dplyr::summarise(mean = mean(corr, na.rm = TRUE),
                    sd = sd(corr, na.rm = TRUE),
                    n = n()) %>%
    mutate(se = sd / sqrt(n),
            lower_ci = mean - qt(1 - (0.05 / 2), n - 1) * se,
            upper_ci = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
    ggplot(aes(x = test_three, y = mean, group = social_cond,  fill = social_cond)) +
    scale_fill_manual(values = c(cbPalette[1], cbPalette[8])) +
    geom_bar(color = "black",
              position = position_dodge(),
              width = 0.7,
              stat = "summary",
              fun = "mean") +
    geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                  width = .1,
                  position = position_dodge(width = 0.7)) +
    geom_line(aes(color = social_cond),
              position = position_dodge(width=0.7),
              size = 1,
              stat = "summary",
               fun = "mean") +
    geom_point(color = "black",
               position = position_dodge(width=0.7),
               shape = 21,
               size = 3,
               stat = "summary",
               fun = "mean") +
    # scale_fill_manual(values=c("white", "grey")) +
    #facet_grid(~word_type + test_time + group,  labeller = (labeller(word_type = labsWord))) +
    facet_grid(~group,  labeller = (labeller(word_type = labsWord))) +
   # guides(fill = guide_legend(title="Social Condition")) +
     labs(x = "Test Time After Word Learning",  # Change x-axis label
          y = "Accuracy (%)") +
      labs(title = paste("Accuracy in", word_class1, word_class2)) +
      theme(
      plot.title = element_text(size = 30, face = "bold"),
      axis.title.x = element_text(size = 26, face = "bold"),
      axis.title.y = element_text(size = 22, face = "bold"),
      axis.text = element_text(size = 24, face = "bold"),
      legend.text = element_text(size = 22, face = "bold"),
      legend.title = element_text(size = 22, face = "bold"),
      panel.background = element_rect(fill = "white"),
      # Set plot background to whit
      axis.line.x = element_line(colour = "black", size = 1),
      # Add line to x axis
      axis.line.y = element_line(colour = "black", size = 1),
      # Add line to y axis
      strip.text = element_text(size = 24, face = "bold"),
      # Change facet text
      strip.background = element_rect(fill = "white", size = 1),
      # Change facet color
      panel.spacing = unit(.05, "lines"),
      # Add panel border
      panel.border = element_rect(color = "black", fill = NA, size = 0.5),
      # Change panel border color and size
      legend.background = element_rect(fill = "#ffffff00")
      # strip.text = element_blank()
    ) +
     guides(fill = guide_legend(title = "Social Condition")) +
    guides(color = "none") +
    coord_cartesian(ylim = c(0.5, 0.91))
  }
  # guides(color = guide_legend(override.aes = list(fill = c("white", "gray"))))

plot_retention <-
  function(group_name, word_class1, word_class2, df) {
  df %>%
    filter(word_type == word_class1 | word_type == word_class2) %>%
    # filter(group == group_name) %>%
    filter(!is.na(corr)) %>%
    # filter(!is.na(test_three)) %>%
    filter(test_three != "immediate") %>%
    arrange(group) %>%  # First sort by val. This sort the dataframe but NOT the factor levels
    mutate(group = factor(group, levels=c("TD", "ASD"))) %>%
    mutate(social_cond = dplyr::recode(social_cond, Direct = "Direct Address"),
           test_three = dplyr::recode(test_three, immediate = "Immediate", attainment = "Short-Term Retention", retention = "Long-Term Retention")) %>%
    group_by(group, social_cond, test_three) %>%
    dplyr::summarise(mean = mean(corr, na.rm = TRUE),
                    sd = sd(corr, na.rm = TRUE),
                    n = n()) %>%
    mutate(se = sd / sqrt(n),
            lower_ci = mean - qt(1 - (0.05 / 2), n - 1) * se,
            upper_ci = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
    ggplot(aes(x = group, y = mean, group = social_cond,  fill = group)) +
    geom_bar(color = "black",
              position = position_dodge(),
              width = 0.7,
              stat = "summary",
              fun = "mean") +
    scale_fill_manual(values = c(cbPalette[1], cbPalette[8])) +
    scale_color_manual(values = c("black")) +
    geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                  width = .1,
                  position = position_dodge(width = 0.7)) +
    geom_line(aes(color = "black"),
              position = position_dodge(width=0.7),
              size = 0.8,
              stat = "summary",
               fun = "mean") +
    geom_point(color = "black",
               position = position_dodge(width=0.7),
               shape = 21,
               size = 3,
               stat = "summary",
               fun = "mean") +
    facet_grid(~test_three,  labeller = (labeller(word_type = labsWord))) +
    # scale_fill_manual(values=c("white", "grey")) +
   # guides(fill = guide_legend(title="Social Condition")) +
     labs(x = "Test Time",  # Change x-axis label
          y = "Accuracy (%)") +
      # labs(title = paste("Accuracy in", word_class1, word_class2)) +
      theme(
      plot.title = element_text(size = 30, face = "bold"),
      axis.title.x = element_blank(),
      axis.title.y = element_text(size = 22, face = "bold"),
      axis.text = element_text(size = 24, face = "bold"),
      legend.text = element_text(size = 22, face = "bold"),
      legend.title = element_text(size = 22, face = "bold"),
      panel.background = element_rect(fill = "white"),
      # Set plot background to whit
      axis.line.x = element_line(colour = "black", size = 1),
      # Add line to x axis
      axis.line.y = element_line(colour = "black", size = 1),
      # Add line to y axis
      strip.text = element_text(size = 26, face = "bold"),
      # Change facet text
      strip.background = element_rect(fill = "white", size = 1),
      # Change facet color
      panel.spacing = unit(.05, "lines"),
      # Add panel border
      panel.border = element_rect(color = "black", fill = NA, size = 0.5),
      # Change panel border color and size
      legend.background = element_rect(fill = "#ffffff00")
      # strip.text = element_blank()
      # legend.position = c(.78, 0.85)
    ) +
     guides(fill = guide_legend(title = "Group")) +
    guides(color = "none") +
    coord_cartesian(ylim = c(0.57, 0.87)) +
    geom_segment(data = data.frame(test_three = "Long-Term Retention", group = "ASD", social_cond = "Direct"),
                 aes(x = 0.75, xend = 1.25, y = 0.8, yend = 0.8)) +
    # geom_text(aes(x = 1, y = 0.805, label = paste0("*")), size = 11, color = "black") +
    geom_segment(data = data.frame(test_three = "Long-Term Retention", group = "ASD", social_cond = "Direct"),
                 aes(x = 1.75, xend = 2.25, y = 0.735, yend = 0.735)) +
    geom_segment(data = data.frame(test_three = "Long-Term Retention", group = "ASD", social_cond = "Direct"),
                 aes(x = 1, xend = 2, y = 0.83, yend = 0.83)) +
    geom_segment(data = data.frame(test_three = "Long-Term Retention", group = "ASD", social_cond = "Direct"),
                 aes(x = 1, xend = 1, y = 0.83, yend = 0.82)) +
    geom_segment(data = data.frame(test_three = "Long-Term Retention", group = "ASD", social_cond = "Direct"),
                 aes(x = 2, xend = 2, y = 0.83, yend = 0.76)) +
    geom_segment(data = data.frame(test_three = "Long-Term Retention", group = "ASD", social_cond = "Direct"),
                 aes(x = 1.5, xend = 1.5, y = 0.83, yend = 0.835)) +
    geom_text(size = 5, color = "black", 
              data = data.frame(test_three = "Long-Term Retention", group = "ASD", social_cond = "Direct"),
              aes(x = 2, y = 0.75, label = paste0(""))) +
    geom_text(size = 7, color = "black", 
              data = data.frame(test_three = "Long-Term Retention", group = "ASD", social_cond = "Direct"),
              aes(x = 1.5, y = 0.855, label = paste0(""))) 
    # geom_text(aes(x = 1.5, y = 0.855, label = paste0("")), size = 7, color = "black")
  }

plot_group <-
  function(group_name, word_class1, word_class2, df) {
  df %>%
    filter(word_type == word_class1 | word_type == word_class2) %>%
    # filter(group == group_name) %>%
    filter(!is.na(corr)) %>%
    # filter(!is.na(test_three)) %>%
    filter(test_three != "immediate") %>%
    arrange(group) %>%  # First sort by val. This sort the dataframe but NOT the factor levels
    mutate(group = factor(group, levels=c("TD", "ASD"))) %>%
    mutate(social_cond = dplyr::recode(social_cond, Direct = "Direct Address"),
           test_three = dplyr::recode(test_three, immediate = "0 min", attainment = "Short-Term Retention", retention = "Long-Term Retention")) %>%
    group_by(group, social_cond, test_three) %>%
    dplyr::summarise(mean = mean(corr, na.rm = TRUE),
                    sd = sd(corr, na.rm = TRUE),
                    n = n()) %>%
    mutate(se = sd / sqrt(n),
            lower_ci = mean - qt(1 - (0.05 / 2), n - 1) * se,
            upper_ci = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
    ggplot(aes(x = test_three, y = mean, group = social_cond,  fill = group)) +
    geom_bar(color = "black",
              position = position_dodge(),
              width = 0.7,
              stat = "summary",
              fun = "mean") +
    scale_fill_manual(values = c(cbPalette[1], cbPalette[8])) +
    scale_color_manual(values = c("black")) +
    geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                  width = .1,
                  position = position_dodge(width = 0.7)) +
    geom_line(aes(color = "black"),
              position = position_dodge(width=0.7),
              size = 0.8,
              stat = "summary",
               fun = "mean") +
    geom_point(color = "black",
               position = position_dodge(width=0.7),
               shape = 21,
               size = 3,
               stat = "summary",
               fun = "mean") +
    facet_grid(~group,  labeller = (labeller(word_type = labsWord))) +
    # scale_fill_manual(values=c("white", "grey")) +
   # guides(fill = guide_legend(title="Social Condition")) +
     labs(x = "Test Time",  # Change x-axis label
          y = "Accuracy (%)") +
      # labs(title = paste("Accuracy in", word_class1, word_class2)) +
      theme(
      plot.title = element_text(size = 30, face = "bold"),
      axis.title.x = element_text(size = 26, face = "bold"),
      axis.title.y = element_text(size = 22, face = "bold"),
      axis.text = element_text(size = 24, face = "bold"),
      legend.text = element_text(size = 22, face = "bold"),
      legend.title = element_text(size = 22, face = "bold"),
      panel.background = element_rect(fill = "white"),
      # Set plot background to whit
      axis.line.x = element_line(colour = "black", size = 1),
      # Add line to x axis
      axis.line.y = element_line(colour = "black", size = 1),
      # Add line to y axis
      strip.text = element_text(size = 24, face = "bold"),
      # Change facet text
      strip.background = element_rect(fill = "white", size = 1),
      # Change facet color
      panel.spacing = unit(.05, "lines"),
      # Add panel border
      panel.border = element_rect(color = "black", fill = NA, size = 0.5),
      # Change panel border color and size
      legend.background = element_rect(fill = "#ffffff00")
      # strip.text = element_blank()
      # legend.position = c(.78, 0.85)
    ) +
     guides(fill = guide_legend(title = "Group")) +
    guides(color = "none") +
    coord_cartesian(ylim = c(0.57, 0.87)) +
    geom_segment(data = data.frame(test_three = "Long-Term Retention", group = "ASD", social_cond = "Direct"),
                 aes(x = 0.75, xend = 1.25, y = 0.8, yend = 0.8)) +
    # geom_text(aes(x = 1, y = 0.805, label = paste0("*")), size = 11, color = "black") +
    geom_segment(data = data.frame(test_three = "Long-Term Retention", group = "ASD", social_cond = "Direct"),
                 aes(x = 1.75, xend = 2.25, y = 0.735, yend = 0.735)) +
    geom_segment(data = data.frame(test_three = "Long-Term Retention", group = "ASD", social_cond = "Direct"),
                 aes(x = 1, xend = 2, y = 0.83, yend = 0.83)) +
    geom_segment(data = data.frame(test_three = "Long-Term Retention", group = "ASD", social_cond = "Direct"),
                 aes(x = 1, xend = 1, y = 0.83, yend = 0.82)) +
    geom_segment(data = data.frame(test_three = "Long-Term Retention", group = "ASD", social_cond = "Direct"),
                 aes(x = 2, xend = 2, y = 0.83, yend = 0.75)) +
    geom_segment(data = data.frame(test_three = "Long-Term Retention", group = "ASD", social_cond = "Direct"),
                 aes(x = 1.5, xend = 1.5, y = 0.83, yend = 0.835)) +
    geom_text(size = 7, color = "black", 
              data = data.frame(test_three = "Long-Term Retention", group = "ASD", social_cond = "Direct"),
              aes(x = 1.5, y = 0.855, label = paste0(""))) 
    # geom_text(aes(x = 1.5, y = 0.855, label = paste0("")), size = 7, color = "black")
  }
```


# Calculate mean accuracy by subject (meanAcc)
```{r}
meanAcc <- 
  allRe %>%
  group_by(Participant.Public.ID, group, age_year, age_month, age_group, scaled_age, test_three, word_type, social_cond) %>%
  dplyr::summarise(corr = mean(corr, na.rm = T)) %>%
  arrange(group, word_type, social_cond, test_three)
```


```{r}
plot_across_time("noun", "verb", meanAcc)
ggsave(paste0(output_path, "meanAcc_all_across_age.png"), bg="transparent", width = 35, height = 15, units = "cm")
plot_across_time("noun", "noun", meanAcc)
ggsave(paste0(output_path, "meanAcc_noun.png"), bg="transparent", width = 35, height = 15, units = "cm")
plot_across_time("verb", "verb", meanAcc)
ggsave(paste0(output_path, "meanAcc_verb.png"), bg="transparent", width = 35, height = 15, units = "cm")

plot_retention("TD", "noun", "verb", meanAcc)
ggsave(paste0(output_path, "att_ret_across_group.png"), bg="transparent", width = 25, height = 15, units = "cm")

plot_group("TD", "noun", "verb", meanAcc)
ggsave(paste0(output_path, "att_retTD.png"), bg="transparent", width = 25, height = 15, units = "cm")
# plot_group("TD", "noun", "noun", meanAcc)
# plot_group("TD", "verb", "verb", meanAcc)
# plot_group("ASD", "noun", "verb", meanAcc)
# plot_group("ASD", "noun", "noun", meanAcc)
# plot_group("ASD", "verb", "verb", meanAcc)
```


```{r}
# should we compute based on inidividual participants or based on groups?
allRe %>%
  group_by(group, test_three, scaled_time, word_type, social_cond) %>%
  dplyr::summarise(sum = sum(corr, na.rm = T), n = n()) %>%
  arrange(group, word_type, social_cond, test_three)

meanAcc %>%
  group_by(group, test_three, word_type, social_cond) %>%
  dplyr::summarise(sum = sum(corr, na.rm = T), n = n()) %>%
  arrange(group, word_type, social_cond, test_three)


plot_across_time("noun", "verb", allRe)
ggsave(paste0(output_path, "allRe_acc.png"), bg="transparent", width = 35, height = 15, units = "cm")

plot_across_time("noun", "noun", allRe)
ggsave(paste0(output_path, "allRe_acc_noun.png"), bg="transparent", width = 35, height = 15, units = "cm")

plot_across_time("verb", "verb", allRe)
ggsave(paste0(output_path, "allRe_acc_verb.png"), bg="transparent", width = 35, height = 15, units = "cm")
```


```{r}
library(ggpattern)

plot_immediate <-
  function(df) {
  df %>%
    # filter(word_type == word_class1 | word_type == word_class2) %>%
    # filter(group == group_name) %>%
    filter(!is.na(corr)) %>%
    # filter(!is.na(test_three)) %>%
    filter(test_three == "immediate") %>%
    arrange(group) %>%  # First sort by val. This sort the dataframe but NOT the factor levels
    mutate(group = factor(group, levels=c("TD", "ASD"))) %>%
    mutate(social_cond = dplyr::recode(social_cond, Direct = "Direct Address"),
           test_three = dplyr::recode(test_three, immediate = "Immediate Test", attainment = "Short-Term Retention", retention = "Long-Term Retention")) %>%
    group_by(group, social_cond, test_three) %>%
    dplyr::summarise(mean = mean(corr, na.rm = TRUE),
                    sd = sd(corr, na.rm = TRUE),
                    n = n()) %>%
    mutate(se = sd / sqrt(n),
            lower_ci = mean - qt(1 - (0.05 / 2), n - 1) * se,
            upper_ci = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
    ggplot(aes(x = group, y = mean, pattern = social_cond,  fill = group)) +
    geom_col_pattern(aes(pattern = social_cond),
                     stat = "summary",
                     fun = "mean",
                     width = 0.7,
                     position = position_dodge(),
                     pattern_density = 0.1,
                     pattern_spacing = 0.025,
                     pattern_key_scale_factor = 0.6,
                     color = "#000000",
                     pattern_colour = "black",
                     pattern_fill = "black") +
  scale_pattern_manual(values = c("stripe", "none")) +
  # scale_pattern_spacing_discrete(range = c(0.025, 0.05)) + 
    scale_fill_manual(values = c(cbPalette[1], cbPalette[8])) +
    scale_color_manual(values = c("black")) +
    geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                  width = .1,
                  position = position_dodge(width = 0.7)) +
    # geom_line(aes(color = "black"),
    #           position = position_dodge(width=0.7),
    #           size = 0.8,
    #           stat = "summary",
    #            fun = "mean") +
    geom_point(color = "black",
               position = position_dodge(width=0.7),
               shape = 21,
               size = 3,
               stat = "summary",
               fun = "mean") +
    guides(color = guide_legend(override.aes = list(pattern = "none", "none")),,
           fill = guide_legend(override.aes = list(pattern = "none", "none")),
           pattern = guide_legend(title="Social Condition", color = "black", override.aes = list(fill = c("white", "white")))) +
    facet_grid(~test_three,  labeller = (labeller(word_type = labsWord))) +
    # scale_fill_manual(values=c("white", "grey")) +
   # guides(fill = guide_legend(title="Social Condition")) +
     labs(x = "Test Time",  # Change x-axis label
          y = "Accuracy (%)") +
      # labs(title = paste("Accuracy in", word_class1, word_class2)) +
      theme(
      plot.title = element_text(size = 30, face = "bold"),
      axis.title.x = element_blank(),
      axis.title.y = element_text(size = 22, face = "bold"),
      axis.text = element_text(size = 24, face = "bold"),
      legend.text = element_text(size = 22, face = "bold"),
      legend.title = element_text(size = 22, face = "bold"),
      panel.background = element_rect(fill = "white"),
      # Set plot background to whit
      axis.line.x = element_line(colour = "black", size = 1),
      # Add line to x axis
      axis.line.y = element_line(colour = "black", size = 1),
      # Add line to y axis
      strip.text = element_text(size = 28, face = "bold"),
      # Change facet text
      strip.background = element_rect(fill = "white", size = 1),
      # Change facet color
      panel.spacing = unit(.05, "lines"),
      # Add panel border
      panel.border = element_rect(color = "black", fill = NA, size = 0.5),
      # Change panel border color and size
      legend.background = element_rect(fill = "#ffffff00")
      # strip.text = element_blank()
      # legend.position = c(.78, 0.85)
    ) +
     guides(fill = guide_legend(title = "Group")) +
    guides(color = "none") +
    coord_cartesian(ylim = c(0, 0.87))
  }

plot_immediate(meanAcc)
ggsave(paste0(output_path, "imm_across_group.png"), bg="transparent", width = 20, height = 15, units = "cm")
```



```{r}
allRe %>%
  filter(!is.na(allRe$corr)) %>%
  # filter(group == "TD") %>%
  filter(test_time == "attainment") %>%
  mutate(social_cond = dplyr::recode(social_cond, front = "Direct", side = "Overhearing")) %>%
  ggplot(aes(x = age_year, y = corr, group = social_cond)) +
  geom_point(aes(color = social_cond),
             stat = "summary",
             fun.y = "mean",
             position = position_dodge(width = 0.2),
             alpha = 0.7,
             size = 3) +
  geom_smooth(method='lm', formula= y~x, aes(color = social_cond), se = F) +
  guides(fill = guide_legend(title = "Social Condition")) +
  facet_grid(~group + word_type + test_three,  labeller = (labeller(word_type = labsWord))) +
  guides(fill = guide_legend(title = "Social Condition")) +
  labs(title = "Attainment and Retention vs. Age",
       x = "Age (months)",  # Change x-axis label
       y = "Accuracy (%)")

```



# Extract Individual Differences Assessment Data
```{r}
meanAcc <- merge(meanAcc, ipad, by.x = c("Participant.Public.ID"), by.y = c("part_id"), all.x = T)

meanAcc <- 
  meanAcc %>%
  dplyr::select(Participant.Public.ID, corr, group, age_year, scaled_age, social_cond, test_three, word_type, pvt_raw_score, pvt_std_score, orr_raw_score, orr_std_score, scq_total, mite_total_score)

meanAcc %>%
  dplyr::select(Participant.Public.ID, group, pvt_raw_score, orr_raw_score) %>%
  distinct(.) %>%
  group_by(group) %>%
  dplyr::summarise(across(c("pvt_raw_score", "orr_raw_score"), ~ sum(is.na(.x))))

allRe %>%
  group_by(group, test_time) %>%
  dplyr::select(Participant.Public.ID, test_time) %>%
  distinct(.) %>%
  dplyr::summarise(n = n())
```


```{r}
# Use Mean Acc scores for every cell of the experimental design
meanAcc$group <- factor(meanAcc$group, levels = c("ASD", "TD"))
meanAcc <- meanAcc[order(meanAcc$group),]

meanAcc$social_cond <- factor(meanAcc$social_cond, levels = c("Direct", "Overhearing"))
meanAcc <- meanAcc[order(meanAcc$social_cond),]

meanAcc$word_type <- factor(meanAcc$word_type, levels = c("noun", "verb"))
meanAcc <- meanAcc[order(meanAcc$word_type),]

meanAcc$test_three <- factor(meanAcc$test_three, levels = c("immediate", "attainment", "retention"))
meanAcc <- meanAcc[order(meanAcc$test_three),]


meanAccTD <- meanAcc[which(meanAcc$group == "TD"),]
meanAccASD <- meanAcc[which(meanAcc$group == "ASD"),]

meanAcc %>%
  dplyr::select(group, Participant.Public.ID, pvt_raw_score) %>%
  distinct(.) %>%
  dplyr::summarise(n = length(!is.na(pvt_raw_score)))
```

# Vocabulary Analysis
```{r}
vocab_m1 <- lm(corr ~ social_cond*pvt_raw_score*word_type*test_three + scaled_age, data = meanAccTD,
               contrasts = list(
                   social_cond = c(-0.5, 0.5),
                   word_type = c(-0.5, 0.5),
                   test_three = three_helmert
                   ))
summary(vocab_m1)
```


```{r}
meanAccImm <- meanAcc[which(meanAcc$test_three == "immediate"),]
meanAccAtt <- meanAcc[which(meanAcc$test_three == "attainment"),]
meanAccRe <- meanAcc[which(meanAcc$test_three == "retention"),]
```


```{r}
vocabImm_m1 <- lm(corr ~ social_cond*pvt_std_score*word_type + scaled_age, data = meanAccImm[which(meanAccImm$group == "TD"),],
               contrasts = list(
                   social_cond = c(-0.5, 0.5),
                   word_type = c(-0.5, 0.5)
                   ))
summary(vocabImm_m1)

vocabAtt_m1 <- lm(corr ~ social_cond*pvt_std_score*word_type*scaled_age, data = meanAccAtt[which(meanAccAtt$group == "ASD"),],
               contrasts = list(
                   social_cond = c(-0.5, 0.5),
                   word_type = c(-0.5, 0.5)
                   ))
summary(vocabAtt_m1)

vocabRe_m1 <- lm(corr ~ social_cond*pvt_std_score*word_type + scaled_age, data = meanAccRe[which(meanAccRe$group == "TD"),],
               contrasts = list(
                   social_cond = c(-0.5, 0.5),
                   word_type = c(-0.5, 0.5)
                   ))
summary(vocabRe_m1)
```

# Reading Analysis
```{r}
orr_m1 <- lm(corr ~ social_cond*orr_raw_score*word_type*test_three + scaled_age, data = meanAccTD,
               contrasts = list(
                   social_cond = c(-0.5, 0.5),
                   word_type = c(-0.5, 0.5),
                   test_three = three_helmert
                   ))
summary(orr_m1)


orrImm_m1 <- lm(corr ~ social_cond*orr_raw_score*word_type + scaled_age, data = meanAccImm[which(meanAccImm$group == "TD"),],
               contrasts = list(
                   social_cond = c(-0.5, 0.5),
                   word_type = c(-0.5, 0.5)
                   ))
summary(orrImm_m1)

orrAtt_m1 <- lm(corr ~ social_cond*orr_raw_score*word_type + scaled_age, data = meanAccAtt[which(meanAccAtt$group == "TD"),],
               contrasts = list(
                   social_cond = c(-0.5, 0.5),
                   word_type = c(-0.5, 0.5)
                   ))
summary(orrAtt_m1)

orrRe_m1 <- lm(corr ~ social_cond*orr_raw_score*word_type + scaled_age, data = meanAccRe[which(meanAccRe$group == "TD"),],
               contrasts = list(
                   social_cond = c(-0.5, 0.5),
                   word_type = c(-0.5, 0.5)
                   ))
summary(orrRe_m1)
```


# SCQ Analysis
```{r}
scq_m1 <- lm(corr ~ social_cond*scq_total*word_type*test_three + scaled_age, data = meanAccTD,
               contrasts = list(
                   social_cond = c(-0.5, 0.5),
                   word_type = c(-0.5, 0.5),
                   test_three = three_helmert
                   ))
summary(scq_m1)


scqImm_m1 <- lm(corr ~ social_cond*scq_total*word_type + scaled_age, data = meanAccImm[which(meanAccImm$group == "TD"),],
               contrasts = list(
                   social_cond = c(-0.5, 0.5),
                   word_type = c(-0.5, 0.5)
                   ))
summary(scqImm_m1)

scqAtt_m1 <- lm(corr ~ social_cond*scq_total*word_type + scaled_age, data = meanAccAtt[which(meanAccAtt$group == "TD"),],
               contrasts = list(
                   social_cond = c(-0.5, 0.5),
                   word_type = c(-0.5, 0.5)
                   ))
summary(scqAtt_m1)

scqRe_m1 <- lm(corr ~ social_cond*scq_total*word_type + scaled_age, data = meanAccRe[which(meanAccRe$group == "TD"),],
               contrasts = list(
                   social_cond = c(-0.5, 0.5),
                   word_type = c(-0.5, 0.5)
                   ))
summary(scqRe_m1)
```


```{r}
library("RcmdrMisc")

astCorr <- function(df, group, condition) {
  rcorr.adjust(as.matrix(df[which(df$group == group & df$social_cond == condition), c(
    "corr",
    "age_year",
    # "kbit_matrices_raw",
    # "kbit_matrices_std",
    "orr_raw_score",
    "orr_std_score",
    # "orr_national_percentile",
    "pvt_raw_score",
    "pvt_std_score",
    "scq_total",
    "mite_total_score"
    # "pvt_national_percentile"
  )]),
  use = c("pairwise.complete.obs"))
}

astCorr(meanAccImm, "TD", "Overhearing")
astCorr(meanAccImm, "TD", "Direct")
```

# Plot Vocab and Accuracy
```{r}
meanAcc %>%
  filter(!is.na(corr)) %>%
  filter(group == "TD") %>%
  filter(test_three == "immediate") %>%
  mutate(social_cond = dplyr::recode(social_cond, Direct = "Direct Address", Overhearing = "Overhear"),
        test_three = dplyr::recode(test_three, immediate = "0 min", attainment = "10 min", retention = "1 week"),
        pvt_std_score = as.numeric(as.character(pvt_std_score)),
        mite_total_all = as.numeric(as.character(mite_total_score))) %>%
  ggplot(aes(x = pvt_std_score, y = corr, group = social_cond)) +
  geom_point(aes(color = social_cond),
             # stat = "summary",
             # fun = "mean",
             position = position_dodge(width = 3),
             alpha = 0.7,
             size = 3) +
  geom_smooth(method='lm', formula= y~x, aes(color = social_cond), se = F) +
  guides(fill = guide_legend(title = "Social Condition")) +
  facet_grid(~ group + test_three,  labeller = (labeller(word_type = labsWord))) +
  guides(fill = guide_legend(title = "Social Condition")) +
  labs(title = "Novel Word Recall Accuracy vs. PVT",
       x = "PVT Standard Scores",  # Change x-axis label
       y = "Accuracy (%)") +
 # guides(fill = guide_legend(title="Social Condition")) +
   theme(
    plot.title = element_text(size = 30, face = "bold"),
    axis.title.x = element_text(size = 26, face = "bold"),
    axis.title.y = element_text(size = 22, face = "bold"),
    axis.text.x = element_text(size = 15, face = "bold"),
    axis.text.y = element_text(size = 24, face = "bold"),
    legend.text = element_text(size = 22, face = "bold"),
    legend.title = element_text(size = 22, face = "bold"),
    panel.background = element_rect(fill = "white"),
    # Set plot background to whit
    axis.line.x = element_line(colour = "black", size = 1),
    # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1),
    # Add line to y axis
    strip.text = element_text(size = 24, face = "bold"),
    # Change facet text
    strip.background = element_rect(fill = "white", size = 1),
    # Change facet color
    panel.spacing = unit(.05, "lines"),
    # Add panel border
    panel.border = element_rect(color = "black", fill = NA, size = 0.5),
    # Change panel border color and size
    legend.background = element_rect(fill = "#ffffff00")
    # strip.text = element_blank()
  ) +
  guides(color = guide_legend(title = "Social Condition"))

# ggsave(paste0(output_path, "allRe_pvt.png"), bg="transparent", width = 30, height = 15, units = "cm")

meanAcc %>%
  filter(!is.na(mite_total_score)) %>%
  filter(!is.na(corr)) %>%
  dplyr::select(Participant.Public.ID, group, social_cond, test_three, mite_total_score, corr) %>%
  group_by(group, social_cond, test_three) %>%
  distinct(.) %>%
  dplyr::summarise(n = length(unique(Participant.Public.ID)))

ggsave("results/pvt_acc_td_imm.png", width = 20, height = 15, units="cm")
```


# Plot Mite and Accuracy
```{r}
meanAcc %>%
  filter(!is.na(corr)) %>%
  # filter(group == "ASD") %>%
  filter(test_three == "attainment") %>%
  # mutate(social_cond = dplyr::recode(social_cond, Direct = "Direct Address", Overhearing = "Overhear"),
  #        test_three = dplyr::recode(test_three, immediate = "0 min", attainment = "10 min", retention = "1 week")) %>%
  ggplot(aes(x = mite_total_score, y = corr, group = social_cond)) +
  geom_point(aes(color = social_cond),
             # stat = "summary",
             # fun = "mean",
             position = position_dodge(width = 3),
             alpha = 0.7,
             size = 3) +
  geom_smooth(method='lm', formula= y~x, aes(color = social_cond), se = F) +
  guides(fill = guide_legend(title = "Social Condition")) +
  facet_grid(~ test_three,  labeller = (labeller(word_type = labsWord))) +
  guides(fill = guide_legend(title = "Social Condition")) +
  labs(title = "Novel Word Recall Accuracy vs. MITE",
       x = "MITE Total Scores",  # Change x-axis label
       y = "Accuracy (%)") +
 # guides(fill = guide_legend(title="Social Condition")) +
   theme(
    plot.title = element_text(size = 30, face = "bold"),
    axis.title.x = element_text(size = 26, face = "bold"),
    axis.title.y = element_text(size = 22, face = "bold"),
    axis.text.x = element_text(size = 15, face = "bold"),
    axis.text.y = element_text(size = 24, face = "bold"),
    legend.text = element_text(size = 22, face = "bold"),
    legend.title = element_text(size = 22, face = "bold"),
    panel.background = element_rect(fill = "white"),
    # Set plot background to whit
    axis.line.x = element_line(colour = "black", size = 1),
    # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1),
    # Add line to y axis
    strip.text = element_text(size = 24, face = "bold"),
    # Change facet text
    strip.background = element_rect(fill = "white", size = 1),
    # Change facet color
    panel.spacing = unit(.05, "lines"),
    # Add panel border
    panel.border = element_rect(color = "black", fill = NA, size = 0.5),
    # Change panel border color and size
    legend.background = element_rect(fill = "#ffffff00")
    # strip.text = element_blank()
  ) +
  guides(color = guide_legend(title = "Social Condition"))

ggsave("results/mite_acc_att.png", width = 30, height = 15, units = "cm")
```


# Plot Reading and Accuracy
```{r}
meanAcc %>%
  filter(!is.na(corr)) %>%
  filter(group == "TD") %>%
  mutate(social_cond = dplyr::recode(social_cond, Direct = "Direct Address"),
         test_three = dplyr::recode(test_three, immediate = "0 min", attainment = "5 min", retention = "1 week")) %>%
  ggplot(aes(x = orr_raw_score, y = corr, group = social_cond)) +
  geom_point(aes(color = social_cond),
             stat = "summary",
             fun = "mean",
             position = position_dodge(width = 3),
             alpha = 0.7,
             size = 3) +
  geom_smooth(method='lm', formula= y~x, aes(color = social_cond), se = F) +
  guides(fill = guide_legend(title = "Social Condition")) +
  facet_grid(~word_type + test_three,  labeller = (labeller(word_type = labsWord))) +
  guides(fill = guide_legend(title = "Social Condition")) +
  labs(title = "Novel Word Recall Accuracy vs. Decoding",
       x = "Oral Reading Raw Scores",  # Change x-axis label
       y = "Accuracy (%)") +
 # guides(fill = guide_legend(title="Social Condition")) +
   theme(
    plot.title = element_text(size = 30, face = "bold"),
    axis.title.x = element_text(size = 26, face = "bold"),
    axis.title.y = element_text(size = 22, face = "bold"),
    axis.text.x = element_text(size = 15, face = "bold"),
    axis.text.y = element_text(size = 24, face = "bold"),
    legend.text = element_text(size = 22, face = "bold"),
    legend.title = element_text(size = 22, face = "bold"),
    panel.background = element_rect(fill = "white"),
    # Set plot background to whit
    axis.line.x = element_line(colour = "black", size = 1),
    # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1),
    # Add line to y axis
    strip.text = element_text(size = 24, face = "bold"),
    # Change facet text
    strip.background = element_rect(fill = "white", size = 1),
    # Change facet color
    panel.spacing = unit(.05, "lines"),
    # Add panel border
    panel.border = element_rect(color = "black", fill = NA, size = 0.5),
    # Change panel border color and size
    legend.background = element_rect(fill = "#ffffff00")
    # strip.text = element_blank()
  ) +
  guides(color = guide_legend(title = "Social Condition"))

# ggsave(paste0(output_path, "allRe_orr.png"), bg="transparent", width = 30, height = 15, units = "cm")
```



# Plot SCQ and Accuracy
```{r}
meanAcc %>%
  filter(!is.na(corr)) %>%
  filter(group == "TD") %>%
  mutate(social_cond = dplyr::recode(social_cond, Direct = "Direct Address"),
         test_three = dplyr::recode(test_three, immediate = "0 min", attainment = "5 min", retention = "1 week")) %>%
  ggplot(aes(x = scq_total, y = corr, group = social_cond)) +
  geom_point(aes(color = social_cond),
             stat = "summary",
             fun = "mean",
             position = position_dodge(width = 3),
             alpha = 0.7,
             size = 3) +
  geom_smooth(method='lm', formula= y~x, aes(color = social_cond), se = F) +
  guides(fill = guide_legend(title = "Social Condition")) +
  facet_grid(~word_type + test_three,  labeller = (labeller(word_type = labsWord))) +
  guides(fill = guide_legend(title = "Social Condition")) +
  labs(title = "Novel Word Recall Accuracy vs. Decoding",
       x = "Oral Reading Raw Scores",  # Change x-axis label
       y = "Accuracy (%)") +
 # guides(fill = guide_legend(title="Social Condition")) +
   theme(
    plot.title = element_text(size = 30, face = "bold"),
    axis.title.x = element_text(size = 26, face = "bold"),
    axis.title.y = element_text(size = 22, face = "bold"),
    axis.text.x = element_text(size = 15, face = "bold"),
    axis.text.y = element_text(size = 24, face = "bold"),
    legend.text = element_text(size = 22, face = "bold"),
    legend.title = element_text(size = 22, face = "bold"),
    panel.background = element_rect(fill = "white"),
    # Set plot background to whit
    axis.line.x = element_line(colour = "black", size = 1),
    # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1),
    # Add line to y axis
    strip.text = element_text(size = 24, face = "bold"),
    # Change facet text
    strip.background = element_rect(fill = "white", size = 1),
    # Change facet color
    panel.spacing = unit(.05, "lines"),
    # Add panel border
    panel.border = element_rect(color = "black", fill = NA, size = 0.5),
    # Change panel border color and size
    legend.background = element_rect(fill = "#ffffff00")
    # strip.text = element_blank()
  ) +
  guides(color = guide_legend(title = "Social Condition"))

# ggsave(paste0(output_path, "allRe_orr.png"), bg="transparent", width = 30, height = 15, units = "cm")
```





